### 2019-06-19 Growth curves and yields.Rmd
Scripts from Matlab and R

---
title: "Growth Yield Figures"
author: "Juan P Barraza"
date: "1/28/2019"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(magrittr)
library(plotrix)#this allows the std.error function to work
library(cowplot)

#this is co-culture data from PA14 using exponential phase cultures
coCultureGCFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/pqsL SCFM2/PA14 exp growth curves.csv"
coCultureGCData <-read.csv(coCultureGCFile)
coCultureGCData%>% group_by(condition, bug, time, strain) %>% summarise(cellCount = mean(countsmL), cellSE = std.error(countsmL),  cellSD = sd(countsmL)) %>% as.data.frame() -> coCultureGCDataStats
levels(coCultureGCDataStats$condition)<-c("Stirred", "Static")

##this data is from non-exponential phase cultures, but the yeld should be fine for the mono-cultures
#Data from PAO1
nonExpPAO1File<-"/Users/jupabago/Documents/Whiteley/PROJECTS/pqsL SCFM2/PAO1 growth curves.csv"
nonExpPAO1Data <-read.csv(nonExpPAO1File)
nonExpPAO1Data<- na.omit(nonExpPAO1Data)
nonExpPAO1Data$countsmL<-as.numeric(levels(nonExpPAO1Data$countsmL))[nonExpPAO1Data$countsmL]
nonExpPAO1Data %>% filter(condition=="Mono")->nonExpPAO1DataMono
#Data from PA14
nonExpPA14File<-"/Users/jupabago/Documents/Whiteley/PROJECTS/pqsL SCFM2/PA14 growth curves.csv"
nonExpPA14Data <-read.csv(nonExpPA14File)
nonExpPA14Data<- na.omit(nonExpPA14Data)
nonExpPA14Data %>% filter(condition=="Mono")->nonExpPA14DataMono

nonExpAllData<-rbind(nonExpPAO1DataMono,nonExpPA14DataMono)
nonExpAllData %>% filter(bug=="Sa")->nonExpAllDataSa#All non-exponential data from Sa
nonExpAllData %>% filter(!bug=="Sa")->nonExpAllDataPa#All non-exponential data from Pa

```
These are the growth curves for non exponential phase Pa and Sa mono culture growth curves. The growth yield should not be affected as cultures are still approaching carrying capacity since they are not being outcompeted by Pa. There are two data points significantly lower than the other 3.
```{r growth curves nonExp, echo=FALSE, warning=FALSE,fig.width=9, fig.height=7}
##Graph growth yields for non-exponential data
#First for Sa:
ggplot(nonExpAllDataSa, aes(x=time, y = countsmL, color = bug))+
  geom_jitter(height = 0, width = .2)+
  scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  #scale_x_continuous(breaks = c(0,4,8,12,16))+
  ggtitle("SCFM2 NonExp Sa mono growth")

#Then for Pa:
ggplot(nonExpAllDataPa, aes(x=time, y = countsmL, color = bug))+
  geom_jitter(height = 0, width = .2)+
  scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  #scale_x_continuous(breaks = c(0,4,8,12,16))+
  ggtitle("SCFM2 NonExp Pa mono growth")

```

This is the data yield starting from exponential phase and going up to 16 hours:

```{r exponential phase yield, echo=FALSE, warning=FALSE,fig.width=9, fig.height=7}
##Lines below are to go from 12hr growth curve to growth yield
#First for Sa:
nonExpAllDataSa %>% filter(time=="12")->nonExpAllDataSaYield
nonExpAllDataSaYield %>% select(countsmL,rep,bug) %>% mutate(condition = "static")->nonExpAllDataSaYieldSimple
nonExpAllDataSaYieldSimple<-nonExpAllDataSaYieldSimple[c(1,2,4,3)]
colnames(nonExpAllDataSaYieldSimple) <- c("bugs","rep", "condition", "strain")
#Then for Pa:
nonExpAllDataPa %>% filter(time=="12")->nonExpAllDataPaYield
nonExpAllDataPaYield %>% select(countsmL,rep,bug) %>% mutate(condition = "static")->nonExpAllDataPaYieldSimple
nonExpAllDataPaYieldSimple<-nonExpAllDataPaYieldSimple[c(1,2,4,3)]
colnames(nonExpAllDataPaYieldSimple) <- c("bugs","rep", "condition", "strain")

##Now get the growth yield for mono starting from exponential phase
#First for Sa:
yieldSaFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/pqsL SCFM2/Pa growth yields 16 hrs/Sa growth yields 16 hrs.csv"
yieldSaData <-read.csv(yieldSaFile)
ggplot()+
  geom_point(data=yieldSaData, aes(x=condition, y=bugs), size=4)+
  scale_y_log10(limits= c(1e6,1e10), name=expression(paste('CFUs per mL' )), breaks = c(10^(seq(6,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  labs(title =expression(paste("Sa growth yield (16 hrs)")), x = "condtion")
#Then for Pa:
yieldPaFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/pqsL SCFM2/Pa growth yields 16 hrs/Pa growth yields 16 hrs.csv"
yieldPaData <-read.csv(yieldPaFile)
yieldPaData<-yieldPaData %>% filter(!bio.rep==3)#third replicate was thrown out because plate counts were off
ggplot()+
  geom_jitter(data=yieldPaData, aes(x=condition, y=bugs, color = strain), size=4, height = 0, width = .1)+
  scale_y_log10(limits= c(1e6,1e10), name=expression(paste('CFUs per mL' )), breaks = c(10^(seq(6,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  labs(title =expression(paste("Pa growth yield (16 hrs)")), x = "condition")
```

Shown below are the combination of the 12th hr timepoint of non exponential growth curves and the yield after 16 hrs of exp growth.
```{r combined yield, echo=FALSE, warning=FALSE,fig.width=9, fig.height=7}
##now, combining both exponential and non-exponential, we get this:
#First for Sa:
allYieldsSa <- gdata::combine(yieldSaData, nonExpAllDataSaYieldSimple)
ggplot()+
  geom_jitter(data=allYieldsSa, aes(x=condition, y=bugs, color = source), size=4, height = 0, width = .1)+
  scale_y_log10(limits= c(1e6,1e10), name=expression(paste('CFUs per mL' )), breaks = c(10^(seq(6,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  scale_color_discrete(name = "Source",labels = c("Exp", "NonExp"))+
  labs(title =expression(paste("Sa Growth Yield Combined")), x = "condition")

allYieldsSa %>% group_by(condition) %>% summarise(meanYield = mean(bugs), SEYield = std.error(bugs)) %>% as.data.frame()->yieldsSaFinal

#Now for Pa:
yieldPaData<-yieldPaData %>% group_by(bio.rep, condition, strain) %>% summarise(bugsmL= mean(bugs))%>% as.data.frame() #data from Pa were not as simple as for Sa
yieldPaData<-yieldPaData[c(4,1,2,3)]
colnames(yieldPaData) <- c("bugs","rep", "condition", "strain")

allYieldsPa <- gdata::combine(yieldPaData, nonExpAllDataPaYieldSimple)
allYieldsPa<-allYieldsPa %>% mutate(strains = recode(allYieldsPa$strain, wt = "PA14wt", pqsL = "PA14-pqsL")) %>% as.data.frame()

ggplot()+
  geom_jitter(data=allYieldsPa, aes(x=condition, y=bugs, color = source, shape = strains), width = .1, height = 0,size=4)+
  scale_y_log10(limits= c(1e7,1e10), name=expression(paste('CFUs per mL' )), breaks = c(10^(seq(6,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  scale_color_discrete(name = "Source",labels = c("Exp", "NonExp"))+
  labs(title =expression(paste("Pa Growth Yield Combined")), x = "condition")

allYieldsPa %>% group_by(condition, strains) %>% summarise(meanYield = mean(bugs), SEYield = std.error(bugs)) %>% as.data.frame()->yieldsPaFinal
ggplot()+
  geom_jitter(data=allYieldsPa, aes(x=condition, y=bugs, color = source), width = .1, height = 0,size=4)+
  #geom_point(aes(x = condition, y-meanYield-SEYield, ymax=meanYield+SEYield), data =yieldsPaFinal, width=.1)+
  geom_errorbar(aes(x = condition, ymin=meanYield-SEYield, ymax=meanYield+SEYield), data =yieldsPaFinal, width=.1)+
  scale_y_log10(limits= c(1e8,1e10), name=expression(paste('CFUs per mL' )), breaks = c(10^(seq(6,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  labs(title =expression(paste("Pa Growth Yield Combined")), x = "condition")+
  scale_color_discrete(name = "Source",labels = c("Exp", "NonExp"))+
  facet_grid(.~strains)
```

This is the growth curve, followed by the plots with horizontal bars showing the average growth yield among all replicates.

```{r final plots, echo=FALSE, warning=FALSE,fig.width=9, fig.height=7}

ggplot()+
  geom_line(data=coCultureGCDataStats,aes(x=time, y=cellCount, color = bug, linetype = strain), size = 1)+
  geom_errorbar(aes(x = time, ymin=cellCount-cellSD, ymax=cellCount+cellSD, color = bug), data =coCultureGCDataStats, width=.2, size = 1)+
  geom_errorbar(aes(x = time, ymin=cellCount-cellSD, ymax=cellCount+cellSD,color = bug), data =coCultureGCDataStats, width=.2, size = 1)+
  scale_y_log10(limits= c(1e5,1e10), name=expression(paste('CFUs per mL' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_grid(.~condition)+
  scale_x_continuous(breaks = c(0,4,8,12,16))+
  #scale_linetype_discrete(guide = FALSE)+
  labs(title =expression(paste(italic("P. aeruginosa"), " PA14 wt and ", italic("S. aureus"), " coculture in SCFM2")), x = "Time (hours)", shape = "Strain", color = "Species")

coCultureGCDataStatsMixed<-coCultureGCDataStats %>% filter(condition == "Stirred") %>% as.data.frame()
coCultureGCDataStatsMixedSa<-coCultureGCDataStatsMixed %>% filter(bug == "Sa") %>% as.data.frame()
coCultureGCDataStatsMixedPa<-coCultureGCDataStatsMixed %>% filter(bug == "Pa") %>% as.data.frame()

coCultureGCDataStatsStatic<-coCultureGCDataStats %>% filter(condition == "Static") %>% as.data.frame()
coCultureGCDataStatsStaticSa<-coCultureGCDataStatsStatic %>% filter(bug == "Sa") %>% as.data.frame()
coCultureGCDataStatsStaticPa<-coCultureGCDataStatsStatic %>% filter(bug == "Pa") %>% as.data.frame()

##Now we have everything we need for the final plot
#these are the yields:
yieldPaShMut<-yieldsPaFinal[1,3]
yieldPaShWt<-yieldsPaFinal[2,3]
yieldPaStMut<-yieldsPaFinal[3,3]
yieldPaStWt<-yieldsPaFinal[4,3]
yieldSaSt<-yieldsSaFinal[1,2]
yieldSaSh<-yieldsSaFinal[2,2]

#Plot for static data
ggplot()+
  geom_line(data=coCultureGCDataStatsStaticSa,aes(x=time, y=cellCount, linetype = strain), color = "red2", size = 1)+
  geom_line(data=coCultureGCDataStatsStaticPa,aes(x=time, y=cellCount, linetype = strain), color = "green3", size = 1)+
  geom_errorbar(aes(x = time, ymin=cellCount-cellSD, ymax=cellCount+cellSD), color = "red2", data =coCultureGCDataStatsStaticSa, width=.2, size = 1)+
  geom_errorbar(aes(x = time, ymin=cellCount-cellSD, ymax=cellCount+cellSD), color = "green3", data =coCultureGCDataStatsStaticPa, width=.2, size = 1)+
  scale_y_log10(limits= c(1e6,1e10), name=expression(paste('CFUs per mL' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  geom_hline(yintercept=yieldSaSt, linetype = "solid", color = "red2", size = 1)+
  geom_hline(yintercept=yieldPaStWt, linetype = "solid", color = "green3",size = 1)+
  geom_hline(yintercept=yieldPaStMut, linetype = "dashed", color = "green3",size = 1)+
  scale_x_continuous(breaks = c(0,4,8,12,16))+
  #scale_linetype_discrete(guide = FALSE)+
  labs(title =expression(paste(italic("P. aeruginosa"), " PA14 wt and ", italic("S. aureus"), " coculture static in SCFM2")), x = "Time (hours)", shape = "Strain", color = "Species")

ggplot()+
  geom_line(data=coCultureGCDataStatsMixedSa,aes(x=time, y=cellCount, linetype = strain), color = "red2", size = 1)+
  geom_line(data=coCultureGCDataStatsMixedPa,aes(x=time, y=cellCount, linetype = strain), color = "green3", size = 1)+
  geom_errorbar(aes(x = time, ymin=cellCount-cellSD, ymax=cellCount+cellSD), color = "red2", data =coCultureGCDataStatsMixedSa, width=.2, size = 1)+
  geom_errorbar(aes(x = time, ymin=cellCount-cellSD, ymax=cellCount+cellSD), color = "green3", data =coCultureGCDataStatsMixedPa, width=.2, size = 1)+
  scale_y_log10(limits= c(1e5,1e10), name=expression(paste('CFUs per mL' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  geom_hline(yintercept=yieldSaSh, linetype = "solid", color = "red2", size = 1)+
  geom_hline(yintercept=yieldPaShWt, linetype = "solid", color = "green3",size = 1)+
  geom_hline(yintercept=yieldPaShMut, linetype = "dashed", color = "green3",size = 1)+
  scale_x_continuous(breaks = c(0,4,8,12,16))+
  #scale_linetype_discrete(guide = FALSE)+
  labs(title =expression(paste(italic("P. aeruginosa"), " PA14 wt and ", italic("S. aureus"), " coculture stirred in SCFM2")), x = "Time (hours)", shape = "Strain", color = "Species")

```
And shown below are the same graphs but only using the data from exp phase growth yields
```{r final plots exp only, echo=FALSE, warning=FALSE,fig.width=9, fig.height=7}

yieldSaData %>% group_by(condition) %>% summarise(meanYield = mean(bugs), SEYield = std.error(bugs)) %>% as.data.frame()->yieldsSaFinalExpOnly

yieldPaData %>% group_by(condition, strain) %>% summarise(meanYield = mean(bugs), SEYield = std.error(bugs)) %>% as.data.frame()->yieldsPaFinalExpOnly

yieldPaShMutExp<-yieldsPaFinalExpOnly[1,3]
yieldPaShWtExp<-yieldsPaFinalExpOnly[2,3]
yieldPaStMutExp<-yieldsPaFinalExpOnly[3,3]
yieldPaStWtExp<-yieldsPaFinalExpOnly[4,3]
yieldSaStExp<-yieldsSaFinalExpOnly[1,2]
yieldSaShExp<-yieldsSaFinalExpOnly[2,2]

ggplot()+
  geom_line(data=coCultureGCDataStatsStaticSa,aes(x=time, y=cellCount, linetype = strain), color = "red2", size = 1)+
  geom_line(data=coCultureGCDataStatsStaticPa,aes(x=time, y=cellCount, linetype = strain), color = "green3", size = 1)+
  geom_errorbar(aes(x = time, ymin=cellCount-cellSD, ymax=cellCount+cellSD), color = "red2", data =coCultureGCDataStatsStaticSa, width=.2, size = 1)+
  geom_errorbar(aes(x = time, ymin=cellCount-cellSD, ymax=cellCount+cellSD), color = "green3", data =coCultureGCDataStatsStaticPa, width=.2, size = 1)+
  scale_y_log10(limits= c(1e6,1e10), name=expression(paste('CFUs per mL' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  geom_hline(yintercept=yieldSaStExp, linetype = "solid", color = "red2", size = 1)+
  geom_hline(yintercept=yieldPaStWtExp, linetype = "solid", color = "green3",size = 1)+
  geom_hline(yintercept=yieldPaStMutExp, linetype = "dashed", color = "green3",size = 1)+
  scale_x_continuous(breaks = c(0,4,8,12,16))+
  #scale_linetype_discrete(guide = FALSE)+
  labs(title =expression(paste(italic("P. aeruginosa"), " PA14 wt and ", italic("S. aureus"), " coculture static in SCFM2 (only exp yield)")), x = "Time (hours)", shape = "Strain", color = "Species")

ggplot()+
  geom_line(data=coCultureGCDataStatsMixedSa,aes(x=time, y=cellCount, linetype = strain), color = "red2", size = 1)+
  geom_line(data=coCultureGCDataStatsMixedPa,aes(x=time, y=cellCount, linetype = strain), color = "green3", size = 1)+
  geom_errorbar(aes(x = time, ymin=cellCount-cellSD, ymax=cellCount+cellSD), color = "red2", data =coCultureGCDataStatsMixedSa, width=.2, size = 1)+
  geom_errorbar(aes(x = time, ymin=cellCount-cellSD, ymax=cellCount+cellSD), color = "green3", data =coCultureGCDataStatsMixedPa, width=.2, size = 1)+
  scale_y_log10(limits= c(1e5,1e10), name=expression(paste('CFUs per mL' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  geom_hline(yintercept=yieldSaShExp, linetype = "solid", color = "red2", size = 1)+
  geom_hline(yintercept=yieldPaShWtExp, linetype = "solid", color = "green3",size = 1)+
  geom_hline(yintercept=yieldPaShMutExp, linetype = "dashed", color = "green3",size = 1)+
  scale_x_continuous(breaks = c(0,4,8,12,16))+
  #scale_linetype_discrete(guide = FALSE)+
  labs(title =expression(paste(italic("P. aeruginosa"), " PA14 wt and ", italic("S. aureus"), " coculture stirred in SCFM2 (only exp yield)")), x = "Time (hours)", shape = "Strain", color = "Species")
```

```{r killing assays, echo=FALSE, warning=FALSE,fig.width=9, fig.height=7}
diskFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/pqsL SCFM2/Staph killing assays/disk difussion assays.csv"
diskData <-read.csv(diskFile)
diskData<-diskData %>% mutate (zoneInhibition = avg-6)
diskData%>% group_by(condition, strain) %>% summarise(meanZone = mean(zoneInhibition), SEZone = std.error(zoneInhibition)) %>% as.data.frame() -> diskDataStats

ggplot()+#both PA and Sa
  geom_point(data=diskData, aes(x=condition, y=zoneInhibition, shape = factor(tech.rep), color = factor(bio.rep)), size=4)+
  facet_grid(.~strain)+
  labs(title =expression(paste("Zone of inhibition")), x = "condtion",shape = "tech rep", color = "bio rep")

ggplot()+#both PA and Sa
  geom_point(data=diskDataStats, aes(x=condition, y=meanZone, color =  strain), size=4)+
  geom_errorbar(aes(x = condition, ymin=meanZone-SEZone, ymax=meanZone+SEZone, color = strain), data =diskDataStats, width=.2, size = 1)+
  labs(title =expression(paste("Zone of inhibition")), x = "condtion",shape = "tech rep", color = "bio rep")

```

### 2019-06-19 Microscopy Data.Rmd
Scripts from Matlab and R

---
title: "Microscopy Data"
author: "Juan P Barraza"
date: "6/19/2019"
output: html_document
---

```{r setup, include=FALSE}

PA14wt<- c('3-13-19', '3-19-19', '4-17-19')
PA14mut<- c('4-24-19', '4-25-19', '5-8-19')
PA01wt<- c('3-26-19','4-18-19')
PA01mut<- c('4-23-19')

Get<- function (sample){
  bugCounts<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/", sample,"/results"),header = TRUE)
  bugCounts<- na.omit(bugCounts)
  bugCounts<-bugCounts %>% mutate(logTranformed = log10(CFU))
  bugCounts$sample<-sample
  return(bugCounts)
}

```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}

testFile2<-"/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/3-13-19/results/t00_p1.csv"

GetResults<-function(sample){
  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/',sample,'/results')
  fileList<-list.files(path = folder, full.names = TRUE)
  growthDf<-data.frame()
  for (position in 0:5){
    currentPosition<-fileList[grep(paste0("p",position,"."),fileList)]
    for (timepoint in 0:17){
      currentTimePoint<-currentPosition[grep(paste0("t",GetNumber(timepoint),"_"),currentPosition)]
      growthDf<-rbind(growthDf,ReadResultsFile(currentTimePoint, position, timepoint))}}
return(growthDf)
}

testGetResults<- GetResults("3-13-19")

ReadResultsFile<-function(file, position, timepoint){#This function outputs total number of pixels in the csv file from matlab
  datos <-read.csv(file, header = FALSE)
  colnames(datos)<-c('Red', 'Green', 'Slice')
  datos<-datos %>% mutate(Position = position)
  datos<-datos %>% mutate(TimePoint = timepoint)
  return(datos)
}
```

## Including Plots
```{r aggregates}

testFile2<-"/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/3-13-19/aggregateSizes/t00_p1.csv"

GetAggregates<-function(sample){
  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/',sample,'/aggregateSizes')
  fileList<-list.files(path = folder, full.names = TRUE)
  growthDf<-data.frame()
  for (position in 0:5){
    currentPosition<-fileList[grep(paste0("p_",position,"."),fileList)]
    for (timepoint in 0:17){
      currentTimePoint<-currentPosition[grep(paste0("t_",GetNumber(timepoint),"_"),currentPosition)]
      growthDf<-rbind(growthDf,ReadAggregateFile(currentTimePoint, position, timepoint))}}
return(growthDf)
}

testGetResults<- GetResults("3-13-19")

ReadAggregateFile<-function(file, position, timepoint){#This function outputs total number of pixels in the csv file from matlab
  datos <-read.csv(file, header = TRUE)
  colnames(datos)<-c('Size', 'Species')
  datos<-datos %>% mutate(Position = position)
  datos<-datos %>% mutate(TimePoint = timepoint)
  return(datos)
}

testReadAggregateFile<-ReadAggregateFile(tes)
```
You can also embed plots, for example:

```{r pressure, echo=FALSE}
GetNumber<-function(idx){
  if (idx<10){
    idx = paste0(0,idx)
  }
  return (idx)
}
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2019-06-19 GetImageData.m

@@ -1,0 +1,106 @@
+function image = GetImageData(name,date)
+slices = 91;
+timepoints = 17;
+positions = 5;
+path = '/nv/hp10/jbarraza6/scratch/RawDataMicroscope';
+    for position = 0:positions
+        [thR,thG] = CollectThresholds(path, date, name, slices, timepoints, position);
+        ThresholdImage(path, date, name, slices, timepoints, position,thR,thG);
+    end
+    image = 1;
+end
+
+
+function [ThresholdRed,ThresholdGreen] = CollectThresholds(path, date, name, slices, timepoints, position)
+%This function gives you the red and green thresholds of each timepoint per
+%position
+    ThresholdRed = zeros(timepoints+1, 1);%this is a list where the threshold of each stack is stored    
+    ThresholdGreen = zeros(timepoints+1, 1);
+    for timepoint = 0:timepoints
+        totalCountsR = zeros(256,1);%creates array to store histograms
+        totalCountsG = zeros(256,1);
+        for slice = 0:slices
+            filename = strcat(path, '/', name, '/', name, '_z', GetSlice(slice), '_t', GetSlice(timepoint),'_p', num2str(position));
+            I = stitchImage(filename);%opens image in a range of 0 to 1
+            %extract individual channels
+            ImR = squeeze(I(:,:,1));
+            ImG = squeeze(I(:,:,2));
+            %change range
+            ImR1 = mat2gray(ImR);%this rescales the range of intensities of the image, bioasing the results...
+            ImG1 = mat2gray(ImG);
+            %get histogram
+            [countsR] = imhist(ImR1);
+            [countsG] = imhist(ImG1);
+            %add pixels of stack to total pixels
+            totalCountsR= totalCountsR+countsR;
+            totalCountsG= totalCountsG+countsG;
+            %binarize using "global" algorithm     
+        end
+        ThresholdRed(timepoint+1)=otsuthresh(totalCountsR);%this correction is because matlab starts at 1 and timepoints at 0
+        ThresholdGreen(timepoint+1)=otsuthresh(totalCountsG);
+    end
+    fileName = strcat('/nv/hp10/jbarraza6/data/Matlab/Mat2Gray/Output/Thresholds/',date,'/threshold_p_',num2str(position),'.csv');
+    thresholdArray = cat (2,ThresholdRed,ThresholdGreen);
[…]

### 2019-06-19 Thresholding.m

@@ -1,0 +1,170 @@
+timepoints = 17;
+positions = 5;
+slices = 91;%these are # of slices -1, the number on the file
+path ='/Volumes/Seagate Backup Plus Drive/Good images/';
+
+%{        
+filename = stitchImage(strcat(path, date, '/',name, '/', name, '_z', GetSlice(22), '_t', GetSlice(8),'_p', num2str(0))); 
+imred = squeeze(filename(:,:,1));
+imred = imbinarize(imred);
+[labels1,numLabels1] = bwlabel(imred);
+%}
+
+%[thR,thG] = CollectThresholds(path, date, name, 40, 1, 4);
+%testThresholdImage = ThresholdImage(path, date, name, 40, 1, 4);
+%[thR,thG] = CollectThresholds(path, date, name, slices,17, 4);
+%testThresholdImages = ThresholdImage(path, date, name, slices, 17, 4,thR,thG);
+pa14wt_1 = GetImageData(path, '3-13-19', '62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-13-19', slices, timepoints, positions);
+pa14wt_2 = GetImageData(path, '3-19-19', '62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-19-19', slices, timepoints, positions);
+pa14wt_3 = GetImageData(path, '4-17-19', '62x_Salac_Pa14wt_SaPa14wt1-11-10100-110-1_co_SCFM2_tile2x2_4-17-19', slices, timepoints, positions);
+
+pa14mut_1 = GetImageData(path, '4-24-19', '62x_Salac_Pa14pqsLclean_SaPa14pqsLclean=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_4-24-19', slices, timepoints, positions);
+pa14mut_2 = GetImageData(path, '4-25-19', '62x_Salac_Pa14pqsLclean_SaPa14pqsLclean=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_4-25-19', slices, timepoints, positions);
[…]

### 2019-06-19 WriteAggregateFiles.m

@@ -1,0 +1,73 @@
+
+path ='/Volumes/Seagate Backup Plus Drive/Good images/';
+
+testWriteAggregateFiles = WriteAggregateFiles(path,'3-13-19',2,2,10);
+
+function writeFiles = WriteAggregateFiles(path, date, timepoints, positions, slices)
+resultsfilepath = strcat(path, date,'/aggregateSizes');
+[~,~] = mkdir(resultsfilepath);
+for position = 0:positions
+    for timepoint = 0:timepoints
+        GetAggegateSizes(path, date, timepoint, position, slices)
+    end
+end
+writeFiles = 1;
+end
+
+function aggregateSizeList = GetAggegateSizes(path, date, timepoint, position, slices) %this function has input 
+imagesfilepath = strcat(path, date,'/images');
+imageFile = strcat(imagesfilepath,'/t',GetSlice(timepoint),'_p',num2str(position),'_s');%create image name to store
+redStucture = Get3DImage(imageFile, 1, slices);
+greenStucture = Get3DImage(imageFile, 2, slices);
+totalAggregates = redStucture.NumObjects+redStucture.NumObjects;
+aggregateSizeList = zeros(totalAggregates,2);
+count = 1;
+for agg1 = 1:redStucture.NumObjects
+    %aggregateSizeList{count,1}= agg1;%aggregate 1 number
+    aggregateSizeList{count,1}= GetObjectSize(redStucture,agg1);%volume aggregate 1
+    aggregateSizeList{count,2}= "Sa";
+    count= count+1;
+end
+
+for agg2 = 1:greenStucture.NumObjects
+    %aggregateSizeList{count,1}= agg2;%aggregate 1 number
+    aggregateSizeList{count,1}= GetObjectSize(greenStucture,agg2);%volume ofaggregate
+    aggregateSizeList{count,2}= "Pa";
+    count= count+1;
+end
+filename = strcat(path, date,'/aggregateSizes/t_',GetSlice(timepoint),'p_',num2str(position),'.csv');
+csvwrite(filename,aggregateSizeList)
+end
+
+function objectSize = GetObjectSize(threeDStructure,aggNumber)
+objectSize = numel(threeDStructure.PixelIdxList{aggNumber});
+objectSize = objectSize*.264*.264*.440;
+end
+
+function threeDStructure = Get3DImage(filename, channel, slices)%this function creates a 3D matrix of a single channel containing all the objects in the confocal stack
+%the x increases to the right, left increases down and z starts at the
[…]

### 2019-06-20 Microscopy Data.Rmd
finished functions for aggregate sizes

@@
 
-testFile2<-"/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/3-13-19/aggregateSizes/t00_p1.csv"
+testAggFile1<-"/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/3-13-19/aggregateSizes/t_00p_1.csv"
 
@@
     for (timepoint in 0:17){
-      currentTimePoint<-currentPosition[grep(paste0("t_",GetNumber(timepoint),"_"),currentPosition)]
-      growthDf<-rbind(growthDf,ReadAggregateFile(currentTimePoint, position, timepoint))}}
+
+      currentTimePoint<-currentPosition[grep(paste0("t_",GetNumber(timepoint),"p_"),currentPosition)]
+
+      growthDf<-rbind(growthDf,ReadAggregateFile(currentTimePoint, position, timepoint))
+
+      }
+    }
 return(growthDf)
@@
 
-testGetResults<- GetResults("3-13-19")
+testGetAggregates<- GetAggregates("3-13-19")
 
@@
 
-testReadAggregateFile<-ReadAggregateFile(tes)
+testReadAggregateFile<-ReadAggregateFile(testAggFile1, 1 ,2)
 ```

### 2019-06-26 Microscopy Data.Rmd
ggplot functions added

--- 2019-06-19 Microscopy Data.Rmd
@@
 ```{r setup, include=FALSE}
+library(pixmap)
+library(rtiff)
+library(reshape2)
+library(gplots)
+library(dplyr)
+library(gdata)
+library(ggplot2)
+library(cowplot)
+library(magrittr)
+library(tidyr)
+library(purrr)
 
@@
 PA01mut<- c('4-23-19')
+names3<-c('rep1','rep2','rep3')
+names2<-c('rep1','rep2')
 
-Get<- function (sample){
-  bugCounts<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/", sample,"/results"),header = TRUE)
-  bugCounts<- na.omit(bugCounts)
-  bugCounts<-bugCounts %>% mutate(logTranformed = log10(CFU))
-  bugCounts$sample<-sample
-  return(bugCounts)
+```
+
+```{r thresholds}
+
+testThresholdFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/3-13-19/threshold/threshold_p_0.csv"
+
+wtThresholds<-MapThreshold(PA14wt, names3)
+mutThresholds<-MapThreshold(PA14mut, names3)
+Pa01Thresholds<-MapThreshold(PA01wt, names2)
+Pa01mutThresholds<-MapThreshold(PA01mut, 'rep1')
+
+MapThreshold<- function(listSamples, reps){
+  mappedData<-map2(listSamples, reps, GetThresholds)
+  boundData<-bind_rows(mappedData)
+  return(boundData)
+  }
+
+GetThresholds<-function(sample, samplename){
+  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/',sample,'/threshold')
+  fileList<-list.files(path = folder, full.names = TRUE)
+  growthDf<-data.frame()
+  for (position in 0:5){
+    currentPosition<-fileList[grep(paste0("p_",position,"."),fileList)]
+    growthDf<-rbind(growthDf,ReadThresholdFile(currentPosition, position))}
+  growthDf<-growthDf %>% mutate(Sample = samplename)
+return(growthDf)
+}
+
+ReadThresholdFile<-function(file, position ){#This function outputs total number of pixels in the csv file from matlab
+  datos <-read.csv(file, header = FALSE)
+  colnames(datos)<-c('Red', 'Green')
+  datos<-datos %>% mutate(Position = position)
+  datos<-datos %>% mutate(TimePoint = row_number()-1)
+  return(datos)
 }
@@
 
-## R Markdown
+```{r biomass}
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+wtResults<-MapResults(PA14wt, names3)
+mutResults<-MapResults(PA14mut, names3)
+Pa01Results<-MapResults(PA01wt, names2)
+Pa01mutResults<-MapResults(PA01mut, 'rep1')
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+MapResults<- function(listSamples, reps){
+  blah <-deparse(substitute(listSamples))
+  mappedData<-map2(listSamples, reps, GetResults)
+  boundData<-bind_rows(mappedData)
+  boundData<-boundData %>% mutate(Strain = blah)
+  return(boundData)
+  }
 
-```{r cars}
-
-testFile2<-"/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/3-13-19/results/t00_p1.csv"
-
-GetResults<-function(sample){
+GetResults<-function(sample, samplename){
   folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/',sample,'/results')
@@
       growthDf<-rbind(growthDf,ReadResultsFile(currentTimePoint, position, timepoint))}}
+  growthDf<-growthDf %>% mutate(Sample = samplename)
 return(growthDf)
@@
 
-testGetResults<- GetResults("3-13-19")
-
-ReadResultsFile<-function(file, position, timepoint){#This function outputs total number of pixels in the csv file from matlab
+ReadResultsFile<-function(file, position, timepoint){
   datos <-read.csv(file, header = FALSE)
@@
 }
+
 ```
@@
 
-testFile2<-"/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/3-13-19/aggregateSizes/t00_p1.csv"
+wtAggregates<-MapAggregates(PA14wt, names3)
+mutAggregates<-MapAggregates(PA14mut, names3)
+Pa01Results<-MapAggregates(PA01wt, names2)
+Pa01mutResults<-MapAggregates(PA01mut, 'rep1')
 
-GetAggregates<-function(sample){
+MapAggregates<- function(listSamples, reps){
+  mappedData<-map2(listSamples, reps, GetAggregates)
+  boundData<-bind_rows(mappedData)
+  blah <-deparse(substitute(listSamples))
+  boundData<-boundData %>% mutate(Strain = blah)#needs to be two lines, it doesnt work if you do it directly
+  return(boundData)
+  }
+
+GetAggregates<-function(sample, samplename){
   folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/',sample,'/aggregateSizes')
@@
     for (timepoint in 0:17){
-      currentTimePoint<-currentPosition[grep(paste0("t_",GetNumber(timepoint),"_"),currentPosition)]
-      growthDf<-rbind(growthDf,ReadAggregateFile(currentTimePoint, position, timepoint))}}
+      currentTimePoint<-currentPosition[grep(paste0("t_",GetNumber(timepoint),"p_"),currentPosition)]
+      growthDf<-rbind(growthDf,ReadAggregateFile(currentTimePoint, position, timepoint))
+      }
+  }
+  growthDf<-growthDf %>% mutate(Sample = samplename)
 return(growthDf)
 }
-
-testGetResults<- GetResults("3-13-19")
 
@@
 
-testReadAggregateFile<-ReadAggregateFile(tes)
 ```
@@
 
-```{r pressure, echo=FALSE}
+```{r support functions, echo=FALSE}
+
 GetNumber<-function(idx){

### 2019-06-27 Microscopy Data.Rmd
Added some figures and wrote more ggplot functions for thresholds, z-slices and growth curves

@@
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
@@
 names2<-c('rep1','rep2')
+names1<-c('rep1')
+figuresPath<-"/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Figures"#this is to save the figures as I am making them
 
@@
 ```{r thresholds}
-
-testThresholdFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/3-13-19/threshold/threshold_p_0.csv"
-
-wtThresholds<-MapThreshold(PA14wt, names3)
-mutThresholds<-MapThreshold(PA14mut, names3)
-Pa01Thresholds<-MapThreshold(PA01wt, names2)
-Pa01mutThresholds<-MapThreshold(PA01mut, 'rep1')
-
 MapThreshold<- function(listSamples, reps){
@@
   boundData<-bind_rows(mappedData)
+  blah <-deparse(substitute(listSamples))#this is to obtain the name of the list as a string
+  boundData<-boundData %>% mutate(Strain = blah)#this inserts the name into a column, but it wont work in just one line =(
+  boundData<- gather(boundData, "Color", "Value", -Position, -Sample, -TimePoint, -Strain)
+  boundData<-boundData %>% mutate(Condition = recode(Position, "0" = "Sa Mono", "1" = "Pa Mono", "2" = "Pa:Sa 1:1", "3" = "Pa:Sa 10:1", "4" = "Pa:Sa 1:100", "5" = "Pa:Sa 1:10") )%>% mutate(Species = recode(Color, "Red" = "Sa", "Green" = "Pa"))
+  boundData$Condition<-as.factor(boundData$Condition)
+  boundData$Condition<-factor(boundData$Condition, levels = c("Sa Mono", "Pa Mono", "Pa:Sa 1:1", "Pa:Sa 1:10", "Pa:Sa 1:100","Pa:Sa 10:1"))
+  boundData$Species<-as.factor(boundData$Species)
+  boundData$Strain<-as.factor(boundData$Strain)
   return(boundData)
@@
   datos<-datos %>% mutate(Position = position)
+  datos$Position<-as.factor(datos$Position)
   datos<-datos %>% mutate(TimePoint = row_number()-1)
@@
 
+wtThresholds<-MapThreshold(PA14wt, names3)
+mutThresholds<-MapThreshold(PA14mut, names3)
+Pa01Thresholds<-MapThreshold(PA01wt, names2)
+Pa01mutThresholds<-MapThreshold(PA01mut, names1)
+
+thresholdData<-rbind(wtThresholds,mutThresholds,Pa01Thresholds,Pa01mutThresholds)
+
+#This is to get an idea of the thresholding levels
+#this is for all samples
+ggplot()+
+  geom_jitter(data=thresholdData %>% filter(Species=="Pa"),height = 0, width = .1, aes(x=TimePoint, y=Value, shape = Sample, color = Strain), size=3)+
+  facet_grid(.~Condition)
+#This is only for PA14 since they seem to be the most consistent
+ggplot()+
+  geom_jitter(data=PA14thresholdData %>% filter(Species=="Pa"),height = 0, width = .1, aes(x=TimePoint, y=Value, shape = Sample, color = Strain), size=3)+
+  facet_grid(.~Condition)
+
+PA14thresholdData <-thresholdData%>%filter(Species=="Pa") %>% filter(Strain %in% c("PA14wt", "PA14mut"))
+
+  #scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  #geom_vline(xintercept=3, linetype = "dashed")+
+  #annotate("text", x = 3, y = 10e6, label = "TOB added")+
+  #labs(title =expression(paste(italic("S. aureus"), " growth in mono or coculture in SCFM2 with 128 ug/mL TOB")), x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")
+
 ```
 
-```{r biomass}
-
-wtResults<-MapResults(PA14wt, names3)
-mutResults<-MapResults(PA14mut, names3)
-Pa01Results<-MapResults(PA01wt, names2)
-Pa01mutResults<-MapResults(PA01mut, 'rep1')
-
+```{r biomass functions}
 MapResults<- function(listSamples, reps){
@@
   boundData<-boundData %>% mutate(Strain = blah)
+  boundData<-gather(boundData,"Color","Value",-Slice,-Position,-Sample,-TimePoint,-Strain) %>% mutate(LogValue=ifelse(Value>0,log10(Value),0))
+  boundData<-boundData %>% mutate(Condition = recode(Position, "0" = "Sa Mono", "1" = "Pa Mono", "2" = "Pa:Sa 1:1", "3" = "Pa:Sa 10:1", "4" = "Pa:Sa 1:100", "5" = "Pa:Sa 1:10" )) %>% mutate(Species = recode(Color, "Red" = "Sa", "Green" = "Pa")) %>% mutate(ZDistance = Slice *0.44)
+  boundData$Condition<-as.factor(boundData$Condition)
+  boundData$Condition<-factor(boundData$Condition, levels = c("Sa Mono", "Pa Mono", "Pa:Sa 1:1", "Pa:Sa 1:10", "Pa:Sa 1:100","Pa:Sa 10:1"))
+  boundData$Species<-as.factor(boundData$Species)
+  boundData$Strain<-as.factor(boundData$Strain)
   return(boundData)
@@
 }
+```
+#Biomass per slice.
+
+Where is the majority of the biomass at any given time and How dos it grow over time.
+It additionally helps identify how reproducible are the experiments
+```{r biomass per slice}
+#Run the biomass functions on each set of samples and combine them at the end 
+wtResults<-MapResults(PA14wt, names3)
+mutResults<-MapResults(PA14mut, names3)
+Pa01Results<-MapResults(PA01wt, names2)
+Pa01mutResults<-MapResults(PA01mut, names1)
+
+ResultsData<-rbind(wtResults,mutResults,Pa01Results,Pa01mutResults)
+
+#This function uses facets to show the abundance of cells according to height over time
+GraphSlices<-function (data, bug, facete){
+  #first which bug is being selected
+  if(bug=="Sa"){data <-data %>% filter(Species == "Sa")%>% filter(!Condition == "Pa Mono");nombre<-"S. aureus"}
+  if(bug=="Pa"){data<-data %>% filter(Species == "Pa")%>% filter(!Condition == "Sa Mono");nombre<-"P. aeruginosa"}
+  #then what kind of facet can be used
+  if(missing(facete)){facete=facet_grid(Condition~TimePoint);condicion <- "Strain";forma <- NULL}
+  else{facete <-facet_wrap(~TimePoint,ncol = 6 );condicion <- "Condition";forma<-"Strain"}
+  ggplot()+
+    geom_point(data=data, aes_string(x="ZDistance", y="Value", color = condicion, shape = forma),size=1)+
+    scale_y_log10(name=expression(paste('Biomass from voxel counts' )), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    #labs(title =expression(paste(italic(nombre), " biomass value per slice in SCFM2" )),  x = "Distance from bottom (z-slice)")+
+    labs(title =paste0(nombre, " biomass value per slice in SCFM2" ),  x = "Distance from bottom (z-slice)")+
+    facete
+}
+
+ggsave("Sa z-slice condition-timepoint.png", plot = GraphSlices(ResultsData, "Sa"), path = figuresPath)
+ggsave("Sa z-slice timepoint.png", plot = GraphSlices(ResultsData, "Sa", "BLAH"), path = figuresPath)
+ggsave("Pa z-slice condition-timepoint.png", plot = GraphSlices(ResultsData, "Pa"), path = figuresPath)
+ggsave("Pa z-slice timepoint.png", plot = GraphSlices(ResultsData, "Pa", "BLAH"), path = figuresPath)
+
+#This graph shows how the distribution of biomass changes over time per experiment.
+GraphSlicesTime<-function(datos, bug, strain){
+  if(bug=="Sa"){datos<-datos %>% filter(Species == "Sa")%>% filter(!Condition == "Pa Mono");nombre<-"S. aureus"}
+  if(bug=="Pa"){datos<-datos %>% filter(Species == "Pa")%>% filter(!Condition == "Sa Mono");nombre<-"P. aeruginosa"}
+  ggplot()+
+    geom_point(data=datos %>% filter(Strain == strain) , aes(x=ZDistance, y=Value, color = TimePoint),size=1)+
+    scale_y_log10(name=expression(paste('Biomass from voxel counts' )), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    labs(title =paste(bug, "biomass value per slice in SCFM2 using",strain  ),  x = "Distance from bottom (z-slice)")+
+    facet_grid(Condition~Sample)
+}
+
+ggsave("Sa z-slice PA14wt grid.png", plot = GraphSlicesTime(ResultsData, "Sa", "PA14wt"), path = figuresPath)
+ggsave("Sa z-slice PA14mut grid.png", plot = GraphSlicesTime(ResultsData, "Sa", "PA14mut"), path = figuresPath)
+ggsave("Pa z-slice PA14wt grid.png", plot = GraphSlicesTime(ResultsData, "Pa", "PA14wt"), path = figuresPath)
+ggsave("Pa z-slice PA14mut grid.png", plot = GraphSlicesTime(ResultsData, "Pa", "PA14mut"), path = figuresPath)
 
@@
 
+Data from S. aureus. 
+Remember that all mono cultures of Sa are essentially the same: Same strain, same inoculum, same condition. So this is the only condition where you have several replicates.
+```{r biomass Sa}
+#Now that I have analyzed the individual slices, I can analyze each time point
+cleanResults<-ResultsData %>% group_by(TimePoint,Sample,Strain,Condition,Species) %>% summarise(Totals = sum (Value))%>% mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))
+cleanResultsStats<-cleanResults %>% group_by(TimePoint,Strain,Condition,Species) %>% summarise(MeanTotals = mean(Totals), MeanLogTotals = mean(LogTotals), SDTotals = sd(Totals),SDLogTotals = sd(LogTotals))
+
+cleanResultsStats1<-cleanResultsStats %>% mutate(CheckLog = MeanLogTotals^10) %>% mutate(CheckLog2 = log10(MeanTotals)) %>% mutate(DiffLog = abs(MeanLogTotals-CheckLog2)) %>% mutate(DiffTotals = abs(MeanTotals - CheckLog))
+
+GraphGrowthCurves<-function (dataRaw, dataStats, bug){
+  if(bug=="Sa"){dataRaw<-dataRaw %>% filter(Species == "Sa")%>% filter(!Condition == "Pa Mono");
+  dataStats<-dataStats %>% filter(Species == "Sa")%>% filter(!Condition == "Pa Mono");nombre<-"S. aureus"}
+  if(bug=="Pa"){dataRaw<-dataRaw %>% filter(Species == "Pa")%>% filter(!Condition == "Sa Mono");
+  dataStats<-dataStats %>% filter(Species == "Pa")%>% filter(!Condition == "Sa Mono");nombre<-"P. aeruginosa"}
+  ggplot()+
+    geom_point(data=dataRaw, aes(x=TimePoint, y=Totals),  color = "Black", size=2)+
+    geom_point(data=dataStats, aes(x=TimePoint, y=MeanTotals),  color = "Red", size=2)+
+    geom_line(data=dataStats, aes(x=TimePoint, y=MeanTotals),  color = "Red", size=2)+
+    scale_y_log10(limits= c(1e4,1e7), name=expression(paste('Biomass from voxel counts' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    labs(title =paste(bug, " growth in mono in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
+    facet_grid(Condition~Strain)
+}
+GraphGrowthCurvesExp<-function (dataRaw,dataStats, bug){
+  if(bug=="Sa"){dataRaw<-dataRaw %>% filter(Species == "Sa")%>% filter(!Condition == "Pa Mono");
+  dataStats<-dataStats %>% filter(Species == "Sa")%>% filter(!Condition == "Pa Mono");colore<-"Red"}
+  if(bug=="Pa"){dataRaw<-dataRaw %>% filter(Species == "Pa")%>% filter(!Condition == "Sa Mono");
+  dataStats<-dataStats %>% filter(Species == "Pa")%>% filter(!Condition == "Sa Mono");colore<-"Green"}
+  ggplot()+
+    geom_point(data=dataRaw, aes(x=TimePoint, y=LogTotals),  color = "Black", size=2)+
+    geom_point(data=dataStats, aes(x=TimePoint, y=MeanLogTotals),  color = colore, size=2)+
+    geom_line(data=dataStats, aes(x=TimePoint, y=MeanLogTotals),  color = colore, size=2)+
+    labs(title =paste(bug, " growth in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
+    facet_grid(Condition~Strain)
+}
+GraphGrowthCurvesExpClean<-function (dataRaw, dataStats, bug){
+  if(bug=="Sa"){dataStats<-dataStats %>% filter(Species == "Sa")%>% filter(!Condition == "Pa Mono");colore<-"Red"}
+  if(bug=="Pa"){dataStats<-dataStats %>% filter(Species == "Pa")%>% filter(!Condition == "Sa Mono");colore<-"Green"}
+  ggplot()+
+    geom_point(data=dataStats, aes(x=TimePoint, y=MeanLogTotals,  color = Condition), size=2)+
+    geom_line(data=dataStats, aes(x=TimePoint, y=MeanLogTotals,  color = Condition), size=2)+
+    labs(title =paste(bug, " growth in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
+    facet_grid(.~Strain)
+}
+
+GraphGrowthCurvesExp(cleanResults,cleanResultsStats, "Sa")
+GraphGrowthCurvesExp(cleanResults,cleanResultsStats, "Pa")
+GraphGrowthCurvesExpClean(cleanResults,cleanResultsStats, "Sa")
+GraphGrowthCurvesExpClean(cleanResults,cleanResultsStats, "Pa")
+
+#First Isolate Sa Mono
+
+cleanResultsSaMono<- cleanResultsSa %>% filter(Condition == "Sa Mono")
+
+ggplot()+
+  geom_point(data=cleanResultsSa %>% filter(Condition == "Sa Mono"), aes(x=TimePoint, y=Totals),  color = "Black", size=2)+
+  geom_smooth(data=cleanResultsSaMono, aes(x=TimePoint, y=Totals), size=3, color = "red")+
+  scale_y_log10(limits= c(1e4,1e7), name=expression(paste('Biomass from voxel counts' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  labs(title =expression(paste(italic("S. aureus"), " growth in mono in SCFM2" )),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")
+
+ggplot()+
+  geom_point(data=cleanResultsSa, aes(x=TimePoint, y=Totals, shape = NULL,  color =Strain), size=3)+
+  scale_y_log10(limits= c(1e4,1e7), name=expression(paste('Biomass' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  facet_grid(~Condition)+
+  labs(title =expression(paste(italic("S. aureus"), " growth in mono or coculture in SCFM2" )),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")
+
+#Now Sa Co-culture
+cleanResultsSaCo<- cleanResultsSa %>% filter(!Condition == "Sa Mono")
+ggplot()+
+  geom_point(data=cleanResultsSaCo, aes(x=TimePoint, y=Totals,  color = Strain), size=2)+
+  geom_smooth(data=cleanResultsSaCo, aes(x=TimePoint, y=Totals, color = Strain), size=3)+
+  scale_y_log10(limits= c(1e4,1e7), name=expression(paste('Biomass from voxel counts' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  labs(title =expression(paste(italic("S. aureus"), " growth in mono in SCFM2" )),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
+  facet_grid(~Condition)
+
+```
+
+```{r growth rates Sa}
+
+#first try to fit it to a model fro exponential growth:
+exponential.model <- lm(log(cleanResultsSaMono$Totals)~ cleanResultsSaMono$TimePoint)
+summary(exponential.model)
+
+#not very good... So I found the package "growthrates", so I'll try that
+#https://cran.r-project.org/web/packages/growthrates/vignettes/Introduction.html
+splitted.data <- multisplit(cleanResultsSaMono, c("Strain", "Sample"))
+dat<-splitted.data[[1]]
+fit <- fit_easylinear(dat$TimePoint, dat$Totals)
+summary(fit)#summary of values
+coef(fit) #exponential growth parameters
+rsquared(fit)  # coefficient of determination (of log-transformed data)
+deviance(fit)  # residual sum of squares of log-transformed data
+
+par(mfrow = c(1, 2))
+plot(fit, log = "y")
+plot(fit)
+
+many_fits <- all_easylinear(Totals ~ TimePoint | Strain + Sample, data = cleanResultsSaMono, h = 4)#the h is the number of points considered for fit
+
+par(mfrow = c(3, 3))#establish the grid
+plot(many_fits,log = "y")#plot many things
+testdf<-data.frame(as.list(rsquared))#convert to data frame
+
+#this is the mean rsquared for the growth curves. Not super useful, but it is the syntax for more interesting stuff
+pa14GrowthRates<- testdf %>% select(contains("PA14")) %>% gather() %>% summarise(mean = mean(value))
+#Now with all the conditions and find different growth rates
+
+```
+
+Data from P. aeruginosa
+
+This is a completely different story since I used different Strains of Pa throughout the project. So here they are:
+```{r biomass Pa}
+cleanResultsPaMono<- cleanResultsPa %>% filter(Condition == "Pa Mono")
+ggplot()+
+  geom_point(data=cleanResultsPaMono, aes(x=TimePoint, y=Totals, color =Strain), size=2)+
+  geom_smooth(data=cleanResultsPaMono, aes(x=TimePoint, y=Totals, color = Strain), size=3)+
+  #geom_smooth(data=cleanResultsPaMono, method = "gam",  aes(x=TimePoint, y=Totals, color = Strain), linetype = "dashed", size=3)+
+  scale_y_log10(limits= c(1e4,1e7), name=expression(paste('CFUs per mL' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))
+  #facet_grid(~Strain)
+
+#model to Fit into an exponential 
+```
+
+```{r biomass Pa and Sa}
+ggplot()+
+  geom_point(data=cleanResultsSaMono, aes(x=TimePoint, y=Totals),  color = "Black", size=2)+
+  geom_point(data=cleanResultsPaMono, aes(x=TimePoint, y=Totals, color =Strain), size=2)+
+  geom_smooth(data=cleanResultsPaMono, aes(x=TimePoint, y=Totals, color = Strain), size=3)+
+  geom_smooth(data=cleanResultsSaMono, aes(x=TimePoint, y=Totals), size=3, color = "red")+
+  #geom_smooth(data=cleanResultsPaMono, method = "gam",  aes(x=TimePoint, y=Totals, color = Strain), linetype = "dashed", size=3)+
+  scale_y_log10(limits= c(1e4,1e7), name=expression(paste('Biomass in voxels' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  labs(title =expression(paste(italic("S. aureus"), " and ", italic("P. aeruginosa"), "growth in mono in SCFM2" )),  x = "Time (hours)")
+
+ggplot()+
+  scale_y_log10(limits= c(1e4,1e7), name=expression(paste('Biomass from voxel counts' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  labs(title =expression(paste(italic("S. aureus"), " growth in mono in SCFM2" )),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")
+
+```
 ## Including Plots
 ```{r aggregates}
-
-wtAggregates<-MapAggregates(PA14wt, names3)
-mutAggregates<-MapAggregates(PA14mut, names3)
-Pa01Results<-MapAggregates(PA01wt, names2)
-Pa01mutResults<-MapAggregates(PA01mut, 'rep1')
-
 MapAggregates<- function(listSamples, reps){
@@
 
+wtAggregates<-MapAggregates(PA14wt, names3)
+mutAggregates<-MapAggregates(PA14mut, names3)
+Pa01Results<-MapAggregates(PA01wt, names2)
+Pa01mutResults<-MapAggregates(PA01mut, 'rep1')
+
 ```

### 2019-08-12 Microscopy Data.Rmd
more functions

@@
 names1<-c('rep1')
-figuresPath<-"/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Figures"#this is to save the figures as I am making them
+figuresPath<-"/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Figures1"#this is to save the figures as I am making them
 
+GetNumber<-function(idx){
+  if (idx<10){
+    idx = paste0(0,idx)
+  }
+  return (idx)
+}
 ```
@@
 #This is to get an idea of the thresholding levels
-#this is for all samples
+#this is for all samples of Pa 
 ggplot()+
@@
 #This is only for PA14 since they seem to be the most consistent
+PA14thresholdData <-thresholdData%>%filter(Species=="Pa") %>% filter(Strain %in% c("PA14wt", "PA14mut")) %>% group_by(Position, TimePoint, Strain, Condition, Species)%>% summarise(MeanThreshold = mean(Value), SDThreshold = sd(Value))
+PA14average<-PA14thresholdData %>% group_by(Position, Strain, Condition, Species)%>% summarise(MeanThreshold = mean(MeanThreshold), SDThreshold = sd(MeanThreshold))
+
 ggplot()+
-  geom_jitter(data=PA14thresholdData %>% filter(Species=="Pa"),height = 0, width = .1, aes(x=TimePoint, y=Value, shape = Sample, color = Strain), size=3)+
+  geom_point(data=thresholdData %>% filter(Species=="Pa")%>% filter(Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=Value, shape = Sample, color = Strain), size=2)+
+  geom_line(data=PA14thresholdData,aes(x = TimePoint, y = MeanThreshold, color =Strain), size = 1)+
+  geom_errorbar(data=PA14thresholdData,aes(x = TimePoint, ymin = MeanThreshold-SDThreshold, ymax = MeanThreshold+SDThreshold, color = Strain), width=.5, size = .5)+
+  geom_hline(data = PA14average, aes(yintercept = MeanThreshold, color = Strain), size = 3)+
   facet_grid(.~Condition)
 
-PA14thresholdData <-thresholdData%>%filter(Species=="Pa") %>% filter(Strain %in% c("PA14wt", "PA14mut"))
+#Now we do Staph
+SathresholdData <-thresholdData%>%filter(Species=="Sa") %>% group_by(Position, TimePoint, Strain, Condition, Species)%>% summarise(MeanThreshold = mean(Value), SDThreshold = sd(Value))
+Saaverage<-SathresholdData %>% group_by(Position, Strain, Condition, Species)%>% summarise(MeanThreshold = mean(MeanThreshold), SDThreshold = sd(MeanThreshold))
 
-  #scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  #geom_vline(xintercept=3, linetype = "dashed")+
-  #annotate("text", x = 3, y = 10e6, label = "TOB added")+
-  #labs(title =expression(paste(italic("S. aureus"), " growth in mono or coculture in SCFM2 with 128 ug/mL TOB")), x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")
+ggplot()+
+  geom_point(data=thresholdData %>% filter(Species=="Sa"), aes(x=TimePoint, y=Value, shape = Sample, color = Strain), size=2)+
+  geom_line(data=SathresholdData,aes(x = TimePoint, y = MeanThreshold, color =Strain), size = 1)+
+  geom_errorbar(data=SathresholdData,aes(x = TimePoint, ymin = MeanThreshold-SDThreshold, ymax = MeanThreshold+SDThreshold, color = Strain), width=2, size = .1)+
+  geom_hline(data = Saaverage, aes(yintercept = MeanThreshold, color = Strain), size = 3)+
+  facet_grid(.~Condition)
+
+```
+
+```{r threshold weighted growth curves}
+#These are the dataframes that we need to merge
+thresholdResultsDf<-merge(cleanResults, thresholdData) %>% mutate(WeightedLogValue = Value*LogTotals) %>% mutate(WeightedValue = Value *Totals) %>% mutate(correctedWeightedLogValue = WeightedLogValue+5)
+
+thresholdData$Condition<-as.factor(thresholdData$Condition)
+ boundData$Condition<-as.factor(boundData$Condition)
+  ggplot()+
+    geom_point(data=thresholdResultsDf%>% filter(Species == "Pa"), aes(x=TimePoint, y=correctedWeightedLogValue,  shape = Sample), size=2)+
+    geom_point(data=cleanResults%>% filter(Species == "Pa"), aes(x=TimePoint, y=LogTotals,  shape = Sample), size=2, color = "red")+
+    facet_grid(Strain~Condition)
+
+ggplot()+
+    geom_point(data=thresholdResultsDf%>% filter(Species == "Sa"), aes(x=TimePoint, y=correctedWeightedLogValue,  shape = Sample), size=2)+
+    geom_point(data=cleanResults%>% filter(Species == "Sa"), aes(x=TimePoint, y=LogTotals,  shape = Sample), size=2, color = "red")+
+    facet_grid(Strain~Condition)
+
+#Linear regressions
+#First get a df with only Sa Mono Red Channel
+SaMonoTrhesholdDf<-thresholdData%>% filter(Condition == "Sa Mono") %>% filter(Species == "Sa")
+
+#Linear regression for Thresholds
+lm(SaMonoTrhesholdDf$Value ~ SaMonoTrhesholdDf$TimePoint) 
+plot(SaMonoTrhesholdDf$TimePoint, SaMonoTrhesholdDf$Value)
+abline( 0.18154, 0.00819 )
+
+#Linear regression for Weighted Growth Curves
+SaMonoWeightedGrowthCurve<-thresholdResultsDf%>% filter(Condition == "Sa Mono") %>% filter(Species == "Sa")
+lmWeighted<-lm(SaMonoWeightedGrowthCurve$WeightedLogValue ~ SaMonoWeightedGrowthCurve$TimePoint) 
+plot(SaMonoWeightedGrowthCurve$TimePoint, SaMonoWeightedGrowthCurve$WeightedLogValue)
+abline( 1.01962, 0.06641 )
+
+#Non-linear model
+ggplot()+
+  geom_smooth(data=SaMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)+
+  geom_point(data=SaMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)
+
+ggplot()+
+  geom_smooth(data=SaMonoTrhesholdDf, method = lm, aes(x=TimePoint, y=Value), size=2)+
+  geom_point(data=SaMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)
+
+#Now do the same for Pa
+Pa14wtMonoTrhesholdDf<-thresholdData%>% filter(Condition == "Pa Mono") %>% filter(Species == "Pa") %>% filter(Strain == "PA14wt")
+Pa14mutMonoTrhesholdDf<-thresholdData%>% filter(Condition == "Pa Mono") %>% filter(Species == "Pa") %>% filter(Strain == "PA14mut")
+#Linear regression for Thresholds PA14wt
+lm(Pa14wtMonoTrhesholdDf$Value ~ Pa14wtMonoTrhesholdDf$TimePoint) 
+plot(Pa14wtMonoTrhesholdDf$TimePoint, Pa14wtMonoTrhesholdDf$Value)
+abline( 0.08775, -0.001566 )
+
+lm(Pa14mutMonoTrhesholdDf$Value ~ Pa14mutMonoTrhesholdDf$TimePoint) 
+plot(Pa14mutMonoTrhesholdDf$TimePoint, Pa14mutMonoTrhesholdDf$Value)
+abline( 0.082315, -0.001234 )
+
+#Non-linear model
+#PA14wt
+ggplot()+
+  geom_smooth(data=Pa14wtMonoTrhesholdDf, method = lm, aes(x=TimePoint, y=Value), size=2)+
+  geom_point(data=Pa14wtMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)
+ggplot()+
+  geom_smooth(data=Pa14wtMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)+
+  geom_point(data=Pa14wtMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)
+#PA14mut
+ggplot()+
+  geom_smooth(data=Pa14mutMonoTrhesholdDf, method = lm, aes(x=TimePoint, y=Value), size=2)+
+  geom_point(data=Pa14mutMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)
+ggplot()+
+  geom_smooth(data=Pa14mutMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)+
+  geom_point(data=Pa14mutMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)
 
@@
   if(missing(facete)){facete=facet_grid(Condition~TimePoint);condicion <- "Strain";forma <- NULL}
-  else{facete <-facet_wrap(~TimePoint,ncol = 6 );condicion <- "Condition";forma<-"Strain"}
+  else{facete <-facet_wrap(.~TimePoint,ncol = 6 );condicion <- "Condition";forma<-"Strain"}
   ggplot()+
@@
 
-ggsave("Sa z-slice condition-timepoint.png", plot = GraphSlices(ResultsData, "Sa"), path = figuresPath)
+ggsave("Sa z-slice condition-timepoint1.png", plot = GraphSlices(ResultsData, "Sa"), path = figuresPath)
 ggsave("Sa z-slice timepoint.png", plot = GraphSlices(ResultsData, "Sa", "BLAH"), path = figuresPath)
@@
     labs(title =paste(bug, "biomass value per slice in SCFM2 using",strain  ),  x = "Distance from bottom (z-slice)")+
-    facet_grid(Condition~Sample)
+    facet_grid(Sample~Condition)
 }
@@
 
+#This is just to check the difference between the mean log and the log of the mean, which are quite different as it turns out...
 cleanResultsStats1<-cleanResultsStats %>% mutate(CheckLog = MeanLogTotals^10) %>% mutate(CheckLog2 = log10(MeanTotals)) %>% mutate(DiffLog = abs(MeanLogTotals-CheckLog2)) %>% mutate(DiffTotals = abs(MeanTotals - CheckLog))
@@
     labs(title =paste(bug, " growth in mono in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
-    facet_grid(Condition~Strain)
+    facet_grid(Strain~Condition)
 }
@@
     labs(title =paste(bug, " growth in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
-    facet_grid(Condition~Strain)
+    facet_grid(Strain~Condition)
 }
@@
     labs(title =paste(bug, " growth in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
-    facet_grid(.~Strain)
+    facet_grid(Strain~.)
 }
@@
 ## Including Plots
+
 ```{r aggregates}
+
 MapAggregates<- function(listSamples, reps){
@@
 
-GetNumber<-function(idx){
-  if (idx<10){
-    idx = paste0(0,idx)
-  }
-  return (idx)
-}
 ```

### 2019-08-12 ThresholdingWithFunctions.m

@@ -14,6 +14,9 @@ imred = imbinarize(imred);
 %testThresholdImage = ThresholdImage(path, date, name, 40, 1, 4);
 %[thR,thG] = CollectThresholds(path, date, name, slices,17, 4);
 %testThresholdImages = ThresholdImage(path, date, name, slices, 17, 4,thR,thG);
+
+%{
+%This is how to run the script while you calculate the threshold per image:
 pa14wt_1 = GetImageData(path, '3-13-19', '62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-13-19', slices, timepoints, positions);
 pa14wt_2 = GetImageData(path, '3-19-19', '62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-19-19', slices, timepoints, positions);
 pa14wt_3 = GetImageData(path, '4-17-19', '62x_Salac_Pa14wt_SaPa14wt1-11-10100-110-1_co_SCFM2_tile2x2_4-17-19', slices, timepoints, positions);
@@ -27,6 +30,31 @@ pao1wt_2 = GetImageData(path, '4-18-19', '62x_Salac_Pa01wt_SaPa01wt=1-1,1-10,100
 pao1mut_1 = GetImageData(path, '4-23-19', '62x_Salac_Pa01pqsL_SaPa01pqsL=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_4-23-19', slices, timepoints, positions);
 
 extra = GetImageData(path, '3-28-19', '62x_SaLac-PA14wt-PA14pqsL-SaPa14wt-SaPa14pqsL-bkgd_co_SCFM2_18hrTimeLapse_tile2x2_3-28-18', 139, 11, positions);
+%}
+
+%This is how to do it with the thresholds calculated from analyzing the
+%thresholds from previous analysis
+SaThreshold = ones(18,1)*0.2143;
+Pa14wtThreshold = ones(18,1)*0.081486;
+Pa14mutThreshold = ones(18,1)*0.077379;
+pa14wt_1 = GetImageData2(path, '3-13-19', '62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-13-19', slices, timepoints, positions, SaThreshold,Pa14wtThreshold);
[…]

### 2019-08-13 Microscopy Data.Rmd
Added data using the new thresholds

@@
 names1<-c('rep1')
-figuresPath<-"/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Figures1"#this is to save the figures as I am making them
+figuresPath<-"/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Figures"#this is to save the figures as I am making them
 
@@
 #These are the dataframes that we need to merge
+#I am not entirely sure what this should tell you, but I thought about multiplying the threshold by the value to see if something comes up
 thresholdResultsDf<-merge(cleanResults, thresholdData) %>% mutate(WeightedLogValue = Value*LogTotals) %>% mutate(WeightedValue = Value *Totals) %>% mutate(correctedWeightedLogValue = WeightedLogValue+5)
@@
 
-Where is the majority of the biomass at any given time and How dos it grow over time.
+Where is the majority of the biomass at any given time? and How dos it grow over time.
 It additionally helps identify how reproducible are the experiments
-```{r biomass per slice}
+```{r biomass data}
 #Run the biomass functions on each set of samples and combine them at the end 
@@
 
-#This function uses facets to show the abundance of cells according to height over time
-GraphSlices<-function (data, bug, facete){
-  #first which bug is being selected
-  if(bug=="Sa"){data <-data %>% filter(Species == "Sa")%>% filter(!Condition == "Pa Mono");nombre<-"S. aureus"}
-  if(bug=="Pa"){data<-data %>% filter(Species == "Pa")%>% filter(!Condition == "Sa Mono");nombre<-"P. aeruginosa"}
-  #then what kind of facet can be used
-  if(missing(facete)){facete=facet_grid(Condition~TimePoint);condicion <- "Strain";forma <- NULL}
-  else{facete <-facet_wrap(.~TimePoint,ncol = 6 );condicion <- "Condition";forma<-"Strain"}
-  ggplot()+
-    geom_point(data=data, aes_string(x="ZDistance", y="Value", color = condicion, shape = forma),size=1)+
-    scale_y_log10(name=expression(paste('Biomass from voxel counts' )), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-    #labs(title =expression(paste(italic(nombre), " biomass value per slice in SCFM2" )),  x = "Distance from bottom (z-slice)")+
-    labs(title =paste0(nombre, " biomass value per slice in SCFM2" ),  x = "Distance from bottom (z-slice)")+
-    facete
-}
+#Now make it tidy and do some stats:
+cleanResults<-ResultsData %>% group_by(TimePoint,Sample,Strain,Condition,Species) %>% summarise(Totals = sum (Value))%>% mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))#this adds up all the data on each slice and then gets the log of that total
+cleanResultsStats<-cleanResults %>% group_by(TimePoint,Strain,Condition,Species) %>% summarise(MeanTotals = mean(Totals), SDTotals = sd(Totals), MeanLogTotals = mean(LogTotals), SDLogTotals = sd(LogTotals)) %>% mutate(MeanLogTotalsRevd = 10^MeanLogTotals, SDLogTotalsRevd =10^(SDLogTotals)) #stats between reps
 
-ggsave("Sa z-slice condition-timepoint1.png", plot = GraphSlices(ResultsData, "Sa"), path = figuresPath)
-ggsave("Sa z-slice timepoint.png", plot = GraphSlices(ResultsData, "Sa", "BLAH"), path = figuresPath)
-ggsave("Pa z-slice condition-timepoint.png", plot = GraphSlices(ResultsData, "Pa"), path = figuresPath)
-ggsave("Pa z-slice timepoint.png", plot = GraphSlices(ResultsData, "Pa", "BLAH"), path = figuresPath)
-
-#This graph shows how the distribution of biomass changes over time per experiment.
-GraphSlicesTime<-function(datos, bug, strain){
-  if(bug=="Sa"){datos<-datos %>% filter(Species == "Sa")%>% filter(!Condition == "Pa Mono");nombre<-"S. aureus"}
-  if(bug=="Pa"){datos<-datos %>% filter(Species == "Pa")%>% filter(!Condition == "Sa Mono");nombre<-"P. aeruginosa"}
-  ggplot()+
-    geom_point(data=datos %>% filter(Strain == strain) , aes(x=ZDistance, y=Value, color = TimePoint),size=1)+
-    scale_y_log10(name=expression(paste('Biomass from voxel counts' )), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-    labs(title =paste(bug, "biomass value per slice in SCFM2 using",strain  ),  x = "Distance from bottom (z-slice)")+
-    facet_grid(Sample~Condition)
-}
-
-ggsave("Sa z-slice PA14wt grid.png", plot = GraphSlicesTime(ResultsData, "Sa", "PA14wt"), path = figuresPath)
-ggsave("Sa z-slice PA14mut grid.png", plot = GraphSlicesTime(ResultsData, "Sa", "PA14mut"), path = figuresPath)
-ggsave("Pa z-slice PA14wt grid.png", plot = GraphSlicesTime(ResultsData, "Pa", "PA14wt"), path = figuresPath)
-ggsave("Pa z-slice PA14mut grid.png", plot = GraphSlicesTime(ResultsData, "Pa", "PA14mut"), path = figuresPath)
-
+#This is just to check the difference between the mean log and the log of the mean, which are quite different as it turns out...
+clean1ResultsStats<-cleanResultsStats %>% mutate(CheckLog = MeanLogTotals^10) %>% mutate(CheckLog2 = log10(MeanTotals)) %>% mutate(DiffLog = abs(MeanLogTotals-CheckLog2)) %>% mutate(DiffTotals = abs(MeanTotals - CheckLog))
 ```
@@
 ```{r biomass Sa}
-#Now that I have analyzed the individual slices, I can analyze each time point
-cleanResults<-ResultsData %>% group_by(TimePoint,Sample,Strain,Condition,Species) %>% summarise(Totals = sum (Value))%>% mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))
-cleanResultsStats<-cleanResults %>% group_by(TimePoint,Strain,Condition,Species) %>% summarise(MeanTotals = mean(Totals), MeanLogTotals = mean(LogTotals), SDTotals = sd(Totals),SDLogTotals = sd(LogTotals))
-
-#This is just to check the difference between the mean log and the log of the mean, which are quite different as it turns out...
-cleanResultsStats1<-cleanResultsStats %>% mutate(CheckLog = MeanLogTotals^10) %>% mutate(CheckLog2 = log10(MeanTotals)) %>% mutate(DiffLog = abs(MeanLogTotals-CheckLog2)) %>% mutate(DiffTotals = abs(MeanTotals - CheckLog))
 
@@
     scale_y_log10(limits= c(1e4,1e7), name=expression(paste('Biomass from voxel counts' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-    labs(title =paste(bug, " growth in mono in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
+    labs(title =paste(bug, "growth in mono in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
     facet_grid(Strain~Condition)
@@
     geom_line(data=dataStats, aes(x=TimePoint, y=MeanLogTotals),  color = colore, size=2)+
-    labs(title =paste(bug, " growth in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
+    labs(title =paste(bug, "growth in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
     facet_grid(Strain~Condition)
@@
   ggplot()+
-    geom_point(data=dataStats, aes(x=TimePoint, y=MeanLogTotals,  color = Condition), size=2)+
+    #geom_point(data=dataStats, aes(x=TimePoint, y=MeanLogTotals,  color = Condition), size=2)+
     geom_line(data=dataStats, aes(x=TimePoint, y=MeanLogTotals,  color = Condition), size=2)+
-    labs(title =paste(bug, " growth in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
-    facet_grid(Strain~.)
+    labs(title =paste(bug, "growth in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
+    facet_grid(.~Strain)
 }
@@
 
+cleanResultsSa <- cleanResults %>% filter(Species == "Sa")
 cleanResultsSaMono<- cleanResultsSa %>% filter(Condition == "Sa Mono")
@@
   facet_grid(~Condition)
-
 ```
@@
 ```
-## Including Plots
+## Now we are showing the
 
@@
 Pa01mutResults<-MapAggregates(PA01mut, 'rep1')
+```
+
+```{r Biomass per slice }
+#This function uses facets to show the abundance of cells according to height over time
+GraphSlices<-function (data, bug, facete){
+  #first which bug is being selected
+  if(bug=="Sa"){data <-data %>% filter(Species == "Sa")%>% filter(!Condition == "Pa Mono");nombre<-"S. aureus"}
+  if(bug=="Pa"){data<-data %>% filter(Species == "Pa")%>% filter(!Condition == "Sa Mono");nombre<-"P. aeruginosa"}
+  #then what kind of facet can be used
+  if(missing(facete)){facete=facet_grid(Condition~TimePoint);condicion <- "Strain";forma <- NULL}
+  else{facete <-facet_wrap(.~TimePoint,ncol = 6 );condicion <- "Condition";forma<-"Strain"}
+  ggplot()+
+    geom_point(data=data, aes_string(x="ZDistance", y="Value", color = condicion, shape = forma),size=1)+
+    scale_y_log10(name=expression(paste('Biomass from voxel counts' )), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    #labs(title =expression(paste(italic(nombre), " biomass value per slice in SCFM2" )),  x = "Distance from bottom (z-slice)")+
+    labs(title =paste0(nombre, " biomass value per slice in SCFM2" ),  x = "Distance from bottom (z-slice)")+
+    facete
+}
+
+ggsave("Sa z-slice condition-timepoint1.png", plot = GraphSlices(ResultsData, "Sa"), path = figuresPath)
+ggsave("Sa z-slice timepoint.png", plot = GraphSlices(ResultsData, "Sa", "BLAH"), path = figuresPath)
+ggsave("Pa z-slice condition-timepoint.png", plot = GraphSlices(ResultsData, "Pa"), path = figuresPath)
+ggsave("Pa z-slice timepoint.png", plot = GraphSlices(ResultsData, "Pa", "BLAH"), path = figuresPath)
+
+#This graph shows how the distribution of biomass changes over time per experiment.
+GraphSlicesTime<-function(datos, bug, strain){
+  if(bug=="Sa"){datos<-datos %>% filter(Species == "Sa")%>% filter(!Condition == "Pa Mono");nombre<-"S. aureus"}
+  if(bug=="Pa"){datos<-datos %>% filter(Species == "Pa")%>% filter(!Condition == "Sa Mono");nombre<-"P. aeruginosa"}
+  ggplot()+
+    geom_point(data=datos %>% filter(Strain == strain) , aes(x=ZDistance, y=Value, color = TimePoint),size=1)+
+    scale_y_log10(name=expression(paste('Biomass from voxel counts' )), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    labs(title =paste(bug, "biomass value per slice in SCFM2 using",strain  ),  x = "Distance from bottom (z-slice)")+
+    facet_grid(Sample~Condition)
+}
+
+ggsave("Sa z-slice PA14wt grid.png", plot = GraphSlicesTime(ResultsData, "Sa", "PA14wt"), path = figuresPath)
+ggsave("Sa z-slice PA14mut grid.png", plot = GraphSlicesTime(ResultsData, "Sa", "PA14mut"), path = figuresPath)
+ggsave("Pa z-slice PA14wt grid.png", plot = GraphSlicesTime(ResultsData, "Pa", "PA14wt"), path = figuresPath)
+ggsave("Pa z-slice PA14mut grid.png", plot = GraphSlicesTime(ResultsData, "Pa", "PA14mut"), path = figuresPath)
+```
+
+```{r new threshold images}
+#To get the data from the new results folder I have to rewrite this function:
+GetResults<-function(sample, samplename){
+  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data1/',sample,'/results')#the path needs to be "Other Data1"
+  fileList<-list.files(path = folder, full.names = TRUE)
+  growthDf<-data.frame()
+  for (position in 0:5){
+    currentPosition<-fileList[grep(paste0("p",position,"."),fileList)]
+    for (timepoint in 0:17){
+      currentTimePoint<-currentPosition[grep(paste0("t",GetNumber(timepoint),"_"),currentPosition)]
+      growthDf<-rbind(growthDf,ReadResultsFile(currentTimePoint, position, timepoint))}}
+  growthDf<-growthDf %>% mutate(Sample = samplename)
+return(growthDf)
+}
+
+#This is also useful so that I know how the pipeline works
+#first run MapResults which gets you all the data:
+wtResults1<-MapResults(PA14wt, names3)
+mutResults1<-MapResults(PA14mut, names3)
+#combine them:
+ResultsData1<-rbind(wtResults1,mutResults1)
+#Get stats:
+cleanResults1<-ResultsData1 %>% group_by(TimePoint,Sample,Strain,Condition,Species) %>% summarise(Totals = sum (Value))%>% mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))#this adds up all the data on each slice and then gets the log of that total
+cleanResultsStats1<-cleanResults1 %>% group_by(TimePoint,Strain,Condition,Species) %>% summarise(MeanTotals = mean(Totals), SDTotals = sd(Totals), MeanLogTotals = mean(LogTotals), SDLogTotals = sd(LogTotals)) %>% mutate(MeanLogTotalsRevd = 10^MeanLogTotals, SDLogTotalsRevd =10^(SDLogTotals))
+#Graph
+
+#This Graphs 
+GraphGrowthCurves(cleanResults%>%filter(Strain%in%c("PA14wt","PA14mut")),cleanResultsStats%>%filter(Strain%in%c("PA14wt","PA14mut")),"Sa")
+GraphGrowthCurves(cleanResults1,cleanResultsStats1, "Sa")
+
+#This graphs the mean of the log totals along with the log of the totals themselves
+GraphGrowthCurvesExp(cleanResults%>%filter(Strain%in%c("PA14wt","PA14mut")),cleanResultsStats%>%filter(Strain%in%c("PA14wt","PA14mut")), "Sa")
+GraphGrowthCurvesExp(cleanResults1,cleanResultsStats1, "Sa")
+
+#This graphs only the mean of the log values, no other points
+GraphGrowthCurvesExpClean(cleanResults%>%filter(Strain%in%c("PA14wt","PA14mut")),cleanResultsStats%>%filter(Strain%in%c("PA14wt","PA14mut")), "Sa")
+GraphGrowthCurvesExpClean(cleanResults1,cleanResultsStats1, "Sa")
+
+#Isolate Sa
+
+cleanResultsSa1 <- cleanResults1 %>% filter(Species == "Sa")
+cleanResultsSaMono1<- cleanResultsSa1 %>% filter(Condition == "Sa Mono")
+
+ggplot()+
+  geom_point(data=cleanResultsSa1 %>% filter(Condition == "Sa Mono"), aes(x=TimePoint, y=Totals),  color = "Black", size=2)+
+  geom_smooth(data=cleanResultsSaMono1, aes(x=TimePoint, y=Totals), size=3, color = "red")+
+  scale_y_log10(limits= c(1e4,1e7), name=expression(paste('Biomass from voxel counts' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  labs(title =expression(paste(italic("S. aureus"), " growth in mono in SCFM2" )),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")
+
+GraphGrowthCurvesExp(cleanResults1,cleanResultsStats1, "Pa")
+GraphGrowthCurvesExpClean(cleanResults1,cleanResultsStats1, "Pa")
+
+GraphGrowthCurvesExpCleanCoCulture<-function (dataStats){
+  ggplot()+
+    geom_line(data=dataStats %>% filter(!Condition %in% c("Pa Mono", "Sa Mono")), aes(x=TimePoint, y=MeanLogTotals,  color = Strain, linetype = Species), size=2)+
+    labs(title =paste("Growth in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
+    facet_grid(.~Condition)
+}
+
+GraphGrowthCurvesExpCleanCoCulture(cleanResultsStats)
 
 ```
-You can also embed plots, for example:
-
-```{r support functions, echo=FALSE}
-
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2019-08-14 CFU Data.Rmd
new file with the CFU data with the new SCFM2

---
title: "Growth Curves Paper"
author: "Juan P Barraza"
date: "8/14/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(pixmap)
library(rtiff)
library(reshape2)
library(gplots)
library(dplyr)
library(gdata)
library(ggplot2)
library(cowplot)
library(magrittr)
library(tidyr)
library(plotrix)
library(purrr)

#Data gathering functions:
GetGrowthCurveReplicate<- function (sample){
  bugCounts<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/GrowthCurves/", sample, ".csv"),header = TRUE)
  bugCounts<- na.omit(bugCounts)
  bugCounts<-bugCounts %>% mutate(logCFU = log10(CFU))
  bugCounts$sample<-sample
  return(bugCounts)
}
GetGrowthCurveCondition<-function(datalist){
  mappedData<-map(datalist, GetGrowthCurveReplicate)#this line reads all the files on the list
  boundData<-bind_rows(mappedData)
  colnames(boundData)[5] <- "strain"
  colnames(boundData)[8] <- "condition"
  return(boundData)
}
#Graphing functions
##this one graphs the log values
GraphGrowthCurveLog<-function (rawData, statsData){
    ggplot()+
    geom_point(data=rawData, aes(x=time, y=logCFU,color = bug, shape = strain),   size=2)+
    geom_point(data=statsData, aes(x=time, y=logCFUmean,  color = bug, shape = strain), size=2)+
    geom_line(data=statsData, aes(x=time, y=logCFUmean,  color = bug, linetype = strain), size=2)+
    #geom_errorbar(data=statsData, aes(x = time, ymin = logCFUmean-logCFUsd, ymax = logCFUmean+logCFUsd, color = bug, linetype = strain), width = 0, size = 1)+
    geom_errorbar(data=statsData, aes(x = time, ymin = logCFUmean-logCFUse, ymax = logCFUmean+logCFUse, color = bug, linetype = strain), width = 0, size = 1)+
    labs(title =paste("Growth in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Bug")+
    facet_grid(.~condition)
}
##this one graphs the normal values
GraphGrowthCurve<-function (rawData, statsData){
    ggplot()+
    geom_point(data=rawData, aes(x=time, y=CFU,color = bug, shape = strain),   size=2)+
    geom_point(data=statsData, aes(x=time, y=CFUmean,  color = bug, shape = strain), size=2)+
    geom_line(data=statsData, aes(x=time, y=CFUmean,  color = bug, linetype = strain), size=2)+
    geom_errorbar(data=statsData, aes(x = time, ymin = CFUmean-CFUsd, ymax = CFUmean+CFUsd, color = bug, linetype = strain), width = 0, size = 1)+
    labs(title =paste("Growth in SCFM2" ),  x = "Time (hours)",shape = "strain", color = "Bug")+
    scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_grid(.~condition)
}
```

```{r results}
#these are the list with the spreadsheets of experiments under different conditions
PA14 = c('2-11-19','2-7-19','2-5-19')
#get data
PA14Data<-GetGrowthCurveCondition(PA14)
#do stats
PA14DataStats<-PA14Data%>% group_by(condition, bug, time,strain) %>% summarise(CFUmean = mean (CFU), CFUsd = sd(CFU), CFUse = std.error(CFU), logCFUmean = mean (logCFU), logCFUsd = sd(logCFU),logCFUse = std.error(logCFU))
#Graph logs
GraphGrowthCurveLog(PA14Data,PA14DataStats)
#Graph regular numbers
GraphGrowthCurve(PA14Data,PA14DataStats)

```

### 2019-08-16 CFU Data.Rmd
added comparison of CFUs to Confocal biomass

@@
 library(purrr)
+library(moderndive)
 
@@
 
-```{r results}
+```{r CFU results}
 #these are the list with the spreadsheets of experiments under different conditions
@@
 ```
+
+```{r Confocal vs CFUs data wrangling}
+#first pull confocal data:
+##functions to read data
+MapResults<- function(listSamples, reps){
+  blah <-deparse(substitute(listSamples))
+  mappedData<-map2(listSamples, reps, GetResults)
+  boundData<-bind_rows(mappedData)
+  boundData<-boundData %>% mutate(Strain = blah)
+  boundData<-gather(boundData,"Color","Value",-Slice,-Position,-Sample,-TimePoint,-Strain) %>% mutate(LogValue=ifelse(Value>0,log10(Value),0))
+  boundData<-boundData %>% mutate(Condition = recode(Position, "0" = "Sa Mono", "1" = "Pa Mono", "2" = "Pa:Sa 1:1", "3" = "Pa:Sa 10:1", "4" = "Pa:Sa 1:100", "5" = "Pa:Sa 1:10" )) %>% mutate(Species = recode(Color, "Red" = "Sa", "Green" = "Pa")) %>% mutate(ZDistance = Slice *0.44)
+  boundData$Condition<-as.factor(boundData$Condition)
+  boundData$Condition<-factor(boundData$Condition, levels = c("Sa Mono", "Pa Mono", "Pa:Sa 1:1", "Pa:Sa 1:10", "Pa:Sa 1:100","Pa:Sa 10:1"))
+  boundData$Species<-as.factor(boundData$Species)
+  boundData$Strain<-as.factor(boundData$Strain)
+  return(boundData)
+  }
+ReadResultsFile<-function(file, position, timepoint){
+  datos <-read.csv(file, header = FALSE)
+  colnames(datos)<-c('Red', 'Green', 'Slice')
+  datos<-datos %>% mutate(Position = position)
+  datos<-datos %>% mutate(TimePoint = timepoint)
+  return(datos)
+}
+GetResults<-function(sample, samplename){
+  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data1/',sample,'/results')#the path needs to be "Other Data1"
+  fileList<-list.files(path = folder, full.names = TRUE)
+  growthDf<-data.frame()
+  for (position in 0:5){
+    currentPosition<-fileList[grep(paste0("p",position,"."),fileList)]
+    for (timepoint in 0:17){
+      currentTimePoint<-currentPosition[grep(paste0("t",GetNumber(timepoint),"_"),currentPosition)]
+      growthDf<-rbind(growthDf,ReadResultsFile(currentTimePoint, position, timepoint))}}
+  growthDf<-growthDf %>% mutate(Sample = samplename)
+return(growthDf)
+}
+
+PA14wt<- c('3-13-19', '3-19-19', '4-17-19')#sample names 
+PA14mut<- c('4-24-19', '4-25-19', '5-8-19')
+names3<-c('rep1','rep2','rep3')
+
+wtConfocalResults<-MapResults(PA14wt, names3)
+mutConfocalResults<-MapResults(PA14mut, names3)
+#combine them:
+allConfocalResults<-rbind(wtConfocalResults,mutConfocalResults)
+#Get stats:
+##this adds up all the data on each slice and then gets the log of that total
+allConfocalResults<-allConfocalResults %>% group_by(TimePoint,Sample,Strain,Condition,Species) %>% summarise(Totals = sum (Value))%>% mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))
+
+##this calculates mean and error
+allConfocalResultsStats<-allConfocalResults %>% group_by(TimePoint,Strain,Condition,Species) %>% summarise(MeanTotals = mean(Totals), SDTotals = sd(Totals), MeanLogTotals = mean(LogTotals), SDLogTotals = sd(LogTotals))
+
+##remove all the conditions I didn't do in the plate counts and fix time points:
+DataComparisonScope<-allConfocalResultsStats %>% filter (Strain %in% c("PA14wt","PA14mut")) %>% filter(Condition == "Pa:Sa 1:1") %>%  filter(TimePoint %in% c(0,3,7,11,15)) %>% select(Condition,TimePoint, Strain, Species, MeanTotals, MeanLogTotals) %>% mutate(time = ifelse(TimePoint>0, TimePoint+1, 0)) #The timePoint thing is because I start imaging after one hour and I don't have a time zero on scope
+
+##remove conditions I didn't do in the scope and fix strain names:
+DataComparisonCFU<-PA14DataStats %>% filter (condition == "Static") %>% select(bug, strain, CFUmean, logCFUmean, condition, time)%>% as.data.frame() %>% mutate(Strain = recode(DataComparisonCFU$strain, wt = "PA14wt", mut = "PA14mut"))
+
+#name columns so that they match with the columns in the other df
+colnames(DataComparisonCFU)<- c("Species", "strain", "CFUs", "logCFUs","Static", "time", "Strain")
+
+#merge data frames and fix numeric for time
+comparisonDf <- merge(DataComparisonCFU,DataComparisonScope,by=c("Species","Strain", "time"))
+comparisonDf$time<-as.numeric(as.character(comparisonDf$time))
+
+##Adding more data from the TOB experiments!
+#first select relevant conditions and fix column names
+DataComparisonCFUSa<-newSCFMDataSa%>%  filter(!culture == "mono") %>% filter(antibiotic == "Control") %>% select(CFU, culture, bug, timePoint, antibiotic, logTranformed,sample, condition) %>% group_by(culture, timePoint) %>% summarise(meanCFU = mean(CFU), meanLogCFU = mean(logTranformed))
+DataComparisonCFUSa<-DataComparisonCFUSa%>% as.data.frame() %>%mutate(Strain = recode(DataComparisonCFUSa$culture, wt = "PA14wt", mut = "PA14mut"))
+
+colnames(DataComparisonCFUSa)<-c("strain", "time", "CFUs", "logCFUs", "Strain")
+#then do the same for the scope data
+DataComparisonScopeSa<-allConfocalResultsStats %>% filter(Species == "Sa")%>% filter (Strain %in% c("PA14wt","PA14mut")) %>% filter(Condition == "Pa:Sa 1:1") %>%  filter(TimePoint %in% c(0,2,3,4)) %>% select(Condition,TimePoint, strain, Species, MeanTotals, MeanLogTotals) %>% mutate(time = ifelse(TimePoint>0, TimePoint+1, 0)) #The timePoint thing is because I start imaging after one hour and I don't have a time zero on scope
+#merge them!
+comparisonSaDf <- merge(DataComparisonCFUSa,DataComparisonScopeSa,by=c("time","Strain"))
+
+```
+
+```{r graph CFU vs Confocal}
+#Graph both Pa and Sa
+##Original data as input:
+ggplot()+
+    geom_point(data=comparisonDf, aes(x=CFUs, y=MeanTotals,color = Species, shape = Strain),   size=4)+
+    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))
+
+##Log-tranformed data as input:
+ggplot()+
+    geom_point(data=comparisonDf, aes(x=logCFUs, y=MeanLogTotals, color = Species, shape = Strain),   size=4)
+
+#Pa seems to be pretty straightforward, lets do linear regression:
+Pa14LinearModel <- lm(MeanLogTotals ~logCFUs, data = comparisonDf %>% filter (Species == "Pa"))
+coefficients(Pa14LinearModel)
+get_regression_summaries(Pa14LinearModel, print = TRUE)
+
+##Log-tranformed data as input for PA14 only:
+ggplot()+
+  geom_abline(intercept = 1.9623899, slope = 0.4639804, color = "red", size = 3 )+
+  geom_point(data=comparisonDf%>% filter(Species == "Pa"), aes(x=logCFUs,y=MeanLogTotals,  color = Species, shape = Strain),   size=4)
+#then fit it without the zero point since that was not even at the same time
+Pa14LinearModel1 <- lm(MeanLogTotals ~logCFUs, data = comparisonDf %>% filter (Species == "Pa") %>% filter(!time == 0))
+get_regression_summaries(Pa14LinearModel1, print = TRUE)
+  ggplot()+
+    geom_abline(intercept =-2.882887,slope = 1.006844, color = "red", size = 1, linetype = "dashed" )+
+    geom_point(data=comparisonDf %>% filter(Species == "Pa"), aes(x=logCFUs,y=MeanLogTotals,  color = time, shape = Strain),size=4)+
+    scale_color_gradient(low="blue", high="red")+
+    annotate("text", x = 7.5, y = 6, label = expression(paste("y=1.007x-2.883  ", R^2, "= 0.9")), color = "red", size = 8)+
+    labs(title =expression(paste(italic("P. aeruginosa"), " CFU vs Confocal Biomass")), x = "Log CFUs",y = "Biomass from Scope")
+
+#Now we go to Sa
+SaLinearModel <- lm(MeanLogTotals ~logCFUs, data = comparisonDf %>% filter (Species == "Sa"))
+coefficients(SaLinearModel)
+get_regression_summaries(SaLinearModel, print = TRUE)
+
+SaLinearModel1 <- lm(MeanLogTotals ~logCFUs, data = comparisonDf %>% filter (Species == "Sa")%>% filter(!time == 0))
+coefficients(SaLinearModel1)
+get_regression_summaries(SaLinearModel1, print = TRUE)
+
+ggplot()+
+  geom_point(data=comparisonDf %>% filter(Species == "Sa"), aes(x=logCFUs,y=MeanLogTotals,  color = time, shape = Strain),size=4)+
+  geom_abline(intercept =25.73, slope = -2.44, color = "red", size = 1, linetype = "dashed" )+
+  scale_color_gradient(low="blue", high="red")+
+  annotate("text", x = 7.9, y = 4.75, label = expression(paste("y=-2.44x+25.73  ", R^2, "= 0.619")), color = "red", size = 8)+
+  labs(title =expression(paste(italic("S. aureus"), " CFU vs Confocal Biomass")), x = "Log CFUs",y = "Biomass from Scope")
+
+#Adding the early time points of Staph:
+SaLinearModel2 <- lm(MeanLogTotals ~logCFUs, data = comparisonSaDf%>% filter(!time == 0))
+coefficients(SaLinearModel2)
+get_regression_summaries(SaLinearModel2, print = TRUE)
+ggplot()+
+  geom_point(data=comparisonSaDf %>% filter(Species == "Sa"), aes(x=logCFUs,y=MeanLogTotals,  color = time, shape = Strain),size=4)+
+  geom_abline(intercept =-2.693, slope = 0.928, color = "red", size = 1, linetype = "dashed" )+
+  scale_color_gradient(low="blue", high="red")+
+  annotate("text", x = 7.9, y = 5.2, label = expression(paste("y=0.928x-2.693 ", R^2, "= 0.59")), color = "red", size = 8)+
+  labs(title =expression(paste(italic("S. aureus"), " CFU vs Confocal Biomass")), x = "Log CFUs",y = "Biomass from Scope")
+
+```
+
+```{r using old Sa data instead? Nope, didnt work}
+#Change the function so that it takes the old data
+GetResults<-function(sample, samplename){
+  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/',sample,'/results')#the path needs to be "Other Data"
+  fileList<-list.files(path = folder, full.names = TRUE)
+  growthDf<-data.frame()
+  for (position in 0:5){
+    currentPosition<-fileList[grep(paste0("p",position,"."),fileList)]
+    for (timepoint in 0:17){
+      currentTimePoint<-currentPosition[grep(paste0("t",GetNumber(timepoint),"_"),currentPosition)]
+      growthDf<-rbind(growthDf,ReadResultsFile(currentTimePoint, position, timepoint))}}
+  growthDf<-growthDf %>% mutate(Sample = samplename)
+return(growthDf)
+}
+wtConfocalResults1<-MapResults(PA14wt, names3)
+mutConfocalResults1<-MapResults(PA14mut, names3)
+#combine them:
+allConfocalResults1<-rbind(wtConfocalResults1,mutConfocalResults1)
+#Get stats:
+##this adds up all the data on each slice and then gets the log of that total
+allConfocalResults1<-allConfocalResults1%>% group_by(TimePoint,Sample,Strain,Condition,Species) %>% summarise(Totals = sum (Value))%>% mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))
+
+##this calculates mean and error
+allConfocalResultsStats1<-allConfocalResults1%>% group_by(TimePoint,Strain,Condition,Species) %>% summarise(MeanTotals = mean(Totals), SDTotals = sd(Totals), MeanLogTotals = mean(LogTotals), SDLogTotals = sd(LogTotals))
+
+##remove all the conditions I didn't do in the plate counts and fix time points:
+DataComparisonScope1<-allConfocalResultsStats1 %>% filter (Strain %in% c("PA14wt","PA14mut")) %>% filter(Condition == "Pa:Sa 1:1") %>%  filter(TimePoint %in% c(0,3,7,11,15)) %>% select(Condition,TimePoint, Strain, Species, MeanTotals, MeanLogTotals) %>% mutate(time = ifelse(TimePoint>0, TimePoint+1, 0)) #The timePoint thing is because I start imaging after one hour and I don't have a time zero on scope
+
+comparisonDf1 <- merge(DataComparisonCFU,DataComparisonScope1,by=c("Species","Strain", "time"))
+comparisonDf1$time<-as.numeric(as.character(comparisonDf1$time))
+
+ggplot()+
+    geom_point(data=comparisonDf1 %>% filter(Species == "Sa"), aes(x=logCFUs, y=MeanLogTotals, color = time, shape = Strain),   size=4)+
+  scale_color_gradient(low="blue", high="red")
+```

### 2019-08-16 Microscopy Data.Rmd
added comparison of CFUs to Confocal biomass

@@
 #First Isolate Sa Mono
-
 cleanResultsSa <- cleanResults %>% filter(Species == "Sa")

### 2019-08-16 Growth curves and yields.Rmd
fixed spelling errors

@@
 
-##this data is from non-exponential phase cultures, but the yeld should be fine for the mono-cultures
+##this data is from non-exponential phase cultures, but the yield should be fine for the mono-cultures
 #Data from PAO1

### 2019-08-21 Microscopy Data.Rmd
added aggregate data from new thresholded images

@@
 #Isolate Sa
-
 cleanResultsSa1 <- cleanResults1 %>% filter(Species == "Sa")
@@
 GraphGrowthCurvesExpCleanCoCulture(cleanResultsStats)
+```
+#This 
+```{r new threshold images aggregates data}
+GetAggregates<-function(sample, samplename){
+  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data1/',sample,'/aggregateSizes1')
+  fileList<-list.files(path = folder, full.names = TRUE)
+  growthDf<-data.frame()
+  for (position in 0:5){
+    currentPosition<-fileList[grep(paste0("p_",position,"."),fileList)]
+    for (timepoint in 0:17){
+      currentTimePoint<-currentPosition[grep(paste0("t_",GetNumber(timepoint),"p_"),currentPosition)]
+      growthDf<-rbind(growthDf,ReadAggregateFile(currentTimePoint, position, timepoint))
+      }
+  }
+  growthDf<-growthDf %>% mutate(Sample = samplename)
+return(growthDf)
+}
+
+wtAggregates1<-MapAggregates(PA14wt, names3)
+mutAggregates1<-MapAggregates(PA14mut, names3)
+allAggregates<-bind_rows(wtAggregates1,mutAggregates1)
+allAggregates<-allAggregates %>% filter(!Size<0.5)
+
+ggplot()+
+  geom_point(data = allAggregates)
+  scale_y_log10(limits= c(1e4,1e7), name=expression(paste('Biomass from voxel counts' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  labs(title =expression(paste(italic("S. aureus"), " growth in mono in SCFM2" )),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") 
+```
+
+```{r new threshold images aggregates graph}
+TotalHistogram<-function(df){
+  biomass<-df$Size
+  totalbiomass<-sum(biomass)
+  upperLim<-max(biomass)+5-mod(max(biomass),5)
+  breaksSequence<-seq(0,upperLim,5)#this makes breaks every 100 pixels
+  histogram<-data.frame()
+  currentHist<-hist(biomass, plot = F, breaks = breaksSequence)
+  histogram<-data.frame(currentHist$counts,currentHist$mids)
+  colnames(histogram)<-c("Counts", "Midpoint")
+  histogram<-histogram[!(histogram$Counts==0),]
+  histogram%>%mutate(BiomassBin=Counts*Midpoint)->histogram
+  histogram%>%mutate(NormBiomassBin=BiomassBin/totalbiomass)->histogram
+  return(histogram)
+}
+
+testSplit<-split(allAggregates, c("Sa","Pa"))
+allAggregates1<-allAggregates %>% filter(Species %in% c("Pa", "Sa"))
+allAggregates$Strain<-as.factor(allData$Strain)
+allAggregates$Sample<-as.factor(allData$Sample)
+allAggregates$TimePoint<-as.factor(allData$TimePoint)
+allAggregates$Position<-as.factor(allData$Position)
+
+allData<-allAggregates %>% group_by(Species, Position, TimePoint, Sample, Strain)
+yas<- group_split(allData)
+
+ggplot()+
+  geom_point(data = allAggregates, aes(x = TimePoint, y= Position, color = Sample, shape = Species))+
+  facet_wrap(.~Strain)
+
+plotHist3DBiomassCounts<-function(df1, title){
+  ggplot()+
+    geom_point(data=df1,aes(x=Midpoint, y=Counts, color = source))+
+    scale_y_log10(name=expression(paste('counts' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    xlab('Biomass (um^3)')+
+    ylab('Counts')+
+    ggtitle(paste0("Raw biomass Distribution (bin size = 10 um) ",title))
+    #facet_wrap(~TimePoint, nrow=4)
+  }
+plotHist3DBiomassBinBiomass<-function(df1, title){
+  ggplot()+
+    geom_point(data=df1,aes(x=Midpoint, y=BiomassBin, color = source))+
+    scale_y_log10(name=expression(paste('counts' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    xlab('Biomass (um^3)')+
+    ylab('Counts')+
+    ggtitle(paste0("Raw biomass Distribution (bin size = 10 um) ",title))
+    #facet_wrap(~TimePoint, nrow=4)
+  }
+plotHist3DBiomassNormBinBiomass<-function(df1, title){
+  ggplot()+
+    geom_point(data=df1,aes(x=Midpoint, y=NormBiomassBin))+
+    #scale_y_log10(name=expression(paste('counts' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    xlab('Biomass (um^3)')+
+    ylab('Counts')+
+    ggtitle(paste0("Raw biomass Distribution (bin size = 10 um) ",title))
+    #facet_wrap(~TimePoint, nrow=4)
+  }
 

### 2019-08-21 Microscopy Data.Rmd
Added graphs for aggregate sizes and changed folders

--- 2019-08-13 Microscopy Data.Rmd
@@
 library(purrr)
-
+#library(moderndive)
 PA14wt<- c('3-13-19', '3-19-19', '4-17-19')
@@
 figuresPath<-"/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Figures"#this is to save the figures as I am making them
-
 GetNumber<-function(idx){
@@
 }
-
 ReadThresholdFile<-function(file, position ){#This function outputs total number of pixels in the csv file from matlab
@@
 }
-
 wtThresholds<-MapThreshold(PA14wt, names3)
@@
 Pa01mutThresholds<-MapThreshold(PA01mut, names1)
-
 thresholdData<-rbind(wtThresholds,mutThresholds,Pa01Thresholds,Pa01mutThresholds)
-
 #This is to get an idea of the thresholding levels
@@
 PA14average<-PA14thresholdData %>% group_by(Position, Strain, Condition, Species)%>% summarise(MeanThreshold = mean(MeanThreshold), SDThreshold = sd(MeanThreshold))
-
 ggplot()+
@@
   facet_grid(.~Condition)
-
 #Now we do Staph
@@
 Saaverage<-SathresholdData %>% group_by(Position, Strain, Condition, Species)%>% summarise(MeanThreshold = mean(MeanThreshold), SDThreshold = sd(MeanThreshold))
-
 ggplot()+
@@
   facet_grid(.~Condition)
-
 ```
@@
 thresholdResultsDf<-merge(cleanResults, thresholdData) %>% mutate(WeightedLogValue = Value*LogTotals) %>% mutate(WeightedValue = Value *Totals) %>% mutate(correctedWeightedLogValue = WeightedLogValue+5)
-
 thresholdData$Condition<-as.factor(thresholdData$Condition)
@@
     facet_grid(Strain~Condition)
-
 #Linear regressions
@@
 SaMonoTrhesholdDf<-thresholdData%>% filter(Condition == "Sa Mono") %>% filter(Species == "Sa")
-
 #Linear regression for Thresholds
@@
 abline( 0.18154, 0.00819 )
-
 #Linear regression for Weighted Growth Curves
@@
 abline( 1.01962, 0.06641 )
-
 #Non-linear model
@@
   geom_point(data=SaMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)
-
 ggplot()+
@@
 abline( 0.08775, -0.001566 )
-
 lm(Pa14mutMonoTrhesholdDf$Value ~ Pa14mutMonoTrhesholdDf$TimePoint) 
@@
 abline( 0.082315, -0.001234 )
-
 #Non-linear model
@@
   geom_point(data=Pa14mutMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)
-
 ```
@@
   }
-
 GetResults<-function(sample, samplename){
@@
 }
-
 ReadResultsFile<-function(file, position, timepoint){
@@
 Pa01mutResults<-MapResults(PA01mut, names1)
-
 ResultsData<-rbind(wtResults,mutResults,Pa01Results,Pa01mutResults)
-
 #Now make it tidy and do some stats:
@@
 cleanResultsStats<-cleanResults %>% group_by(TimePoint,Strain,Condition,Species) %>% summarise(MeanTotals = mean(Totals), SDTotals = sd(Totals), MeanLogTotals = mean(LogTotals), SDLogTotals = sd(LogTotals)) %>% mutate(MeanLogTotalsRevd = 10^MeanLogTotals, SDLogTotalsRevd =10^(SDLogTotals)) #stats between reps
-
 #This is just to check the difference between the mean log and the log of the mean, which are quite different as it turns out...
@@
 ```{r biomass Sa}
-
 GraphGrowthCurves<-function (dataRaw, dataStats, bug){
@@
 }
-
 GraphGrowthCurvesExp(cleanResults,cleanResultsStats, "Sa")
@@
 GraphGrowthCurvesExpClean(cleanResults,cleanResultsStats, "Pa")
-
 #First Isolate Sa Mono
-
 cleanResultsSa <- cleanResults %>% filter(Species == "Sa")
 cleanResultsSaMono<- cleanResultsSa %>% filter(Condition == "Sa Mono")
-
 ggplot()+
@@
   labs(title =expression(paste(italic("S. aureus"), " growth in mono in SCFM2" )),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") 
-
 ggplot()+
@@
   labs(title =expression(paste(italic("S. aureus"), " growth in mono or coculture in SCFM2" )),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") 
-
 #Now Sa Co-culture
@@
 ```{r growth rates Sa}
-
 #first try to fit it to a model fro exponential growth:
@@
 summary(exponential.model)
-
 #not very good... So I found the package "growthrates", so I'll try that
@@
 deviance(fit)  # residual sum of squares of log-transformed data
-
 par(mfrow = c(1, 2))
@@
 plot(fit)
-
 many_fits <- all_easylinear(Totals ~ TimePoint | Strain + Sample, data = cleanResultsSaMono, h = 4)#the h is the number of points considered for fit
-
 par(mfrow = c(3, 3))#establish the grid
@@
 testdf<-data.frame(as.list(rsquared))#convert to data frame
-
 #this is the mean rsquared for the growth curves. Not super useful, but it is the syntax for more interesting stuff
@@
 #Now with all the conditions and find different growth rates
-
 ```
@@
   #facet_grid(~Strain)
-
 #model to Fit into an exponential 
@@
   labs(title =expression(paste(italic("S. aureus"), " and ", italic("P. aeruginosa"), "growth in mono in SCFM2" )),  x = "Time (hours)")
-
 ggplot()+
@@
   labs(title =expression(paste(italic("S. aureus"), " growth in mono in SCFM2" )),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") 
-
 ```
@@
 ```{r aggregates}
-
 MapAggregates<- function(listSamples, reps){
@@
   }
-
 GetAggregates<-function(sample, samplename){
@@
 }
-
 ReadAggregateFile<-function(file, position, timepoint){#This function outputs total number of pixels in the csv file from matlab
@@
 }
-
 wtAggregates<-MapAggregates(PA14wt, names3)
@@
 }
-
 ggsave("Sa z-slice condition-timepoint1.png", plot = GraphSlices(ResultsData, "Sa"), path = figuresPath)
@@
 ggsave("Pa z-slice timepoint.png", plot = GraphSlices(ResultsData, "Pa", "BLAH"), path = figuresPath)
-
 #This graph shows how the distribution of biomass changes over time per experiment.
@@
 }
-
 ggsave("Sa z-slice PA14wt grid.png", plot = GraphSlicesTime(ResultsData, "Sa", "PA14wt"), path = figuresPath)
@@
 }
-
 #This is also useful so that I know how the pipeline works
@@
 #Graph
-
 #This Graphs 
@@
 GraphGrowthCurves(cleanResults1,cleanResultsStats1, "Sa")
-
 #This graphs the mean of the log totals along with the log of the totals themselves
@@
 GraphGrowthCurvesExp(cleanResults1,cleanResultsStats1, "Sa")
-
 #This graphs only the mean of the log values, no other points
@@
 GraphGrowthCurvesExpClean(cleanResults1,cleanResultsStats1, "Sa")
-
 #Isolate Sa
-
 cleanResultsSa1 <- cleanResults1 %>% filter(Species == "Sa")
 cleanResultsSaMono1<- cleanResultsSa1 %>% filter(Condition == "Sa Mono")
-
 ggplot()+
@@
   labs(title =expression(paste(italic("S. aureus"), " growth in mono in SCFM2" )),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") 
-
 GraphGrowthCurvesExp(cleanResults1,cleanResultsStats1, "Pa")
 GraphGrowthCurvesExpClean(cleanResults1,cleanResultsStats1, "Pa")
-
 GraphGrowthCurvesExpCleanCoCulture<-function (dataStats){
@@
 }
+GraphGrowthCurvesExpCleanCoCulture(cleanResultsStats)
+```
+#This 
+```{r new threshold images aggregates data}
+GetAggregates<-function(sample, samplename){
+  folder<- paste0('/media/whiteley/Samsung USB/Juan Data/',sample,'/aggregateSizes1')
+  fileList<-list.files(path = folder, full.names = TRUE)
+  growthDf<-data.frame()
+  for (position in 0:5){
+    currentPosition<-fileList[grep(paste0("p_",position,"."),fileList)]
+    for (timepoint in 0:17){
+      currentTimePoint<-currentPosition[grep(paste0("t_",GetNumber(timepoint),"p_"),currentPosition)]
+      growthDf<-rbind(growthDf,ReadAggregateFile(currentTimePoint, position, timepoint))
+      }
+  }
+  growthDf<-growthDf %>% mutate(Sample = samplename)
+return(growthDf)
+}
 
-GraphGrowthCurvesExpCleanCoCulture(cleanResultsStats)
+TotalHistogram<-function(df){
+  biomass<-df$Size
+  totalbiomass<-sum(biomass)
+  upperLim<-max(biomass)+5-mod(max(biomass),5)
+  breaksSequence<-seq(0,upperLim,5)#this makes breaks every 100 pixels
+  histogram<-data.frame()
+  currentHist<-hist(biomass, plot = F, breaks = breaksSequence)
+  histogram<-data.frame(currentHist$counts,currentHist$mids)
+  colnames(histogram)<-c("Counts", "Midpoint")
+  histogram<-histogram[!(histogram$Counts==0),]
+  histogram%>%mutate(BiomassBin=Counts*Midpoint)->histogram
+  histogram%>%mutate(NormBiomassBin=BiomassBin/totalbiomass)->histogram
+  return(histogram)
+}
+wtAggregates1<-MapAggregates(PA14wt, names3)
+mutAggregates1<-MapAggregates(PA14mut, names3)
+allAggregates<-bind_rows(wtAggregates1,mutAggregates1)
+allAggregates1<-allAggregates %>% filter(!Size<0.5) %>% filter(!(Position==1 & Species=="Sa")) %>% filter(!(Position==0 & Species=="Pa"))%>% filter(!Species =="")
+allAggregates1$Strain<-as.factor(allAggregates1$Strain)
+allAggregates1$Sample<-as.factor(allAggregates1$Sample)
+allAggregates1$TimePoint<-as.factor(allAggregates1$TimePoint)
+allAggregates1$Position<-as.factor(allAggregates1$Position)
+allAggregates1<-allAggregates1 %>% mutate(Condition = recode(Position, "0" = "Sa Mono", "1" = "Pa Mono", "2" = "Pa:Sa 1:1", "3" = "Pa:Sa 10:1", "4" = "Pa:Sa 1:100", "5" = "Pa:Sa 1:10" ))
+
+#get some stats on aggregates
+allDataSummary<-allAggregates1 %>% group_by(Species, Condition, TimePoint, Sample, Strain) %>% summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), sDAggSize = sd(Size), maxSize = max(Size), minSize = min(Size))
+#group them to get histograms for each experiment
+allData<-allAggregates1 %>% group_by(Species, Condition, TimePoint, Sample, Strain)#first do the correct grouping
+yas<- group_split(allData)#create list of dataframes
+allDataHistograms<-map(yas, TotalHistogram)#apply histogram function to all items in the list
 
 ```
+
+```{r new threshold images aggregates graph}
+ggplot()+
+  geom_jitter(data = allDataSummary, aes(x = TimePoint, y= Aggs, color = Species, shape = Strain), width = 0, height = 0)+
+  geom_smooth(data = allDataSummary, aes(x = TimePoint, y= Aggs, color = Species, linetype = Strain, group = interaction(Species, Strain)))+
+  facet_wrap(.~Condition)+
+  ggtitle('Number of aggregates per experiment')+
+  labs(x = "Time (hours)",y = "Number of Aggregates")
+
+#this is a decent outline of the aggregates but I need to still subset it
+ggplot()+
+  geom_point(data = allDataSummary, aes(x = TimePoint, y= meanAggSize, color = Species,shape = "Mean"))+
+  geom_point(data = allDataSummary, aes(x = TimePoint, y= maxSize, color = Species, shape = "Max"))+
+  geom_point(data = allDataSummary, aes(x = TimePoint, y= biomass, color = Species, shape = "Total"))+  
+  geom_smooth(data = allDataSummary, aes(x = TimePoint, y= meanAggSize, color = Species, linetype = Strain, group = interaction(Species)))+
+  facet_wrap(Strain~Condition)+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  ggtitle('Aggregates summary: Mean, largest and total biomass')+
+  labs(x = "Time (hours)",y = "Number of Aggregates")+
+  scale_shape_manual(name="Metric",values=c(Mean=1, Max=2, Total=17))
+
+#this led me to introduce another metric: ratio of largest aggregate to total biomass
+allDataSummary<-allDataSummary %>% mutate(RatioMaxTotal = maxSize/biomass )
+
+ggplot()+
+  geom_jitter(data = allDataSummary, aes(x = TimePoint, y= RatioMaxTotal, color = Species, shape = Strain), width = 0, height = 0)+
+  geom_smooth(data = allDataSummary, aes(x = TimePoint, y= RatioMaxTotal, color = Species, linetype = Strain, group = interaction(Species, Strain)))+
+  facet_wrap(.~Condition)+
+  ggtitle('Ratio of largest aggregate to total biomass')+
+  labs(x = "Time (hours)",y = "Proportion of largest aggregate to total biomass")
+#this seems to have a lot of noise, how does that compare to actual biomass?
+ggplot()+
+  geom_jitter(data = allDataSummary, aes(x = TimePoint, y= biomass, color = Species, shape = Strain), width = 0, height = 0)+
+  geom_smooth(data = allDataSummary, aes(x = TimePoint, y= biomass, color = Species, linetype = Strain, group = interaction(Species, Strain)))+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  facet_wrap(.~Condition)+
+  ggtitle("Total biomass")+
+  labs(x = "Time (hours)",y = "Total biomass")
+
+plotHist3DBiomassCounts<-function(df1, title){
+  ggplot()+
+    geom_point(data=df1,aes(x=Midpoint, y=Counts, color = source))+
+    scale_y_log10(name=expression(paste('counts' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    xlab('Biomass (um^3)')+
+    ylab('Counts')+
+    ggtitle(paste0("Raw biomass Distribution (bin size = 10 um) ",title))
+    #facet_wrap(~TimePoint, nrow=4)
+  }
+plotHist3DBiomassBinBiomass<-function(df1, title){
+  ggplot()+
+    geom_point(data=df1,aes(x=Midpoint, y=BiomassBin, color = source))+
+    scale_y_log10(name=expression(paste('counts' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    xlab('Biomass (um^3)')+
+    ylab('Counts')+
+    ggtitle(paste0("Raw biomass Distribution (bin size = 10 um) ",title))
+    #facet_wrap(~TimePoint, nrow=4)
+  }
+plotHist3DBiomassNormBinBiomass<-function(df1, title){
+  ggplot()+
+    geom_point(data=df1,aes(x=Midpoint, y=NormBiomassBin))+
+    #scale_y_log10(name=expression(paste('counts' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    xlab('Biomass (um^3)')+
+    ylab('Counts')+
+    ggtitle(paste0("Raw biomass Distribution (bin size = 10 um) ",title))
+    #facet_wrap(~TimePoint, nrow=4)
+  }
+```

### 2019-09-11 PropOc Data.Rmd
New script for the proportional occupancy stuff and relocation of other figs

---
title: "Proportional Occupancy"
author: "Juan P Barraza"
date: "9/11/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(pixmap)
library(rtiff)
library(reshape2)
library(gplots)
library(dplyr)
library(gdata)
library(ggplot2)
library(cowplot)
library(magrittr)
library(tidyr)
library(purrr)
library(moderndive)
```

```{r read data, include=FALSE}
#names of samples
wtsamplesList<-c("PA14wt_1","PA14wt_2","PA14wt_3")
mutsamplesList<-c("PA14mut_1","PA14mut_2","PA14mut_3")

ReadPropOcFile<-function(sample, strain){#This function outputs total number of pixels in the csv file from matlab
  file<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/PropOc Data1/',sample,'.csv')
  datos <-read.csv(file, header = TRUE)
  datos<-datos %>% mutate(TimePoint = timePoint+1)
  datos<-datos %>% mutate(Sample = sample)
  datos$Sample<-as.factor(datos$Sample)
  datos<-datos %>% mutate(Strain = strain)
  datos$Strain<-as.factor(datos$Strain)
  datos<-datos %>% mutate(Relation = recode(source, "finalGG" = "Pa->Pa","finalRG" = "Sa->Pa","finalRR" = "Sa->Sa","finalGR" = "Pa->Sa"))%>%mutate(Condition = recode(position, "2" = "Pa:Sa 1:1", "3" = "Pa:Sa 10:1", "4" = "Pa:Sa 1:100", "5" = "Pa:Sa 1:10"))
  datos$Relation<-as.factor(datos$Relation)
  datos$Relation<-factor(datos$Relation, levels = c("Pa->Pa", "Sa->Sa", "Sa->Pa","Pa->Sa"))
  datos$Condition<-as.factor(datos$Condition)
  datos$Condition<-factor(datos$Condition, levels = c("Pa:Sa 1:1", "Pa:Sa 1:10", "Pa:Sa 1:100","Pa:Sa 10:1"))
  return(datos)
}
#combine the data from all samples
wtpropOcData.list<-map2(wtsamplesList, "wt", ReadPropOcFile)
mutpropOcData.list<-map2(mutsamplesList, "mut", ReadPropOcFile)
propOcData<-bind_rows(wtpropOcData.list,mutpropOcData.list)
```

```{r graphing all data}
#Start building some graphs:
graphAllData<-function(relation){
ggplot()+
  geom_point(data = propOcData%>% filter(Relation == relation), aes (x = distance, y = normPropOccup, color = Strain))+
  facet_grid(Condition~TimePoint)+
  ylab("Proportional occupancy")+
  ggtitle(paste0("Proportional occupancy ",relation, " (All data)"))
}
graphAllData("Pa->Pa")
graphAllData("Sa->Sa")
graphAllData("Sa->Pa")
graphAllData("Pa->Sa")
```

```{r graph stats}
#do stats:
propOcData.stats<-propOcData %>% group_by(distance, Relation, Condition, Strain, TimePoint) %>% summarize(MeanPropOc = mean(normPropOccup), SDPropOc = sd(normPropOccup)) 
#graph them:
graphStatsData<-function(relation){
ggplot()+
  geom_line(data = propOcData.stats%>% filter(Relation == relation), aes (x = distance, y = MeanPropOc, color = Strain))+
  geom_errorbar(data = propOcData.stats%>% filter(Relation == relation), aes (x = distance, ymin = MeanPropOc-SDPropOc,ymax = MeanPropOc+SDPropOc, color = Strain))+
  facet_grid(Condition~TimePoint)+
  ylab("Proportional Occupancy")+
  ggtitle(paste0("Proportional occupancy ",relation, " (Stats)"))
}
graphStatsData("Pa->Pa")
graphStatsData("Sa->Sa")
graphStatsData("Sa->Pa")
graphStatsData("Pa->Sa")
```

### 2019-09-26 CFU Data.Rmd
edits before sending figures to Marvin for the first time.

@@
     geom_point(data=rawData, aes(x=time, y=logCFU,color = bug, shape = strain),   size=2)+
-    geom_point(data=statsData, aes(x=time, y=logCFUmean,  color = bug, shape = strain), size=2)+
+    #geom_point(data=statsData, aes(x=time, y=logCFUmean,  color = bug, shape = strain), size=2)+
     geom_line(data=statsData, aes(x=time, y=logCFUmean,  color = bug, linetype = strain), size=2)+
@@
     geom_errorbar(data=statsData, aes(x = time, ymin = logCFUmean-logCFUse, ymax = logCFUmean+logCFUse, color = bug, linetype = strain), width = 0, size = 1)+
-    labs(title =paste("Growth in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Bug")+
+    labs(title =paste("Growth in SCFM2" ),  x = "Time (hours)",shape = "Strain",linetype = "Strain", color = "Bug")+
     facet_grid(.~condition)
@@
     geom_point(data=rawData, aes(x=time, y=CFU,color = bug, shape = strain),   size=2)+
-    geom_point(data=statsData, aes(x=time, y=CFUmean,  color = bug, shape = strain), size=2)+
     geom_line(data=statsData, aes(x=time, y=CFUmean,  color = bug, linetype = strain), size=2)+
     geom_errorbar(data=statsData, aes(x = time, ymin = CFUmean-CFUsd, ymax = CFUmean+CFUsd, color = bug, linetype = strain), width = 0, size = 1)+
-    labs(title =paste("Growth in SCFM2" ),  x = "Time (hours)",shape = "strain", color = "Bug")+
+    labs(title =paste("Growth in SCFM2" ),  x = "Time (hours)",shape = "strain", color = "Species")+
     scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
     facet_grid(.~condition)
+}
+
+GetNumber<-function(idx){
+  if (idx<10){
+    idx = paste0(0,idx)
+  }
+  return (idx)
 }
@@
 ##remove conditions I didn't do in the scope and fix strain names:
-DataComparisonCFU<-PA14DataStats %>% filter (condition == "Static") %>% select(bug, strain, CFUmean, logCFUmean, condition, time)%>% as.data.frame() %>% mutate(Strain = recode(DataComparisonCFU$strain, wt = "PA14wt", mut = "PA14mut"))
+DataComparisonCFU<-PA14DataStats %>% filter (condition == "Static") %>% select(bug, strain, CFUmean, logCFUmean, condition, time)%>% as.data.frame() 
+DataComparisonCFU<-DataComparisonCFU%>% mutate(Strain = recode(DataComparisonCFU$strain, wt = "PA14wt", mut = "PA14mut"))
 
@@
 DataComparisonCFUSa<-newSCFMDataSa%>%  filter(!culture == "mono") %>% filter(antibiotic == "Control") %>% select(CFU, culture, bug, timePoint, antibiotic, logTranformed,sample, condition) %>% group_by(culture, timePoint) %>% summarise(meanCFU = mean(CFU), meanLogCFU = mean(logTranformed))
+
 DataComparisonCFUSa<-DataComparisonCFUSa%>% as.data.frame() %>%mutate(Strain = recode(DataComparisonCFUSa$culture, wt = "PA14wt", mut = "PA14mut"))
@@
 #then do the same for the scope data
-DataComparisonScopeSa<-allConfocalResultsStats %>% filter(Species == "Sa")%>% filter (Strain %in% c("PA14wt","PA14mut")) %>% filter(Condition == "Pa:Sa 1:1") %>%  filter(TimePoint %in% c(0,2,3,4)) %>% select(Condition,TimePoint, strain, Species, MeanTotals, MeanLogTotals) %>% mutate(time = ifelse(TimePoint>0, TimePoint+1, 0)) #The timePoint thing is because I start imaging after one hour and I don't have a time zero on scope
+DataComparisonScopeSa<-allConfocalResultsStats %>% filter(Species == "Sa")%>% filter (Strain %in% c("PA14wt","PA14mut")) %>% filter(Condition == "Pa:Sa 1:1") %>%  filter(TimePoint %in% c(0,2,3,4)) %>% select(Condition,TimePoint, Strain, Species, MeanTotals, MeanLogTotals) %>% mutate(time = ifelse(TimePoint>0, TimePoint+1, 0)) #The timePoint thing is because I start imaging after one hour and I don't have a time zero on scope
 #merge them!

### 2019-09-26 Microscopy Data.Rmd
edits before sending figures to Marvin for the first time.

@@
 #Graph
-#This Graphs 
+#This Graphs the raw results
 GraphGrowthCurves(cleanResults%>%filter(Strain%in%c("PA14wt","PA14mut")),cleanResultsStats%>%filter(Strain%in%c("PA14wt","PA14mut")),"Sa")
@@
   labs(title =expression(paste(italic("S. aureus"), " growth in mono in SCFM2" )),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")
+
+#Now for Pa
 GraphGrowthCurvesExp(cleanResults1,cleanResultsStats1, "Pa")
@@
 }
-GraphGrowthCurvesExpCleanCoCulture(cleanResultsStats)
+GraphGrowthCurvesExpCleanCoCulture(cleanResultsStats1)
+
 ```
-#This 
-```{r new threshold images aggregates data}
+#Functions for histograms
+```{r new threshold images aggregates functions and data collection}
 GetAggregates<-function(sample, samplename){
-  folder<- paste0('/media/whiteley/Samsung USB/Juan Data/',sample,'/aggregateSizes1')
+  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data1/', sample, '/aggregateSizes1')
   fileList<-list.files(path = folder, full.names = TRUE)
@@
 
+wtAggregates1<-MapAggregates(PA14wt, names3)
+mutAggregates1<-MapAggregates(PA14mut, names3)
+allAggregates<-bind_rows(wtAggregates1,mutAggregates1)
+allAggregates1<-allAggregates %>% filter(!Size<0.5) %>% filter(!(Position==1 & Species=="Sa")) %>% filter(!(Position==0 & Species=="Pa"))%>% filter(!Species =="")
+allAggregates1$Strain<-as.factor(allAggregates1$Strain)
+allAggregates1$Sample<-as.factor(allAggregates1$Sample)
+allAggregates1$TimePoint<-as.factor(allAggregates1$TimePoint)
+allAggregates1$Position<-as.factor(allAggregates1$Position)
+allAggregates1<-allAggregates1 %>% mutate(Condition = recode(Position, "0" = "Sa Mono", "1" = "Pa Mono", "2" = "Pa:Sa 1:1", "3" = "Pa:Sa 10:1", "4" = "Pa:Sa 1:100", "5" = "Pa:Sa 1:10" ))
+
+```
+
+```{r new threshold agggregates, include=FALSE}
+#get some stats on aggregates
+allDataSummary<-allAggregates1 %>% group_by(Species, Condition, TimePoint, Sample, Strain) %>% summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), sDAggSize = sd(Size), maxSize = max(Size), minSize = min(Size))
+
+##Figure 6
+#Summary figure for total aggregate numbers
+ggplot()+
+  geom_jitter(data = allDataSummary, aes(x = TimePoint, y= Aggs, color = Species, shape = Strain), width = 0, height = 0)+
+  geom_smooth(data = allDataSummary, aes(x = TimePoint, y= Aggs, color = Species, linetype = Strain, group = interaction(Species, Strain)))+
+  facet_wrap(.~Condition)+
+  scale_y_continuous(limits= c(0,1e4))+
+  ggtitle('Number of aggregates per experiment')+
+  labs(x = "Time (hours)",y = "Number of Aggregates") 
+#this is a decent outline of the aggregates but I need to still subset it
+ggplot()+
+  geom_point(data = allDataSummary, aes(x = TimePoint, y= meanAggSize, color = Species,shape = "Mean"))+
+  geom_point(data = allDataSummary, aes(x = TimePoint, y= maxSize, color = Species, shape = "Max"))+
+  geom_point(data = allDataSummary, aes(x = TimePoint, y= biomass, color = Species, shape = "Total"))+  
+  geom_smooth(data = allDataSummary, aes(x = TimePoint, y= meanAggSize, color = Species, linetype = Strain, group = interaction(Species)))+
+  facet_wrap(Strain~Condition)+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  ggtitle('Aggregates summary: Mean, largest and total biomass')+
+  labs(x = "Time (hours)",y = "Biomass")+
+  scale_shape_manual(name="Metric",values=c(Mean=1, Max=2, Total=17))
+
+#this led me to introduce another metric: ratio of largest aggregate to total biomass
+allDataSummary<-allDataSummary %>% mutate(RatioMaxTotal = maxSize/biomass )
+
+ggplot()+
+  geom_jitter(data = allDataSummary, aes(x = TimePoint, y= RatioMaxTotal, color = Species, shape = Strain), width = 0, height = 0)+
+  geom_hline(yintercept=1, linetype = "dashed")+
+  geom_smooth(data = allDataSummary, aes(x = TimePoint, y= RatioMaxTotal, color = Species, linetype = Strain, group = interaction(Species, Strain)))+
+  facet_wrap(.~Condition)+
+  ggtitle('Ratio of largest aggregate to total biomass')+
+  labs(x = "Time (hours)",y = "Proportion of largest aggregate to total biomass")
+#this seems to have a lot of noise, how does that compare to actual biomass?
+ggplot()+
+  geom_jitter(data = allDataSummary, aes(x = TimePoint, y= biomass, color = Species, shape = Strain), width = 0, height = 0)+
+  geom_smooth(data = allDataSummary, aes(x = TimePoint, y= biomass, color = Species, linetype = Strain, group = interaction(Species, Strain)))+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  facet_wrap(.~Condition)+
+  ggtitle("Total biomass")+
+  labs(x = "Time (hours)",y = "Total biomass")
+```
+
+#Aggregate histograms
+```{r Aggregate histograms functions}
+FancyHistogram<-function(df, sec){#my own way of doing histograms which includes the sum and mean of values whitin each bin
+  results<-data.frame()
+  for( i in 1:(length(sec)-1)){
+    df %>% filter(Size > sec[i] &Size<=sec[i+1])%>%summarise(frequency = n(), avg = mean(Size),suma = sum(Size)) %>% mutate(bin = i, min = sec[i],max = sec[i+1])->blah 
+    if(blah$frequency>0){
+    results<-rbind(results, blah)}
+  }
+  return(results)
+  }
+TotalFancyHistogram<-function(df,binsize){
+  totalbiomass<-sum(df$Size)#total biomass per sample
+  totalfrequency<-length(df$Size)#total number of objects
+  upperLim<-max(df$Size)+binsize-(max(df$Size)%%binsize)#largest bin size based in largest object
+  breaksSequence<-seq(0,upperLim,binsize)#this makes breaks every "binsize" 
+  histogram<-FancyHistogram(df,breaksSequence)#apply "fancy histogram" to get distributions
+  histogram%>%mutate(BiomassBin=suma/totalbiomass)->histogram#add column with proportion of biomas per bin
+  histogram%>%mutate(Density=frequency/totalfrequency)->histogram#add column with proportion of counts per bin
+  histogram%>%mutate(Species=df$Species[1])->histogram#add column maintaining sample and so on...
+  histogram%>%mutate(Condition=df$Condition[1])->histogram
+  histogram%>%mutate(TimePoint=df$TimePoint[1])->histogram
+  histogram%>%mutate(Sample=df$Sample[1])->histogram
+  histogram%>%mutate(Strain=df$Strain[1])->histogram
+  return(histogram)
+}
 TotalHistogram<-function(df){
@@
 }
-wtAggregates1<-MapAggregates(PA14wt, names3)
-mutAggregates1<-MapAggregates(PA14mut, names3)
-allAggregates<-bind_rows(wtAggregates1,mutAggregates1)
-allAggregates1<-allAggregates %>% filter(!Size<0.5) %>% filter(!(Position==1 & Species=="Sa")) %>% filter(!(Position==0 & Species=="Pa"))%>% filter(!Species =="")
-allAggregates1$Strain<-as.factor(allAggregates1$Strain)
-allAggregates1$Sample<-as.factor(allAggregates1$Sample)
-allAggregates1$TimePoint<-as.factor(allAggregates1$TimePoint)
-allAggregates1$Position<-as.factor(allAggregates1$Position)
-allAggregates1<-allAggregates1 %>% mutate(Condition = recode(Position, "0" = "Sa Mono", "1" = "Pa Mono", "2" = "Pa:Sa 1:1", "3" = "Pa:Sa 10:1", "4" = "Pa:Sa 1:100", "5" = "Pa:Sa 1:10" ))
 
-#get some stats on aggregates
-allDataSummary<-allAggregates1 %>% group_by(Species, Condition, TimePoint, Sample, Strain) %>% summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), sDAggSize = sd(Size), maxSize = max(Size), minSize = min(Size))
-#group them to get histograms for each experiment
+##This is done just once, afterwards I just pull them up from the csv file since it takes some time to get them.
+#group them to get histograms for each experimental condition
 allData<-allAggregates1 %>% group_by(Species, Condition, TimePoint, Sample, Strain)#first do the correct grouping
-yas<- group_split(allData)#create list of dataframes
-allDataHistograms<-map(yas, TotalHistogram)#apply histogram function to all items in the list
+aggregatesList<- group_split(allData)#create list of dataframes
+allDataHistograms.5<-map2(aggregatesList, 5,TotalFancyHistogram)#apply histogram function to all items in the list
+allDataHistograms.10<-map2(aggregatesList, 10,TotalFancyHistogram)#apply histogram function to all items in the list
+allDataHistograms.50<-map2(aggregatesList, 50,TotalFancyHistogram)#apply histogram function to all items in the list
+allDataHistograms.100<-map2(aggregatesList, 100,TotalFancyHistogram)#apply histogram function to all items in the list
 
+allDataHistograms.5df<- bind_rows(allDataHistograms.5)
+allDataHistograms.10df<- bind_rows(allDataHistograms.10)
+allDataHistograms.50df<- bind_rows(allDataHistograms.50)
+allDataHistograms.100df<- bind_rows(allDataHistograms.100)
+
+write.csv(allDataHistograms.5df, file = '/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Histograms1/histograms5.csv')
+write.csv(allDataHistograms.10df,file = '/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Histograms1/histograms10.csv')
+write.csv(allDataHistograms.50df,file = '/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Histograms1/histograms50.csv')
+write.csv(allDataHistograms.100df,file = '/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Histograms1/histograms100.csv')
 ```
 
-```{r new threshold images aggregates graph}
+```{r new threshold images histogram plots}
+allDataHistograms.5df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Histograms1/histograms5.csv',header=T)
+allDataHistograms.10df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Histograms1/histograms10.csv',header=T)
+allDataHistograms.50df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Histograms1/histograms50.csv',header=T)
+allDataHistograms.100df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Histograms1/histograms100.csv',header=T)
+allDataHistograms.100df<-allDataHistograms.100df %>% mutate(Coculture = recode(Condition, "Sa Mono" = "No", "Pa Mono" = "No", "Pa:Sa 1:1" = "Yes","Pa:Sa 10:1"= "Yes", "Pa:Sa 1:100" = "Yes", "Pa:Sa 1:10" = "Yes"))
+allDataHistograms.5df<-allDataHistograms.5df %>% mutate(Coculture = recode(Condition, "Sa Mono" = "No", "Pa Mono" = "No", "Pa:Sa 1:1" = "Yes","Pa:Sa 10:1"= "Yes", "Pa:Sa 1:100" = "Yes", "Pa:Sa 1:10" = "Yes"))
+
+plotHist3DBiomassCountsLog<-function(df1, title){
   ggplot()+
-  geom_jitter(data = allDataSummary, aes(x = TimePoint, y= Aggs, color = Species, shape = Strain), width = 0, height = 0)+
-  geom_smooth(data = allDataSummary, aes(x = TimePoint, y= Aggs, color = Species, linetype = Strain, group = interaction(Species, Strain)))+
-  facet_wrap(.~Condition)+
-  ggtitle('Number of aggregates per experiment')+
-  labs(x = "Time (hours)",y = "Number of Aggregates")
-
-#this is a decent outline of the aggregates but I need to still subset it
-ggplot()+
-  geom_point(data = allDataSummary, aes(x = TimePoint, y= meanAggSize, color = Species,shape = "Mean"))+
-  geom_point(data = allDataSummary, aes(x = TimePoint, y= maxSize, color = Species, shape = "Max"))+
-  geom_point(data = allDataSummary, aes(x = TimePoint, y= biomass, color = Species, shape = "Total"))+  
-  geom_smooth(data = allDataSummary, aes(x = TimePoint, y= meanAggSize, color = Species, linetype = Strain, group = interaction(Species)))+
-  facet_wrap(Strain~Condition)+
-  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  ggtitle('Aggregates summary: Mean, largest and total biomass')+
-  labs(x = "Time (hours)",y = "Number of Aggregates")+
-  scale_shape_manual(name="Metric",values=c(Mean=1, Max=2, Total=17))
-
-#this led me to introduce another metric: ratio of largest aggregate to total biomass
-allDataSummary<-allDataSummary %>% mutate(RatioMaxTotal = maxSize/biomass )
-
-ggplot()+
-  geom_jitter(data = allDataSummary, aes(x = TimePoint, y= RatioMaxTotal, color = Species, shape = Strain), width = 0, height = 0)+
-  geom_smooth(data = allDataSummary, aes(x = TimePoint, y= RatioMaxTotal, color = Species, linetype = Strain, group = interaction(Species, Strain)))+
-  facet_wrap(.~Condition)+
-  ggtitle('Ratio of largest aggregate to total biomass')+
-  labs(x = "Time (hours)",y = "Proportion of largest aggregate to total biomass")
-#this seems to have a lot of noise, how does that compare to actual biomass?
-ggplot()+
-  geom_jitter(data = allDataSummary, aes(x = TimePoint, y= biomass, color = Species, shape = Strain), width = 0, height = 0)+
-  geom_smooth(data = allDataSummary, aes(x = TimePoint, y= biomass, color = Species, linetype = Strain, group = interaction(Species, Strain)))+
-  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  facet_wrap(.~Condition)+
-  ggtitle("Total biomass")+
-  labs(x = "Time (hours)",y = "Total biomass")
+    geom_point(data=df1,aes(x=max, y=frequency, color = Coculture, shape = Condition))+
+    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    xlab('Biomass (um^3)')+
+    ylab('Frequency')+
+    ggtitle(paste0(title," Raw biomass Distribution (bin size = 100 um)"))+
+    facet_wrap(~TimePoint, nrow=4)
+}
+#This shows that the Sa biomass that gets eaten by Staph is from the largest aggregates, not from the small ones
+plotHist3DBiomassCountsLog(allDataHistograms.100df %>% filter(Species == "Sa"), "Sa co-culture vs mono")
+plotHist3DBiomassCountsLog(allDataHistograms.100df %>% filter(Species == "Pa"), "Pa co-culture vs mono")
 
@@
   ggplot()+
-    geom_point(data=df1,aes(x=Midpoint, y=Counts, color = source))+
-    scale_y_log10(name=expression(paste('counts' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    geom_point(data=df1,aes(x=max, y=frequency, color = Strain, shape = Sample))+
+    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    xlab('Biomass (um^3)')+
+    ylab('Frequency')+
+    ggtitle(paste0(title," Raw biomass Distribution (bin size = 5 um)"))+
+    facet_wrap(~TimePoint, nrow=4)
+}
+#this shows how different ratios work to delay the dissapearance of large aggregates of staph in the samples
+plotHist3DBiomassCounts(allDataHistograms.5df%>%filter(Species=="Sa") %>% filter(Condition == "Pa:Sa 1:100")%>% filter(max<101),"Sa in Pa:Sa 1:100 only")
+plotHist3DBiomassCounts(allDataHistograms.5df%>%filter(Species =="Sa") %>% filter(Condition=="Pa:Sa 1:10")%>% filter(max<101),"Sa in Pa:Sa 1:10 only")
+plotHist3DBiomassCounts(allDataHistograms.5df%>%filter(Species == "Sa") %>%filter(Condition=="Pa:Sa 10:1")%>% filter(max<101),"Sa in Pa:Sa 10:1 only")
+#this shows how early or late large aggregates of pseudomonas appear according to the ratio
+plotHist3DBiomassCounts(allDataHistograms.5df%>%filter(Species=="Pa") %>% filter(Condition == "Pa:Sa 1:100")%>% filter(max<101),"Pa in Pa:Sa 1:100 only")
+plotHist3DBiomassCounts(allDataHistograms.5df%>%filter(Species =="Pa") %>% filter(Condition=="Pa:Sa 1:10")%>% filter(max<101),"Pa in Pa:Sa 1:10 only")
+plotHist3DBiomassCounts(allDataHistograms.5df%>%filter(Species == "Pa") %>%filter(Condition=="Pa:Sa 10:1")%>% filter(max<101),"Pa in Pa:Sa 10:1 only")
+
+#This plots how much biomass is on each bin, it should be exponential in y-axis, but I don't think it is super useful
+plotHist3DBiomassBinBiomass<-function(df1, title, binSize){
+  ggplot()+
+    geom_point(data=df1,aes(x=max, y=suma, color = Strain, shape = Condition))+
+    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
     scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-    xlab('Biomass (um^3)')+
-    ylab('Counts')+
-    ggtitle(paste0("Raw biomass Distribution (bin size = 10 um) ",title))
-    #facet_wrap(~TimePoint, nrow=4)
+    xlab('Bin size')+
+    ylab('Biomass (um^3)')+
+    ggtitle(paste0("Total Biomass per bin (bin size = ",binSize," um) ",title))+
+    facet_wrap(~TimePoint, nrow=4)
 }
-plotHist3DBiomassBinBiomass<-function(df1, title){
+plotHist3DBiomassBinBiomass(allDataHistograms.100df %>% filter(Species == "Sa") %>% filter (Coculture=="No"), "Sa co-culture vs mono", "100")
+
+#This shows how much of the total biomass is on each bin. it should just go from 0 to one, so not a great idea to make it exponential.
+plotHist3DBiomassNormBinBiomass<-function(df1, title, binSize){
   ggplot()+
-    geom_point(data=df1,aes(x=Midpoint, y=BiomassBin, color = source))+
-    scale_y_log10(name=expression(paste('counts' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    geom_point(data=df1,aes(x=max, y=BiomassBin, color = Strain, shape = Sample))+
+    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
     scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-    xlab('Biomass (um^3)')+
-    ylab('Counts')+
-    ggtitle(paste0("Raw biomass Distribution (bin size = 10 um) ",title))
-    #facet_wrap(~TimePoint, nrow=4)
+    xlab('Bin size')+
+    ylab('Contribution to total biomass')+
+    ggtitle(paste0("Biomass contribution per bin (bin size = ",binSize," um) ",title))+
+    facet_wrap(~TimePoint, nrow=4)
 }
-plotHist3DBiomassNormBinBiomass<-function(df1, title){
+#binsize of 100
+plotHist3DBiomassNormBinBiomass(allDataHistograms.100df %>% filter(Species == "Sa") %>% filter (Coculture=="No"), "Sa mono culture", "100")
+plotHist3DBiomassNormBinBiomass(allDataHistograms.100df %>% filter(Species == "Pa") %>% filter (Coculture=="No"), "Pa mono culture", "100")
+
+plotHist3DBiomassNormBinBiomass<-function(df1, title, binSize){
   ggplot()+
-    geom_point(data=df1,aes(x=Midpoint, y=NormBiomassBin))+
-    #scale_y_log10(name=expression(paste('counts' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    geom_point(data=df1,aes(x=max, y=BiomassBin, color = Strain, shape = Condition))+
+    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
     scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-    xlab('Biomass (um^3)')+
-    ylab('Counts')+
-    ggtitle(paste0("Raw biomass Distribution (bin size = 10 um) ",title))
-    #facet_wrap(~TimePoint, nrow=4)
+    xlab('Bin size')+
+    ylab('Contribution to total biomass')+
+    ggtitle(paste0("Biomass contribution per bin (bin size = ",binSize," um) ",title))+
+    facet_wrap(~TimePoint, nrow=4)
 }
+plotHist3DBiomassNormBinBiomass(allDataHistograms.100df %>% filter(Species == "Sa") %>% filter (Coculture=="Yes"), "Sa co-cultures", "100")
+plotHist3DBiomassNormBinBiomass(allDataHistograms.100df %>% filter(Species == "Pa") %>% filter (Coculture=="Yes"), "Pa co-cultures", "100")
+
+#binsize of 5
+plotHist3DBiomassNormBinBiomass(allDataHistograms.5df%>% filter(Species == "Sa") %>% filter (Coculture=="No")%>% filter(max<101), "Sa mono culture", "5")
+plotHist3DBiomassNormBinBiomass(allDataHistograms.5df%>% filter(Species == "Pa") %>% filter (Coculture=="No")%>% filter(max<101), "Pa mono culture", "5")
+
 ```

### 2019-09-26 PropOc Data.Rmd
edits before sending figures to Marvin for the first time.

@@
   geom_line(data = propOcData.stats%>% filter(Relation == relation), aes (x = distance, y = MeanPropOc, color = Strain))+
-  geom_errorbar(data = propOcData.stats%>% filter(Relation == relation), aes (x = distance, ymin = MeanPropOc-SDPropOc,ymax = MeanPropOc+SDPropOc, color = Strain))+
+  #geom_errorbar(data = propOcData.stats%>% filter(Relation == relation), aes (x = distance, ymin = MeanPropOc-SDPropOc,ymax = MeanPropOc+SDPropOc, color = Strain))+
   facet_grid(Condition~TimePoint)+

### 2020-03-03 Microscopy Data.Rmd
This is right before I start to make some changes to benchmark thresholoding with plate counts

@@
 #Non-linear model
+
 #PA14wt
@@
 allDataSummary<-allAggregates1 %>% group_by(Species, Condition, TimePoint, Sample, Strain) %>% summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), sDAggSize = sd(Size), maxSize = max(Size), minSize = min(Size))
+SaSummary<-allDataSummary %>% filter(Species == "Sa" & TimePoint == 7 & Condition == "Sa Mono") %>% ungroup()%>% summarise(MeanAgg = mean(meanAggSize) )
 

### 2020-03-03 Microscopy Data.Rmd
Scratch previous commit. These are some changes in the comments and other small things.

@@
 
-```{r thresholds}
+#Analysis of thresholds
+```{r thresholds functions}
 MapThreshold<- function(listSamples, reps){
@@
 }
+```
+
+```{r thresholds data and figures}
 wtThresholds<-MapThreshold(PA14wt, names3)
@@
 ```
-
-```{r biomass functions}
+#Biomass with threshold by time points
+```{r biomass functions to read data}
 MapResults<- function(listSamples, reps){
@@
 GetResults<-function(sample, samplename){
-  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/',sample,'/results')
+  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Other Data/',sample,'/results')
   fileList<-list.files(path = folder, full.names = TRUE)
@@
 ```
-#Biomass per slice.
 
-Where is the majority of the biomass at any given time? and How dos it grow over time.
-It additionally helps identify how reproducible are the experiments
 ```{r biomass data}
@@
 ResultsData<-rbind(wtResults,mutResults,Pa01Results,Pa01mutResults)
-#Now make it tidy and do some stats:
+#combine data for all slices, make it tidy and do  stats:
 cleanResults<-ResultsData %>% group_by(TimePoint,Sample,Strain,Condition,Species) %>% summarise(Totals = sum (Value))%>% mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))#this adds up all the data on each slice and then gets the log of that total
@@
 
-Data from S. aureus. 
-Remember that all mono cultures of Sa are essentially the same: Same strain, same inoculum, same condition. So this is the only condition where you have several replicates.
-```{r biomass Sa}
+```{r biomass plotting functions}
 GraphGrowthCurves<-function (dataRaw, dataStats, bug){
@@
 GraphGrowthCurvesExpClean(cleanResults,cleanResultsStats, "Pa")
+```
+Data from S. aureus. 
+Remember that all mono cultures of Sa are essentially the same: Same strain, same inoculum, same condition. So this is the only condition where you have several replicates.
+```{r Biomass Sa}
 #First Isolate Sa Mono
@@
 ```
-## Now we are showing the
 
@@
 ```
+##Biomass per slice.
 
+Where is the majority of the biomass at any given time? and how does it grow over time.
+It additionally helps identify how reproducible are the experiments
 ```{r Biomass per slice }
@@
   colnames(histogram)<-c("Counts", "Midpoint")
-  histogram<-histogram[!(histogram$Counts==0),]
+  histogram<-histogram[!(histogram$Counts==0),]#remove zeros
   histogram%>%mutate(BiomassBin=Counts*Midpoint)->histogram

### 2020-03-04 R Analysis Scripts/ImageSliceData.Rmd
This script pulls out data from each raw slice including numbers of zeros, intensity, etc

---
title: "Image Data per Slice"
author: "Juan P Barraza"
date: "2/25/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
GetSliceHistogramData<-function(sample){
  file<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/singleImageData/RawImgData_',sample,'.csv')
  datos <-read.csv(file, header = FALSE)
  colnames(datos)<-c('ZeroFreq','ZeroProp','MaxFreq','firstZero','totalZeroes','Otsu','TopPercentile','TailBins', 'TailFreq','OptimalG','MeanIntensity','SDIntensity','Channel','Slice','TimePoint','Position','Tile')
  datos<-datos %>% mutate(MaxProp = MaxFreq/262144,TailProp = TailFreq/262144, Sample = sample)
  return(datos)
}
DataRep3<-GetSliceHistogramData('4-17-19')
DataRep2<-GetSliceHistogramData('3-19-19')
DataRep1<-GetSliceHistogramData('3-13-19')
allData<-bind_rows(DataRep3,DataRep2,DataRep1)

PlotDataPerSlice<-function(y.var, canal){
  y.var <- enquo(y.var)
  canal <- enquo(canal)
ggplot()+
  geom_point(data=allData %>% filter(channel==!!canal), aes(x=slice, y=!!y.var, shape = factor(tile), color = factor(Sample)), size=2)+
  facet_wrap(~timePoint, nrow = 3)+
  theme_minimal_grid(12)
}
PlotDataPerSliceLog<-function(y.var, canal){
  y.var <- enquo(y.var)
  canal <- enquo(canal)
ggplot()+
  geom_point(data=allData %>% filter(channel==!!canal), aes(x=slice, y=!!y.var, shape = factor(tile), color = factor(Sample)), size=2)+
  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_wrap(~timePoint, nrow = 3)+
  theme_minimal_grid(12)
}

PlotDataPerTimePoint<-function(y.var, canal){
  y.var <- enquo(y.var)
  canal <- enquo(canal)
ggplot()+
  geom_point(data=allData %>% filter(channel==!!canal), aes(x=timePoint, y=!!y.var, shape = factor(tile), color = factor(Sample)), size=2)+
  facet_wrap(~slice, nrow = 9)+
  theme_minimal_grid(12)
}
PlotDataPerTimePointLog<-function(y.var, canal){
  y.var <- enquo(y.var)
  canal <- enquo(canal)
ggplot()+
  geom_point(data=allData %>% filter(channel==!!canal), aes(x=timePoint, y=!!y.var, shape = factor(tile), color = factor(Sample)), size=2)+
  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_wrap(~slice, nrow = 9)+
  theme_minimal_grid(12)
}
```

```{r zeroInt}
PlotDataPerSlice(zeroInt, 1)
PlotDataPerTimePoint(zeroInt, 1)
#this shows that there are a lot of zeros in all of the timepoints and they cahnge more dramatically with slice than with timepoints
#the real data is only up to slice 34, afterwards its all zeros for Staph, and there is a somewhat decent variation with the tiles
```
```{r zeroPercent}
PlotDataPerSlice(zeroPercent, 1)
PlotDataPerTimePoint(zeroPercent, 1)
```
```{r maxint}
PlotDataPerSliceLog(maxInt, 1)
PlotDataPerTimePoint(maxint, 1)

#oddly enough, it seems like Staph has indeed a good amount of high intensity voxels compared to pseudomonas, all in the early slices
#you can see more clearly here that up until slice 12 you get some super high intensity voxels
#pseudomonas does have some max intensity voxels but not as many as Staph, and also up until slice 10 ish

```

```{r firstZero}
#This is a measure of what is the maximum intensity on the images
PlotDataPerSliceLog(maxInt, 1)
PlotDataPerTimePoint(maxint, 1)

#both Pseudomonas and Staph decay at relatively the same amount over the z-slice

```

```{r TailBins}
#This is how many no-zero values have higher intensity than the first zero frequency intensity
PlotDataPerSlice(orphanZeros, 1)
PlotDataPerTimePoint(orphanZeros, 1)

#both Pseudomonas and Staph decay at relatively the same amount over the z-slice
```

```{r totalZeroes}
#This is how many bins are empty from the histograms.
ggplot()+
  geom_point(data=testGetSliceHistogramData, aes(x=slice, y=totalZeroes, shape = factor(tile), color = factor(channel)), size=2)+
  facet_wrap(~timePoint, nrow = 3)+
  theme_minimal_grid(12)
#Again, it seems like both Pseudomonas and Staph have relatively the same amount over the z-slice, with staph approaching it a bit faster
ggplot()+
  geom_point(data=testGetSliceHistogramData, aes(x=timePoint, y=totalZeroes, shape = factor(tile), color = factor(channel)), size=2)+
  facet_wrap(~slice, nrow = 9)+
  theme_minimal_grid(12)

ggplot()+
  geom_point(data=testGetSliceHistogramData %>% filter(channel == 1), aes(x=slice, y=totalZeroes, shape = factor(tile), color = factor(channel)), size=2)+
  facet_wrap(~timePoint, nrow = 3)+
  theme_minimal_grid(12)

ggplot()+
  geom_point(data=testGetSliceHistogramData %>% filter(channel == 2), aes(x=slice, y=totalZeroes, shape = factor(tile), color = factor(channel)), size=2)+
  facet_wrap(~timePoint, nrow = 3)+
  theme_minimal_grid(12)
```
```{r level}
#This is how many bins are empty from the histograms.
ggplot()+
  geom_point(data=testGetSliceHistogramData, aes(x=slice, y=level, shape = factor(tile), color = factor(channel)), size=2)+
  facet_wrap(~timePoint, nrow = 3)+
  theme_minimal_grid(12)
#Very uniform for pseudomonas but quite variable for staph, specially since there are a lot of inter-tile variation
ggplot()+
  geom_point(data=testGetSliceHistogramData, aes(x=timePoint, y=level, shape = factor(tile), color = factor(channel)), size=2)+
  facet_wrap(~slice, nrow = 9)+
  theme_minimal_grid(12)

ggplot()+
  geom_point(data=testGetSliceHistogramData %>% filter(channel == 1), aes(x=slice, y=level, shape = factor(tile), color = factor(channel)), size=2)+
  facet_wrap(~timePoint, nrow = 3)+
  theme_minimal_grid(12)

ggplot()+
  geom_point(data=testGetSliceHistogramData %>% filter(channel == 2), aes(x=slice, y=level, shape = factor(tile), color = factor(channel)), size=2)+
  facet_wrap(~timePoint, nrow = 3)+
  theme_minimal_grid(12)
```

```{r calculatedGlow}
PlotDataPerSliceLog(calculatedGhigh, 1)
PlotDataPerTimePointLog(calculatedGhigh, 1)
#stretchlim(I) computes the lower and upper limits that can be used for contrast stretching grayscale or RGB image I. The limits are returned in lowhigh. By default, the limits specify the bottom 1% and the top 1% of all pixel values.
#this is the top 1% of all pixels 
#Now THIS is interesting... there is essentially a bimodal relationship at the later slices.
#Nope... What causes this is the fact that more than 99 percent of the pixels are at an intensity of zero

```

```{r meanIntensity}
#This is how many bins are empty from the histograms.
ggplot()+
  geom_point(data=testGetSliceHistogramData, aes(x=slice, y=meanIntensity, shape = factor(tile), color = factor(channel)), size=2)+
  facet_wrap(~timePoint, nrow = 3)+
  theme_minimal_grid(12)

ggplot()+
  geom_point(data=testGetSliceHistogramData, aes(x=timePoint, y=meanIntensity, shape = factor(tile), color = factor(channel)), size=2)+
  facet_wrap(~slice, nrow = 9)+
  theme_minimal_grid(12)

ggplot()+
  geom_point(data=testGetSliceHistogramData %>% filter(channel == 1), aes(x=slice, y=meanIntensity, shape = factor(tile), color = factor(channel)), size=2)+
  facet_wrap(~timePoint, nrow = 3)+
  theme_minimal_grid(12)
#mean intensity only reaches a maximum of 2 at the highest points. and it decays with slice number
ggplot()+
  geom_point(data=testGetSliceHistogramData %>% filter(channel == 1), aes(x=timePoint, y=meanIntensity, shape = factor(tile), color = factor(channel)), size=2)+
  facet_wrap(~slice, nrow = 9)+
  theme_minimal_grid(12)

ggplot()+
  geom_point(data=testGetSliceHistogramData %>% filter(channel == 2), aes(x=slice, y=meanIntensity, shape = factor(tile), color = factor(channel)), size=2)+
  facet_wrap(~timePoint, nrow = 3)+
  theme_minimal_grid(12)
#mean intensity reaches a maximum of around 20 at the highest points. and it decays with slice number
```
#Histograms
```{r read histogram data}
GetSliceHistograms<-function(sample){
  file<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/singleImageData/Histograms_',sample,'.csv')
  datos <-read.csv(file, header = FALSE)
  colnames(datos)<-c('Frequency','Intensity', 'Channel', 'Slice', 'TimePoint', 'Position', 'Tile')
  datos<-datos %>% mutate(Sample = sample)
  return(datos)
}
HistogramsRep3<-GetSliceHistograms('4-17-19')
HistogramsRep2<-GetSliceHistograms('3-19-19')
HistogramsRep1<-GetSliceHistograms('3-13-19')
allHistograms<-bind_rows(HistogramsRep3,HistogramsRep2,HistogramsRep1)
```

```{r death curves}
#this code is copied from the original code from the Denmark Project
getSliceDeathCurve<-function(df){
  df<-df[!(df$Frequency==0),]#remove zeros
  totalAbundance = sum(df$Frequency)
  currentAbundance = 0
  for (i in 1 : nrow(df)){
    addedAbundance<-totalAbundance-currentAbundance
    df[i,9]<-addedAbundance
    currentAbundance = currentAbundance+df[i,1]
  }
  colnames(df)<-c('Frequency','Intensity', 'Channel', 'Slice', 'TimePoint', 'Position', 'Tile', 'Sample','Decay')
  df<-df%>% mutate (normDecay = 100*(Decay - min(Decay)) / (max(Decay) - min(Decay)))
  return(df)
  }
processImageData<-function(df){
  allData<-df %>% group_by(Channel, Slice, TimePoint, Position, Tile,Sample)
  splitData<- group_split(allData)
  mappedData<-map(splitData, getSliceDeathCurve)
  boundData<-bind_rows(mappedData)
  colnames(boundData)<-c('Frequency','Intensity', 'Channel', 'Slice', 'TimePoint', 'Position', 'Tile', 'Sample','Decay', 'normDecay')
  return(boundData)
}
deathCurveData<-processImageData(allHistograms)
write.csv(deathCurveData, file ='/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/singleImageData/deathCurves.csv')
deathCurveData <-read.csv('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/singleImageData/deathCurves.csv', header = FALSE)
```

### 2020-03-05 R Analysis Scripts/CFU Data.Rmd
moved here

--- 2019-09-26 CFU Data.Rmd
@@
 GetGrowthCurveReplicate<- function (sample){
-  bugCounts<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/GrowthCurves/", sample, ".csv"),header = TRUE)
+  bugCounts<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/GrowthCurves/", sample, ".csv"),header = TRUE)
   bugCounts<- na.omit(bugCounts)
@@
 GraphGrowthCurveLog<-function (rawData, statsData){
-    ggplot()+
-    geom_point(data=rawData, aes(x=time, y=logCFU,color = bug, shape = strain),   size=2)+
-    #geom_point(data=statsData, aes(x=time, y=logCFUmean,  color = bug, shape = strain), size=2)+
-    geom_line(data=statsData, aes(x=time, y=logCFUmean,  color = bug, linetype = strain), size=2)+
-    #geom_errorbar(data=statsData, aes(x = time, ymin = logCFUmean-logCFUsd, ymax = logCFUmean+logCFUsd, color = bug, linetype = strain), width = 0, size = 1)+
-    geom_errorbar(data=statsData, aes(x = time, ymin = logCFUmean-logCFUse, ymax = logCFUmean+logCFUse, color = bug, linetype = strain), width = 0, size = 1)+
-    labs(title =paste("Growth in SCFM2" ),  x = "Time (hours)",shape = "Strain",linetype = "Strain", color = "Bug")+
-    facet_grid(.~condition)
+    staticPlot<-ggplot()+
+      geom_line(data=statsData%>% filter(bug == "Sa"& condition == "Static"), aes(x=time, y=logCFUmean, linetype = strain), size=1)+
+      geom_errorbar(data=statsData%>% filter(bug == "Sa"& condition == "Static"), aes(x = time, ymin = logCFUmean-logCFUse, ymax = logCFUmean+logCFUse), width = 0, size = 1)+
+      scale_linetype_manual(values = c( "dotted","solid"), labels = c("- HQNO", "wild type"))+
+      labs(x = "Time (hours)", y = "log CFU", linetype = "Pa strain")+
+      scale_y_continuous(limits = c(4,9))+
+      theme_cowplot(12)
+
+    wellmixedPlot<-ggplot()+
+      geom_line(data=statsData%>% filter(bug == "Sa" & condition == "Shaking"), aes(x=time, y=logCFUmean, linetype = strain), size=1)+
+      geom_errorbar(data=statsData%>% filter(bug == "Sa"& condition == "Shaking"), aes(x = time, ymin = logCFUmean-logCFUse, ymax = logCFUmean+logCFUse), width = 0, size = 1)+
+      scale_linetype_manual(values = c( "dotted", "solid"), labels = c("- HQNO","wild type"))+
+      labs(x = "Time (hours)", y = "log CFU", linetype = "Pa strain")+
+      scale_y_continuous(limits=c(4,9))+
+      theme_cowplot(12)
+    legend <- get_legend(staticPlot + theme(legend.box.margin = margin(0, 0, 0, 12)))
+    prow <- plot_grid(wellmixedPlot+theme(legend.position="none"),staticPlot+theme(legend.position="none"),align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)
+    plot_grid(prow,legend,rel_widths = c(3, .4))
+}
+GraphGrowthCurveLog1<-function (rawData, statsData){
+    wtPlot<-ggplot()+
+      geom_line(data=statsData%>% filter(bug == "Sa"& strain == "wt"), aes(x=time, y=logCFUmean, linetype = condition), size=1)+
+      geom_errorbar(data=statsData%>% filter(bug == "Sa"& strain == "wt"), aes(x = time, ymin = logCFUmean-logCFUse, ymax = logCFUmean+logCFUse), width = 0, size = 0.5)+
+      scale_linetype_manual(values = c( "solid","dotted"), labels = c("well-mixed","static"))+
+      labs(x = "Time (hours)", y = "log CFU", linetype = "Condition")+
+      scale_y_continuous(limits = c(4,9.2))+
+      scale_x_continuous(breaks = c(4,8,12,16))+
+      theme_cowplot(12)
+
+    hqnoPlot<-ggplot()+
+      geom_line(data=statsData%>% filter(bug == "Sa" & strain == "mut"), aes(x=time, y=logCFUmean, linetype = condition), size=1)+
+      geom_errorbar(data=statsData%>% filter(bug == "Sa"& strain == "mut"), aes(x = time, ymin = logCFUmean-logCFUse, ymax = logCFUmean+logCFUse), width = 0, size = 0.5)+
+      scale_linetype_manual(values = c( "solid","dotted"), labels = c("well-mixed","static"))+
+      labs(x = "Time (hours)", y = "log CFU", linetype = "Condition")+
+      scale_y_continuous(limits=c(4,9.2))+
+      scale_x_continuous(breaks = c(4,8,12,16))+
+      theme_cowplot(12)
+    legend <- get_legend(wtPlot + theme(legend.box.margin = margin(0, 0, 0, 12)))
+    prow <- plot_grid(wtPlot+theme(legend.position="none"),hqnoPlot+theme(legend.position="none"),align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)
+    plot_grid(prow,legend,rel_widths = c(3, .4))
     }
@@
     geom_point(data=rawData, aes(x=time, y=CFU,color = bug, shape = strain),   size=2)+
-    geom_line(data=statsData, aes(x=time, y=CFUmean,  color = bug, linetype = strain), size=2)+
+    geom_line(data=statsData, aes(x=time, y=CFUmean,  color = bug, linetype = strain), size=1)+
     geom_errorbar(data=statsData, aes(x = time, ymin = CFUmean-CFUsd, ymax = CFUmean+CFUsd, color = bug, linetype = strain), width = 0, size = 1)+
@@
 PA14Data<-GetGrowthCurveCondition(PA14)
+PA14Data$strain <- factor(PA14Data$strain, levels = c("wt", "mut"))
+
 #do stats
@@
 GraphGrowthCurveLog(PA14Data,PA14DataStats)
+GraphGrowthCurveLog1(PA14Data,PA14DataStats)
 #Graph regular numbers
 GraphGrowthCurve(PA14Data,PA14DataStats)
-
 ```
@@
 GetResults<-function(sample, samplename){
-  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data1/',sample,'/results')#the path needs to be "Other Data1"
+  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Other Data1/',sample,'/results')#the path needs to be "Other Data1"
   fileList<-list.files(path = folder, full.names = TRUE)
@@
 
-##remove conditions I didn't do in the scope and fix strain names:
+##remove stirred condition I didn't do in the scope and fix strain names:
 DataComparisonCFU<-PA14DataStats %>% filter (condition == "Static") %>% select(bug, strain, CFUmean, logCFUmean, condition, time)%>% as.data.frame() 
@@
 #Now we go to Sa
-SaLinearModel <- lm(MeanLogTotals ~logCFUs, data = comparisonDf %>% filter (Species == "Sa"))
+
+SaLinearModel <- lm(MeanLogTotals ~logCFUs, data = comparisonDf %>% filter (Species == "Sa")%>% filter(!time == 0))
 coefficients(SaLinearModel)
 get_regression_summaries(SaLinearModel, print = TRUE)
-
-SaLinearModel1 <- lm(MeanLogTotals ~logCFUs, data = comparisonDf %>% filter (Species == "Sa")%>% filter(!time == 0))
-coefficients(SaLinearModel1)
-get_regression_summaries(SaLinearModel1, print = TRUE)
 
@@
   scale_color_gradient(low="blue", high="red")+
-  annotate("text", x = 7.9, y = 4.75, label = expression(paste("y=-2.44x+25.73  ", R^2, "= 0.619")), color = "red", size = 8)+
-  labs(title =expression(paste(italic("S. aureus"), " CFU vs Confocal Biomass")), x = "Log CFUs",y = "Biomass from Scope")
+  annotate("text", x = 7.9, y = 4.5, label = expression(paste("y=-2.44x+25.73  ", R^2, "= 0.619")), color = "red", size = 8)+
+  labs(title =expression(paste(italic("S. aureus"), " CFU vs Confocal Biomass")), x = "Log CFUs",y = "Biomass from CLSM")+
+  theme_cowplot(12)
 

### 2020-03-05 Microscopy Data.Rmd
Changed folders for right project and added Staph thresholding studies

@@
 GetThresholds<-function(sample, samplename){
-  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/',sample,'/threshold')
+  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Other Data/',sample,'/threshold')
   fileList<-list.files(path = folder, full.names = TRUE)
@@
   facet_grid(.~Condition)
+#For now, lets focus on the PA14 strains:
+ggplot()+
+  geom_point(data=thresholdData %>% filter(Species=="Sa") %>%filter(Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=Value, shape = Sample, color = Strain), size=2)+
+  geom_line(data=SathresholdData%>%filter(Strain %in% c("PA14wt", "PA14mut")),aes(x = TimePoint, y = MeanThreshold, color =Strain), size = 1)+
+  geom_errorbar(data=SathresholdData%>%filter(Strain %in% c("PA14wt", "PA14mut")),aes(x = TimePoint, ymin = MeanThreshold-SDThreshold, ymax = MeanThreshold+SDThreshold, color = Strain), width=2, size = .1)+
+  geom_hline(data = Saaverage%>%filter(Strain %in% c("PA14wt", "PA14mut")), aes(yintercept = MeanThreshold, color = Strain), size = 3)+
+  facet_grid(.~Condition)+
+    theme_cowplot(12)
 ```
@@
     facet_grid(Strain~Condition)
+```
+
+```{r regression models for thresholds}
 #Linear regressions
-#First get a df with only Sa Mono Red Channel
+
+#First get a df with only condition wanted in Red Channel
 SaMonoTrhesholdDf<-thresholdData%>% filter(Condition == "Sa Mono") %>% filter(Species == "Sa")
+PaSa1.1TrhesholdDf<-thresholdData%>% filter(Condition == "Pa:Sa 1:1") %>% filter(Species == "Sa") %>% filter(Strain %in% c("PA14wt","PA14mut"))
+
 #Linear regression for Thresholds
+#Mono
 lm(SaMonoTrhesholdDf$Value ~ SaMonoTrhesholdDf$TimePoint) 
@@
   geom_point(data=SaMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)
+
+#Co 1:1
+lm(PaSa1.1TrhesholdDf$Value ~ PaSa1.1TrhesholdDf$TimePoint) 
+plot(PaSa1.1TrhesholdDf$TimePoint, PaSa1.1TrhesholdDf$Value)
+abline( 0.1909, -0.00386 )
 
@@
 ResultsData<-rbind(wtResults,mutResults,Pa01Results,Pa01mutResults)
-#combine data for all slices, make it tidy and do  stats:
-cleanResults<-ResultsData %>% group_by(TimePoint,Sample,Strain,Condition,Species) %>% summarise(Totals = sum (Value))%>% mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))#this adds up all the data on each slice and then gets the log of that total
+#Make it tidy and dostats (Add up all the data on each slice and then gets the log of that total)
+cleanResults<-ResultsData %>% group_by(TimePoint,Sample,Strain,Condition,Species) %>% summarise(Totals = sum (Value))%>% mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))
 cleanResultsStats<-cleanResults %>% group_by(TimePoint,Strain,Condition,Species) %>% summarise(MeanTotals = mean(Totals), SDTotals = sd(Totals), MeanLogTotals = mean(LogTotals), SDLogTotals = sd(LogTotals)) %>% mutate(MeanLogTotalsRevd = 10^MeanLogTotals, SDLogTotalsRevd =10^(SDLogTotals)) #stats between reps
@@
     labs(title =paste(bug, "growth in mono in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
-    facet_grid(Strain~Condition)
+    facet_grid(Strain~Condition)+
+    theme_cowplot(12)
 }
@@
     labs(title =paste(bug, "growth in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
-    facet_grid(Strain~Condition)
+    facet_grid(Strain~Condition)+
+    theme_cowplot(12)
 }
@@
 GetResults<-function(sample, samplename){
-  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data1/',sample,'/results')#the path needs to be "Other Data1"
+  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Other Data1/',sample,'/results')
+  #the path just needs to be changed to"Other Data1"
   fileList<-list.files(path = folder, full.names = TRUE)
@@
 GraphGrowthCurvesExpCleanCoCulture(cleanResultsStats1)
+```
+
+```{r threshold Sa by time}
+#This function keeps getting changed but using the same name... so heads up on that
+GetResults<-function(sample, samplename){
+  #folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Threshold by time/',sample,'/resultsByTime')
+  folder<- paste0('/Volumes/Seagate Backup Plus Drive/Good images/',sample,'/resultsByTime6')
+  fileList<-list.files(path = folder, full.names = TRUE)
+  growthDf<-data.frame()
+  #for (position in 2:3){
+  #  currentPosition<-fileList[grep(paste0("p",position,"."),fileList)]
+  currentPosition<-fileList[grep(paste0("p2."),fileList)]
+    for (timepoint in 0:17){
+      currentTimePoint<-currentPosition[grep(paste0("t",GetNumber(timepoint),"_"),currentPosition)]
+      growthDf<-rbind(growthDf,ReadResultsFile(currentTimePoint, 2, timepoint))
+      #growthDf<-rbind(growthDf,ReadResultsFile(currentTimePoint, position, timepoint))
+      }
+    #}
+  growthDf<-growthDf %>% mutate(Sample = samplename)
+return(growthDf)
+}
+
+ProcessResults <-function(){
+  wt<-MapResults(PA14wt, names3)
+  mut<-MapResults(PA14mut, names3)
+  #combine them:
+  results<-rbind(wt,mut)
+  #Add up all the data on each slice and then gets the log of that total
+  resultsSum<-results %>% group_by(TimePoint,Sample,Strain,Condition,Species)%>% 
+    summarise(Totals = sum (Value))%>%
+    mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))
+  #get stats between replicates
+  resultsStats<-resultsSum %>% group_by(TimePoint,Strain,Condition,Species) %>% 
+    summarise(MeanTotals = mean(Totals), SDTotals = sd(Totals), MeanLogTotals = mean(LogTotals), SDLogTotals = sd(LogTotals)) %>% 
+    mutate(MeanLogTotalsRevd = 10^MeanLogTotals, SDLogTotalsRevd =10^(SDLogTotals))
+  results <- list(resultsSum,resultsStats)
+  return(results)
+} 
+#this is super bad, but the way I am generating the seccessive "linearx" below is by manually changing the folder in the function "GetResults" above, running it and then storing the results using "ProcessResults" below...
+I know, it sucks, but it works
+linear6<-ProcessResults()
+linearThresholdGrowthCurves<-combine(cleanResults,cleanResults1,cleanResultsByTime,linear1[[1]],linear2[[1]],linear4[[1]],linear5[[1]],linear6[[1]])
+linearThresholdGrowthCurvesStats<-combine(linear1[[2]],linear2[[2]],linear4[[2]],linear5[[2]],linear6[[2]])
+
+#these are the first few sets of data:
+ggplot()+
+  geom_line(data=cleanResults%>% filter(Species == "Sa") %>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=LogTotals),color = "Black", size=2)+
+  geom_line(data=cleanResults1%>% filter(Species == "Sa") %>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=LogTotals),color = "Red", size=2)+
+  geom_line(data=cleanResultsByTime%>% filter(Species == "Sa") %>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=LogTotals),color = "Blue", size=2)+
+  geom_line(data=linear1[[1]]%>% filter(Species == "Sa") %>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=LogTotals),color = "Green", size=2)+
+  facet_grid(Strain~Sample)+
+  theme_cowplot(12)
+
+ggplot()+
+  geom_line(data=linearThresholdGrowthCurves%>% filter(Species == "Sa") %>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=LogTotals,color = source), size=2)+
+  facet_grid(Strain~Sample)+
+  theme_cowplot(12)
+
+ggplot()+
+  geom_line(data=linearThresholdGrowthCurvesStats%>% filter(Species == "Sa") %>% 
+              filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=MeanLogTotals,color = source), size=2)+
+  facet_grid(Condition~Strain)+
+  theme_cowplot(12)
 
 ```
+
 #Functions for histograms

### 2020-03-05 SaPa TOB growth curves clean.Rmd
Removed old data and added final figures

---
title: "Sa TOB Report"
author: "Juan P Barraza"
date: "2/14/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r setup, include=FALSE}
library(rdist)
library(pixmap)
library(rtiff)
library(reshape2)
library(gplots)
library(dplyr)
library(gdata)
library(ggplot2)
library(cowplot)
library(magrittr)
library(scales)
library(purrr)
library(plotrix)#for std.error
library(ggpubr)#for p-values
```
# Good data
Shown below is the data using the new SCFM2 with extra lipids

```{r reading data functions , echo=FALSE, warning=FALSE,fig.width=9, fig.height=7}
#these are the list with the spreadsheets of experiments under different conditions
GetTobReplicate<- function (sample){
  bugCounts<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/TOB/", sample, ".csv"),header = TRUE)
  bugCounts<- na.omit(bugCounts)
  bugCounts<-bugCounts %>% mutate(logTranformed = log10(CFU))
  bugCounts$sample<-sample
  return(bugCounts)
}
GetTOBcondition<-function(datalist, conditionName){
  mappedData<-map(datalist, GetTobReplicate)#this line reads all the files on the list
  boundData<-bind_rows(mappedData)
  boundData$condition<-conditionName
  return(boundData)
}
mutLib128 = c('2-21-19','2-19-19','2-14-19')
cleanDelScfm128 = c('5-10-19','5-11-19')
cleanDelScfm64 = c('5-15-19','5-16-19')
cleanDelEndpoint<-c("1-25-20A","1-25-20B","1-28-20","1-29-20")
```

```{r reading data, echo=FALSE, warning=FALSE,fig.width=9, fig.height=7}
mutLib128Data<-GetTOBcondition(mutLib128, "mutLib128")
cleanDelScfm64Data<-GetTOBcondition(cleanDelScfm64, "cleanDelScfm64")
cleanDelScfm128Data<-GetTOBcondition(cleanDelScfm128, "cleanDelScfm128")
cleanDelEndpointData<-GetTOBcondition(cleanDelEndpoint,"cleanDelEndpoint")

newSCFMData<-rbind(mutLib128Data,cleanDelScfm128Data,cleanDelScfm64Data,cleanDelEndpointData)#combine all conditions
newSCFMData<-newSCFMData %>% mutate(strain = ifelse(condition == "mutLib128", "Tn", "Clean"))

#I have to remove one replicate from 5-16-19 TOB 3 HRS because I lost the mono data :(
removable <- newSCFMData %>% filter(antibiotic == "TOB" & bug == "Sa" & sample == "5-16-19" & timePoint == 3 )
newSCFMDataComparison <- anti_join(newSCFMData, removable)

newSCFMDataSaComparison<-newSCFMDataComparison%>%filter(bug == "Sa") %>%  group_by(antibiotic, bug, timePoint, sample, condition) %>% mutate(ratioCFU = CFU / CFU[culture =="mono"])%>% mutate(ratiolog = logTranformed / logTranformed[culture =="mono"])%>%  ungroup()

#this is to average the two technical replicates
techReps<-newSCFMDataSaComparison %>% filter(sample %in% c("1-25-20A", "1-25-20B")) %>% group_by(culture,bug,timePoint, antibiotic, condition, strain) %>% summarise(CFU = mean(CFU)) %>% mutate(sample = "1-25-20")
```

```{r calculating mean and ratios}
cleanDelEndpointData <-cleanDelEndpointData %>% group_by(timePoint,antibiotic,sample) %>% mutate(ratioMono = CFU/CFU[culture=="mono"],ratioMonoLog = logTranformed/logTranformed[culture=="mono"]) %>% ungroup()

cleanDelEndpointData <-cleanDelEndpointData %>%  group_by(timePoint,antibiotic,culture) %>% mutate( meanLog = mean(logTranformed),SDLog = sd(logTranformed), meanCFU = mean(CFU), SDCFU = sd(CFU), meanRatioLog = mean(ratioMonoLog), sdRatioMonoLog = sd(ratioMonoLog),meanRatio = mean(ratioMono), sdRatioMono = sd(ratioMono))%>% ungroup()
```

```{r graph end point numbers}
#This shows growth curves of all replicates
ggplot()+
  geom_jitter(data=cleanDelEndpointData , aes(x=timePoint, y=CFU, color = culture), height = 0, width = .2, size=4)+
  scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  #geom_vline(xintercept=3, linetype = "dashed")+
  #annotate("text", x = 3, y = 10e6, label = "TOB added")+
  labs(title =expression(paste(italic("S. aureus"), " growth in mono or coculture in SCFM2 with 256 ug/mL TOB")), x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") +
  facet_grid(sample~antibiotic)+
  theme_cowplot()+
  panel_border()+
  background_grid()

#CFU numbers with means
ggplot()+
  geom_jitter(data=cleanDelEndpointData , aes(x=timePoint, y=CFU, shape = culture, color = antibiotic), height = 0, width = .2, size=2)+
  geom_point(data=cleanDelEndpointData , aes(x=timePoint, y=meanCFU, shape = culture, color = antibiotic), size=4)+
  scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  #geom_vline(xintercept=3, linetype = "dashed")+
  #annotate("text", x = 3, y = 10e6, label = "TOB added")+
  labs(title =expression(paste(italic("S. aureus"), " growth in mono or coculture in SCFM2 with 256 ug/mL TOB")), x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") +
  theme_cowplot()+
  panel_border()+
  background_grid()

#Log numbers with log means
ggplot()+
  geom_jitter(data=cleanDelEndpointData , aes(x=timePoint, y=logTranformed, shape = culture, color = antibiotic), height = 0, width = .2, size=2)+
  geom_point(data=cleanDelEndpointData , aes(x=timePoint, y=meanLog, shape = culture, color = antibiotic), size=4)+
  #scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  #geom_vline(xintercept=3, linetype = "dashed")+
  #annotate("text", x = 3, y = 10e6, label = "TOB added")+
  labs(title =expression(paste(italic("S. aureus"), " growth in mono or coculture in SCFM2 with 256 ug/mL TOB")), x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") +
  theme_cowplot()+
  panel_border()+
  background_grid()

#ONLY ENDPOINTS CFU
ggplot()+
  geom_jitter(data=cleanDelEndpointData %>% filter(timePoint==5) , aes(x=culture, y=CFU,  color = antibiotic), height = 0, width = .2, size=2)+
  geom_errorbar(data=cleanDelEndpointData %>% filter(timePoint==5) , aes(x=culture, ymin=meanCFU-SDCFU,ymax = meanCFU+SDCFU,  color = antibiotic), height = 0, width = .2, size=2)+
  geom_point(data=cleanDelEndpointData %>% filter(timePoint==5), aes(x=culture, y=meanCFU, color = antibiotic), height = 0, width = .2, size=4)+
  scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  #geom_vline(xintercept=3, linetype = "dashed")+
  #annotate("text", x = 3, y = 10e6, label = "TOB added")+
  labs(title =expression(paste(italic("S. aureus"), " growth in mono or coculture in SCFM2 with 256 ug/mL TOB")), x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") +
  theme_cowplot()+
  panel_border()+
  background_grid()
#ONLY ENDPOINTS log
ggplot()+
  geom_jitter(data=cleanDelEndpointData %>% filter(timePoint==5) , aes(x=culture, y=logTranformed,  color = antibiotic), height = 0, width = .2, size=2)+
  geom_errorbar(data=cleanDelEndpointData %>% filter(timePoint==5) , aes(x=culture, ymin=meanLog-SDLog,ymax = meanLog+SDLog,  color = antibiotic), height = 0, width = .2, size=2)+
  geom_point(data=cleanDelEndpointData %>% filter(timePoint==5), aes(x=culture, y=meanLog, color = antibiotic),  size=4)+
  #scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  #geom_vline(xintercept=3, linetype = "dashed")+
  #annotate("text", x = 3, y = 10e6, label = "TOB added")+
  labs(title =expression(paste(italic("S. aureus"), " growth in mono or coculture in SCFM2 with 256 ug/mL TOB")), x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") +
  theme_cowplot()+
  panel_border()+
  background_grid()
#only endpoints ratio log
ggplot()+
  geom_jitter(data=cleanDelEndpointData %>% filter(timePoint==5) , aes(x=culture, y=ratioMonoLog,  color = antibiotic), height = 0, width = .2, size=2)+
  geom_errorbar(data=cleanDelEndpointData %>% filter(timePoint==5) , aes(x=culture, ymin=meanRatioLog-sdRatioMonoLog,ymax = meanRatioLog+sdRatioMonoLog,  color = antibiotic), height = 0, width = .2, size=2)+
  geom_point(data=cleanDelEndpointData %>% filter(timePoint==5), aes(x=culture, y=meanRatioLog, color = antibiotic), size=4)+
  #scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  #geom_vline(xintercept=3, linetype = "dashed")+
  #annotate("text", x = 3, y = 10e6, label = "TOB added")+
  labs(title =expression(paste(italic("S. aureus"), " growth in mono or coculture in SCFM2 with 256 ug/mL TOB")), x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") +
  theme_cowplot()+
  panel_border()+
  background_grid()
```

```{r graph end point ratios}
#ratio facets
ggplot()+
  geom_jitter(data=cleanDelEndpointData , aes(x=timePoint, y=ratioMono, color = culture), height = 0, width = .2, size=4)+
  scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  #geom_vline(xintercept=3, linetype = "dashed")+
  #annotate("text", x = 3, y = 10e6, label = "TOB added")+
  labs(title =expression(paste(italic("S. aureus"), " growth ratio compared to Mono culture")), x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") +
  facet_grid(sample~antibiotic)+
  theme_cowplot()+
  panel_border()+
  background_grid()

#ratio mono by shapes
ggplot()+
  geom_jitter(data=cleanDelEndpointData , aes(x=timePoint, y=ratioMono, shape = culture, color = antibiotic), height = 0, width = .2, size=4)+
  #geom_point(data=cleanDelEndpoint , aes(x=timePoint, y=meanLog, shape = culture, color = antibiotic), height = 0, width = .2, size=4)+
  scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  #geom_vline(xintercept=3, linetype = "dashed")+
  #annotate("text", x = 3, y = 10e6, label = "TOB added")+
  labs(title =expression(paste(italic("S. aureus"), " growth in mono or coculture in SCFM2 with 256 ug/mL TOB")), x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") +
  theme_cowplot()+
  panel_border()+
  background_grid()
#ratio mono log by shapes
ggplot()+
  geom_jitter(data=cleanDelEndpointData , aes(x=timePoint, y=ratioMonoLog, shape = culture, color = antibiotic), height = 0, width = .2, size=4)+
  #geom_point(data=cleanDelEndpoint , aes(x=timePoint, y=meanLog, shape = culture, color = antibiotic), height = 0, width = .2, size=4)+
  #scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  #geom_vline(xintercept=3, linetype = "dashed")+
  #annotate("text", x = 3, y = 10e6, label = "TOB added")+
  labs(title =expression(paste(italic("S. aureus"), " growth in mono or coculture in SCFM2 with 256 ug/mL TOB")), x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") +
  theme_cowplot()+
  panel_border()+
  background_grid()

#only endpoints ratio log
ggplot()+
  geom_jitter(data=cleanDelEndpointData %>% filter(timePoint==5) , aes(x=culture, y=ratioMono,  color = antibiotic), height = 0, width = .2, size=2)+
  geom_errorbar(data=cleanDelEndpointData %>% filter(timePoint==5) , aes(x=culture, ymin=meanRatio-sdRatioMono,ymax = meanRatio+sdRatioMono,  color = antibiotic), height = 0, width = .2, size=2)+
  geom_point(data=cleanDelEndpointData %>% filter(timePoint==5), aes(x=culture, y=meanRatio, color = antibiotic), height = 0, width = .2, size=4)+
  scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  #geom_vline(xintercept=3, linetype = "dashed")+
  #annotate("text", x = 3, y = 10e6, label = "TOB added")+
  labs(title =expression(paste(italic("S. aureus"), " growth in mono or coculture in SCFM2 with 256 ug/mL TOB")), x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") +
  theme_cowplot()+
  panel_border()+
  background_grid()
```

#now I think it would be better to pool all the data and see how it looks like:

```{r pooling data from january 2020 and feb 2019}
#Make both data sets have all the same columns an rows:
newSCFMDataEndpointOnly<-newSCFMData %>% select(CFU, culture, bug, timePoint, antibiotic, sample, condition, strain) %>% filter(timePoint %in% c(0,5))

cleanDelEndpointDataEndpointOnly<-newSCFMDataEndpointOnly %>% select(CFU,culture, bug, timePoint, antibiotic, sample, condition, strain)%>% filter(!sample %in% c("1-25-20A", "1-25-20B")) %>% bind_rows(techReps)

#here I will calculate mean and standard deviation, removing the TOB SO4 replicates and previous replicates of the clean deletion since they had different concentrations of TOB and were below the limit of detection.
percentChange<-cleanDelEndpointDataEndpointOnly%>%
  filter(!condition %in% c("cleanDelScfm128", "cleanDelScfm64"))%>%
  filter(!antibiotic == "TOB SO4")%>%
  filter(timePoint == 5 & bug == "Sa")%>%
  mutate(logTransform = log10(CFU))%>% 
  group_by(culture,sample)%>% mutate(LogKill = logTransform-logTransform[antibiotic=="TOB"]) %>% ungroup()

percentChange <- percentChange %>% group_by(culture, antibiotic) %>% mutate(MeanLogKill = mean(LogKill), SeLogKill = std.error(LogKill)) %>% ungroup()
percentChange$culture <- factor(percentChange$culture, levels = c("mono", "wt", "mut"))
```

```{r graphing pooled data} 
#now lets graph to see the inoculum consistency:
ggplot()+
  geom_jitter(data=cleanDelEndpointDataEndpointOnly %>% filter(timePoint==0) , aes(x=sample, y=CFU, color =condition, shape = culture), height = 0, width = .2, size=4)+
  scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  labs(title =expression(paste(italic("S. aureus"), " inoculum")), x = "Sample",color = "Culture condition") +
  theme_cowplot()+
  panel_border()+
  background_grid()

#and control end point
ggplot()+
  geom_jitter(data=cleanDelEndpointDataEndpointOnly %>% filter(timePoint==5 & antibiotic == "Control") , aes(x=sample, y=CFU, color = condition, shape = culture), height = 0, width = .2, size=4)+
  scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  labs(title =expression(paste(italic("S. aureus"), " end point")), x = "Sample",color = "Culture condition") +
  theme_cowplot()+
  panel_border()+
  background_grid()

#this is all the data
ggplot()+
  geom_jitter(data=cleanDelEndpointDataEndpointOnly %>% filter(timePoint==0) , aes(x=sample, y=CFU, shape =culture), height = 0, width = .2, size = 3, color = "black")+
  geom_jitter(data=cleanDelEndpointDataEndpointOnly %>% filter( timePoint==5) , aes(x=sample, y=CFU, color = antibiotic, shape =culture), height = 0, width = .2, size = 3)+
  scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  labs(title =expression(paste(italic("S. aureus"), " inoculum and end point")), x = "Sample",shape = "Culture",color = "Condition") +
  facet_grid(.~condition,scales = "free", space = "free")+
  theme_cowplot()+
  panel_border()+
  background_grid()
```

```{r data wrangling with all data}
#this is the difference between wt and mutant logs
allDataNoControl <- cleanDelEndpointDataEndpointOnly %>% filter(timePoint == 5 & bug == "Sa") %>% filter(!antibiotic =="Control") %>% mutate(logTransform = log10(CFU))

allDataNoControlCoComparison <- cleanDelEndpointDataEndpointOnly %>% filter(timePoint == 5 & bug == "Sa") %>% filter(!culture == "mono") %>% filter(!antibiotic =="Control") %>% mutate(logTransform = log10(CFU))%>% group_by(sample,bug,timePoint,antibiotic)%>% mutate(difCoC =logTransform[culture=="wt"]-logTransform[culture=="mut"])
#this is the difference between mono and wt logs
allDataNoControlMonoWtComparison <- cleanDelEndpointDataEndpointOnly %>% filter(timePoint == 5 & bug == "Sa") %>% filter(!culture == "mut") %>% filter(!antibiotic =="Control") %>% mutate(logTransform = log10(CFU))%>% group_by(sample,bug,timePoint,antibiotic)%>% mutate(difCoC =logTransform[culture=="mono"]-logTransform[culture=="wt"]) 
#this is the difference between mono and mut logs
allDataNoControlMonoMutComparison <- cleanDelEndpointDataEndpointOnly %>% filter(timePoint == 5 & bug == "Sa") %>% filter(!culture == "wt") %>% filter(!antibiotic =="Control") %>% mutate(logTransform = log10(CFU))%>% group_by(sample,bug,timePoint,antibiotic)%>% mutate(difCoC =logTransform[culture=="mono"]-logTransform[culture=="mut"])

differenceLog<-bind_rows(allDataNoControlMonoWtComparison%>% filter(culture=="wt"),allDataNoControlCoComparison%>% filter(culture=="mut"),allDataNoControlMonoMutComparison%>% filter(culture=="mono") )
#here I will calculate mean and standard deviation, removing the TOB SO4 replicates and previous replicates of the clean deletion since they had different concentrations of TOB and were below the limit of detection.
differenceLog<-differenceLog %>%filter (!condition %in% c("cleanDelScfm128", "cleanDelScfm64")) %>% filter(!antibiotic == "TOB SO4") %>% group_by(culture) %>% mutate(meanDifference = mean(difCoC), sdDifference = sd(difCoC), seDifference = std.error(difCoC)) %>% ungroup()

```

```{r graphing wrangled data}
#This is all the data without any stats
ggplot()+
  geom_point(data=differenceLog , aes(x=sample, y=difCoC, color = culture),size=4)+
  #scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  labs(title =expression(paste(italic("S. aureus"), " end point")), x = "Sample",color = "Culture condition") +
  theme_cowplot()+
  panel_border()+
  background_grid()

#Adding stats
ggplot()+
  geom_jitter(data=differenceLog , aes(x=culture, y=difCoC, color = culture),height = 0, width = .2,shape = 1, size=2)+
  geom_point(data=differenceLog , aes(x=culture, y=meanDifference, color = culture),size=4)+
  geom_errorbar(data=differenceLog , aes(x=culture, ymax=meanDifference+sdDifference,ymin=meanDifference-sdDifference, color = culture),size=1,width = .5)+
  geom_errorbar(data=differenceLog , aes(x=culture, ymax=meanDifference+(2*sdDifference),ymin=meanDifference-(2*sdDifference), color = culture),linetype = "dashed", size=.5,width = .5)+
  geom_errorbar(data=differenceLog , aes(x=culture, ymax=meanDifference+(3*sdDifference),ymin=meanDifference-(3*sdDifference), color = culture),linetype = "dotted", size=.5,width = .5)+
  labs(title =expression(paste(italic("S. aureus"), " end point log differences between conditions (SD)")),y = "Log10 Difference", x = "Sample",color = "Culture condition") +
  scale_color_discrete(labels=c("mono-culture vs w/Mutant","co-culture w/Mutant vs w/Wt","mono-culture vs co-culture w/Wt"))+
  theme_cowplot()+
  panel_border()+
  background_grid()

ggplot()+
  geom_jitter(data=differenceLog , aes(x=culture, y=difCoC, color = culture),height = 0, width = .2,shape = 1, size=2)+
  geom_point(data=differenceLog , aes(x=culture, y=meanDifference, color = culture),size=4)+
  geom_errorbar(data=differenceLog , aes(x=culture, ymax=meanDifference+seDifference,ymin=meanDifference-seDifference, color = culture),size=1,width = .5)+
  labs(title =expression(paste(italic("S. aureus"), " end point log differences between conditions (SE)")),y = "Log10 Difference", x = "Sample",color = "Culture condition") +
  scale_color_discrete(labels=c("mono-culture vs w/Mutant","co-culture w/Mutant vs w/Wt","mono-culture vs co-culture w/Wt"))+
  theme_cowplot()+
  panel_border()+
  background_grid()

#find trends between the killing of TOB

```

```{r exploring the wilcoxon.test function}
#first try magnitude
wilcox.test(c(1,2,3,  2,3,4) ~ c(1, 1, 1, 2, 2, 2))#this ties and p = .3687
wilcox.test(c(1,2,3,  4,3,2) ~ c(1, 1, 1, 2, 2, 2))#this ties and p = .3687 #this shows that this is not paired

wilcox.test(c(1,2,3,  2,3,4) ~ c(1, 1, 1, 2, 2, 2), paired = T)#this ties and p = .1489
wilcox.test(c(3,2,1,  2,3,4) ~ c(1, 1, 1, 2, 2, 2), paired = T)#this ties and p = .5862
wilcox.test(c(1,2,3,  4,3,2) ~ c(1, 1, 1, 2, 2, 2), paired = T)#this ties and p = .5862 #this shows that this is paired and order matters
#Does magnitude matter?
wilcox.test(c(1,2,3,  2,3,4) ~ c(1, 1, 1, 2, 2, 2), paired = T)#this ties and p = .1489
wilcox.test(c(1,2,3,  3,4,5) ~ c(1, 1, 1, 2, 2, 2), paired = T)#this ties and p = .1489 #Nope! Magnitude doesnt matter
wilcox.test(c(1,2,3,  300,400,500) ~ c(1, 1, 1, 2, 2, 2), paired = T)#this ties and p = .25 #yeah, it does, but idk how
wilcox.test(c(1,2,3,  300,301,302) ~ c(1, 1, 1, 2, 2, 2), paired = T)#this ties and p = .1489 #what seems to matter is the difference between them
wilcox.test(c(1,2,3,  5,5,5) ~ c(1, 1, 1, 2, 2, 2), paired = T)#this doesn't tie and p = .25 #wtf???
#so the tie seems to be the difference between the vectors, not the repeated numbers, and it just throws them out
wilcox.test(c(1,2,3,  5,5,6) ~ c(1, 1, 1, 2, 2, 2), paired = T)#this ties and p = .1736, here there's only one tie...
#and if there are no ties, 3 replicates per condition and all by a different number, then the p-value will be .25
wilcox.test(c(1,2,3,  6,6,6) ~ c(1, 1, 1, 2, 2, 2), paired = T)#this doesn't tie and p = .25 again
#so... what if I have more replicates?
wilcox.test(c(1,1,1,1,  6,6,6,6) ~ c(1, 1, 1, 1, 2, 2, 2,2), paired = T)#this ties and p = .07186
wilcox.test(c(1,2,3,4,  6,6,6,6) ~ c(1, 1, 1, 1, 2, 2, 2,2), paired = T)#this doesn't tie and p = .125
wilcox.test(c(1,2,3,4,5,  6,6,6,6,6) ~ c(1, 1, 1, 1,1,2, 2, 2, 2,2), paired = T)#this doesn't tie and p = .0625
wilcox.test(c(1,2,3,4,5,6,  7,7,7,7,7,7) ~ c(1, 1, 1, 1,1,1,2,2, 2, 2, 2,2), paired = T)#this doesn't tie and p = .03125
#what is weird is that if the difference between them is the same, aka there's a tie, then p-value goes down..
wilcox.test(c(1,2,3,4,5,6,  7,7,7,7,6,7) ~ c(1, 1, 1, 1,1,1,2,2, 2, 2, 2,2), paired = T)#this ties and p = .03552, now this is weird, one tie increases the metric
wilcox.test(c(1,2,3,4,5,6,  7,7,7,5,6,7) ~ c(1, 1, 1, 1,1,1,2,2, 2, 2, 2,2), paired = T)#this ties and p = .03401, 2 ties...
wilcox.test(c(1,2,3,4,5,6,  7,7,4,5,6,7) ~ c(1, 1, 1, 1,1,1,2,2, 2, 2, 2,2), paired = T)#this ties and p = .03103, 3 ties...
wilcox.test(c(1,2,3,4,5,6,  7,3,4,5,6,7) ~ c(1, 1, 1, 1,1,1,2,2, 2, 2, 2,2), paired = T)#this ties and p = .02627, 4 ties...
wilcox.test(c(1,2,3,4,5,6,  2,3,4,5,6,7) ~ c(1, 1, 1, 1,1,1,2,2, 2, 2, 2,2), paired = T)#this ties and p = .01966, these are all ties
#so I think I should have my answer now... I need 6 samples for it to be significant, and in this case I can just use both the mutant and the clean deletion replicates

```

```{r Wilcoxon Tests}
#Wilcoxon test:
#it works better with log CFUs than CFUs, so I'll stick to it...

wtMonoWilcoxonLogAll<- wilcox.test(allDataEndPointAll %>% filter(culture == "mono"& antibiotic == "TOB") %>% pull(logTransform),
                    allDataEndPointAll %>% filter(culture == "wt"& antibiotic == "TOB") %>% pull(logTransform),paired = T)

mutWtWilcoxonLogAll<- wilcox.test(allDataEndPointAll %>% filter(culture == "wt" & antibiotic == "TOB") %>% pull(logTransform),
                    allDataEndPointAll %>% filter(culture == "mut"& antibiotic == "TOB") %>% pull(logTransform),paired = T, exact = T)

mutMonoWilcoxonLogAll<- wilcox.test(allDataEndPointAll %>% filter(culture == "mono"& antibiotic == "TOB") %>% pull(CFU),
                                    allDataEndPointAll %>% filter(culture == "mut"& antibiotic == "TOB") %>% pull(CFU),paired = T)

mutMonoWilcoxonLog<- wilcox.test(allDataEndPointAll %>% filter(culture == "mono" & antibiotic == "TOB" &condition %in% c("cleanDelEndpoint", "mutLib128")) %>% pull(logTransform),
                                 allDataEndPointAll %>% filter(culture == "mut"& antibiotic == "TOB"&condition%in% c("cleanDelEndpoint", "mutLib128")) %>% pull(logTransform),paired = T)

wtMonoWilcoxonLog<- wilcox.test(allDataEndPointAll %>% filter(culture == "mono" & antibiotic == "TOB" &condition %in% c("cleanDelEndpoint", "mutLib128")) %>% pull(logTransform),
                                allDataEndPointAll %>% filter(culture == "wt"& antibiotic == "TOB"&condition%in% c("cleanDelEndpoint", "mutLib128")) %>% pull(logTransform),paired = T)

mutWtWilcoxonLog<- wilcox.test(allDataEndPointAll %>% filter(culture == "wt" & antibiotic == "TOB" &condition %in% c("cleanDelEndpoint", "mutLib128")) %>% pull(logTransform),
                               allDataEndPointAll %>% filter(culture == "mut"& antibiotic == "TOB"&condition%in% c("cleanDelEndpoint", "mutLib128")) %>% pull(logTransform),paired = T)

wilcoxDataAll<- allDataEndPoint%>% filter(timePoint == 5 & bug == "Sa") %>% filter(!antibiotic == "TOB SO4") %>% mutate(logTransform = log10(CFU))

```

```{r What is the wilcoxon test comparing?}
wilcoxDataAll<- cleanDelEndpointDataEndpointOnly%>% filter(timePoint == 5 & bug == "Sa") %>% filter(!antibiotic == "TOB SO4") %>% mutate(logTransform = log10(CFU)) %>% group_by(culture, antibiotic)%>%  mutate(meanLog = mean (logTransform), sdLog = sd(logTransform), seLog = std.error(logTransform))
wilcoxDataAll$culture <- factor(wilcoxDataAll$culture, levels = c("mono", "wt", "mut"))

wilcoxDataGood<-cleanDelEndpointDataEndpointOnly%>% filter(timePoint == 5 & bug == "Sa") %>%  filter(!antibiotic == "TOB SO4") %>% filter(condition %in% c("cleanDelEndpoint", "mutLib128"))%>% mutate(logTransform = log10(CFU)) %>% group_by(culture, antibiotic) %>% mutate(meanLog = mean (logTransform), sdLog = sd(logTransform), seLog = std.error(logTransform))
wilcoxDataGood$culture <- factor(wilcoxDataGood$culture, levels = c("mono", "wt", "mut"))

ggplot()+
  geom_jitter(data=wilcoxDataAll , aes(x=culture, y=logTransform),height = 0, width = .2,shape = 1, size=2)+
  geom_point(data=wilcoxDataAll , aes(x=culture, y=meanLog),size=4)+
  geom_errorbar(data=wilcoxDataAll , aes(x=culture, ymax=meanLog+sdLog,ymin=meanLog-sdLog),size=1,width = .5)+
  labs(title =expression(paste(italic("S. aureus"), " end point log differences between conditions")),y = "Log10 Difference", x = "Sample",color = "Culture condition") +
  scale_color_discrete(labels=c("co-culture w/Mutant vs w/Wt ","mono-culture vs co-culture w/Wt "))+
  #facet_grid(.~condition,scales = "free", space = "free")+
  theme_cowplot()+
  panel_border()+
  background_grid()

ggplot()+
  geom_jitter(data=wilcoxDataGood , aes(x=culture, y=logTransform),height = 0, width = .2,shape = 1, size=2)+
  geom_point(data=wilcoxDataGood , aes(x=culture, y=meanLog),size=4)+
  geom_errorbar(data=wilcoxDataGood , aes(x=culture, ymax=meanLog+sdLog,ymin=meanLog-sdLog),size=1,width = .5)+
  labs(title =expression(paste(italic("S. aureus"), " end point Tobramycin")),y = "Log10 CFUs", x = "Sample",color = "Culture condition") +
  scale_color_discrete(labels=c("co-culture w/Mutant vs w/Wt ","mono-culture vs co-culture w/Wt "))+
  #facet_grid(.~condition,scales = "free", space = "free")+
  theme_cowplot()+
  panel_border()+
  background_grid()

ggplot() +
  geom_col(data = wilcoxDataAll, aes (x = culture, y = meanLog, fill = antibiotic, group = antibiotic), position = position_dodge( ))+
  geom_linerange(data = wilcoxDataAll, aes(x = culture, ymin = meanLog - sdLog, ymax = meanLog + sdLog,group = antibiotic),position = position_dodge(width = .9))+
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)))+
  labs(title =expression(paste(italic("S. aureus"), " growth at 5 hours (all data)")),y = "Log10 CFUs", x = "Culture condition") +
  scale_fill_grey()+
  theme_cowplot()+
  theme_half_open()+
  background_grid()
ggsave("plotEndPointAllData.eps", dpi = "print", width = 8, height = 6)

ggplot() +
  geom_col(data = wilcoxDataGood, aes (x = culture, y = meanLog, fill = antibiotic, group = antibiotic), position = position_dodge( ))+
  geom_linerange(data = wilcoxDataGood, aes(x = culture, ymin = meanLog - seLog, ymax = meanLog + seLog,group = antibiotic),position = position_dodge(width = .9))+
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)))+
  labs(title =expression(paste(italic("S. aureus"), " growth at 5 hours")),y = "Log10 CFUs", x = "Culture condition") +
  scale_fill_grey()+
  theme_cowplot()+
  theme_half_open()+
  background_grid()
ggsave("plotEndPointGoodData.eps", dpi = "print", width = 8, height = 6)
```

```{r paper figures}
#All data
ggplot()+
  geom_jitter(data=cleanDelEndpointDataEndpointOnly %>% filter(bug == "Sa") %>% filter(condition %in% c("mutLib128", "cleanDelEndpoint")) %>% filter(!antibiotic == "TOB SO4") , aes(x=timePoint, y=CFU, color = culture), height = 0, width = .2, size=4)+
  scale_y_log10(name=expression(paste('CFUs per mL' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  geom_vline(xintercept=3, linetype = "dashed")+
  annotate("text", x = 3, y = 10e6, label = "TOB added")+
  labs(title =expression(paste(italic("S. aureus"), " growth in mono or coculture in SCFM2 with 256 ug/mL TOB")), x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") +
  facet_grid(sample~antibiotic)+
  theme_cowplot()+
  panel_border()+
  background_grid()

#Ratio between end point conditions with std error
ggplot()+
  geom_jitter(data=differenceLog , aes(x=culture, y=difCoC, color = culture),height = 0, width = .2,shape = 1, size=2)+
  geom_point(data=differenceLog , aes(x=culture, y=meanDifference, color = culture),size=4)+
  geom_errorbar(data=differenceLog , aes(x=culture, ymax=meanDifference+seDifference,ymin=meanDifference-seDifference, color = culture),size=1,width = .5)+
  labs(title =expression(paste(italic("S. aureus"), " end point log differences between conditions (SE)")),y = "Log10 Difference", x = "Sample",color = "Culture condition") +
  scale_color_discrete(labels=c("mono-culture vs w/Mutant","co-culture w/Mutant vs w/Wt","mono-culture vs co-culture w/Wt"))+
  theme_cowplot()+
  panel_border()+
  background_grid()

#End point bar graph with std error
ggplot() +
  geom_col(data = wilcoxDataGood, aes (x = culture, y = meanLog, fill = antibiotic, group = antibiotic), position = position_dodge( ))+
  geom_linerange(data = wilcoxDataGood, aes(x = culture, ymin = meanLog - seLog, ymax = meanLog + seLog,group = antibiotic),position = position_dodge(width = .9))+
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)))+
  labs(title =expression(paste(italic("S. aureus"), " growth at 5 hours")),y = "Log10 CFUs", x = "Culture condition") +
  scale_fill_grey()+
  theme_cowplot()+
  theme_half_open()+
  background_grid()

ggplot() +
  geom_col(data = percentChange %>% filter(sample == "1-25-20"), aes (x = culture, y = MeanLogKill))+
  geom_linerange(data = percentChange, aes(x = culture, ymin = MeanLogKill - SeLogKill/2, ymax = MeanLogKill + SeLogKill/2))+
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)))+
  labs(title =expression(paste(italic("S. aureus"), " killing by Tobramycin")),y = "Log10 kill", x = "Culture condition") +
  scale_fill_grey()+
  theme_cowplot()+
  theme_half_open()+
  background_grid()

```

### 2020-03-13 R Analysis Scripts/PropOc Data 3D.Rmd
New script analysis

---
title: "PropOcData2"
author: "Juan P Barraza"
date: "3/5/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(pixmap)
library(rtiff)
library(reshape2)
library(gplots)
library(gdata)
library(plyr)
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
library(plotrix)
library(ggsignif)
library(rdist)

source('/Users/jupabago/Documents/Whiteley/PROJECTS/Rpackage/PropOc Package/R/PropOcFunctions2.0.R') #using the new 3D script with capped spheres.
```

```{r Get Prop Oc Data}
GetNewPropOcOralData<-function(sample){
  imagesFolder<-"/Users/jupabago/Documents/Whiteley/PROJECTS/Oral Penn/Images/WT&Mut&GtfB/"
  folder<-paste0(imagesFolder, sample, "/combined Bin",sample) 
  fileList<-list.files(path = folder, full.names = TRUE)
  fileList2<-fileList[grep("tif",fileList)]
  propOc<- NormRawPipeline(SlicesTo3D(fileList2,"red"),SlicesTo3D(fileList2,"green"),xydimSearch = 54, zdimSearch = 9,sampleSize = 1000,xyRealDim = 0.156,zRealDim = 0.93, pipeBinSize = 1)
  return(propOc)
}

samples = c("WT1","WT2","WT3","Mut1","Mut2","Mut3","GtfB1","GtfB2","GtfB3")

propOcDataList<-map(samples, GetNewPropOcOralData)#get the data
propOcDataNames<-map2(propOcDataList, samples, ~.x %>% mutate(Sample = .y))#add sample column
propOcData<-bind_rows(propOcDataNames)#it's aliveeeee
write.csv(propOcData,"/Users/jupabago/545455Documents/Whiteley/PROJECTS/Oral Penn/Images/WT&Mut&GtfB/ PropOc Data AllData.csv")
```

```{r PropOc DATA}

GetPropOcData<-function(sample, timepoints, positions){
  folder<- paste0('/Volumes/Seagate Backup Plus Drive/Good images/',sample,'/images1')
  growthDf<-data.frame()#data frame to add all timepoints and positions
  fileList<-list.files(path = folder, full.names = TRUE)
  print(folder)
  for (position in 0:positions){
    currentPosition<-fileList[grep(paste0("p",position,"_"),fileList)]
    print(paste0('analyzing position ', position))
    for (timepoint in 0:timepoints){
      currentTimePoint<-currentPosition[grep(paste0("t",GetSlice(timepoint),"_"),currentPosition)]
      dataTimePoint<-NormRawPipeline(SlicesTo3D(currentTimePoint,"red"),SlicesTo3D(currentTimePoint,"green"), 
                                               #xydimSearch=114,zdimSearch = 70, sampleSize=1,xyRealDim=0.264,
                                     xydimSearch=11,zdimSearch = 7, sampleSize=100,xyRealDim=0.264,
                                               #zRealDim = 0.44, pipeBinSize = 1)
                                     zRealDim = 0.44, pipeBinSize = 1)
      dataTimePoint$TimePoint <- timepoint
      dataTimePoint$Position <- position
      growthDf<-rbind(growthDf,dataTimePoint)
      }
    }
  return(growthDf)
  }

GetSlice<-function(idx){
if (idx<10){num = paste0(0,idx)}
  else
    {num = idx}
  return(num)}

test1<-GetPropOcData("3-13-19", 0, 0)
test2<-GetPropOcData("3-13-19", 1, 1)

propOcPA14wt_1.1<-GetImageFiles("/media/whiteley/Seagate Backup Plus Drive/Good images/3-13-19/images1", timepoints = 10, positions = 5)
propOcPA14wt_2.1<-GetImageFiles("/media/whiteley/Seagate Backup Plus Drive/Good images/3-19-19/images1", timepoints = 10, positions = 5)
propOcPA14wt_3.1<-GetImageFiles("/media/whiteley/Seagate Backup Plus Drive/Good images/4-17-19/images1", timepoints = 10, positions = 5)

propOcPA14mut_1.1<-GetImageFiles("/media/whiteley/Seagate Backup Plus Drive/Good images/4-24-19/images1", timepoints = 10, positions = 5)
propOcPA14mut_2.1<-GetImageFiles("/media/whiteley/Seagate Backup Plus Drive/Good images/4-25-19/images1", timepoints = 10, positions = 5)
propOcPA14mut_3.1<-GetImageFiles("/media/whiteley/Seagate Backup Plus Drive/Good images/5-8-19/images1", timepoints = 10, positions = 5)

write.csv(propOcPA14wt_1.1, file = "/media/whiteley/Seagate Backup Plus Drive/Good images/PropOc Data/results1/PA14wt_1.csv", row.names = FALSE)
write.csv(propOcPA14wt_2.1, file = "/media/whiteley/Seagate Backup Plus Drive/Good images/PropOc Data/results1/PA14wt_2.csv", row.names = FALSE)
write.csv(propOcPA14wt_3.1, file = "/media/whiteley/Seagate Backup Plus Drive/Good images/PropOc Data/results1/PA14wt_3.csv", row.names = FALSE)

write.csv(propOcPA14mut_1.1, file = "/media/whiteley/Seagate Backup Plus Drive/Good images/PropOc Data/results1/PA14mut_1.csv", row.names = FALSE)
write.csv(propOcPA14mut_2.1, file = "/media/whiteley/Seagate Backup Plus Drive/Good images/PropOc Data/results1/PA14mut_2.csv", row.names = FALSE)
write.csv(propOcPA14mut_3.1, file = "/media/whiteley/Seagate Backup Plus Drive/Good images/PropOc Data/results1/PA14mut_3.csv", row.names = FALSE)

```

### 2020-03-13 R Analysis Scripts/CFU Data.Rmd
fixed some titles

@@
 
-```{r Confocal vs CFUs data wrangling}
+```{r Confocal data wrangling}
 #first pull confocal data:
@@
 DataComparisonScope<-allConfocalResultsStats %>% filter (Strain %in% c("PA14wt","PA14mut")) %>% filter(Condition == "Pa:Sa 1:1") %>%  filter(TimePoint %in% c(0,3,7,11,15)) %>% select(Condition,TimePoint, Strain, Species, MeanTotals, MeanLogTotals) %>% mutate(time = ifelse(TimePoint>0, TimePoint+1, 0)) #The timePoint thing is because I start imaging after one hour and I don't have a time zero on scope
+```
 
+```{r CFU data wrangling}
 ##remove stirred condition I didn't do in the scope and fix strain names:
@@
 ##Adding more data from the TOB experiments!
+
 #first select relevant conditions and fix column names
@@
 colnames(DataComparisonCFUSa)<-c("strain", "time", "CFUs", "logCFUs", "Strain")
+
 #then do the same for the scope data

### 2020-03-18 R Analysis Scripts/CFU Data.Rmd
added comparisons of plate counts to the images I made with different thresholds

@@
 library(moderndive)
-
+```
+```{r data gathering functions}
 #Data gathering functions:
@@
 }
+```
+
+```{r graphing functions}
 #Graphing functions
+
 ##this one graphs the log values
@@
 ```{r CFU data wrangling}
+
+#GROWTH CURVES PLATE COUNTS DATA
 ##remove stirred condition I didn't do in the scope and fix strain names:
 DataComparisonCFU<-PA14DataStats %>% filter (condition == "Static") %>% select(bug, strain, CFUmean, logCFUmean, condition, time)%>% as.data.frame() 
-DataComparisonCFU<-DataComparisonCFU%>% mutate(Strain = recode(DataComparisonCFU$strain, wt = "PA14wt", mut = "PA14mut"))
+DataComparisonCFU<-DataComparisonCFU%>% mutate(Strain = recode(DataComparisonCFU$strain, wt = "PA14wt", mut = "PA14mut"))#add new column with proper name
 
@@
 
-##Adding more data from the TOB experiments!
+#FOR SA I can also use the Tob data, but first isolate from the other plate counts data:
+DataComparisonCFUSaGrowthCurves<-DataComparisonCFU %>% filter(Species == "Sa") %>% select(Species, strain, CFUs, logCFUs, time, Strain)
 
+#TOB PLATE COUNTS DATA
+#this is dataframe is in the "SaPa TOB grwoth curves.RMD" file
 #first select relevant conditions and fix column names
-DataComparisonCFUSa<-newSCFMDataSa%>%  filter(!culture == "mono") %>% filter(antibiotic == "Control") %>% select(CFU, culture, bug, timePoint, antibiotic, logTranformed,sample, condition) %>% group_by(culture, timePoint) %>% summarise(meanCFU = mean(CFU), meanLogCFU = mean(logTranformed))
+DataComparisonCFUSa<-newSCFMDataSa%>%  filter(!culture == "mono") %>% filter(antibiotic == "Control") %>% select(CFU, culture, bug, timePoint, antibiotic, logTranformed,sample, condition) %>% group_by(bug, culture, timePoint) %>% summarise(meanCFU = mean(CFU), meanLogCFU = mean(logTranformed)) %>% ungroup()
 
-DataComparisonCFUSa<-DataComparisonCFUSa%>% as.data.frame() %>%mutate(Strain = recode(DataComparisonCFUSa$culture, wt = "PA14wt", mut = "PA14mut"))
+DataComparisonCFUSa<-DataComparisonCFUSa%>% mutate(Strain = recode(DataComparisonCFUSa$culture, wt = "PA14wt", mut = "PA14mut"))
+colnames(DataComparisonCFUSa)<-c("Species", "strain", "time", "CFUs", "logCFUs", "Strain")
 
-colnames(DataComparisonCFUSa)<-c("strain", "time", "CFUs", "logCFUs", "Strain")
+DataCFUAllSa<-bind_rows(DataComparisonCFUSa,DataComparisonCFUSaGrowthCurves)#combine growth curves and TOB
+DataCFUAllSa<-DataCFUAllSa%>% group_by(Strain,time) %>% summarise(CFU = mean(CFUs), LogCFU = mean(logCFUs)) %>% ungroup()
 
 #then do the same for the scope data
-DataComparisonScopeSa<-allConfocalResultsStats %>% filter(Species == "Sa")%>% filter (Strain %in% c("PA14wt","PA14mut")) %>% filter(Condition == "Pa:Sa 1:1") %>%  filter(TimePoint %in% c(0,2,3,4)) %>% select(Condition,TimePoint, Strain, Species, MeanTotals, MeanLogTotals) %>% mutate(time = ifelse(TimePoint>0, TimePoint+1, 0)) #The timePoint thing is because I start imaging after one hour and I don't have a time zero on scope
+DataComparisonScopeSa<-allConfocalResultsStats %>% filter(Species == "Sa")%>% filter (Strain %in% c("PA14wt","PA14mut")) %>% filter(Condition == "Pa:Sa 1:1") %>%  filter(TimePoint %in% c(0,2,3,4,7,11,15)) %>% select(Condition,TimePoint, Strain, Species, MeanTotals, MeanLogTotals) %>% mutate(time = ifelse(TimePoint>0, TimePoint+1, 0)) #The timePoint thing is because I start imaging after one hour and I don't have a time zero on scope
 #merge them!
-comparisonSaDf <- merge(DataComparisonCFUSa,DataComparisonScopeSa,by=c("time","Strain"))
+comparisonSaDf <- merge(DataCFUAllSa,DataComparisonScopeSa,by=c("time","Strain"))
+comparisonSaDfTOB <- merge(DataComparisonCFUSa,DataComparisonScopeSa,by=c("time","Strain"))
+
+```
+```{r microscopy data from different thresholds}
+linear1Stats<-linear1[[2]] %>% filter(Species == "Sa")%>% filter (Strain %in% c("PA14wt","PA14mut")) %>% filter(Condition == "Pa:Sa 1:1") %>%  filter(TimePoint %in% c(0,2,3,4,7,11,15)) %>% select(Condition,TimePoint, Strain, Species, MeanTotals, MeanLogTotals) %>% mutate(time = ifelse(TimePoint>0, TimePoint+1, 0))
+
+linear2Stats<-linear2[[2]] %>% filter(Species == "Sa")%>% filter (Strain %in% c("PA14wt","PA14mut")) %>% filter(Condition == "Pa:Sa 1:1") %>%  filter(TimePoint %in% c(0,2,3,4,7,11,15)) %>% select(Condition,TimePoint, Strain, Species, MeanTotals, MeanLogTotals) %>% mutate(time = ifelse(TimePoint>0, TimePoint+1, 0))
+
+linear4Stats<-linear4[[2]] %>% filter(Species == "Sa")%>% filter (Strain %in% c("PA14wt","PA14mut")) %>% filter(Condition == "Pa:Sa 1:1") %>%  filter(TimePoint %in% c(0,2,3,4,7,11,15)) %>% select(Condition,TimePoint, Strain, Species, MeanTotals, MeanLogTotals) %>% mutate(time = ifelse(TimePoint>0, TimePoint+1, 0))
+
+linear5Stats<-linear5[[2]] %>% filter(Species == "Sa")%>% filter (Strain %in% c("PA14wt","PA14mut")) %>% filter(Condition == "Pa:Sa 1:1") %>%  filter(TimePoint %in% c(0,2,3,4,7,11,15)) %>% select(Condition,TimePoint, Strain, Species, MeanTotals, MeanLogTotals) %>% mutate(time = ifelse(TimePoint>0, TimePoint+1, 0))
+
+linear6Stats<-linear6[[2]] %>% filter(Species == "Sa")%>% filter (Strain %in% c("PA14wt","PA14mut")) %>% filter(Condition == "Pa:Sa 1:1") %>%  filter(TimePoint %in% c(0,2,3,4,7,11,15)) %>% select(Condition,TimePoint, Strain, Species, MeanTotals, MeanLogTotals) %>% mutate(time = ifelse(TimePoint>0, TimePoint+1, 0))
+
+#merging with the whole growth curve data, not only TOB
+comparisonSaDflinear1 <- merge(DataCFUAllSa,linear1Stats,by=c("time","Strain"))
+comparisonSaDflinear2 <- merge(DataCFUAllSa,linear2Stats,by=c("time","Strain"))
+comparisonSaDflinear4 <- merge(DataCFUAllSa,linear4Stats,by=c("time","Strain"))
+comparisonSaDflinear5 <- merge(DataCFUAllSa,linear5Stats,by=c("time","Strain"))
+comparisonSaDflinear6 <- merge(DataCFUAllSa,linear6Stats,by=c("time","Strain"))
 
@@
 
-```{r graph CFU vs Confocal}
+```{r graph CFU vs Confocal Pa}
 #Graph both Pa and Sa
@@
 
+```
+
+```{r graph CFU vs Confocal Sa}
+
 #Now we go to Sa
-
+#this is using only Growth cruves data
 SaLinearModel <- lm(MeanLogTotals ~logCFUs, data = comparisonDf %>% filter (Species == "Sa")%>% filter(!time == 0))
@@
   theme_cowplot(12)
+#adding TOB data only
+SaLinearModelTOB <- lm(MeanLogTotals ~logCFUs, data = comparisonSaDfTOB%>% filter(!time == 0))
+coefficients(SaLinearModelTOB)
+get_regression_summaries(SaLinearModelTOB, print = TRUE)
+ggplot()+
+  geom_point(data=comparisonSaDf, aes(x=LogCFU,y=MeanLogTotals,  color = time, shape = Strain),size=4)+
+  geom_abline(intercept =20.243855, slope = -1.810558, color = "red", size = 1, linetype = "dashed" )+
+  scale_color_gradient(low="blue", high="red")+
+  annotate("text", x = 7.9, y = 5.2, label = expression(paste("y=-1.810+20.243855 ", R^2, "= 0.631")), color = "red", size = 8)+
+  labs(title =expression(paste(italic("S. aureus"), " CFU vs Confocal Biomass")), x = "Log CFUs",y = "Biomass from Scope")
 
-#Adding the early time points of Staph:
-SaLinearModel2 <- lm(MeanLogTotals ~logCFUs, data = comparisonSaDf%>% filter(!time == 0))
+#combining TOB and growth curves data
+SaLinearModel2 <- lm(MeanLogTotals ~LogCFU, data = comparisonSaDf%>% filter(!time == 0))
 coefficients(SaLinearModel2)
@@
 ggplot()+
-  geom_point(data=comparisonSaDf %>% filter(Species == "Sa"), aes(x=logCFUs,y=MeanLogTotals,  color = time, shape = Strain),size=4)+
-  geom_abline(intercept =-2.693, slope = 0.928, color = "red", size = 1, linetype = "dashed" )+
+  geom_point(data=comparisonSaDf, aes(x=LogCFU,y=MeanLogTotals,  color = time, shape = Strain),size=4)+
+  geom_abline(intercept =20.243855, slope = -1.810558, color = "red", size = 1, linetype = "dashed" )+
   scale_color_gradient(low="blue", high="red")+
-  annotate("text", x = 7.9, y = 5.2, label = expression(paste("y=0.928x-2.693 ", R^2, "= 0.59")), color = "red", size = 8)+
+  annotate("text", x = 7.9, y = 5.2, label = expression(paste("y=-1.810+20.243855 ", R^2, "= 0.631")), color = "red", size = 8)+
   labs(title =expression(paste(italic("S. aureus"), " CFU vs Confocal Biomass")), x = "Log CFUs",y = "Biomass from Scope")
+
+SaLinearModel3 <- lm(MeanLogTotals ~LogCFU, data = comparisonSaDf%>% filter(!time %in% c(0,16)))
+coefficients(SaLinearModel3)
+get_regression_summaries(SaLinearModel3, print = TRUE)
+
+SaLinearModel4 <- lm(MeanLogTotals ~LogCFU, data = comparisonSaDf%>% filter(!time %in% c(0,12,16)))
+coefficients(SaLinearModel4)
+get_regression_summaries(SaLinearModel4, print = TRUE)
+
+SaLinearModel5 <- lm(MeanLogTotals ~LogCFU, data = comparisonSaDf%>% filter(!time %in% c(0,8,12,16)))
+coefficients(SaLinearModel5)
+get_regression_summaries(SaLinearModel5, print = TRUE)
+ggplot()+
+  geom_point(data=comparisonSaDf, aes(x=LogCFU,y=MeanLogTotals,  color = time, shape = Strain),size=4)+
+  geom_abline(intercept =-.982, slope = .7210531, color = "red", size = 1, linetype = "dashed" )+
+  scale_color_gradient(low="blue", high="red")+
+  annotate("text", x = 7.9, y = 5.2, label = expression(paste("y=-1.810+20.243855 ", R^2, "= 0.631")), color = "red", size = 8)+
+  labs(title =expression(paste(italic("S. aureus"), " CFU vs Confocal Biomass")), x = "Log CFUs",y = "Biomass from Scope")
+
+#Testing the images with different thresholds
+
+SaLinearModelLinear1 <- lm(MeanLogTotals ~LogCFU, data = comparisonSaDflinear1%>% filter(!time %in% c(0,12,16)))
+coefficients(SaLinearModelLinear1)
+
+SaLinearModelLinear2 <- lm(MeanLogTotals ~LogCFU, data = comparisonSaDflinear2%>% filter(!time %in% c(0,12,16)))
+coefficients(SaLinearModelLinear2)
+
+SaLinearModelLinear4 <- lm(MeanLogTotals ~LogCFU, data = comparisonSaDflinear4%>% filter(!time %in% c(0,12,16)))
+coefficients(SaLinearModelLinear4)
+
+SaLinearModelLinear5 <- lm(MeanLogTotals ~LogCFU, data = comparisonSaDflinear5%>% filter(!time %in% c(0,8,12,16)))
+coefficients(SaLinearModelLinear5)
+
+SaLinearModelLinear6 <- lm(MeanLogTotals ~LogCFU, data = comparisonSaDflinear6%>% filter(!time %in% c(0,8,12,16)))
+coefficients(SaLinearModelLinear6)
 

### 2020-03-23 ThresholdingWithFunctions.m
Corrected scirpt to subtract red channel from green channel to prevent overlapping voxels.

@@ -37,33 +37,32 @@ extra = GetImageData(path, '3-28-19', '62x_SaLac-PA14wt-PA14pqsL-SaPa14wt-SaPa14
 SaThreshold = ones(18,1)*0.2143;
 Pa14wtThreshold = ones(18,1)*0.081486;
 Pa14mutThreshold = ones(18,1)*0.077379;
-pa14wt_1 = GetImageData2(path, '3-13-19', '62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-13-19', slices, timepoints, positions, SaThreshold,Pa14wtThreshold);
-pa14wt_2 = GetImageData2(path, '3-19-19', '62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-19-19', slices, timepoints, positions, SaThreshold,Pa14wtThreshold);                                           
-pa14wt_3 = GetImageData2(path, '4-17-19', '62x_Salac_Pa14wt_SaPa14wt1-11-10100-110-1_co_SCFM2_tile2x2_4-17-19', slices, timepoints, positions, SaThreshold,Pa14wtThreshold);
+GetImageData2(path, '3-13-19', '62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-13-19', slices, timepoints, positions, SaThreshold,Pa14wtThreshold);
+GetImageData2(path, '3-19-19', '62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-19-19', slices, timepoints, positions, SaThreshold,Pa14wtThreshold);                                           
+GetImageData2(path, '4-17-19', '62x_Salac_Pa14wt_SaPa14wt1-11-10100-110-1_co_SCFM2_tile2x2_4-17-19', slices, timepoints, positions, SaThreshold,Pa14wtThreshold);
                                            
-pa14mut_1 = GetImageData2(path, '4-24-19', '62x_Salac_Pa14pqsLclean_SaPa14pqsLclean=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_4-24-19', slices, timepoints, positions, SaThreshold,Pa14mutThreshold);
[…]

### 2020-03-23 R Analysis Scripts/PropOc Data 3D.Rmd
Repurposed it to tray to actually run the code, but it didnt work...

@@
 
-source('/Users/jupabago/Documents/Whiteley/PROJECTS/Rpackage/PropOc Package/R/PropOcFunctions2.0.R') #using the new 3D script with capped spheres.
-```
-
-```{r Get Prop Oc Data}
-GetNewPropOcOralData<-function(sample){
-  imagesFolder<-"/Users/jupabago/Documents/Whiteley/PROJECTS/Oral Penn/Images/WT&Mut&GtfB/"
-  folder<-paste0(imagesFolder, sample, "/combined Bin",sample) 
-  fileList<-list.files(path = folder, full.names = TRUE)
-  fileList2<-fileList[grep("tif",fileList)]
-  propOc<- NormRawPipeline(SlicesTo3D(fileList2,"red"),SlicesTo3D(fileList2,"green"),xydimSearch = 54, zdimSearch = 9,sampleSize = 1000,xyRealDim = 0.156,zRealDim = 0.93, pipeBinSize = 1)
-  return(propOc)
-}
-
-samples = c("WT1","WT2","WT3","Mut1","Mut2","Mut3","GtfB1","GtfB2","GtfB3")
-
-propOcDataList<-map(samples, GetNewPropOcOralData)#get the data
-propOcDataNames<-map2(propOcDataList, samples, ~.x %>% mutate(Sample = .y))#add sample column
-propOcData<-bind_rows(propOcDataNames)#it's aliveeeee
-write.csv(propOcData,"/Users/jupabago/545455Documents/Whiteley/PROJECTS/Oral Penn/Images/WT&Mut&GtfB/ PropOc Data AllData.csv")
+source('/Users/jupabago/Documents/Whiteley/PROJECTS/Rpackage/PropOc Package/R/PropOcFunctions2.0.R') 
+#using the new 3D script with capped spheres.
 ```
@@
 GetPropOcData<-function(sample, timepoints, positions){
-  folder<- paste0('/Volumes/Seagate Backup Plus Drive/Good images/',sample,'/images1')
+  folder<- paste0('/Volumes/Seagate Backup Plus Drive/Good images/',sample,'/imagesSubtractRed')
   growthDf<-data.frame()#data frame to add all timepoints and positions
@@
       dataTimePoint<-NormRawPipeline(SlicesTo3D(currentTimePoint,"red"),SlicesTo3D(currentTimePoint,"green"), 
-                                               #xydimSearch=114,zdimSearch = 70, sampleSize=1,xyRealDim=0.264,
-                                     xydimSearch=11,zdimSearch = 7, sampleSize=100,xyRealDim=0.264,
-                                               #zRealDim = 0.44, pipeBinSize = 1)
+                                     xydimSearch=114,zdimSearch = 70, sampleSize=1000,xyRealDim=0.264,
                                      zRealDim = 0.44, pipeBinSize = 1)
@@
   return(num)}
-
-test1<-GetPropOcData("3-13-19", 0, 0)
-test2<-GetPropOcData("3-13-19", 1, 1)
-
-propOcPA14wt_1.1<-GetImageFiles("/media/whiteley/Seagate Backup Plus Drive/Good images/3-13-19/images1", timepoints = 10, positions = 5)
-propOcPA14wt_2.1<-GetImageFiles("/media/whiteley/Seagate Backup Plus Drive/Good images/3-19-19/images1", timepoints = 10, positions = 5)
-propOcPA14wt_3.1<-GetImageFiles("/media/whiteley/Seagate Backup Plus Drive/Good images/4-17-19/images1", timepoints = 10, positions = 5)
-
-propOcPA14mut_1.1<-GetImageFiles("/media/whiteley/Seagate Backup Plus Drive/Good images/4-24-19/images1", timepoints = 10, positions = 5)
-propOcPA14mut_2.1<-GetImageFiles("/media/whiteley/Seagate Backup Plus Drive/Good images/4-25-19/images1", timepoints = 10, positions = 5)
-propOcPA14mut_3.1<-GetImageFiles("/media/whiteley/Seagate Backup Plus Drive/Good images/5-8-19/images1", timepoints = 10, positions = 5)
-
-write.csv(propOcPA14wt_1.1, file = "/media/whiteley/Seagate Backup Plus Drive/Good images/PropOc Data/results1/PA14wt_1.csv", row.names = FALSE)
-write.csv(propOcPA14wt_2.1, file = "/media/whiteley/Seagate Backup Plus Drive/Good images/PropOc Data/results1/PA14wt_2.csv", row.names = FALSE)
-write.csv(propOcPA14wt_3.1, file = "/media/whiteley/Seagate Backup Plus Drive/Good images/PropOc Data/results1/PA14wt_3.csv", row.names = FALSE)
-
-write.csv(propOcPA14mut_1.1, file = "/media/whiteley/Seagate Backup Plus Drive/Good images/PropOc Data/results1/PA14mut_1.csv", row.names = FALSE)
-write.csv(propOcPA14mut_2.1, file = "/media/whiteley/Seagate Backup Plus Drive/Good images/PropOc Data/results1/PA14mut_2.csv", row.names = FALSE)
-write.csv(propOcPA14mut_3.1, file = "/media/whiteley/Seagate Backup Plus Drive/Good images/PropOc Data/results1/PA14mut_3.csv", row.names = FALSE)
+```
+```{r run them}
+wt1<-GetPropOcData("3-13-19",6,2)
+wt2<-GetPropOcData("3-19-19",6,2)
+wt3<-GetPropOcData("4-17-19",6,2)
+mut1<-GetPropOcData("4-24-19",6,2)
+mut2<-GetPropOcData("4-25-19",6,2)
+mut3<-GetPropOcData("5-8-19",6,2)
 
 ```
+
+```{r Read data files}
+GetGrowthCurveReplicate<- function (sample){
+  bugCounts<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/GrowthCurves/", sample, ".csv"),header = TRUE)
+  bugCounts<- na.omit(bugCounts)
+  bugCounts<-bugCounts %>% mutate(logCFU = log10(CFU))
+  bugCounts$sample<-sample
+  return(bugCounts)
+}
+
+Get3DPropOcData<-function(strain, biologicalRep){
+  propOcData1<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/3D PropOc Data/", strain,biologicalRep,"-1000-",1,".csv"),header = T)
+  propOcData1<-propOcData1 %>% mutate(Strain = strain,BioRep = biologicalRep, RunRep = 1)
+  propOcData2<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/3D PropOc Data/", strain,biologicalRep,"-1000-",2,".csv"),header = T)
+  propOcData2<-propOcData2 %>% mutate(Strain = strain,BioRep = biologicalRep, RunRep = 2)
+  propOcData3<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/3D PropOc Data/", strain,biologicalRep,"-1000-",3,".csv"),header = T)
+  propOcData3<-propOcData3 %>% mutate(Strain = strain,BioRep = biologicalRep, RunRep = 3)
+  allData<-bind_rows(propOcData1,propOcData2,propOcData3)
+  allData<-allData %>% mutate(Relation = recode(source, "finalGG" = "Pa->Pa","finalRG" = "Sa->Pa","finalRR" = "Sa->Sa","finalGR" = "Pa->Sa"))%>%mutate(Condition = recode(Position, "2" = "Pa:Sa 1:1"))%>%mutate(Interaction = recode(source, "finalGG" = "Self","finalRG" = "Other","finalRR" = "Self","finalGR" = "Other"))
+  allData<-allData %>% filter(TimePoint<6 & Distance<30)
+  }
+wt1<-Get3DPropOcData("wt", 1)
+wt1<-wt1 %>% filter(!TimePoint==1 | !RunRep==2)
+wt2<-Get3DPropOcData("wt", 2)
+wt3<-Get3DPropOcData("wt", 3)
+mut1<-Get3DPropOcData("mut", 1)
+mut2<-Get3DPropOcData("mut", 2)
+mut2<-mut2 %>% filter(!TimePoint==3 | !RunRep==2)
+mut3<-Get3DPropOcData("mut", 3)
+mut3<-mut3 %>% filter(!TimePoint==1 | !RunRep==2)
+
+```
+```{r checking the replicate runs}
+PlotPropOcAll <- function(df, name) {
+ggplot()+
+  geom_point(data=df, aes(x=Distance,y=MeanPropOcc, color = Relation, shape = factor(RunRep)),size=4)+
+  facet_wrap(TimePoint~Relation, ncol = 4)+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  labs(title =name)+
+  theme_cowplot()+
+  background_grid()
+}
+PlotPropOcAll(wt1,"wt1")
+PlotPropOcAll(wt2,"wt2")
+PlotPropOcAll(wt3,"wt3")
+PlotPropOcAll(mut1,"mut1 ")
+PlotPropOcAll(mut2,"mut2")
+PlotPropOcAll(mut3,"mut3")
+
+```

### 2020-04-03 R Analysis Scripts/PropOc Data 3D.Rmd
Cleaned out the script and added figures

--- 2020-03-13 R Analysis Scripts/PropOc Data 3D.Rmd
@@
 
-source('/Users/jupabago/Documents/Whiteley/PROJECTS/Rpackage/PropOc Package/R/PropOcFunctions2.0.R') #using the new 3D script with capped spheres.
+source('/Users/jupabago/Documents/Whiteley/PROJECTS/Rpackage/PropOc Package/R/PropOcFunctions2.0.R') 
+#using the new 3D script with capped spheres.
 ```
 
-```{r Get Prop Oc Data}
-GetNewPropOcOralData<-function(sample){
-  imagesFolder<-"/Users/jupabago/Documents/Whiteley/PROJECTS/Oral Penn/Images/WT&Mut&GtfB/"
-  folder<-paste0(imagesFolder, sample, "/combined Bin",sample) 
-  fileList<-list.files(path = folder, full.names = TRUE)
-  fileList2<-fileList[grep("tif",fileList)]
-  propOc<- NormRawPipeline(SlicesTo3D(fileList2,"red"),SlicesTo3D(fileList2,"green"),xydimSearch = 54, zdimSearch = 9,sampleSize = 1000,xyRealDim = 0.156,zRealDim = 0.93, pipeBinSize = 1)
-  return(propOc)
-}
-
-samples = c("WT1","WT2","WT3","Mut1","Mut2","Mut3","GtfB1","GtfB2","GtfB3")
-
-propOcDataList<-map(samples, GetNewPropOcOralData)#get the data
-propOcDataNames<-map2(propOcDataList, samples, ~.x %>% mutate(Sample = .y))#add sample column
-propOcData<-bind_rows(propOcDataNames)#it's aliveeeee
-write.csv(propOcData,"/Users/jupabago/545455Documents/Whiteley/PROJECTS/Oral Penn/Images/WT&Mut&GtfB/ PropOc Data AllData.csv")
-```
-
-```{r PropOc DATA}
-
+```{r functions to get PropOc Data}
 GetPropOcData<-function(sample, timepoints, positions){
-  folder<- paste0('/Volumes/Seagate Backup Plus Drive/Good images/',sample,'/images1')
+  folder<- paste0('/Volumes/Seagate Backup Plus Drive/Good images/',sample,'/imagesSubtractRed')
   growthDf<-data.frame()#data frame to add all timepoints and positions
@@
   return(num)}
-
-test1<-GetPropOcData("3-13-19", 0, 0)
-test2<-GetPropOcData("3-13-19", 1, 1)
-
-propOcPA14wt_1.1<-GetImageFiles("/media/whiteley/Seagate Backup Plus Drive/Good images/3-13-19/images1", timepoints = 10, positions = 5)
-propOcPA14wt_2.1<-GetImageFiles("/media/whiteley/Seagate Backup Plus Drive/Good images/3-19-19/images1", timepoints = 10, positions = 5)
-propOcPA14wt_3.1<-GetImageFiles("/media/whiteley/Seagate Backup Plus Drive/Good images/4-17-19/images1", timepoints = 10, positions = 5)
-
-propOcPA14mut_1.1<-GetImageFiles("/media/whiteley/Seagate Backup Plus Drive/Good images/4-24-19/images1", timepoints = 10, positions = 5)
-propOcPA14mut_2.1<-GetImageFiles("/media/whiteley/Seagate Backup Plus Drive/Good images/4-25-19/images1", timepoints = 10, positions = 5)
-propOcPA14mut_3.1<-GetImageFiles("/media/whiteley/Seagate Backup Plus Drive/Good images/5-8-19/images1", timepoints = 10, positions = 5)
-
-write.csv(propOcPA14wt_1.1, file = "/media/whiteley/Seagate Backup Plus Drive/Good images/PropOc Data/results1/PA14wt_1.csv", row.names = FALSE)
-write.csv(propOcPA14wt_2.1, file = "/media/whiteley/Seagate Backup Plus Drive/Good images/PropOc Data/results1/PA14wt_2.csv", row.names = FALSE)
-write.csv(propOcPA14wt_3.1, file = "/media/whiteley/Seagate Backup Plus Drive/Good images/PropOc Data/results1/PA14wt_3.csv", row.names = FALSE)
-
-write.csv(propOcPA14mut_1.1, file = "/media/whiteley/Seagate Backup Plus Drive/Good images/PropOc Data/results1/PA14mut_1.csv", row.names = FALSE)
-write.csv(propOcPA14mut_2.1, file = "/media/whiteley/Seagate Backup Plus Drive/Good images/PropOc Data/results1/PA14mut_2.csv", row.names = FALSE)
-write.csv(propOcPA14mut_3.1, file = "/media/whiteley/Seagate Backup Plus Drive/Good images/PropOc Data/results1/PA14mut_3.csv", row.names = FALSE)
+```
+```{r run functions}
+wt1<-GetPropOcData("3-13-19",6,2)
+wt2<-GetPropOcData("3-19-19",6,2)
+wt3<-GetPropOcData("4-17-19",6,2)
+mut1<-GetPropOcData("4-24-19",6,2)
+mut2<-GetPropOcData("4-25-19",6,2)
+mut3<-GetPropOcData("5-8-19",6,2)
 
 ```
+```{r Read data files}
+
+Get3DPropOcData<-function(strain, biologicalRep, experiment){
+  propOcData1<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataRedSub1/", strain,biologicalRep,"-1000-",1,".csv"),header = T)
+  propOcData1<-propOcData1 %>% mutate(Strain = strain,BioRep = biologicalRep, RunRep = 1)
+  propOcData2<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataRedSub1/", strain,biologicalRep,"-1000-",2,".csv"),header = T)
+  propOcData2<-propOcData2 %>% mutate(Strain = strain,BioRep = biologicalRep, RunRep = 2)
+  propOcData3<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataRedSub1/", strain,biologicalRep,"-1000-",3,".csv"),header = T)
+  propOcData3<-propOcData3 %>% mutate(Strain = strain,BioRep = biologicalRep, RunRep = 3)
+  allData<-bind_rows(propOcData1,propOcData2,propOcData3)
+  allData<-allData %>%  mutate(CV = SDPropOcc/MeanPropOcc) %>% mutate(Experiment = experiment)
+  allData<-allData %>% 
+    mutate(Relation = recode(source, "finalGG" = "Pa->Pa","finalRG" = "Sa->Pa","finalRR" = "Sa->Sa","finalGR" = "Pa->Sa")) %>%
+    mutate(Condition = recode(Position, "2" = "Pa:Sa 1:1")) %>%
+    mutate(Interaction = recode(source, "finalGG" = "Self","finalRG" = "Other","finalRR" = "Self","finalGR" = "Other")) %>%
+    mutate(FocusSpecies = recode(source, "finalGG" = "Pa","finalRG" = "Sa","finalRR" = "Sa","finalGR" = "Pa")) %>%
+    mutate(TargetSpecies = recode(source, "finalGG" = "Pa","finalRG" = "Pa","finalRR" = "Sa","finalGR" = "Sa")) %>% 
+    mutate(Time = recode(TimePoint, "0" = "Hour 1","1" = "Hour 2","2" = "Hour 3","3" = "Hour 4","4" = "Hour 5","5" = "Hour 6"))
+
+  allData<-allData %>% filter(TimePoint<6 & Distance<30)#last distance is always off for some reason =(
+  }
+
+wt1<-Get3DPropOcData("wt", 1, "wt1")
+wt2<-Get3DPropOcData("wt", 2, "wt2")
+wt3<-Get3DPropOcData("wt", 3, "wt3")
+wt3<-wt3 %>% filter(!RunRep==2|!TimePoint==1)
+
+mut1<-Get3DPropOcData("mut", 1, "mut1")
+mut2<-Get3DPropOcData("mut", 2, "mut2")
+mut3<-Get3DPropOcData("mut", 3, "mut3")
+
+combinedData<-bind_rows(wt1,wt2,wt3,mut1,mut2,mut3)
+combinedData<-combinedData %>% filter(RunRep==1)#I just saw that theyr are all the same, so no point on dragging that much data
+```
+```{r checking the replicate runs}
+PlotPropOcAll <- function(df, name) {
+  ggplot()+
+    geom_point(data=df, aes(x=Distance,y=MeanPropOcc, color = Relation, shape = factor(RunRep)),size=4)+
+    geom_errorbar(data=df, aes(x=Distance,ymin=MeanPropOcc-SDPropOcc,ymax=MeanPropOcc+SDPropOcc, color = Relation, linetype = factor(RunRep)),size=4)+
+    facet_wrap(TimePoint~Relation, ncol = 4)+
+    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    labs(title =name)+
+    theme_cowplot()+
+    background_grid()
+  }
+PlotPropOcAll(wt1,"wt1")
+PlotPropOcAll(wt2,"wt2")
+PlotPropOcAll(wt3,"wt3")
+PlotPropOcAll(mut1,"mut1 ")
+PlotPropOcAll(mut2,"mut2")
+PlotPropOcAll(mut3,"mut3")
+```
+
+```{r Plot comparison of prop oc between Strains}
+ggplot()+
+  geom_point(data = combinedData %>% filter(Relation == "Pa->Pa"),aes(x=Distance,y=MeanPropOcc, color = Strain, shape =factor(BioRep) ),size=4)+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  facet_wrap( ~ TimePoint, ncol = 3)+
+  labs(title ="Pa->Pa")+
+  theme_cowplot()
+
+ggplot()+
+  geom_point(data = combinedData %>% filter(Relation == "Sa->Pa"),aes(x=Distance,y=MeanPropOcc, color = Strain, shape =factor(BioRep) ),size=4)+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  facet_wrap( ~ TimePoint, ncol = 3)+
+  labs(title ="Sa->Pa")+
+  theme_cowplot()
+
+ggplot()+
+  geom_point(data = combinedData %>% filter(Relation == "Pa->Sa"),aes(x=Distance,y=MeanPropOcc, color = Strain, shape =factor(BioRep)),size=4)+
+  facet_wrap( ~ TimePoint, ncol = 3)+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  labs(title ="Pa->Sa")+
+  theme_cowplot()
+
+ggplot()+
+  geom_point(data = combinedData %>% filter(Relation == "Sa->Sa"),aes(x=Distance,y=MeanPropOcc, color = Strain, shape =factor(BioRep) ),size=4)+
+  facet_wrap( ~ TimePoint, ncol = 3)+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  labs(title ="Sa->Sa")+
+  theme_cowplot()
+```
+
+```{r Plot comparing prop oc between time points}
+ggplot()+
+  geom_point(data = combinedData %>% filter(Relation == "Pa->Pa"), aes(x=Distance,y=MeanPropOcc, color = TimePoint) ,size=4)+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  facet_wrap(BioRep ~ Strain, ncol = 2)+
+  labs(title ="Pa->Pa")+
+  theme_cowplot()
+ggplot()+
+  geom_point(data = combinedData %>% filter(Relation == "Sa->Pa"), aes(x=Distance,y=MeanPropOcc, color = TimePoint) ,size=4)+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  facet_wrap(BioRep ~ Strain, ncol = 2)+
+  labs(title ="Sa->Pa")+
+  theme_cowplot()
+ggplot()+
+  geom_point(data = combinedData %>% filter(Relation == "Pa->Sa"), aes(x=Distance,y=MeanPropOcc, color = TimePoint) ,size=4)+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  facet_wrap(BioRep ~ Strain, ncol = 2)+
+  labs(title ="Pa->Sa")+
+  theme_cowplot()
+ggplot()+
+  geom_point(data = combinedData %>% filter(Relation == "Sa->Sa"), aes(x=Distance,y=MeanPropOcc, color = TimePoint) ,size=4)+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  facet_wrap(BioRep ~ Strain, ncol = 2)+
+  labs(title ="Sa->Sa")+
+  theme_cowplot()
+```
+
+```{r Calculating empty space}
+combinedDataEmptySpaceStaph<-combinedData %>% filter(source %in% c("finalRG", "finalRR")) %>% group_by(Distance, TimePoint, Strain, BioRep, RunRep) %>% mutate(EmptySpace =1-MeanPropOcc[source == "finalRG"]-MeanPropOcc[source == "finalRR"])
+
+combinedDataEmptySpacePa<-combinedData %>% filter(source %in% c("finalGG", "finalGR")) %>% group_by(Distance, TimePoint, Strain, BioRep, RunRep) %>% mutate(EmptySpace =1-MeanPropOcc[source == "finalGG"]-MeanPropOcc[source == "finalGR"])
+
+combinedDataEmptySpace<-bind_rows(combinedDataEmptySpaceStaph,combinedDataEmptySpacePa)
+```
+
+```{r Plot Empty space per condition}
+ggplot()+
+  geom_point(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Pa"),aes(x=Distance,y=EmptySpace, color = Strain, shape =factor(BioRep)),size=4)+
+  labs(title ="Empty Space Pa")+
+  facet_wrap(~ TimePoint, ncol = 3)+
+  theme_cowplot()
+
+ggplot()+
+  geom_point(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Sa"),aes(x=Distance,y=EmptySpace, color = Strain, shape =factor(BioRep)),size=4)+
+  labs(title ="Empty Space Sa")+
+  facet_wrap(~ TimePoint, ncol = 3)+
+  theme_cowplot()
+
+```
+```{r Plot Empty space over time}
+ggplot()+
+  geom_point(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Pa"),aes(x=Distance,y=EmptySpace, color = TimePoint),size=4)+
+  labs(title ="Empty Space Pa")+
+  facet_wrap(BioRep~ Strain , ncol = 2)+
+  theme_cowplot()
+
+ggplot()+
+  geom_point(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Sa"),aes(x=Distance,y=EmptySpace, color = TimePoint),size=4)+
+  labs(title ="Empty Space Sa")+
+  facet_wrap(BioRep~ Strain, ncol = 2)+
+  theme_cowplot()
+
+```
+```{r Plot occupancy based on focus}
+ggplot()+
+  geom_line(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Pa" & Strain == "wt"),aes(x=Distance,y=MeanPropOcc, color = Interaction),size=1)+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  labs(title ="Occupied Space around Pa wt",subtitle = "Over time, per biological replicate")+
+  facet_wrap(BioRep ~ Time , ncol = 6)+
+  theme_minimal_grid()
+
+ggplot()+
+  geom_line(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Pa" & Strain == "mut"),aes(x=Distance,y=MeanPropOcc, color = Interaction),size=1)+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  labs(title ="Occupied Space around Pa mut",subtitle = "Over time, per biological replicate")+
+  facet_wrap(BioRep ~ Time , ncol = 6)+
+  theme_minimal_grid()
+
+ggplot()+
+  geom_line(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Sa" & Strain == "wt"),aes(x=Distance,y=MeanPropOcc, color = Interaction),size=1)+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  labs(title ="Occupied Space around Sa wt",subtitle = "Over time, per biological replicate")+
+  facet_wrap(BioRep ~ Time , ncol = 6)+
+  theme_minimal_grid()
+
+ggplot()+
+  geom_line(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Sa" & Strain == "mut"),aes(x=Distance,y=MeanPropOcc, color = Interaction),size=1)+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  labs(title ="Occupied Space around Sa mut",subtitle = "Over time, per biological replicate")+
+  facet_wrap(BioRep ~ Time , ncol = 6)+
+  theme_minimal_grid()
+
+```
+
+```{r Plot empty space and proportional occupancy*}
+#This is a good idea, but I will get back to it later @3/25/20
+ggplot()+
+  geom_point(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Sa"),aes(x=Distance,y=MeanPropOcc, color = Strain, shape = Interaction),size=4)+
+  geom_line(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Sa"),aes(x=Distance,y=EmptySpace, color = Strain),size=4)+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  facet_wrap(~ TimePoint, ncol = 3)+
+  labs(title ="title")+
+  theme_cowplot()
+
+```
+#Statistical exploration of the data.
+Three individual runs were performed independently on each of the experiments.
+The output of each of them is the mean proportional occupancy and it's SD.
+So, if the runs follow a normal distribution, their variance should be similar.
+
+```{r Plot PropOc mean and SD}
+PlotPropOcMeanSD <- function(df, name) {
+  plot1<- ggplot()+
+    geom_linerange(data=df%>% filter(RunRep==1), aes(x=Distance,ymax=MeanPropOcc+SDPropOcc,ymin=MeanPropOcc-SDPropOcc, color = Relation),size=1)+
+    facet_wrap(Time~Relation, ncol = 4)+
+    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    labs(title =paste0(name, " proportional occupancy mean +/- SD"))+
+    theme_minimal_grid()+
+    background_grid()
+  ggsave(paste0(name,".png"),plot = plot1, width = 17, height = 10)
+  }
+
+PlotPropOcMeanSD(wt1, "wt1")
+PlotPropOcMeanSD(wt2, "wt2")
+PlotPropOcMeanSD(wt3, "wt3")
+PlotPropOcMeanSD(mut1, "mut1")
+PlotPropOcMeanSD(mut2, "mut2")
+PlotPropOcMeanSD(mut3, "mut3")
+
+PlotPropOcAllMeanSD <- function(relation) {
+  plot1<- ggplot()+
+    geom_linerange(data=combinedData %>% filter(Relation ==relation), 
+                   aes(x=Distance,ymax=MeanPropOcc+SDPropOcc,ymin=MeanPropOcc-SDPropOcc, color = Strain, linetype =factor(BioRep), group = Experiment),
+                   position = position_dodge(width =.8), size=.7)+
+    facet_wrap(~Time, ncol = 3)+
+    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    labs(title =paste0(relation, " proportional occupancy mean +/- SD"), linetype = "Biological Replicate")+
+    theme_minimal_grid()+
+    background_grid()+
+    theme(plot.title = element_text(hjust = 0.5))
+  ggsave(paste0(relation,".png"),plot = plot1, width = 20, height = 10)
+}
+PlotPropOcAllMeanSD("Pa->Pa")
+PlotPropOcAllMeanSD("Pa->Sa")
+PlotPropOcAllMeanSD("Sa->Sa")
+PlotPropOcAllMeanSD("Sa->Pa")
+```
+Another metric used is the coefficient of variation, CV, which is the ratio of the standard deviation to the mean.So, let's also visualize that.
+```{r Plot CV}
+PlotCVrelation <- function(relation){
+  plot1<-ggplot()+
+    geom_point(data=combinedData %>% filter(Relation =="Pa->Pa"), 
+               aes(x=Distance,y = CV, color = Strain, shape = factor(BioRep), group = Experiment),
+               position = position_dodge(width =.8), size=4)+
+    geom_hline(yintercept = 1, linetype = "dashed")+
+    facet_wrap( ~ Time, ncol = 3)+
+    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    labs(title =paste0(relation, " proportional occupancy Coefficient of variation (SD/mean)"), linetype = "Biological Replicate")+
+    theme_minimal_grid()+
+    background_grid()+
+    theme(plot.title = element_text(hjust = 0.5))
+  ggsave(paste0(relation,"-CV.eps"),plot = plot1, width = 20, height = 10)
+  ggsave(paste0(relation,"-CV.png"),plot = plot1, width = 20, height = 10)
+  }
+PlotCVrelation("Pa->Pa")
+PlotCVrelation("Pa->Sa")
+PlotCVrelation("Sa->Sa")
+PlotCVrelation("Sa->Pa")
+```

### 2020-04-06 R Analysis Scripts/PropOc Data 3D.Rmd
getting full data distributions

@@
 library(rdist)
+library("vcd")#this is fro fitting models to data
+library(viridis)#color palette
+library(gganimate)#gifs for ggplot
 
@@
 So, if the runs follow a normal distribution, their variance should be similar.
-
 ```{r Plot PropOc mean and SD}
@@
 ```
+# Importing whole data sets to identify distribution of data
+```{r whole data sets}
+wt1.1Whole<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataAll/wt1-1000-1.csv"),header = T)
+
+GetHistPropOc <- function(df,timePoint, sources) {
+  data<-df %>%  filter(TimePoint==timePoint) %>% filter(source==sources) %>% group_by(Distance) %>% filter(PropOc <1.02)
+  dataList<-group_split(data)
+  histogramList<-map(dataList, HistogramDistance)
+  output<-bind_rows(histogramList)
+  return(output)
+}
+HistogramDistance <- function(df) {
+  #histogram<- hist(df$PropOc, breaks = seq.int(0,1.02,.01))
+  histogram<- hist(df$PropOc)
+  output<-data.frame(histogram$mids,histogram$counts)
+  colnames(output)<-c("Value", "Frequency")
+  output<-output %>% mutate(Distance = df$Distance[[1]]) %>% filter(!Frequency==0)
+  return(output)
+}
+PlotAllPropOcData <- function(df, relation, timepoint) {
+  ggplot()+
+    geom_point(data = df,aes(x=Value,y=Frequency, color = Distance),size=2)+
+    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    #scale_x_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    labs(title =paste( relation, timepoint))+
+    #scale_color_viridis(option = "D")+
+    scale_color_gradientn(colours = rainbow(5))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+}
+
+test<-wt1.1Whole %>% filter(source=="finalGG") %>% filter(TimePoint==5)
+wt1.RR<-wt1.1Whole %>% filter(source=="finalRR")
+hist(wt1.RR$PropOc)
+hist(wt1.RR$PropOc, breaks = seq.int(0,1.01,.01))
+
+wt1.GG<-GetHistPropOc(wt1.1Whole, 0, "finalGG")
+wt1.RG<-GetHistPropOc(wt1.1Whole, 0, "finalRG")
+wt1.RR<-GetHistPropOc(wt1.1Whole, 0, "finalRR")
+wt1.GR<-GetHistPropOc(wt1.1Whole, 0, "finalGR")
+
+wt1.GG.5<-GetHistPropOc(wt1.1Whole, 5, "finalGG")
+wt1.RG.5<-GetHistPropOc(wt1.1Whole, 5, "finalRG")
+wt1.RR.5<-GetHistPropOc(wt1.1Whole, 5, "finalRR")
+wt1.GR.5<-GetHistPropOc(wt1.1Whole, 5, "finalGR")
+
+PlotAllPropOcData(wt1.GG)
+PlotAllPropOcData(wt1.GR)
+PlotAllPropOcData(wt1.RR)
+PlotAllPropOcData(wt1.RG)
+
+PlotAllPropOcData(wt1.GG.5,5, "finalGG")
+PlotAllPropOcData(wt1.GR.5,5, "finalGR")
+PlotAllPropOcData(wt1.RR.5,5, "finalRG")
+PlotAllPropOcData(wt1.RG.5,5, "finalRG")
+
+```

### 2020-04-22 Matlab scripts/HistogramData.m
matlab scripts

@@ -1,0 +1,98 @@
+slices = 91;
+positions = 5;
+timePoints = 17;
+
+GetHistograms('3-13-19', '62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-13-19', slices,timePoints);
+GetHistograms('3-19-19', '62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-19-19', slices,timePoints);
+GetHistograms('4-17-19', '62x_Salac_Pa14wt_SaPa14wt1-11-10100-110-1_co_SCFM2_tile2x2_4-17-19', slices,timePoints);
+
+function GetHistograms(date, sample, slices,timePoints)
+directory= strcat('/Volumes/Seagate Backup Plus Drive/Good images/',date,'/', sample,'/',sample);
+dataPoints = (slices+1)*(timePoints+1)*4*2;
+output = zeros(dataPoints,17);
+counter = 1;
+for slice= 0:slices
+    for timePoint = 0:timePoints
+        for tile = 0:3
+            name = strcat(directory,'_z',CorrectIndex(slice),'_t',CorrectIndex(timePoint),'_p3_m',num2str(tile),'.tif');
+            [Ir,Ig] = ReadImage(name);
+            output(counter, :) = GetImageData(Ir, 1, slice, timePoint, 3, tile);
+            output(counter+1, :) = GetImageData(Ig, 2, slice, timePoint, 3, tile);
+            counter = counter+2;
+        end
+    end
+end
+fileName = strcat('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/singleImageData/RawImgData_',date,'.csv');
+csvwrite(fileName,output)
+end
+
+function [redImage, greenImage] = ReadImage(file)
+I = imread(file);
+redImage = squeeze(I(:,:,1));
+greenImage = squeeze(I(:,:,2));
+end
+
+
+function imageData = GetImageData(image, channel, slice, timePoint, position, tile )
+[width, height] = size(image);
+numpixels = width *height;
+[imCounts,~ ] = imhist(image);
+zeroInt = imCounts(1);
+zeroPercent = zeroInt/numpixels; 
+maxInt = imCounts(256);
+[~,firstZero] = min(imCounts);
[…]

### 2020-04-22 Matlab scripts/HistogramDataTest.m

@@ -1,0 +1,54 @@
+%{
+I2 = imread('62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-13-19_z00_t01_p3_m2.tif');
+I0 = imread('62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-13-19_z00_t00_p3_m2.tif');
+I10 = imread('62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-13-19_z00_t10_p3_m2.tif');
+I11 = imread('62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-13-19_z11_t00_p3_m2.tif');
+%}
+Ib = imread('62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-13-19_z25_t04_p3_m3.tif');
+%{
+hist0 = imhist(squeeze(I0(:,:,1)));
+hist2 = imhist(squeeze(I2(:,:,1)));
+hist10 = imhist(squeeze(I10(:,:,1)));
+hist11 = imhist(squeeze(I11(:,:,1)));
+
+imageData2 = GetImageData(I2);
+imageData0 = GetImageData(I0);
+imageData10 = GetImageData(I10);
+imageData11 = GetImageData(I11);
+%}
+
+testGetImageHistogram = GetImageHistogram(Ib, 1, 1,1,3,2);
+function histogram = GetImageHistogram(image, channel, slice, timePoint, position, tile )
+[imCounts,imBins ] = imhist(image);
+histogram = [imCounts,imBins, ones(256,1)*channel, ones(256,1)*slice, ones(256,1)*timePoint, ones(256,1)*position, ones(256,1)*tile]; 
+end
+
+function imageData = GetImageData(im)
+image= squeeze(im(:,:,1));
+[width, height] = size(image);
+numpixels = width *height;
+[imCounts,~ ] = imhist(image);
+zeroInt = imCounts(1);
+zeroPercent = zeroInt/numpixels; 
+maxInt = imCounts(256);
+[~,firstZero] = min(imCounts);
+tailEnd = image>=firstZero;%this thresholds the image after the first instance of zero
+numtailEnd = nnz(tailEnd);%This is the amount of pixels beyond the first zero
[…]

### 2020-04-22 Matlab scripts/ImageHistograms.m

@@ -1,0 +1,46 @@
+slices = 91;
+positions = 5;
+timePoints = 17;
+
+GetHistograms('3-13-19', '62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-13-19', slices,timePoints);
+GetHistograms('3-19-19', '62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-19-19', slices,timePoints);
+GetHistograms('4-17-19', '62x_Salac_Pa14wt_SaPa14wt1-11-10100-110-1_co_SCFM2_tile2x2_4-17-19', slices,timePoints);
+
+function GetHistograms(date, sample, slices,timePoints)
+directory= strcat('/Volumes/Seagate Backup Plus Drive/Good images/',date,'/', sample,'/',sample);
+dataPoints = (slices+1)*(timePoints+1)*4*2*256;
+output = zeros(dataPoints,7);
+counter = 1;
+for slice= 0:slices
+    for timePoint = 0:timePoints
+        for tile = 0:3
+            name = strcat(directory,'_z',CorrectIndex(slice),'_t',CorrectIndex(timePoint),'_p3_m',num2str(tile),'.tif');
+            [Ir,Ig] = ReadImage(name);
+            output(counter:counter+255, 1:7) = GetImageHistogram(Ir, 1, slice, timePoint, 3, tile);
+            output(counter+256:counter+511, 1:7) = GetImageHistogram(Ig, 2, slice, timePoint, 3, tile);
+            counter = counter+512;
+        end
+    end
+end
+fileName = strcat('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/singleImageData/Histograms_',date,'.csv');
+csvwrite(fileName,output)
+end
+
+function histogram = GetImageHistogram(image, channel, slice, timePoint, position, tile )
+[imCounts,imBins ] = imhist(image);
+histogram = [imCounts,imBins, ones(256,1)*channel, ones(256,1)*slice, ones(256,1)*timePoint, ones(256,1)*position, ones(256,1)*tile]; 
+end
+
+function [redImage, greenImage] = ReadImage(file)
+I = imread(file);
+redImage = squeeze(I(:,:,1));
+greenImage = squeeze(I(:,:,2));
+end
+
[…]

### 2020-04-22 Matlab scripts/ThresholdingOverTime.m

@@ -1,0 +1,137 @@
+timepoints = 17;
+positions = 5;
+slices = 91;%these are # of slices -1, the number on the file
+path ='/Volumes/Seagate Backup Plus Drive/Good images/';
+
+%This is how to do it with the thresholds calculated from analyzing the
+%thresholds from previous analysis
+%SaThreshold = ones(18,1)*0.2143;%threshold from time 4 
+%SaThreshold = .18154:0.00819:(.18154+0.00819*17);%trial 1 /resultsByTime
+%SaThreshold = .1909:-0.00386:(.1909-0.00386*17);%trial 2 /resultsByTime1
+SaThreshold = .1909:-0.00819:(.1909-0.00819*17);%trial 3 /resultsByTime2
+
+SaThreshold1 = .1909:-0.00819:(.1909-0.00819*17);%trial 4 /resultsByTime3
+SaThreshold2 = .1909:-0.00919:(.1909-0.00919*17);%trial 5 /resultsByTime4
+SaThreshold3 = .1909:-0.01019:(.1909-0.01019*17);%trial 6 /resultsByTime5
+SaThreshold4 = .1909:-0.01119:(.1909-0.01119*17);%trial 7 /resultsByTime6
+
+Pa14wtThreshold = ones(18,1)*0.081486;
+Pa14mutThreshold = ones(18,1)*0.077379;
+
+GetImageDataByTime(path, '3-13-19', '62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-13-19', slices, timepoints, positions, SaThreshold,Pa14wtThreshold);
+GetImageDataByTime(path, '3-19-19', '62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-19-19', slices, timepoints, positions, SaThreshold,Pa14wtThreshold);                                           
+GetImageDataByTime(path, '4-17-19', '62x_Salac_Pa14wt_SaPa14wt1-11-10100-110-1_co_SCFM2_tile2x2_4-17-19', slices, timepoints, positions, SaThreshold,Pa14wtThreshold);
+                                           
[…]

### 2020-04-22 Matlab scripts/ThresholdingTest.m

@@ -1,0 +1,40 @@
+I = imread('62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-13-19_z25_t17_p3_m3.tif');
+%I = imread('rose.tif');
+Ir = squeeze(I(:,:,1));
+Ig = squeeze(I(:,:,2));
+testImageDataR = GetHistogramData(Ir);
+testImageDataG = GetHistogramData(Ig);
+
+function imageData = GetHistogramData(image)
+[width, height] = size(image);
+numpixels = width *height;
+[imBins,imCounts ] = imhist(image);
+zeroInt = imCounts(1);
+maxInt = imCounts(256);
+[~,firstZero] = min(imCounts);
+totalZeroes = nnz(~imCounts);
+level = graythresh(image);
+calculatedG = stretchlim(imBins,imCounts );
+meanIntensity = sum(imCounts.*imBins)/(numpixels);
+imageData = [zeroInt ,maxInt,firstZero,totalZeroes,level,calculatedG,meanIntensity]; 
+end
+
+%{
+IgAdj = imadjust(Ig);
+IrAdj = imadjust(Ir);
+matIg = mat2gray(Ig);
+matIr = mat2gray(Ir);
+[rawThreshG, rawEffG] = graythresh(Ig)
+[adjThreshG, adjEffG] = graythresh(IgAdj)
+[matThreshG, matEffG] = graythresh(matIg)
+[rawThreshR, rawEffR] = graythresh(Ir)
+[adjThreshR, adjEffR] = graythresh(IrAdj)
+[matThreshR, matEffR] = graythresh(matIr)
+lowhighR = stretchlim(Ir)
+lowhighG = stretchlim(Ig)
+histogram(Ir)
+histogram(matIr)
+histogram(IrAdj)
+%}
+
+

### 2020-04-22 Matlab scripts/batchThresholder.m

@@ -1,0 +1,144 @@
+timepoints = 17;
+positions = 5;
+slices = 91;%these are # of slices -1, the number on the file
+path ='/Volumes/Seagate Backup Plus Drive/Good images/';
+
+%This is how to do it with the thresholds calculated from analyzing the
+%thresholds from previous analysis
+%SaThreshold = ones(18,1)*0.2143;%threshold from time 4 
+%SaThreshold = .18154:0.00819:(.18154+0.00819*17);%trial 1 /resultsByTime
+%SaThreshold = .1909:-0.00386:(.1909-0.00386*17);%trial 2 /resultsByTime1
+SaThreshold = .1909:-0.00819:(.1909-0.00819*17);%trial 3 /resultsByTime2
+
+SaThreshold1 = .1909:-0.00819:(.1909-0.00819*17);%trial 4 /resultsByTime3
+SaThreshold2 = .1909:-0.00919:(.1909-0.00919*17);%trial 5 /resultsByTime4
+SaThreshold3 = .1909:-0.01019:(.1909-0.01019*17);%trial 6 /resultsByTime5
+SaThreshold4 = .1909:-0.01119:(.1909-0.01119*17);%trial 7 /resultsByTime6
+SaThreshold5 = .1909:-0.01119:(.1909-0.01219*17);%trial 8 /resultsByTime7
+
+%batchData(path, slices, timepoints, positions, SaThreshold1, 'resultsByTime3')
+%batchData(path, slices, timepoints, positions, SaThreshold2, 'resultsByTime4')
+%batchData(path, slices, timepoints, positions, SaThreshold3, 'resultsByTime5')
+%batchData(path, slices, timepoints, positions, SaThreshold4, 'resultsByTime6')
+batchData(path, slices, timepoints, positions, SaThreshold5, 'resultsByTime7')
+
+Pa14wtThreshold = ones(18,1)*0.081486;
+Pa14mutThreshold = ones(18,1)*0.077379;
+function batchData(path,slices, timepoints, positions, SaThresh, outfolder) 
+GetImageDataByTime(path, '3-13-19', '62x_Salac_Pa14wt_SaPa14wt=1-1,1-10,100-1,10-1_co_SCFM2_tile2x2_3-13-19', slices, timepoints, positions, SaThresh,outfolder);
[…]

### 2020-04-22 R Analysis Scripts/PropOc Data 3D.Rmd
Adding whole data sets to the analysis instead of just the mean and SD

--- 2020-04-03 R Analysis Scripts/PropOc Data 3D.Rmd
@@
 ```
-#Statistical exploration of the data.
+# Statistical exploration of the data.
 Three individual runs were performed independently on each of the experiments.
@@
 ```
+# Importing whole data sets to identify distribution of data
+```{r read whole data sets}
+wt1.1Whole<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataAll/wt1-1000-1.csv"),header = T)
+wt2.1Whole<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataAll/wt2-1000-1.csv"),header = T)
+wt3.1Whole<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataAll/wt3-1000-1.csv"),header = T)
+
+mut1.1Whole<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataAll/mut1-1000-1.csv"),header = T)
+mut2.1Whole<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataAll/mut2-1000-1.csv"),header = T)
+mut3.1Whole<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataAll/mut3-1000-1.csv"),header = T)
+```
+
+```{r functions to get propOc frequency tables}
+HistogramDistance <- function(df) {
+  histogram<- hist(df$PropOc, breaks = seq.int(0,1.02,.01)) 
+  #histogram<- hist(df$PropOc) 
+  output<-data.frame(histogram$mids,histogram$counts)
+  colnames(output)<-c("Value", "Frequency")
+  output<-output %>% mutate(Distance = df$Distance[[1]]) %>% filter(!Frequency==0)
+  return(output)
+}
+GetHistPropOc <- function(df,timePoint, sources) {
+  data<-df %>%  filter(TimePoint==timePoint) %>% filter(source==sources) %>% group_by(Distance) %>% filter(PropOc <1.02)
+  dataList<-group_split(data)
+  histogramList<-map(dataList, HistogramDistance)
+  output<-bind_rows(histogramList)
+  output<-output %>% mutate(Source = sources)
+  return(output)
+}
+PlotAllPropOcData <- function(df, relation, timepoint) {
+  ggplot()+
+    geom_point(data = df,aes(x=Value,y=Frequency, color = Distance),size=2)+
+    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    #scale_x_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    labs(title =paste( relation, timepoint))+
+    #scale_color_viridis(option = "D")+
+    scale_color_gradientn(colours = rainbow(5))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+}
+GetAllHistPropOc <- function(df, timepoint){
+  data.GG<-GetHistPropOc(df, timepoint, "finalGG")
+  data.RG<-GetHistPropOc(df, timepoint, "finalRG")
+  data.RR<-GetHistPropOc(df, timepoint, "finalRR")
+  data.GR<-GetHistPropOc(df, timepoint, "finalGR")
+return(list(data.GG,data.RR,data.RG,data.GR))
+}
+testGetAllHistPropOc<-GetAllHistPropOc(mut3.1Whole,5)
+
+wt1.GG<-GetHistPropOc(wt1.1Whole, 0, "finalGG")
+wt1.RG<-GetHistPropOc(wt1.1Whole, 0, "finalRG")
+wt1.RR<-GetHistPropOc(wt1.1Whole, 0, "finalRR")
+wt1.GR<-GetHistPropOc(wt1.1Whole, 0, "finalGR")
+
+wt1.GG.5<-GetHistPropOc(wt1.1Whole, 5, "finalGG")
+wt1.RG.5<-GetHistPropOc(wt1.1Whole, 5, "finalRG")
+wt1.RR.5<-GetHistPropOc(wt1.1Whole, 5, "finalRR")
+wt1.GR.5<-GetHistPropOc(wt1.1Whole, 5, "finalGR")
+
+PlotAllPropOcData(wt1.GG)
+PlotAllPropOcData(wt1.GR)
+PlotAllPropOcData(wt1.RR)
+PlotAllPropOcData(wt1.RG)
+
+PlotAllPropOcData(wt1.GG.5,5, "PA->PA")
+PlotAllPropOcData(wt1.GR.5,5, "PA->SA")
+PlotAllPropOcData(wt1.RR.5,5, "SA->SA")
+PlotAllPropOcData(wt1.RG.5,5, "SA->PA")
+
+```

### 2020-04-28 R Analysis Scripts/PropOc Data 3D.Rmd
Up to date with Enrichment data from 50 percentile density from whole distributions

@@
 library(gganimate)#gifs for ggplot
+
+lseq <- function(from, to, length.out) {
+  # logarithmic spaced sequence
+  # blatantly stolen from library("emdbook"), because need only this
+  exp(seq(log(from), log(to), length.out = length.out))}
 
@@
 mut3.1Whole<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataAll/mut3-1000-1.csv"),header = T)
+
+wt1.2Whole<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataAll/wt1-1000-2.csv"),header = T)
+wt2.2Whole<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataAll/wt2-1000-2.csv"),header = T)
+wt3.2Whole<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataAll/wt3-1000-2.csv"),header = T)
+
 ```
 
-```{r functions to get propOc frequency tables}
-HistogramDistance <- function(df) {
-  histogram<- hist(df$PropOc, breaks = seq.int(0,1.02,.01)) 
-  #histogram<- hist(df$PropOc) 
-  output<-data.frame(histogram$mids,histogram$counts)
-  colnames(output)<-c("Value", "Frequency")
-  output<-output %>% mutate(Distance = df$Distance[[1]]) %>% filter(!Frequency==0)
-  return(output)
+```{r Whole PropOc frequency functions }
+GetAllHistPropOc <- function(df, timepoint){
+  data.GG<-GetHistPropOc(df, timepoint, "finalGG")
+  data.RG<-GetHistPropOc(df, timepoint, "finalRG")
+  data.RR<-GetHistPropOc(df, timepoint, "finalRR")
+  data.GR<-GetHistPropOc(df, timepoint, "finalGR")
+  allData<- bind_rows(data.GG,data.RR,data.RG,data.GR)
+return(allData)
 }
+
 GetHistPropOc <- function(df,timePoint, sources) {
@@
 }
-PlotAllPropOcData <- function(df, relation, timepoint) {
-  ggplot()+
+HistogramDistance <- function(df) {
+  #histogram<- hist(df$PropOc, breaks = seq.int(0,1.02,.01)) 
+  #histogram<- hist(df$PropOc) 
+  #histogram<- hist(df$PropOc, breaks = c(0,lseq(.001,1.03,100)))
+  histogram<- hist(df$PropOc, breaks = c(0,lseq(.0001,1.03,100)))
+  output<-data.frame(histogram$mids,histogram$counts, histogram$density)
+  colnames(output)<-c("Value", "Frequency", "Density")
+  output<-output %>% mutate(Distance = df$Distance[[1]]) %>% filter(!Frequency==0)
+  return(output)
+}
+
+#Get all of the distributions
+#below are for first run:
+wt1.1Whole.5<-GetAllHistPropOc(wt1.1Whole,5)
+wt2.1Whole.5<-GetAllHistPropOc(wt2.1Whole,5)
+wt3.1Whole.5<-GetAllHistPropOc(wt3.1Whole,5)
+mut1.1Whole.5<-GetAllHistPropOc(mut1.1Whole,5)
+mut2.1Whole.5<-GetAllHistPropOc(mut2.1Whole,5)
+mut3.1Whole.5<-GetAllHistPropOc(mut3.1Whole,5)
+#second run
+wt1.2Whole.5<-GetAllHistPropOc(wt1.2Whole,5)
+wt2.2Whole.5<-GetAllHistPropOc(wt2.2Whole,5)
+wt3.2Whole.5<-GetAllHistPropOc(wt3.2Whole,5)
+
+#log sequence
+wt1.1Whole.5log<-GetAllHistPropOc(wt1.1Whole,5)  
+wt2.1Whole.5log<-GetAllHistPropOc(wt2.1Whole,5)
+wt3.1Whole.5log<-GetAllHistPropOc(wt3.1Whole,5)
+mut1.1Whole.5log<-GetAllHistPropOc(mut1.1Whole,5)
+mut2.1Whole.5log<-GetAllHistPropOc(mut2.1Whole,5)
+mut3.1Whole.5log<-GetAllHistPropOc(mut3.1Whole,5)
+
+#log starting at .0001
+wt1.1Whole.5log2<-GetAllHistPropOc(wt1.1Whole,5)  
+wt2.1Whole.5log2<-GetAllHistPropOc(wt2.1Whole,5)
+wt3.1Whole.5log2<-GetAllHistPropOc(wt3.1Whole,5)
+mut1.1Whole.5log2<-GetAllHistPropOc(mut1.1Whole,5)
+mut2.1Whole.5log2<-GetAllHistPropOc(mut2.1Whole,5)
+mut3.1Whole.5log2<-GetAllHistPropOc(mut3.1Whole,5)
+```
+
+```{r Whole PropOc frequency Figures}
+PlotAllPropOcData <- function(df, timepoint, relation ) {
+  plot<-ggplot()+ 
     geom_point(data = df,aes(x=Value,y=Frequency, color = Distance),size=2)+
@@
     scale_color_gradientn(colours = rainbow(5))+
+    xlim(0,1)+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+  name<-paste0(relation, ".hour", timepoint,".png")
+  ggsave(paste0(name),plot = plot, width = 17, height = 10)
+}
+
+PlotAllPropOcData(wt1.1Whole.5 %>% filter (Source == "finalGG"), 5, "Wt 1-1 PA->PA")
+PlotAllPropOcData(wt2.1Whole.5 %>% filter (Source == "finalGG"), 5, "Wt 2-1 PA->PA")
+PlotAllPropOcData(wt3.1Whole.5 %>% filter (Source == "finalGG"), 5, "Wt 3-1 PA->PA")
+
+PlotAllPropOcData(wt1.2Whole.5 %>% filter (Source == "finalGG"), 5, "Wt 1-2 PA->PA")
+PlotAllPropOcData(wt2.2Whole.5 %>% filter (Source == "finalGG"), 5, "Wt 2-2 PA->PA")
+PlotAllPropOcData(wt3.2Whole.5 %>% filter (Source == "finalGG"), 5, "Wt 3-2 PA->PA")
+
+PlotAllPropOcData(mut1.1Whole.5 %>% filter (Source == "finalGG"), 5, "Mut 1-1 PA->PA")
+PlotAllPropOcData(mut2.1Whole.5 %>% filter (Source == "finalGG"), 5, "Mut 2-1 PA->PA")
+PlotAllPropOcData(mut3.1Whole.5 %>% filter (Source == "finalGG"), 5, "Mut 3-1 PA->PA")
+
+PlotAllPropOcData(wt1.1Whole.5 %>% filter (Source == "finalRG"), 5, "Wt 1-1 SA->PA")
+PlotAllPropOcData(wt2.1Whole.5 %>% filter (Source == "finalRG"), 5, "Wt 2-1 SA->PA")
+PlotAllPropOcData(wt3.1Whole.5 %>% filter (Source == "finalRG"), 5, "Wt 3-1 SA->PA")
+
+PlotAllPropOcData(wt1.2Whole.5 %>% filter (Source == "finalRG"), 5, "Wt 1-2 SA->PA")
+PlotAllPropOcData(wt2.2Whole.5 %>% filter (Source == "finalRG"), 5, "Wt 2-2 SA->PA")
+PlotAllPropOcData(wt3.2Whole.5 %>% filter (Source == "finalRG"), 5, "Wt 3-2 SA->PA")
+
+PlotAllPropOcData(mut1.1Whole.5 %>% filter (Source == "finalRG"), 5, "Mut1-1 SA->PA")
+PlotAllPropOcData(mut2.1Whole.5 %>% filter (Source == "finalRG"), 5, "Mut2-1 SA->PA")
+PlotAllPropOcData(mut3.1Whole.5 %>% filter (Source == "finalRG"), 5, "Mut3-1 SA->PA")
+
+PlotAllPropOcData(wt1.1Whole.5 %>% filter (Source == "finalRR"), 5, "Wt 1-1 SA->SA")
+PlotAllPropOcData(wt2.1Whole.5 %>% filter (Source == "finalRR"), 5, "Wt 2-1 SA->SA")
+PlotAllPropOcData(wt3.1Whole.5 %>% filter (Source == "finalRR"), 5, "Wt 3-1 SA->SA")
+
+PlotAllPropOcData(mut1.1Whole.5 %>% filter (Source == "finalRR"), 5, "Mut1-1 SA->SA")
+PlotAllPropOcData(mut2.1Whole.5 %>% filter (Source == "finalRR"), 5, "Mut2-1 SA->SA")
+PlotAllPropOcData(mut3.1Whole.5 %>% filter (Source == "finalRR"), 5, "Mut3-1 SA->SA")
+
+PlotAllPropOcData(wt1.1Whole.5 %>% filter (Source == "finalGR"), 5, "Wt 1-1 PA->SA")
+PlotAllPropOcData(wt2.1Whole.5 %>% filter (Source == "finalGR"), 5, "Wt 2-1 PA->SA")
+PlotAllPropOcData(wt3.1Whole.5 %>% filter (Source == "finalGR"), 5, "Wt 3-1 PA->SA")
+
+PlotAllPropOcData(mut1.1Whole.5 %>% filter (Source == "finalGR"), 5, "Mut1-1 PA->SA")
+PlotAllPropOcData(mut2.1Whole.5 %>% filter (Source == "finalGR"), 5, "Mut2-1 PA->SA")
+PlotAllPropOcData(mut3.1Whole.5 %>% filter (Source == "finalGR"), 5, "Mut3-1 PA->SA")
+
+#Honestly, they all look pretty much the same...
+#let's try doing the bins in an exponential function...
+PlotAllPropOcDatalog <- function(df, timepoint, relation ) {
+  plot<-ggplot()+ 
+    geom_point(data = df,aes(x=Value,y=Frequency, color = Distance),size=2)+
+    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = (c(1,1001)))+
+    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = (c(0.0005,1)))+
+    labs(title =paste( relation, timepoint))+
+    #scale_color_viridis(option = "D")+
+    scale_color_gradientn(colours = rainbow(5))+
+    #xlim(0,1)+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+  name<-paste0(relation, ".hour", timepoint,"(log).png")
+  ggsave(paste0(name),plot = plot, width = 17, height = 10)
+}
+
+PlotAllPropOcDatalog(wt1.1Whole.5log %>% filter (Source == "finalRG"), 5, "Wt 1-1 SA->PA")
+PlotAllPropOcDatalog(wt2.1Whole.5log %>% filter (Source == "finalRG"), 5, "Wt 2-1 SA->PA")
+PlotAllPropOcDatalog(wt3.1Whole.5log %>% filter (Source == "finalRG"), 5, "Wt 3-1 SA->PA")
+
+PlotAllPropOcDatalog(mut1.1Whole.5log %>% filter (Source == "finalRG"), 5, "Mut1-1 SA->PA")
+PlotAllPropOcDatalog(mut2.1Whole.5log %>% filter (Source == "finalRG"), 5, "Mut2-1 SA->PA")
+PlotAllPropOcDatalog(mut3.1Whole.5log %>% filter (Source == "finalRG"), 5, "Mut3-1 SA->PA")
+
+PlotAllPropOcDatalog(wt1.1Whole.5log %>% filter (Source == "finalGR"), 5, "Wt 1-1 PA->SA")
+PlotAllPropOcDatalog(wt2.1Whole.5log %>% filter (Source == "finalGR"), 5, "Wt 2-1 PA->SA")
+PlotAllPropOcDatalog(wt3.1Whole.5log %>% filter (Source == "finalGR"), 5, "Wt 3-1 PA->SA")
+
+PlotAllPropOcDatalog(mut1.1Whole.5log %>% filter (Source == "finalGR"), 5, "Mut1-1 PA->SA")
+PlotAllPropOcDatalog(mut2.1Whole.5log %>% filter (Source == "finalGR"), 5, "Mut2-1 PA->SA")
+PlotAllPropOcDatalog(mut3.1Whole.5log %>% filter (Source == "finalGR"), 5, "Mut3-1 PA->SA")
+
+```
+
+```{r Whole PropOc Data wrangling}
+#So, I think the first thing to do would be to get a "mode", or the highest value for frequency of proportional occupancy per distance.
+#at this point I can see at least if the zone of interest is the same for every sample.
+
+GetMaxDensity <- function(df) {#this one is essentially the same as the one below, but thos one doesnt allow repeated max density values
+  df.summary<-df %>% mutate(Density = Frequency/1000) %>% #this is to make it be from 0 to 1
+    group_by(Distance, Source) %>% select(Value, Distance,Density, Source) %>% summarise(DensestValue = Value [Density ==max(Density)], MaxDensity = max(Density))
+  return(df.summary)
+}
+
+DensityCheck <- function(df) {
+  df.summary<-df %>% 
+    mutate(Density = Frequency/1000) %>% #this is to make it be from 0 to 1
+    group_by(Distance, Source) %>% select(Value, Distance,Density, Source) %>% 
+    mutate(MaxDensity = max(Density)) %>% 
+    mutate(DensityCh = ifelse(Density ==max(Density), 1, 0 )) %>% filter(DensityCh==1) %>% ungroup()#find max density, check where it matches
+  df.summary<-df.summary %>% group_by(Distance, Source) %>% mutate(DoubledValues = sum(DensityCh))#this is just to find which values were repeated
+  return(df.summary)
+}
+
+ProcessDensities <- function(histograms) {
+histogramNames<- c("wt1.1","wt2.1","wt3.1","mut1.1","mut2.1","mut3.1")
+mappedDensities<-map(histograms,DensityCheck)
+namedMappedDensities<-map2(mappedDensities, histogramNames, ~.x %>% mutate(Sample = .y))
+allDensities<-bind_rows(namedMappedDensities)
+allDensities<-allDensities %>% ungroup() %>% 
+  mutate(Strain = recode(allDensities$Sample, wt1.1="wt",wt2.1="wt",wt3.1="wt",mut1.1="mut",mut2.1="mut",mut3.1="mut"))
+return(allDensities)}
+
+histograms<- list(wt1.1Whole.5,wt2.1Whole.5,wt3.1Whole.5,mut1.1Whole.5,mut2.1Whole.5,mut3.1Whole.5)
+histogramslog<- list(wt1.1Whole.5log,wt2.1Whole.5log,wt3.1Whole.5log,mut1.1Whole.5log,mut2.1Whole.5log,mut3.1Whole.5log)
+histogramslog2<- list(wt1.1Whole.5log2,wt2.1Whole.5log2,wt3.1Whole.5log2,mut1.1Whole.5log2,mut2.1Whole.5log2,mut3.1Whole.5log2)
+
+allDensitiesFunctions<-ProcessDensities(histograms)
+allDensitiesLog<-ProcessDensities(histogramslog)
+allDensitiesLog2<-ProcessDensities(histogramslog2)
+```
+
+```{r Whole Prop Freq Figures}
+PlotMaxDensities <- function(df) {
+  ggplot()+
+    geom_jitter(data = df,aes(y=Value, color=Density,x = Distance, shape = Sample),size=2)+
+    labs(title ="Maximum Density")+
+    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_wrap( ~ Source, ncol = 2)+
+    scale_color_gradientn(colours = rainbow(5))+
+    scale_shape_manual(values=c(0,1,2, 15,16,17))+
     theme_cowplot()+
@@
 }
-GetAllHistPropOc <- function(df, timepoint){
-  data.GG<-GetHistPropOc(df, timepoint, "finalGG")
-  data.RG<-GetHistPropOc(df, timepoint, "finalRG")
-  data.RR<-GetHistPropOc(df, timepoint, "finalRR")
-  data.GR<-GetHistPropOc(df, timepoint, "finalGR")
-return(list(data.GG,data.RR,data.RG,data.GR))
+PlotMaxDensities(allDensities)
+PlotMaxDensities(allDensitiesFunctions %>% filter(Source=="finalRG"))
+PlotMaxDensities(allDensitiesLog)
+PlotMaxDensities(allDensitiesLog2)
+```
+#Calculating 50 percentile density.
+```{r death curves Functions and data}
+getDeathCurve<-function(df){
+  totalFrequency = sum(df$Frequency)
+  currentFrequency = 0
+  for (i in 1 : nrow(df)){
+    addedFrequency<-totalFrequency-currentFrequency
+    df[i,6]<-addedFrequency
+    currentFrequency = currentFrequency+df[i,2]
   }
-testGetAllHistPropOc<-GetAllHistPropOc(mut3.1Whole,5)
+  colnames(df)<-c("Value","Frequency","Density", "Distance", "Source","Decay")
+  df<-df %>% mutate (normDecay = 100*(Decay - min(Decay)) / (max(Decay) - min(Decay)))
+  return(df)
+  }
+processData<-function(df){
+  allData<-df %>% group_by(Distance, Source)
+  yas<- group_split(allData)
+  mappedData<-map(yas, getDeathCurve)
+  boundData<-bind_rows(mappedData)
+}
+GetPercentiles<-function(histograms){
+  histogramNames<- c("wt1.1","wt2.1","wt3.1","mut1.1","mut2.1","mut3.1")
+  mappedDensities<-map(histograms,processData)
+  namedMappedDensities<-map2(mappedDensities, histogramNames, ~.x %>% mutate(Sample = .y))
+  allDensities<-bind_rows(namedMappedDensities)
+  allDensities<-allDensities %>% ungroup() %>% 
+    mutate(Strain = recode(allDensities$Sample, wt1.1="wt",wt2.1="wt",wt3.1="wt",mut1.1="mut",mut2.1="mut",mut3.1="mut"))
+return(allDensities)}
 
-wt1.GG<-GetHistPropOc(wt1.1Whole, 0, "finalGG")
-wt1.RG<-GetHistPropOc(wt1.1Whole, 0, "finalRG")
-wt1.RR<-GetHistPropOc(wt1.1Whole, 0, "finalRR")
-wt1.GR<-GetHistPropOc(wt1.1Whole, 0, "finalGR")
+PlotPercentiles <- function(df) {
+  ggplot()+
+    geom_point(data = df,aes(y=Value, color=Percentile50,x = Distance, shape = Sample),size=2)+
+    #geom_pointrange(data = df,aes(x = Distance,y=meanValue,ymax=meanValue+SdValue,ymin=meanValue-SdValue, color=Strain),size=2)+
+    labs(title ="50 percentile Density")+
+    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_wrap( ~ Source, ncol = 2)+
+    scale_color_gradientn(colours = rainbow(5))+
+    scale_shape_manual(values=c(0,1,2, 15,16,17))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+  }
 
-wt1.GG.5<-GetHistPropOc(wt1.1Whole, 5, "finalGG")
-wt1.RG.5<-GetHistPropOc(wt1.1Whole, 5, "finalRG")
-wt1.RR.5<-GetHistPropOc(wt1.1Whole, 5, "finalRR")
-wt1.GR.5<-GetHistPropOc(wt1.1Whole, 5, "finalGR")
+allDeathCurvesLog2<-GetPercentiles(histogramslog2)
+#there are, I believe, at least 3 ways to find the 50 percentile.
+one of them is finidng the closest value, regardless of where it comes from, whether it is higher or lower than 50 percentile.
+The other two are either taking the closest to 50, either exclusively larger or exclusively smaller than that.
+That's why there are 3 ways of doing this here:
 
-PlotAllPropOcData(wt1.GG)
-PlotAllPropOcData(wt1.GR)
-PlotAllPropOcData(wt1.RR)
-PlotAllPropOcData(wt1.RG)
+#this is the closest to absolute value 50
+allDeathCurvesLog2midAbs <- allDeathCurvesLog2 %>% group_by(Sample, Distance, Source) %>% 
+  mutate(Percentile50 = min(abs(normDecay - 50)))%>% 
+  mutate(DensityCh = ifelse(Percentile50 ==abs(normDecay - 50), 1, 0 )) %>% filter(DensityCh==1) %>% mutate(DoubledValues = sum(DensityCh)) %>% ungroup()#find max density, check where it matches
 
-PlotAllPropOcData(wt1.GG.5,5, "PA->PA")
-PlotAllPropOcData(wt1.GR.5,5, "PA->SA")
-PlotAllPropOcData(wt1.RR.5,5, "SA->SA")
-PlotAllPropOcData(wt1.RG.5,5, "SA->PA")
+#this is coming from the highest value
+allDeathCurvesLog2topAbs <- allDeathCurvesLog2 %>% group_by(Sample, Distance, Source) %>% 
+  mutate(Percentile50 = (normDecay - 50)) %>% filter (Percentile50>0) %>% filter(Percentile50==min(Percentile50)) %>%  
+  mutate(DensityCh = ifelse(Percentile50 ==(normDecay - 50), 1, 0 )) %>% filter(DensityCh==1) %>% 
+  mutate(DoubledValues = sum(DensityCh)) %>% ungroup()#find max density, check where it matches
+
+#this is coming from the lowest value
+allDeathCurvesLog2bottomAbs <- allDeathCurvesLog2 %>% group_by(Sample, Distance, Source) %>% 
+  mutate(Percentile50 = (50 -normDecay)) %>% filter (Percentile50>0) %>% filter(Percentile50==min(Percentile50)) %>%  
+  mutate(DensityCh = ifelse(Percentile50 ==(50 - normDecay), 1, 0 )) %>% filter(DensityCh==1) %>% 
+  mutate(DoubledValues = sum(DensityCh)) %>% ungroup()#find max density, check where it matches
+
+#Plotting and comparing all 3
+PlotPercentiles(allDeathCurvesLog2midAbs)
+PlotPercentiles(allDeathCurvesLog2topAbs)
+PlotPercentiles(allDeathCurvesLog2bottomAbs)
+#they all look fine, so I'll just stick with the first one
+
+#this looks kind of ok... what is the mean and sd?
+allDeathCurvesLog2midAbsStats<-allDeathCurvesLog2midAbs %>% group_by(Strain, Distance, Source) %>% mutate(LogValue = log10(Value)) %>% mutate(meanValue = mean(Value), sdValue = sd(Value), meanLogValue = mean(LogValue),sdLogValue = sd(LogValue))
+PlotPercentiles(allDeathCurvesLog2midAbsStats)
+
+ggplot()+#linear
+    #geom_point(data = df,aes(y=Value, color=Percentile50,x = Distance, shape = Sample),size=2)+
+    geom_pointrange(data = allDeathCurvesLog2midAbsStats,aes(x = Distance,y=meanValue,ymax=meanValue+sdValue,ymin=meanValue-sdValue, color=Strain),size=.5)+
+    labs(title ="50 percentile Density")+
+    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_wrap( ~ Source, ncol = 2)+
+    #scale_color_gradientn(colours = rainbow(5))+
+    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+
+ggplot()+#log transform
+    geom_pointrange(data = allDeathCurvesLog2midAbsStats,aes(x = Distance,y=meanLogValue,ymax=meanLogValue+sdLogValue,ymin=meanLogValue-sdLogValue, color=Strain),size=.5)+
+    labs(title ="50 percentile Density (Log)")+
+    facet_wrap( ~ Source, ncol = 2)+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+```
+#Enrichment (distance at highest proportional occupancy)
+```{r Enrichment}
+#find the max proportional occupancy value from the 50 percentile
+
+allDeathCurvesLog2midAbsEnrichment<- allDeathCurvesLog2midAbs %>% group_by(Sample, Source)%>%select(Value, Distance, Source,Sample, Strain, Percentile50) %>% mutate(Enrichment = max(Value)) %>%
+  mutate(EnrichmentCh = ifelse(Enrichment == Value, 1, 0 )) %>% filter(EnrichmentCh==1) %>% mutate(DoubledValues = sum(EnrichmentCh)) %>% ungroup()#find max
+
+PlotEnrichment <- function(df) {
+ggplot()+#first run
+    geom_point(data = df,aes(y=Distance, x = Sample, color = Enrichment, shape = Sample),size=2)+
+    labs(title ="50 percentile Enrichment")+
+    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_wrap( ~ Source, ncol = 2)+
+    scale_color_gradientn(colours = rainbow(5))+
+    scale_shape_manual(values=c(0,1,2, 15,16,17))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+}
+
+PlotDataEnrichmentEmphasis <- function(wholeData, EnrichmentData) {
+ggplot()+#including rest of the data
+  geom_point(data = wholeData,aes(y=Value, color=Percentile50,x = Distance, shape = Sample),size=2)+
+  geom_point(data = EnrichmentData,aes(y=Value, color=Percentile50,x = Distance, shape = Sample),size=5)+
+  labs(title ="50 percentile Density (Enrichment emphasis)")+
+  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  facet_wrap( ~ Source, ncol = 2)+
+  scale_color_gradientn(colours = rainbow(5))+
+  scale_shape_manual(values=c(0,1,2, 15,16,17))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+}
+
+PlotEnrichment(allDeathCurvesLog2midAbsEnrichment)
+PlotDataEnrichmentEmphasis(allDeathCurvesLog2midAbs,allDeathCurvesLog2midAbsEnrichment)
+
+#That looks like a lot of the values are just at 0.5 distance, which I dont really care, I can make another argument about direct contact, so I'll filter those out...
+allDeathCurvesLog2midAbsEnrichment2<- allDeathCurvesLog2midAbs %>% filter(!Distance ==0.5)%>% 
+  group_by(Sample, Source) %>% select(Value, Distance, Source,Sample, Strain, Percentile50) %>% mutate(Enrichment = max(Value)) %>%
+  mutate(EnrichmentCh = ifelse(Enrichment == Value, 1, 0 )) %>% filter(EnrichmentCh==1) %>% mutate(DoubledValues = sum(EnrichmentCh)) %>% ungroup()#find max
+
+PlotEnrichment(allDeathCurvesLog2midAbsEnrichment2)
+PlotDataEnrichmentEmphasis(allDeathCurvesLog2midAbs,allDeathCurvesLog2midAbsEnrichment2)
+
+#This looks a little better... now get the mean per condition
+allDeathCurvesLog2midAbsEnrichment2<-allDeathCurvesLog2midAbsEnrichment2 %>% group_by(Source, Sample) %>% mutate(EnrichmentDistance = mean(Distance)) %>% ungroup() %>% group_by(Source, Strain) %>% mutate(meanEnrichment = mean(EnrichmentDistance), sdEnrichment = sd(EnrichmentDistance))
+
+ggplot()+
+    geom_point(data = allDeathCurvesLog2midAbsEnrichment2,aes(y=meanEnrichment, x = Strain, color = Strain),size=4)+
+    geom_errorbar(data = allDeathCurvesLog2midAbsEnrichment2,
+                  aes(ymin = meanEnrichment-sdEnrichment,ymax = meanEnrichment+sdEnrichment, x = Strain, color = Strain),size=1)+
+    geom_jitter(data = allDeathCurvesLog2midAbsEnrichment2,aes(y=Distance, x = Strain, color = Strain, shape = Sample),size=2)+
+    labs(title ="50 percentile Enrichment by strain")+
+    facet_wrap( ~ Source, ncol = 2)+
+    #scale_color_gradientn(colours = rainbow(5))+
+    scale_shape_manual(values=c(0,1,2, 15,16,17))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
 

### 2020-04-30 Microscopy Data.Rmd
Adding red subtracted data

@@
 
+#Images with new threshold
+This threshold is the one calculated with the average of all the conditions
 ```{r new threshold images}
@@
 GetResults<-function(sample, samplename){
-  #folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Threshold by time/',sample,'/resultsByTime')
-  folder<- paste0('/Volumes/Seagate Backup Plus Drive/Good images/',sample,'/resultsByTime6')
+  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Threshold by time/',sample,'/resultsByTime6')
+  #folder<- paste0('/Volumes/Seagate Backup Plus Drive/Good images/',sample,'/resultsByTime6')
   fileList<-list.files(path = folder, full.names = TRUE)
@@
 ggplot()+
-  geom_line(data=linearThresholdGrowthCurves%>% filter(Species == "Sa") %>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=LogTotals,color = source), size=2)+
+  geom_line(data=linearThresholdGrowthCurves%>% filter(Species == "Sa") %>% 
+              filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=LogTotals,color = source), size=2)+
   facet_grid(Strain~Sample)+
@@
 
+```{r Pa Growth curves from RedSubtracted Images}
+#This will give us a sense on how much of the Pa data was erased because it overlapped with the Sa data.
+GetResults<-function(sample, samplename){
+  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/RedSubtractedImages/',sample,'/resultsSubtractRed1')
+  #folder<- paste0('/Volumes/Seagate Backup Plus Drive/Good images/',sample,'/resultsByTime6')
+  fileList<-list.files(path = folder, full.names = TRUE)
+  growthDf<-data.frame()
+  #for (position in 2:3){
+  #  currentPosition<-fileList[grep(paste0("p",position,"."),fileList)]
+  currentPosition<-fileList[grep(paste0("p2."),fileList)]
+    for (timepoint in 0:6){
+      currentTimePoint<-currentPosition[grep(paste0("t",GetNumber(timepoint),"_"),currentPosition)]
+      growthDf<-rbind(growthDf,ReadResultsFile(currentTimePoint, 2, timepoint))
+      #growthDf<-rbind(growthDf,ReadResultsFile(currentTimePoint, position, timepoint))
+      }
+    #}
+  growthDf<-growthDf %>% mutate(Sample = samplename)
+return(growthDf)
+}
+
+redSubtractedData<-ProcessResults()#This was run using the "GetResults" function at the top..
+paRedSubtractResults<-redSubtractedData[[1]]%>% filter(Species == "Pa") %>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut"))
+nonSubtractedData<-ProcessResults()
+paNonSubtractResults<-nonSubtractedData[[1]]%>% filter(Species == "Pa") %>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut"))
+
+ggplot()+
+  geom_line(data=redSubtractedData[[1]]%>% filter(Species == "Pa") %>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=LogTotals),color = "red", size=2)+
+  geom_line(data=nonSubtractedData[[1]]%>% filter(Species == "Pa") %>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=LogTotals),color ="blue", size=2)+
+  facet_grid(Strain~Sample)+
+  theme_cowplot(12)
+
+ggplot()+
+  geom_line(data=redSubtractedData[[2]]%>% filter(Species == "Pa") %>% 
+              filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=MeanLogTotals,color = Strain), size=2)+
+  theme_cowplot(12)
+
+```
 #Functions for histograms

### 2020-05-27 SaPa TOB growth curves clean.Rmd
Added comments from Marvin to figures

@@
 #End point bar graph with std error
-ggplot() +
+tobCFUPlot<-ggplot() +
   geom_col(data = wilcoxDataGood, aes (x = culture, y = meanLog, fill = antibiotic, group = antibiotic), position = position_dodge( ))+
   geom_linerange(data = wilcoxDataGood, aes(x = culture, ymin = meanLog - seLog, ymax = meanLog + seLog,group = antibiotic),position = position_dodge(width = .9))+
-  scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)))+
-  labs(title =expression(paste(italic("S. aureus"), " growth at 5 hours")),y = "Log10 CFUs", x = "Culture condition") +
+  scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)), breaks = c(0,2,4,6,8,10), labels =c(0,2,4,6,8,10))+
+  scale_x_discrete(name ="", breaks = c("mono","wt","mut"), labels =c("mono","co w/wild-type",expression("co w/"*Delta*"pqsL")))+
+  labs(y = expression(paste(Log[10], " CFU")), x = "", fill = "") +
   scale_fill_grey()+
@@
 
-ggplot() +
+tobPercentChangePlot<-ggplot() +
   geom_col(data = percentChange %>% filter(sample == "1-25-20"), aes (x = culture, y = MeanLogKill))+
@@
   scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)))+
-  labs(title =expression(paste(italic("S. aureus"), " killing by Tobramycin")),y = "Log10 kill", x = "Culture condition") +
+  scale_x_discrete(name ="", breaks = c("mono","wt","mut"), labels =c("mono","co w/wild-type",expression("co w/"*Delta*"pqsL")))+
+  labs(y = expression(paste(Log[10], " CFU")), x = "") +
   scale_fill_grey()+
@@
 
+prow <- plot_grid(tobCFUPlot+theme(legend.position="none"),tobPercentChangePlot+theme(legend.position="none"),align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)
+legend <- get_legend(tobCFUPlot + theme(legend.box.margin = margin(0, 0, 0, -6)))
+plot_grid(prow,legend,rel_widths = c(3, .4))
 ```

### 2020-05-28 Staph killing assays/Staph killing report.Rmd
staph killing assays data and scripts, Figure 2 of paper

---
title: "Staph killing assays"
author: "Juan P Barraza"
date: "1/15/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(magrittr)
library(ggplot2)
library(dplyr)
library(cowplot)
library(scales)
library(tidyr)
library(growthcurver)
library(plotrix)

diskFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/pqsL SCFM2/Staph killing assays/disk difussion assays.csv"
diskData <-read.csv(diskFile)
diskData$strain <- factor(diskData$strain, levels = c("wt", "pqsl"))
diskData <- diskData %>% mutate(val1 = value1-6,val2 = value2-6,average = (val1+val2)/2 )#this removes the diameter of the disks
diskDataStats<-diskData %>% group_by(strain, condition, bio.rep) %>% summarise(meanTech = mean(average)) %>% ungroup() %>%group_by(strain, condition) %>% summarise(meanBio = mean(meanTech), SDBio = std.error(meanTech))
diskDataStats$strain <- factor(diskDataStats$strain, levels = c("wt", "pqsl"))
diskDataStats1<-diskDataStats %>% mutate(
  CondStrain = case_when(
    condition == "shaking" & strain == "pqsl" ~ "pqsLShake",
    condition == "shaking" & strain == "wt"~ "wtShake",
    condition == "static" & strain == "pqsl"~ "pqsLStat",
    condition == "static" & strain == "wt"~ "wtStat"))

diskWtShaking<-diskData %>% filter(strain == "wt" & condition == "shaking")
diskMutShaking<-diskData %>% filter(strain == "pqsl" & condition == "shaking")
diskWtStatic<-diskData %>% filter(strain == "wt" & condition == "static")
diskMutStatic<-diskData %>% filter(strain == "pqsl" & condition == "static")

#there is no rep 1 for mutant strain, so remove first one from wt to make paired t-test
diskWtStatic1<-diskData %>% filter(strain == "wt" & condition == "static") %>% filter(!bio.rep==1)
diskWtShaking1<-diskData %>% filter(strain == "wt" & condition == "shaking")%>% filter(!bio.rep==1)

#t-tests
diskWtTtest<-t.test(x = diskWtShaking$avg, y = diskWtStatic$avg, paired = T)
diskMutTtest<-t.test(x = diskMutShaking$avg, y = diskMutStatic$avg, paired = T)
diskShakingTtest<-t.test(x = diskWtShaking1$avg, y = diskMutShaking$avg, paired = T)
diskStaticTtest<-t.test(x = diskMutStatic$avg, y = diskWtStatic1$avg, paired = T)
diskWtStaticMutShakingTtest<-t.test(x = diskMutShaking$avg, y = diskWtStatic1$avg, paired = T)
tTestData<-list(diskWtTtest, diskMutTtest,diskShakingTtest, diskStaticTtest, diskWtStaticMutShakingTtest)
TtestTable<-name <- function(dataPoint) {
  data <-data.frame(dataPoint$data.name, dataPoint$p.value)
}
tTestDataTable<-bind_rows(map(tTestData, TtestTable))

ggplot()+#both PA and Sa
  geom_errorbar(data=diskDataStats1, aes(x = strain, ymin = meanBio - SDBio, ymax = meanBio + SDBio),position = position_dodge2(width =1), width = .3)+
  geom_point(data=diskDataStats1, aes(x=strain, y=meanBio, shape =CondStrain),position = position_dodge2(width = .3), size=3)+
  scale_shape_manual(values = c(1,2,16,17),limits=c("wtStat","pqsLStat","wtShake", "pqsLShake"), 
                     labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type static")),
                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL static")),
                                bquote(paste(italic('P. aeruginosa'), " wild-type shaking")),
                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL shaking"))))+
  scale_x_discrete(name ="", breaks = c("wt","pqsl"), labels =c("wild-type",expression(""*Delta*"pqsL")))+
  labs( y = "Zone of inhibition (mm)", shape = "Growth condtion") +
  theme_cowplot(12)

```

```{r yields}
yieldFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/pqsL SCFM2/Pa growth yields 16 hrs/Pa growth yields 16 hrs.csv"
yieldData <-read.csv(yieldFile)
yieldData %>% filter(!bio.rep==3)->yieldData
ggplot()+#both PA and Sa
  geom_point(data=yieldData, aes(x=condition, y=bugs, shape = factor(tech.rep), color = factor(bio.rep)), size=4)+
  facet_grid(.~strain)+
  scale_y_log10(limits= c(1e6,1e10))+
  labs(title =expression(paste("CFUs per mL")), x = "condtion",shape = "tech rep", color = "bio rep")

```
```{r luminescence, include = FALSE, echo=FALSE, fig.width=12, fig.height=9, results='asis', warning=FALSE, message=FALSE}
recode_if <- function(x, condition, ...) {
  if_else(condition, recode(x, ...), x)
}
luminescenceFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/pqsL SCFM2/Staph killing assays/summary.csv"
luminescenceData <-read.csv(luminescenceFile)
luminescenceData<-luminescenceData %>% group_by(TimePoint, BioReplicate, Condition, Strain) %>% mutate(techMean = mean(Luminescence)) %>% ungroup() %>% group_by(TimePoint, Condition, Strain) %>% mutate(Mean = mean(techMean), SE =std.error(techMean)) %>% ungroup()
luminescenceData1<-luminescenceData %>%  
mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))#this adds up all the data on each slice and then gets the log of that total

luminescenceData1<-luminescenceData %>% mutate(
  CondStrain = case_when(
    Condition == "shaking" & Strain == "pqsL" ~ "pqsLShake",
    Condition == "shaking" & Strain == "wt"~ "wtShake",
    Condition == "static" & Strain == "pqsL"~ "pqsLStat",
    Condition == "static" & Strain == "wt"~ "wtStat"))

ggplot()+#both PA and Sa
  #geom_point(data=luminescenceData, aes(x=TimePoint, y=techMean, shape = Strain, color = Condition), size=1)+
  geom_line(data=luminescenceData1, aes(x=TimePoint, y=Mean, linetype = Condition, group = interaction (Strain, Condition)), size=.5,show.legend = FALSE)+
  geom_point(data=luminescenceData1, aes(x=TimePoint, y=Mean, shape = CondStrain), size=3)+
  scale_y_log10(name=expression(paste(italic('S. aureus'), " % luminescence vs control" )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  labs( x = "Time (minutes)",shape = "") +
  scale_shape_manual(values = c(1,2,16,17),limits=c("wtStat","pqsLStat","wtShake", "pqsLShake"), 
                     labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type static")),
                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL static")),
                                bquote(paste(italic('P. aeruginosa'), " wild-type shaking")),
                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL shaking"))))+
  scale_linetype_manual(values =c("solid","dashed"))+
  theme_cowplot(12)

```

```{r Staph TOB MIC}
micFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/SA TOB MIC/SA TOB MIC.csv"
micData <-read.csv(micFile)
micData<-micData %>% filter(!concentration==0.5) %>% mutate(LogCounts = log10(value)) %>% group_by(concentration, condition) %>% mutate(meanLog = mean(LogCounts), seLog = std.error(LogCounts)) %>% ungroup() %>% group_by(replicate, condition)%>% mutate(LogDifference = LogCounts[concentration==0]-LogCounts) %>% ungroup() %>% group_by(concentration, condition) %>% mutate(meanLogDifference = mean(LogDifference), seLogDifference = std.error(LogDifference)) %>% filter(!concentration==0)
controls<-micData %>% filter(concentration==0)
cleanMicData<-anti_join(micData,controls)

ggplot()+
  geom_point(data=cleanMicData, aes(x=concentration, y=LogCounts, color = condition), size=2)+
  geom_line(data=cleanMicData, aes(x=concentration, y=meanLog, color = condition), size=2)+
  scale_x_log10(name=expression(paste("[TOB] ug/mL" )), breaks = c(2,8,32,64,128,256,512), labels =c(2,8,32,64,128,256,512))+
  scale_y_continuous(name = "Log CFUs", breaks = c(0,2,4,6,8,10), labels =c(0,2,4,6,8,10))+
  labs(title =expression(paste("S. aureus TOB MIC")), x = "[TOB] ug/mL",shape = "tech rep", color = "Condition")+
  scale_color_grey()+
  theme_cowplot(12)

ggplot()+
  geom_col(data=cleanMicData, aes(x=as.factor(concentration), y=meanLogDifference, fill = condition ),position =position_dodge(width = .5), width = .5)+
  geom_linerange(data = cleanMicData, aes(x = as.factor(concentration), ymin = meanLogDifference - seLogDifference, ymax = meanLogDifference + seLogDifference, group = condition),position = position_dodge(width = .5))+
  scale_fill_grey()+
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)), breaks = c(2,4,6,8,10), labels = c(2,4,6,8,10))+
  labs(title =expression(paste("S. aureus TOB MIC")), x = "[TOB] ug/mL",y = "log CFU Change", color = "Condition")+
  theme_cowplot()+
  theme_half_open()+
  background_grid()

  geom_line(data=cleanMicData, aes(x=concentration, y=meanLog, color = condition), size=2)+

  scale_y_continuous(name = "Log CFUs", breaks = c(0,2,4,6,8,10), labels =c(0,2,4,6,8,10))+
  labs(title =expression(paste("S. aureus TOB MIC")), x = "[TOB] ug/mL",shape = "tech rep", color = "Condition")+
  theme_cowplot(12)
```

```{r combined plots}

    DiskPlot<-ggplot()+
      geom_errorbar(data=diskDataStats1, aes(x = strain, ymin = meanBio - SDBio, ymax = meanBio + SDBio, group = condition),position = position_dodge(width = .6), width = .2)+
      geom_point(data=diskDataStats1, aes(x=strain, y=meanBio, shape =CondStrain),position = position_dodge2(width = .6), size=3)+
      scale_shape_manual(values = c(1,2,16,17),limits=c("wtStat","pqsLStat","wtShake", "pqsLShake"), 
                     labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type static")),
                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL static")),
                                bquote(paste(italic('P. aeruginosa'), " wild-type stirred")),
                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL stirred"))))+
      scale_x_discrete(name ="", breaks = c("wt","pqsl"), labels =c("wild-type",expression(""*Delta*"pqsL")))+
      labs( y = "Zone of inhibition (mm)", shape = "Growth condtion") +
      theme_cowplot(12)

    luminescencePlot<-ggplot()+
      geom_line(data=luminescenceData1, aes(x=TimePoint, y=Mean, linetype = Condition, group = interaction (Strain, Condition)), size=.5,show.legend = FALSE)+
      geom_point(data=luminescenceData1, aes(x=TimePoint, y=Mean, shape = CondStrain), size=3)+
      scale_y_log10(name=expression(paste(italic('S. aureus'), " % luminescence vs control" )))+
      labs( x = "Time (minutes)",shape = "") +
      scale_shape_manual(values = c(1,2,16,17),limits=c("wtStat","pqsLStat","wtShake", "pqsLShake"), 
                     labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type static")),
                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL static")),
                                bquote(paste(italic('P. aeruginosa'), " wild-type stirred")),
                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL stirred"))))+
      scale_linetype_manual(values =c("solid","dashed"))+
      theme(legend.position="top")+
      theme_cowplot(12)

    legendFigure2 <- get_legend(luminescencePlot + theme(legend.box.margin = margin(0, 0, 0, -10)))
    figure2 <- plot_grid(DiskPlot+theme(legend.position="none"),luminescencePlot+theme(legend.position="none"),
                      align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)
    plot_grid(figure2,legendFigure2,rel_widths = c(6, 1.7))
```

### 2020-06-24 Staph killing assays/Staph killing report.Rmd
redid figures after talking to Marvin in lab

@@
 library(plotrix)
+```
 
+```{r zone of inhibition data input}
 diskFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/pqsL SCFM2/Staph killing assays/disk difussion assays.csv"
@@
     condition == "static" & strain == "wt"~ "wtStat"))
+```
 
+```{r zone of inhibition t-tests}
+#the following data frames are meant to be used for t-tests
 diskWtShaking<-diskData %>% filter(strain == "wt" & condition == "shaking")
@@
 tTestDataTable<-bind_rows(map(tTestData, TtestTable))
-
+```
+```{r zone of inhibition plot }
 ggplot()+#both PA and Sa
@@
 ```{r luminescence, include = FALSE, echo=FALSE, fig.width=12, fig.height=9, results='asis', warning=FALSE, message=FALSE}
-recode_if <- function(x, condition, ...) {
-  if_else(condition, recode(x, ...), x)
-}
-luminescenceFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/pqsL SCFM2/Staph killing assays/summary.csv"
+luminescenceFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Staph killing assays/summary.csv"
 luminescenceData <-read.csv(luminescenceFile)
 luminescenceData<-luminescenceData %>% group_by(TimePoint, BioReplicate, Condition, Strain) %>% mutate(techMean = mean(Luminescence)) %>% ungroup() %>% group_by(TimePoint, Condition, Strain) %>% mutate(Mean = mean(techMean), SE =std.error(techMean)) %>% ungroup()
-luminescenceData1<-luminescenceData %>%  
-mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))#this adds up all the data on each slice and then gets the log of that total
+#luminescenceData1<-luminescenceData %>%  
+#mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))#this adds up all the data on each slice and then gets the log of that total
 
@@
 
-```{r combined plots}
-
+```{r final plots, version 1}
+#this is the original Figure but it needs to be split in two parts
     DiskPlot<-ggplot()+
@@
 ```
+```{r final plots, version 2}
+#this figure needs to be split to show only wt data and mutant data and limit the time point to 7 minutes for the luminescence.
+
+    DiskPlotWt<-ggplot()+
+      geom_errorbar(data=diskDataStats1 %>% filter (strain == "wt"), aes(x = condition, ymin = meanBio - SDBio, ymax = meanBio + SDBio),width = .2)+
+      geom_point(data=diskDataStats1 %>% filter (strain == "wt"), aes(x=condition, y=meanBio, shape =condition), size=3)+
+      scale_shape_manual(values = c(1,2),limits=c("static","shaking"), 
+                     labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type static")),
+                                bquote(paste(italic('P. aeruginosa'), " wild-type stirred"))))+
+      scale_x_discrete(name ="", breaks = c("static","shaking"), labels =c("Static","Stirred"))+
+    ylim(0,17.5)+
+  labs( y = "Zone of inhibition (mm)", shape = "Growth condtion") +
+      theme_cowplot(12)
+
+    DiskPlotMut<-ggplot()+
+      geom_errorbar(data=diskDataStats1 %>% filter (strain == "pqsl"), aes(x = condition, ymin = meanBio - SDBio, ymax = meanBio + SDBio),width = .2)+
+      geom_point(data=diskDataStats1 %>% filter (strain == "pqsl"), aes(x=condition, y=meanBio, shape =condition), size=3)+
+      scale_shape_manual(values = c(16,17),limits=c("static","shaking"), 
+                     labels = c(bquote(paste(italic('P. aeruginosa '), Delta*"pqsL static")),
+                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL stirred"))))+
+      ylim(0,17.5)+
+      scale_x_discrete(name ="", breaks = c("static","shaking"), labels =c("Static","Stirred"))+
+      labs( y = "Zone of inhibition (mm)", shape = "Growth condtion") +
+      theme_cowplot(12)
+
+    luminescencePlotWt<-ggplot()+
+      geom_line(data=luminescenceData1 %>% filter (Strain == "wt") %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, group = Condition), size=.5, show.legend = FALSE)+
+      geom_point(data=luminescenceData1%>% filter (Strain == "wt") %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, shape = Condition), size=3)+
+      scale_y_log10(name=expression(paste(italic('S. aureus'), " % luminescence vs control" )), limits = c(1,121),labels = c(1, 10, 100),breaks = c(1, 10, 100))+
+      labs( x = "Time (minutes)",shape = "") +
+      scale_shape_manual(values = c(1,2),limits=c("static","shaking"), 
+                     labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type static")),
+                                bquote(paste(italic('P. aeruginosa'), " wild-type stirred"))))+
+      theme(legend.position="top")+
+      theme_cowplot(12)
+
+    luminescencePlotMut<-
+      ggplot()+
+      geom_line(data=luminescenceData1 %>% filter (Strain == "pqsL") %>% filter (TimePoint<8), aes(x=TimePoint, y=Mean, group = Condition), size=.5, show.legend = FALSE)+
+      geom_point(data=luminescenceData1%>% filter (Strain == "pqsL") %>% filter (TimePoint<8), aes(x=TimePoint, y=Mean, shape = Condition), size=3)+
+      scale_y_log10(name=expression(paste(italic('S. aureus'), " % luminescence vs control" )),limits = c(1,121), labels = c(1,10,100),breaks = c(1, 10, 100))+
+      labs( x = "Time (minutes)",shape = "") +
+      scale_shape_manual(values = c(16,17),limits=c("static", "shaking"), 
+                     labels = c(bquote(paste(italic('P. aeruginosa '), Delta*"pqsL static")),
+                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL stirred"))))+
+      theme(legend.position="top")+
+      theme_cowplot(12)
+#Figure 2
+
+    legendFigure2 <- get_legend(DiskPlotWt + theme(legend.box.margin = margin(0, 0, 0, -10)))
+    figure2 <- plot_grid(DiskPlotWt+theme(legend.position="none"),luminescencePlotWt+theme(legend.position="none"),
+                      align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)
+    plot_grid(figure2,legendFigure2,rel_widths = c(6, 1.7))
+
+#Figure 5
+    legendFigure5 <- get_legend(DiskPlotMut + theme(legend.box.margin = margin(0, 0, 0, -10)))
+    figure5 <- plot_grid(DiskPlotMut+theme(legend.position="none"),luminescencePlotMut+theme(legend.position="none"),
+                      align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)
+    plot_grid(figure5,legendFigure5,rel_widths = c(6, 1.7))
+
+```

### 2020-06-24 Paper Figures/Paper figures Scipts.Rmd
figures 1,2,4 and 5 ready

---
title: "Paper Figures and Data"
author: "Juan P Barraza"
date: "12/14/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r data Figure 1, include=FALSE}
#Data gathering functions:
GetGrowthCurveReplicate<- function (sample){
  bugCounts<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/GrowthCurves/", sample, ".csv"),header = TRUE)
  bugCounts<- na.omit(bugCounts)
  bugCounts<-bugCounts %>% mutate(logCFU = log10(CFU))
  bugCounts$sample<-sample
  return(bugCounts)
}
GetGrowthCurveCondition<-function(datalist){
  mappedData<-map(datalist, GetGrowthCurveReplicate)#this line reads all the files on the list
  boundData<-bind_rows(mappedData)
  colnames(boundData)[5] <- "strain"
  colnames(boundData)[8] <- "condition"
  return(boundData)
}

PA14 = c('2-11-19','2-7-19','2-5-19')
#get data
PA14Data<-GetGrowthCurveCondition(PA14)
PA14Data$strain <- factor(PA14Data$strain, levels = c("wt", "mut"))

#do stats
PA14DataStats<-PA14Data%>% group_by(condition, bug, time,strain) %>% summarise(CFUmean = mean (CFU), CFUsd = sd(CFU), CFUse = std.error(CFU), logCFUmean = mean (logCFU), logCFUsd = sd(logCFU),logCFUse = std.error(logCFU))
```

```{r code Figure 1}
GraphGrowthCurveLog1<-function (rawData, statsData){
    shakingWtPlot<-ggplot()+
      geom_line(data=statsData%>% filter(condition == "Shaking" & strain == "wt"), aes(x=time, y=logCFUmean, linetype = bug), size=.5)+
      geom_errorbar(data=statsData%>% filter(condition == "Shaking" & strain == "wt"),aes(x = time, ymin = logCFUmean-logCFUse, ymax=logCFUmean+logCFUse), width = 0, size = 0.5)+
      geom_hline(yintercept=9.619, color='gray', linetype = "solid") + #Pa stirred
      geom_hline(yintercept=9.13, color='gray', linetype = "dashed") + #Sa stirred
      scale_linetype_manual(values = c( "solid","dashed"), labels = c("P.aeruginosa","S. aureus"))+
      labs(x = "Time (hours)", y = expression(paste(Log[10], " CFU")), linetype = "Species")+
      scale_y_continuous(limits = c(4,10))+
      scale_x_continuous(breaks = c(4,8,12,16))+
      theme_cowplot(12)

    staticWtPlot<-ggplot()+
      geom_line(data=statsData%>% filter(condition == "Static" & strain == "wt"), aes(x=time, y=logCFUmean, linetype = bug), size=.5)+
      geom_errorbar(data=statsData%>% filter(condition == "Static" & strain == "wt"),aes(x = time,ymin=logCFUmean-logCFUse, ymax = logCFUmean+logCFUse), width = 0, size = 0.5)+
      scale_linetype_manual(values = c( "solid","dashed"), labels = c("stirred","static"))+
      geom_hline(yintercept=8.88, color='gray', linetype = "dashed") +
      geom_hline(yintercept=9.07, color='gray', linetype = "solid") +
      labs(x = "Time (hours)", y = expression(paste(Log[10], " CFU")), linetype = "")+
      scale_y_continuous(limits=c(4,10))+
      scale_x_continuous(breaks = c(4,8,12,16))+
      theme_cowplot(12)

    legend <- get_legend(shakingWtPlot + theme(legend.box.margin = margin(0, 0, 0, -10)))
    prow <- plot_grid(shakingWtPlot+theme(legend.position="none"),staticWtPlot+theme(legend.position="none"),
                      align='vh',labels = c("Stirred", "Static"),hjust = c(-3, -3.8),nrow = 1)
    plot_grid(prow,legend,rel_widths = c(3, .4))
    }
#Graph logs
GraphGrowthCurveLog1(PA14Data,PA14DataStats)
```
Figures 2 and 5 are on document : "Staph killing assays.Rmd"

```{r Figure 4}
GraphGrowthCurveLog2<-function (rawData, statsData){
  shakingMutPlot<-ggplot()+
    geom_line(data=statsData%>% filter(condition == "Shaking" & strain ==  "mut"), aes(x=time, y=logCFUmean, linetype = bug), size=.5)+
    geom_errorbar(data=statsData%>% filter(condition == "Shaking" & strain == "mut"), aes(x = time, ymin = logCFUmean-logCFUse, ymax = logCFUmean+logCFUse), width = 0, size = 0.5)+
    scale_linetype_manual(values = c( "solid","dashed"), labels = c("P.aeruginosa","S. aureus"))+
    geom_hline(yintercept=9.13, color='gray', linetype = "dashed") +
    geom_hline(yintercept=9.57, color='gray', linetype = "solid") +
    labs(x = "Time (hours)", y = expression(paste(Log[10], " CFU")), linetype = "Species")+
    scale_y_continuous(limits = c(4,10))+
    scale_x_continuous(breaks = c(4,8,12,16))+
    theme_cowplot(12)

  staticMutPlot<-ggplot()+
    geom_line(data=statsData%>% filter(condition == "Static" & strain == "mut"), aes(x=time, y=logCFUmean, linetype = bug), size=.5)+
    geom_errorbar(data=statsData%>% filter(condition == "Static" & strain ==  "mut"), aes(x = time, ymin = logCFUmean-logCFUse, ymax = logCFUmean+logCFUse), width = 0, size = 0.5)+
    scale_linetype_manual(values = c( "solid","dashed"), labels = c("P.aeruginosa","S. aureus"))+
    geom_hline(yintercept=8.88, color='gray', linetype = "dashed") +
    geom_hline(yintercept=8.98, color='gray', linetype = "solid") +
    labs(x = "Time (hours)", y = expression(paste(Log[10], " CFU")), linetype = "")+
    scale_y_continuous(limits = c(4,10))+
    scale_x_continuous(breaks = c(4,8,12,16))+
    theme_cowplot(12)
  legend <- get_legend(shakingMutPlot + theme(legend.box.margin = margin(0, 0, 0, -10)))
  prow <- plot_grid(shakingMutPlot+theme(legend.position="none"),staticMutPlot+theme(legend.position="none"),
                      align='vh',labels = c("Stirred", "Static"),hjust = c(-3, -3.8),nrow = 1)
    plot_grid(prow,legend,rel_widths = c(3, .4))
}

#Graph logs
GraphGrowthCurveLog2(PA14Data,PA14DataStats)
```

```{r Tobramycin}
#data wrangling
cleanSCFM2DataTobSa <- newSCFMDataSa %>% group_by(timePoint, antibiotic, culture) %>% summarise(meanCFUratio = mean(ratioCFU), sdCFUratio = sd(ratioCFU),meanLogRatio = mean(ratiolog), sdLogRatio = sd(ratiolog))

#this is using CFUs
ggplot()+
  #geom_pointrange(data=cleanSCFM2DataTobSa,aes(x=timePoint, y = meanCFUratio, ymin = meanCFUratio - sdCFUratio, ymax = meanCFUratio + sdCFUratio, color = culture), size=1)+
  geom_point(data=cleanSCFM2DataTobSa,aes(x=timePoint, y = meanCFUratio, color = culture), size=3)+
  geom_errorbar(data=cleanSCFM2DataTobSa,aes(x=timePoint,ymin = meanCFUratio - sdCFUratio, ymax = meanCFUratio + sdCFUratio, color = culture), size=1)+
  #geom_vline(xintercept=3, linetype = "dashed")+
  scale_y_log10("Growth ratio compared to co-culture with wt", breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  #annotate("text", x = 3, y = 10e6, label = "TOB added")+
  facet_grid(.~antibiotic)+
  labs(x = "Time (hours)", color="Culture condition", shape =  "Antiobiotic/Control")

#This one is using logCFUs
ggplot()+
  geom_point(data=cleanSCFM2DataTobSa,aes(x=timePoint, y = meanLogRatio, color = culture), size=3)+
  geom_errorbar(data=cleanSCFM2DataTobSa,aes(x=timePoint,ymin = meanLogRatio - sdLogRatio, ymax = meanLogRatio + sdLogRatio, color = culture), size=.5, width = 0)+
  geom_hline(xintercept=3, linetype = "dashed")+
  scale_y_continuous(limits = c(.6,1.6 ))+
  #scale_y_log10("Growth ratio compared to co-culture with wt", breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = c(10e-0.2,10e0.2))+
  annotate("text", x = 3, y = 1.4, label = "TOB added")+
  facet_grid(.~antibiotic)+
  labs(x = "Time (hours)", color="Culture condition", shape =  "Antiobiotic/Control") +
  theme_cowplot(12)

GraphTOBGrowthCurveLog<-function (){
    controlPlot<-ggplot()+
      geom_point(data=cleanSCFM2DataTobSa %>% filter(antibiotic=="Control", culture != "wt"),aes(x=timePoint, y = meanLogRatio, shape = culture), size=3)+
      geom_errorbar(data=cleanSCFM2DataTobSa%>% filter(antibiotic=="Control", culture != "wt"),aes(x=timePoint,ymin = meanLogRatio - sdLogRatio, ymax = meanLogRatio + sdLogRatio), size=.5, width = 0.2)+
      geom_hline(yintercept=1, linetype = "dashed")+
      scale_y_continuous(limits = c(.6,1.6 ))+
      labs(x = "Time (hours)", shape="Culture condition", y = "Log Growth ratio compared to wild-type co-culture ") +
      theme_cowplot(12)

    tobPlot<-ggplot()+
      geom_point(data=cleanSCFM2DataTobSa %>% filter(antibiotic=="TOB", culture != "wt"),aes(x=timePoint, y = meanLogRatio, shape = culture), size=3)+
      geom_errorbar(data=cleanSCFM2DataTobSa%>% filter(antibiotic=="TOB", culture != "wt"),aes(x=timePoint,ymin = meanLogRatio - sdLogRatio, ymax = meanLogRatio + sdLogRatio), size=.5, width = 0.2)+
      scale_y_continuous(limits = c(.6,1.6 ))+
      geom_hline(yintercept=1, linetype = "dashed")+
      labs(x = "Time (hours)", y = "", color="Culture condition") +
      theme_cowplot(12)

    legend <- get_legend(controlPlot + theme(legend.box.margin = margin(0, 200, 300,0)))
    prow <- plot_grid(controlPlot+theme(legend.position="none"),tobPlot+theme(legend.position="none"),align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)
    plot_grid(prow,legend,rel_widths = c(3, .4))
    }
GraphTOBGrowthCurveLog()
```
```{r biomass}
GraphGrowthCurvesExpClean(cleanResults1 %>% filter(TimePoint<10),cleanResultsStats1%>% filter(TimePoint<10), "Sa")

countsFinal1<-countsFinal %>% mutate(logCounts = log10(cellCount)) %>% group_by(bug, condition) %>% mutate(meanLog = mean(logCounts), sdcounts = std.error(logCounts))

ggplot()+
  geom_jitter(data= countsFinal1, aes(x=condition, y= logCounts,  shape= condition),height = 0, width = .2, size = 1)+
  #geom_text(fontface = "bold",position=position_jitter(width=.5,height=0))+
  geom_point(data= countsFinal1, aes(x=condition, y= meanLog,shape= condition), size = 3)+
  geom_errorbar(data=countsFinal1,aes(x=condition,ymin = meanLog - sdcounts, ymax = meanLog + sdcounts), size=.5, width = 0.2)+
  #scale_y_log10(name="Mouse Wound CFU/mL", limits= c(1,1e8),breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  ylim(2,8)+ 
  labs(x = "",  y = expression(paste(Log[10], " CFU")), shape="Strain")+
  facet_grid(.~bug)+
  theme_cowplot(12)

```

```{r invasion ratios graphs}
#functions to get data
GetResults<-function(sample, samplename){
  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Other Data1/',sample,'/results')
  #the path just needs to be changed to"Other Data1"
  fileList<-list.files(path = folder, full.names = TRUE)
  growthDf<-data.frame()
  for (position in 0:5){
    currentPosition<-fileList[grep(paste0("p",position,"."),fileList)]
    for (timepoint in 0:17){
      currentTimePoint<-currentPosition[grep(paste0("t",GetNumber(timepoint),"_"),currentPosition)]
      growthDf<-rbind(growthDf,ReadResultsFile(currentTimePoint, position, timepoint))}}
  growthDf<-growthDf %>% mutate(Sample = samplename)
return(growthDf)
}
ReadResultsFile<-function(file, position, timepoint){
  datos <-read.csv(file, header = FALSE)
  colnames(datos)<-c('Red', 'Green', 'Slice')
  datos<-datos %>% mutate(Position = position)
  datos<-datos %>% mutate(TimePoint = timepoint)
  return(datos)
}
MapResults<- function(listSamples, reps){
  blah <-deparse(substitute(listSamples))
  mappedData<-map2(listSamples, reps, GetResults)
  boundData<-bind_rows(mappedData)
  boundData<-boundData %>% mutate(Strain = blah)
  boundData<-gather(boundData,"Color","Value",-Slice,-Position,-Sample,-TimePoint,-Strain) %>% mutate(LogValue=ifelse(Value>0,log10(Value),0))
  boundData<-boundData %>% mutate(Condition = recode(Position, "0" = "Sa Mono", "1" = "Pa Mono", "2" = "Pa:Sa 1:1", "3" = "Pa:Sa 10:1", "4" = "Pa:Sa 1:100", "5" = "Pa:Sa 1:10" )) %>% mutate(Species = recode(Color, "Red" = "Sa", "Green" = "Pa")) %>% mutate(ZDistance = Slice *0.44)
  boundData$Condition<-as.factor(boundData$Condition)
  boundData$Condition<-factor(boundData$Condition, levels = c("Sa Mono", "Pa Mono", "Pa:Sa 1:1", "Pa:Sa 1:10", "Pa:Sa 1:100","Pa:Sa 10:1"))
  boundData$Species<-as.factor(boundData$Species)
  boundData$Strain<-as.factor(boundData$Strain)
  return(boundData)
  }
PA14wt<- c('3-13-19', '3-19-19', '4-17-19')
PA14mut<- c('4-24-19', '4-25-19', '5-8-19')
names3<-c('rep1','rep2','rep3')
wtBiomassResults<-MapResults(PA14wt, names3)
mutBiomassResults<-MapResults(PA14mut, names3)

biomassData<-rbind(wtBiomassResults,mutBiomassResults)#combine data
#Add up all the data on each slice and then get the log of that total
biomassDataClean<-biomassData %>% 
  group_by(TimePoint,Sample,Strain,Condition,Species) %>% 
  summarise(Totals = sum (Value))%>% 
  mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))
#Get stats
biomassStats<-biomassDataClean %>% 
  group_by(TimePoint,Strain,Condition,Species) %>% 
  summarise(MeanTotals = mean(Totals), SDTotals = sd(Totals), MeanLogTotals = mean(LogTotals), SDLogTotals = sd(LogTotals)) %>%
  mutate(MeanLogTotalsRevd = 10^MeanLogTotals, SDLogTotalsRevd =10^(SDLogTotals))

biomassDataCleantEST <-biomassDataClean %>%filter(!Condition%in%c("Sa Mono", "Pa Mono")) %>% filter(TimePoint<7) %>% group_by(TimePoint, Sample, Strain, Condition) %>% mutate(RatioTotals = Totals[Species == "Pa"]/Totals[Species == "Sa"],LogDiff = LogTotals[Species == "Pa"]-LogTotals[Species == "Sa"]) %>% ungroup() %>% group_by(TimePoint,Strain,Condition,Species) %>% mutate(meanRatio = mean(RatioTotals), meanLogDiff = mean(LogDiff)) %>% ungroup()

ggplot()+#graph all data
  geom_point(data = biomassDataCleantEST,aes(x=TimePoint,y=LogDiff, color = Condition, shape = Strain ), size=4)+
  geom_smooth(data = biomassDataCleantEST,aes(x=TimePoint,y=LogDiff, color = Condition, linetype = Strain ), size=1)+
  labs(title ="title")+
  #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))

ggplot()+#graph means
  geom_point(data = biomassDataCleantEST,aes(x=TimePoint,y=meanLogDiff, color = Condition, shape = Strain ), size=4)+
  #geom_smooth(data = biomassDataCleantEST,aes(x=TimePoint,y=LogDiff, color = Condition, linetype = Strain ), size=1)+
  #labs(title ="title")+
  labs(y = "ratio Pa / Sa")+
  #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))

tenToOneData<-biomassDataCleantEST %>% filter(Condition %in% c("Pa:Sa 1:1","Pa:Sa 10:1")) %>% group_by(Species, Condition, Strain, TimePoint) %>% mutate(logMean = mean(LogTotals))
ggplot()+#graph means
  geom_point(data = tenToOneData,aes(x=TimePoint,y=logMean, color = Condition, shape = Strain ), size=4)+
  geom_line(data = tenToOneData,aes(x=TimePoint,y=logMean, color = Condition, linetype = Strain ), size=4)+
  #geom_smooth(data = biomassDataCleantEST,aes(x=TimePoint,y=LogDiff, color = Condition, linetype = Strain ), size=1)+
  #labs(title ="title")+
  labs(y = "ratio Pa / Sa")+
  #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_grid(~Species)+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
```

### 2020-07-13 Microscopy Data Clean.Rmd
This is the "stripped down version of the original script without extra tests and stuff

--- 2020-03-03 Microscopy Data.Rmd
@@
 ---
-title: "Microscopy Data"
+title: "microscopy Data Clean"
 author: "Juan P Barraza"
-date: "6/19/2019"
+date: "7/8/2020"
 output: html_document
@@
 ---
-
-```{r setup, include=FALSE}
+```{r setup}
 library(pixmap)
@@
 library(purrr)
-#library(moderndive)
+
 PA14wt<- c('3-13-19', '3-19-19', '4-17-19')
@@
 names1<-c('rep1')
-figuresPath<-"/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Figures"#this is to save the figures as I am making them
+
 GetNumber<-function(idx){
@@
 
-#Analysis of thresholds
-```{r thresholds functions}
-MapThreshold<- function(listSamples, reps){
-  mappedData<-map2(listSamples, reps, GetThresholds)
-  boundData<-bind_rows(mappedData)
-  blah <-deparse(substitute(listSamples))#this is to obtain the name of the list as a string
-  boundData<-boundData %>% mutate(Strain = blah)#this inserts the name into a column, but it wont work in just one line =(
-  boundData<- gather(boundData, "Color", "Value", -Position, -Sample, -TimePoint, -Strain)
-  boundData<-boundData %>% mutate(Condition = recode(Position, "0" = "Sa Mono", "1" = "Pa Mono", "2" = "Pa:Sa 1:1", "3" = "Pa:Sa 10:1", "4" = "Pa:Sa 1:100", "5" = "Pa:Sa 1:10") )%>% mutate(Species = recode(Color, "Red" = "Sa", "Green" = "Pa"))
-  boundData$Condition<-as.factor(boundData$Condition)
-  boundData$Condition<-factor(boundData$Condition, levels = c("Sa Mono", "Pa Mono", "Pa:Sa 1:1", "Pa:Sa 1:10", "Pa:Sa 1:100","Pa:Sa 10:1"))
-  boundData$Species<-as.factor(boundData$Species)
-  boundData$Strain<-as.factor(boundData$Strain)
-  return(boundData)
+```{r Pa Growth curves from RedSubtracted Images}
+#This will give us a sense on how much of the Pa data was erased because it overlapped with the Sa data.
+ReadResultsFile<-function(file, position, timepoint){#reads the results file and outputs data
+  datos <-read.csv(file, header = FALSE)
+  colnames(datos)<-c('Red', 'Green', 'Slice')
+  datos<-datos %>% mutate(Position = position)
+  datos<-datos %>% mutate(TimePoint = timepoint)
+  return(datos)
 }
-
-GetThresholds<-function(sample, samplename){
-  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/',sample,'/threshold')
+GetResults<-function(sample, samplename){#points to folder with files. Folder is hardcoded, unfortunately
+  #folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/RedSubtractedImages/',sample,'/resultsSubtractRed1')#for pa co only
+  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Other Data1/',sample,'/results')
   fileList<-list.files(path = folder, full.names = TRUE)
   growthDf<-data.frame()
-  for (position in 0:5){
-    currentPosition<-fileList[grep(paste0("p_",position,"."),fileList)]
-    growthDf<-rbind(growthDf,ReadThresholdFile(currentPosition, position))}
+  #for (position in 2:3){
+  #  currentPosition<-fileList[grep(paste0("p",position,"."),fileList)]
+  currentPosition<-fileList[grep(paste0("p2."),fileList)]#only running p2, which in this case 
+    for (timepoint in 0:6){
+      currentTimePoint<-currentPosition[grep(paste0("t",GetNumber(timepoint),"_"),currentPosition)]
+      growthDf<-rbind(growthDf,ReadResultsFile(currentTimePoint, 2, timepoint))
+      #growthDf<-rbind(growthDf,ReadResultsFile(currentTimePoint, position, timepoint))
+      }
+    #}
   growthDf<-growthDf %>% mutate(Sample = samplename)
@@
 }
-ReadThresholdFile<-function(file, position ){#This function outputs total number of pixels in the csv file from matlab
-  datos <-read.csv(file, header = FALSE)
-  colnames(datos)<-c('Red', 'Green')
-  datos<-datos %>% mutate(Position = position)
-  datos$Position<-as.factor(datos$Position)
-  datos<-datos %>% mutate(TimePoint = row_number()-1)
-  return(datos)
-}
-```
-
-```{r thresholds data and figures}
-wtThresholds<-MapThreshold(PA14wt, names3)
-mutThresholds<-MapThreshold(PA14mut, names3)
-Pa01Thresholds<-MapThreshold(PA01wt, names2)
-Pa01mutThresholds<-MapThreshold(PA01mut, names1)
-thresholdData<-rbind(wtThresholds,mutThresholds,Pa01Thresholds,Pa01mutThresholds)
-#This is to get an idea of the thresholding levels
-#this is for all samples of Pa 
-ggplot()+
-  geom_jitter(data=thresholdData %>% filter(Species=="Pa"),height = 0, width = .1, aes(x=TimePoint, y=Value, shape = Sample, color = Strain), size=3)+
-  facet_grid(.~Condition)
-#This is only for PA14 since they seem to be the most consistent
-PA14thresholdData <-thresholdData%>%filter(Species=="Pa") %>% filter(Strain %in% c("PA14wt", "PA14mut")) %>% group_by(Position, TimePoint, Strain, Condition, Species)%>% summarise(MeanThreshold = mean(Value), SDThreshold = sd(Value))
-PA14average<-PA14thresholdData %>% group_by(Position, Strain, Condition, Species)%>% summarise(MeanThreshold = mean(MeanThreshold), SDThreshold = sd(MeanThreshold))
-ggplot()+
-  geom_point(data=thresholdData %>% filter(Species=="Pa")%>% filter(Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=Value, shape = Sample, color = Strain), size=2)+
-  geom_line(data=PA14thresholdData,aes(x = TimePoint, y = MeanThreshold, color =Strain), size = 1)+
-  geom_errorbar(data=PA14thresholdData,aes(x = TimePoint, ymin = MeanThreshold-SDThreshold, ymax = MeanThreshold+SDThreshold, color = Strain), width=.5, size = .5)+
-  geom_hline(data = PA14average, aes(yintercept = MeanThreshold, color = Strain), size = 3)+
-  facet_grid(.~Condition)
-#Now we do Staph
-SathresholdData <-thresholdData%>%filter(Species=="Sa") %>% group_by(Position, TimePoint, Strain, Condition, Species)%>% summarise(MeanThreshold = mean(Value), SDThreshold = sd(Value))
-Saaverage<-SathresholdData %>% group_by(Position, Strain, Condition, Species)%>% summarise(MeanThreshold = mean(MeanThreshold), SDThreshold = sd(MeanThreshold))
-ggplot()+
-  geom_point(data=thresholdData %>% filter(Species=="Sa"), aes(x=TimePoint, y=Value, shape = Sample, color = Strain), size=2)+
-  geom_line(data=SathresholdData,aes(x = TimePoint, y = MeanThreshold, color =Strain), size = 1)+
-  geom_errorbar(data=SathresholdData,aes(x = TimePoint, ymin = MeanThreshold-SDThreshold, ymax = MeanThreshold+SDThreshold, color = Strain), width=2, size = .1)+
-  geom_hline(data = Saaverage, aes(yintercept = MeanThreshold, color = Strain), size = 3)+
-  facet_grid(.~Condition)
-```
-
-```{r threshold weighted growth curves}
-#These are the dataframes that we need to merge
-#I am not entirely sure what this should tell you, but I thought about multiplying the threshold by the value to see if something comes up
-thresholdResultsDf<-merge(cleanResults, thresholdData) %>% mutate(WeightedLogValue = Value*LogTotals) %>% mutate(WeightedValue = Value *Totals) %>% mutate(correctedWeightedLogValue = WeightedLogValue+5)
-thresholdData$Condition<-as.factor(thresholdData$Condition)
- boundData$Condition<-as.factor(boundData$Condition)
-  ggplot()+
-    geom_point(data=thresholdResultsDf%>% filter(Species == "Pa"), aes(x=TimePoint, y=correctedWeightedLogValue,  shape = Sample), size=2)+
-    geom_point(data=cleanResults%>% filter(Species == "Pa"), aes(x=TimePoint, y=LogTotals,  shape = Sample), size=2, color = "red")+
-    facet_grid(Strain~Condition)
-
-ggplot()+
-    geom_point(data=thresholdResultsDf%>% filter(Species == "Sa"), aes(x=TimePoint, y=correctedWeightedLogValue,  shape = Sample), size=2)+
-    geom_point(data=cleanResults%>% filter(Species == "Sa"), aes(x=TimePoint, y=LogTotals,  shape = Sample), size=2, color = "red")+
-    facet_grid(Strain~Condition)
-#Linear regressions
-#First get a df with only Sa Mono Red Channel
-SaMonoTrhesholdDf<-thresholdData%>% filter(Condition == "Sa Mono") %>% filter(Species == "Sa")
-#Linear regression for Thresholds
-lm(SaMonoTrhesholdDf$Value ~ SaMonoTrhesholdDf$TimePoint) 
-plot(SaMonoTrhesholdDf$TimePoint, SaMonoTrhesholdDf$Value)
-abline( 0.18154, 0.00819 )
-#Linear regression for Weighted Growth Curves
-SaMonoWeightedGrowthCurve<-thresholdResultsDf%>% filter(Condition == "Sa Mono") %>% filter(Species == "Sa")
-lmWeighted<-lm(SaMonoWeightedGrowthCurve$WeightedLogValue ~ SaMonoWeightedGrowthCurve$TimePoint) 
-plot(SaMonoWeightedGrowthCurve$TimePoint, SaMonoWeightedGrowthCurve$WeightedLogValue)
-abline( 1.01962, 0.06641 )
-#Non-linear model
-ggplot()+
-  geom_smooth(data=SaMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)+
-  geom_point(data=SaMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)
-ggplot()+
-  geom_smooth(data=SaMonoTrhesholdDf, method = lm, aes(x=TimePoint, y=Value), size=2)+
-  geom_point(data=SaMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)
-
-#Now do the same for Pa
-Pa14wtMonoTrhesholdDf<-thresholdData%>% filter(Condition == "Pa Mono") %>% filter(Species == "Pa") %>% filter(Strain == "PA14wt")
-Pa14mutMonoTrhesholdDf<-thresholdData%>% filter(Condition == "Pa Mono") %>% filter(Species == "Pa") %>% filter(Strain == "PA14mut")
-#Linear regression for Thresholds PA14wt
-lm(Pa14wtMonoTrhesholdDf$Value ~ Pa14wtMonoTrhesholdDf$TimePoint) 
-plot(Pa14wtMonoTrhesholdDf$TimePoint, Pa14wtMonoTrhesholdDf$Value)
-abline( 0.08775, -0.001566 )
-lm(Pa14mutMonoTrhesholdDf$Value ~ Pa14mutMonoTrhesholdDf$TimePoint) 
-plot(Pa14mutMonoTrhesholdDf$TimePoint, Pa14mutMonoTrhesholdDf$Value)
-abline( 0.082315, -0.001234 )
-#Non-linear model
-
-#PA14wt
-ggplot()+
-  geom_smooth(data=Pa14wtMonoTrhesholdDf, method = lm, aes(x=TimePoint, y=Value), size=2)+
-  geom_point(data=Pa14wtMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)
-ggplot()+
-  geom_smooth(data=Pa14wtMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)+
-  geom_point(data=Pa14wtMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)
-#PA14mut
-ggplot()+
-  geom_smooth(data=Pa14mutMonoTrhesholdDf, method = lm, aes(x=TimePoint, y=Value), size=2)+
-  geom_point(data=Pa14mutMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)
-ggplot()+
-  geom_smooth(data=Pa14mutMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)+
-  geom_point(data=Pa14mutMonoTrhesholdDf, aes(x=TimePoint, y=Value), size=2)
-```
-#Biomass with threshold by time points
-```{r biomass functions to read data}
 MapResults<- function(listSamples, reps){
@@
   }
-GetResults<-function(sample, samplename){
-  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Other Data/',sample,'/results')
-  fileList<-list.files(path = folder, full.names = TRUE)
-  growthDf<-data.frame()
-  for (position in 0:5){
-    currentPosition<-fileList[grep(paste0("p",position,"."),fileList)]
-    for (timepoint in 0:17){
-      currentTimePoint<-currentPosition[grep(paste0("t",GetNumber(timepoint),"_"),currentPosition)]
-      growthDf<-rbind(growthDf,ReadResultsFile(currentTimePoint, position, timepoint))}}
-  growthDf<-growthDf %>% mutate(Sample = samplename)
-return(growthDf)
+ProcessResults <-function(){
+  wt<-MapResults(PA14wt, names3)
+  mut<-MapResults(PA14mut, names3)
+  #combine them:
+  results<-rbind(wt,mut)
+  #Add up all the data on each slice and then get the log of that total
+  resultsSum<-results %>% group_by(TimePoint,Sample,Strain,Condition,Species)%>% 
+    summarise(Totals = sum (Value))%>%
+    mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))
+  #get stats between replicates
+  resultsStats<-resultsSum %>% group_by(TimePoint,Strain,Condition,Species) %>% 
+    summarise(MeanTotals = mean(Totals), SDTotals = sd(Totals), MeanLogTotals = mean(LogTotals), SDLogTotals = sd(LogTotals)) %>% 
+    mutate(MeanLogTotalsRevd = 10^MeanLogTotals, SDLogTotalsRevd =10^(SDLogTotals))
+  results <- list(resultsSum,resultsStats)
+  return(results)
 }
-ReadResultsFile<-function(file, position, timepoint){
-  datos <-read.csv(file, header = FALSE)
-  colnames(datos)<-c('Red', 'Green', 'Slice')
-  datos<-datos %>% mutate(Position = position)
-  datos<-datos %>% mutate(TimePoint = timepoint)
-  return(datos)
-}
+
+redSubtractedData<-ProcessResults()#test function
+redSubtractedDataSummary<-redSubtractedData[[1]]
+paRedSubtractResults<-redSubtractedDataSummary%>% filter(Species == "Pa")
+saRedSubtractResults<-redSubtractedDataSummary%>% filter(Species == "Sa")
+
+nonSubtractedData<-ProcessResults()
+nonSubtractedDataSummary<-nonSubtractedData[[1]]#%>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut"))#this may be used later
+paNonSubtractResults<-nonSubtractedData[[1]]%>% filter(Species == "Pa") 
+saNonSubtractResults<-nonSubtractedData[[1]]%>% filter(Species == "Sa")
+
 ```
 
-```{r biomass data}
-#Run the biomass functions on each set of samples and combine them at the end 
-wtResults<-MapResults(PA14wt, names3)
-mutResults<-MapResults(PA14mut, names3)
-Pa01Results<-MapResults(PA01wt, names2)
-Pa01mutResults<-MapResults(PA01mut, names1)
-ResultsData<-rbind(wtResults,mutResults,Pa01Results,Pa01mutResults)
-#combine data for all slices, make it tidy and do  stats:
-cleanResults<-ResultsData %>% group_by(TimePoint,Sample,Strain,Condition,Species) %>% summarise(Totals = sum (Value))%>% mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))#this adds up all the data on each slice and then gets the log of that total
-cleanResultsStats<-cleanResults %>% group_by(TimePoint,Strain,Condition,Species) %>% summarise(MeanTotals = mean(Totals), SDTotals = sd(Totals), MeanLogTotals = mean(LogTotals), SDLogTotals = sd(LogTotals)) %>% mutate(MeanLogTotalsRevd = 10^MeanLogTotals, SDLogTotalsRevd =10^(SDLogTotals)) #stats between reps
-#This is just to check the difference between the mean log and the log of the mean, which are quite different as it turns out...
-clean1ResultsStats<-cleanResultsStats %>% mutate(CheckLog = MeanLogTotals^10) %>% mutate(CheckLog2 = log10(MeanTotals)) %>% mutate(DiffLog = abs(MeanLogTotals-CheckLog2)) %>% mutate(DiffTotals = abs(MeanTotals - CheckLog))
+```{r biomass data exploration for Sa}
+#comparing the data from red subtracted 
+ggplot()+
+  geom_line(data=redSubtractedData[[1]]%>% filter(Species == "Pa") %>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=LogTotals),color = "red", size=.2)+
+  geom_line(data=nonSubtractedData[[1]]%>% filter(Species == "Pa") %>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=LogTotals),color ="blue", size=.2)+
+  facet_grid(Strain~Sample)+
+  theme_cowplot(12)
+#the numbers for Pa after subracting Sa dont really change, so it should be fine.
+
+ggplot()+#this is a summary of Pa Data for all replicates
+  geom_line(data=redSubtractedData[[2]]%>% filter(Species == "Pa") %>% 
+              filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=MeanLogTotals,color = Strain), size=2)+
+  theme_cowplot(12)
+
+#Compare biomass of Staph wt vs mutant from replicates
+saRedSubtractResults1<-saRedSubtractResults %>% ungroup() %>% group_by(Sample, TimePoint) %>% 
+  mutate (mutantAbsDifference = (abs(Totals -Totals[Strain == "PA14mut"])/Totals )) %>% 
+  mutate (mutantRatio = (Totals[Strain == "PA14mut"])/Totals ) %>% ungroup() %>% 
+  group_by(Strain, TimePoint) %>% mutate (repDifference1.2 = (abs(Totals[Sample == "rep1"] -Totals[Sample == "rep2"]))/Totals[Sample == "rep2"]) %>% 
+  mutate (repDifference2.3 = (abs(Totals[Sample == "rep2"] -Totals[Sample == "rep3"]))/Totals[Sample == "rep3"] ) %>% 
+  mutate (repDifference1.3 = (abs(Totals[Sample == "rep1"] -Totals[Sample == "rep3"]))/Totals[Sample == "rep3"] ) %>% ungroup()
+
+tidysaRedSubtractResults1<-saRedSubtractResults1 %>% gather(Comparison, Difference, -TimePoint, -Sample, -Strain, -Condition, -Species, -Totals, -LogTotals) %>% filter(!Difference == 0)
+
+ggplot()+#plotting the absolute difference between replicates and strains
+  geom_point(data = tidysaRedSubtractResults1 %>% filter(!Comparison=="mutantRatio"),
+              aes(x=TimePoint,y=Difference, color = Comparison, shape = Strain),size=3, height = 0, width = .2)+
+  labs(title ="Variance comparison between strains and replicates")+
+  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+
+ggplot()+#plotting the absolute difference between strains only
+  geom_jitter(data = tidysaRedSubtractResults1 %>% filter(Comparison=="mutantRatio") %>% filter(!Difference == 1),
+              aes(x=TimePoint,y=Difference, color = Comparison, shape = Sample),size=3, height = 0, width = .2)+
+  labs(title ="Variance comparison mutant/wt")+
+  scale_y_log10(breaks = c(0.5,.25,1,2.5,5,10))+#breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
 ```
-
-```{r biomass plotting functions}
-GraphGrowthCurves<-function (dataRaw, dataStats, bug){
-  if(bug=="Sa"){dataRaw<-dataRaw %>% filter(Species == "Sa")%>% filter(!Condition == "Pa Mono");
-  dataStats<-dataStats %>% filter(Species == "Sa")%>% filter(!Condition == "Pa Mono");nombre<-"S. aureus"}
-  if(bug=="Pa"){dataRaw<-dataRaw %>% filter(Species == "Pa")%>% filter(!Condition == "Sa Mono");
-  dataStats<-dataStats %>% filter(Species == "Pa")%>% filter(!Condition == "Sa Mono");nombre<-"P. aeruginosa"}
-  ggplot()+
-    geom_point(data=dataRaw, aes(x=TimePoint, y=Totals),  color = "Black", size=2)+
-    geom_point(data=dataStats, aes(x=TimePoint, y=MeanTotals),  color = "Red", size=2)+
-    geom_line(data=dataStats, aes(x=TimePoint, y=MeanTotals),  color = "Red", size=2)+
-    scale_y_log10(limits= c(1e4,1e7), name=expression(paste('Biomass from voxel counts' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-    labs(title =paste(bug, "growth in mono in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
-    facet_grid(Strain~Condition)
-}
-GraphGrowthCurvesExp<-function (dataRaw,dataStats, bug){
-  if(bug=="Sa"){dataRaw<-dataRaw %>% filter(Species == "Sa")%>% filter(!Condition == "Pa Mono");
-  dataStats<-dataStats %>% filter(Species == "Sa")%>% filter(!Condition == "Pa Mono");colore<-"Red"}
-  if(bug=="Pa"){dataRaw<-dataRaw %>% filter(Species == "Pa")%>% filter(!Condition == "Sa Mono");
-  dataStats<-dataStats %>% filter(Species == "Pa")%>% filter(!Condition == "Sa Mono");colore<-"Green"}
-  ggplot()+
-    geom_point(data=dataRaw, aes(x=TimePoint, y=LogTotals),  color = "Black", size=2)+
-    geom_point(data=dataStats, aes(x=TimePoint, y=MeanLogTotals),  color = colore, size=2)+
-    geom_line(data=dataStats, aes(x=TimePoint, y=MeanLogTotals),  color = colore, size=2)+
-    labs(title =paste(bug, "growth in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
-    facet_grid(Strain~Condition)
-}
-GraphGrowthCurvesExpClean<-function (dataRaw, dataStats, bug){
-  if(bug=="Sa"){dataStats<-dataStats %>% filter(Species == "Sa")%>% filter(!Condition == "Pa Mono");colore<-"Red"}
-  if(bug=="Pa"){dataStats<-dataStats %>% filter(Species == "Pa")%>% filter(!Condition == "Sa Mono");colore<-"Green"}
-  ggplot()+
-    #geom_point(data=dataStats, aes(x=TimePoint, y=MeanLogTotals,  color = Condition), size=2)+
-    geom_line(data=dataStats, aes(x=TimePoint, y=MeanLogTotals,  color = Condition), size=2)+
-    labs(title =paste(bug, "growth in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
-    facet_grid(.~Strain)
-}
-GraphGrowthCurvesExp(cleanResults,cleanResultsStats, "Sa")
-GraphGrowthCurvesExp(cleanResults,cleanResultsStats, "Pa")
-GraphGrowthCurvesExpClean(cleanResults,cleanResultsStats, "Sa")
-GraphGrowthCurvesExpClean(cleanResults,cleanResultsStats, "Pa")
-```
-Data from S. aureus. 
-Remember that all mono cultures of Sa are essentially the same: Same strain, same inoculum, same condition. So this is the only condition where you have several replicates.
-```{r Biomass Sa}
-#First Isolate Sa Mono
-cleanResultsSa <- cleanResults %>% filter(Species == "Sa")
-cleanResultsSaMono<- cleanResultsSa %>% filter(Condition == "Sa Mono")
-ggplot()+
-  geom_point(data=cleanResultsSa %>% filter(Condition == "Sa Mono"), aes(x=TimePoint, y=Totals),  color = "Black", size=2)+
-  geom_smooth(data=cleanResultsSaMono, aes(x=TimePoint, y=Totals), size=3, color = "red")+
-  scale_y_log10(limits= c(1e4,1e7), name=expression(paste('Biomass from voxel counts' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  labs(title =expression(paste(italic("S. aureus"), " growth in mono in SCFM2" )),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") 
-ggplot()+
-  geom_point(data=cleanResultsSa, aes(x=TimePoint, y=Totals, shape = NULL,  color =Strain), size=3)+
-  scale_y_log10(limits= c(1e4,1e7), name=expression(paste('Biomass' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  facet_grid(~Condition)+
-  labs(title =expression(paste(italic("S. aureus"), " growth in mono or coculture in SCFM2" )),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") 
-#Now Sa Co-culture
-cleanResultsSaCo<- cleanResultsSa %>% filter(!Condition == "Sa Mono")
-ggplot()+
-  geom_point(data=cleanResultsSaCo, aes(x=TimePoint, y=Totals,  color = Strain), size=2)+
-  geom_smooth(data=cleanResultsSaCo, aes(x=TimePoint, y=Totals, color = Strain), size=3)+
-  scale_y_log10(limits= c(1e4,1e7), name=expression(paste('Biomass from voxel counts' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  labs(title =expression(paste(italic("S. aureus"), " growth in mono in SCFM2" )),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
-  facet_grid(~Condition)
-```
-
-```{r growth rates Sa}
-#first try to fit it to a model fro exponential growth:
-exponential.model <- lm(log(cleanResultsSaMono$Totals)~ cleanResultsSaMono$TimePoint)
-summary(exponential.model)
-#not very good... So I found the package "growthrates", so I'll try that
-#https://cran.r-project.org/web/packages/growthrates/vignettes/Introduction.html
-splitted.data <- multisplit(cleanResultsSaMono, c("Strain", "Sample"))
-dat<-splitted.data[[1]]
-fit <- fit_easylinear(dat$TimePoint, dat$Totals)
-summary(fit)#summary of values
-coef(fit) #exponential growth parameters
-rsquared(fit)  # coefficient of determination (of log-transformed data)
-deviance(fit)  # residual sum of squares of log-transformed data
-par(mfrow = c(1, 2))
-plot(fit, log = "y")
-plot(fit)
-many_fits <- all_easylinear(Totals ~ TimePoint | Strain + Sample, data = cleanResultsSaMono, h = 4)#the h is the number of points considered for fit
-par(mfrow = c(3, 3))#establish the grid
-plot(many_fits,log = "y")#plot many things
-testdf<-data.frame(as.list(rsquared))#convert to data frame
-#this is the mean rsquared for the growth curves. Not super useful, but it is the syntax for more interesting stuff
-pa14GrowthRates<- testdf %>% select(contains("PA14")) %>% gather() %>% summarise(mean = mean(value))
-#Now with all the conditions and find different growth rates
-```
-
-Data from P. aeruginosa
-
-This is a completely different story since I used different Strains of Pa throughout the project. So here they are:
-```{r biomass Pa}
-cleanResultsPaMono<- cleanResultsPa %>% filter(Condition == "Pa Mono")
-ggplot()+
-  geom_point(data=cleanResultsPaMono, aes(x=TimePoint, y=Totals, color =Strain), size=2)+
-  geom_smooth(data=cleanResultsPaMono, aes(x=TimePoint, y=Totals, color = Strain), size=3)+
-  #geom_smooth(data=cleanResultsPaMono, method = "gam",  aes(x=TimePoint, y=Totals, color = Strain), linetype = "dashed", size=3)+
-  scale_y_log10(limits= c(1e4,1e7), name=expression(paste('CFUs per mL' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))
-  #facet_grid(~Strain)
-#model to Fit into an exponential 
-```
-
-```{r biomass Pa and Sa}
-ggplot()+
-  geom_point(data=cleanResultsSaMono, aes(x=TimePoint, y=Totals),  color = "Black", size=2)+
-  geom_point(data=cleanResultsPaMono, aes(x=TimePoint, y=Totals, color =Strain), size=2)+
-  geom_smooth(data=cleanResultsPaMono, aes(x=TimePoint, y=Totals, color = Strain), size=3)+
-  geom_smooth(data=cleanResultsSaMono, aes(x=TimePoint, y=Totals), size=3, color = "red")+
-  #geom_smooth(data=cleanResultsPaMono, method = "gam",  aes(x=TimePoint, y=Totals, color = Strain), linetype = "dashed", size=3)+
-  scale_y_log10(limits= c(1e4,1e7), name=expression(paste('Biomass in voxels' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  labs(title =expression(paste(italic("S. aureus"), " and ", italic("P. aeruginosa"), "growth in mono in SCFM2" )),  x = "Time (hours)")
-ggplot()+
-  scale_y_log10(limits= c(1e4,1e7), name=expression(paste('Biomass from voxel counts' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  labs(title =expression(paste(italic("S. aureus"), " growth in mono in SCFM2" )),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") 
-```
-
-```{r aggregates}
-MapAggregates<- function(listSamples, reps){
-  mappedData<-map2(listSamples, reps, GetAggregates)
-  boundData<-bind_rows(mappedData)
-  blah <-deparse(substitute(listSamples))
-  boundData<-boundData %>% mutate(Strain = blah)#needs to be two lines, it doesnt work if you do it directly
-  return(boundData)
-  }
-GetAggregates<-function(sample, samplename){
-  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/',sample,'/aggregateSizes')
-  fileList<-list.files(path = folder, full.names = TRUE)
-  growthDf<-data.frame()
-  for (position in 0:5){
-    currentPosition<-fileList[grep(paste0("p_",position,"."),fileList)]
-    for (timepoint in 0:17){
-      currentTimePoint<-currentPosition[grep(paste0("t_",GetNumber(timepoint),"p_"),currentPosition)]
-      growthDf<-rbind(growthDf,ReadAggregateFile(currentTimePoint, position, timepoint))
-      }
-  }
-  growthDf<-growthDf %>% mutate(Sample = samplename)
-return(growthDf)
-}
+#Functions for histograms
+```{r new threshold images aggregates functions and data collection}
 ReadAggregateFile<-function(file, position, timepoint){#This function outputs total number of pixels in the csv file from matlab
@@
 }
-wtAggregates<-MapAggregates(PA14wt, names3)
-mutAggregates<-MapAggregates(PA14mut, names3)
-Pa01Results<-MapAggregates(PA01wt, names2)
-Pa01mutResults<-MapAggregates(PA01mut, 'rep1')
-```
-##Biomass per slice.
 
-Where is the majority of the biomass at any given time? and how does it grow over time.
-It additionally helps identify how reproducible are the experiments
-```{r Biomass per slice }
-#This function uses facets to show the abundance of cells according to height over time
-GraphSlices<-function (data, bug, facete){
-  #first which bug is being selected
-  if(bug=="Sa"){data <-data %>% filter(Species == "Sa")%>% filter(!Condition == "Pa Mono");nombre<-"S. aureus"}
-  if(bug=="Pa"){data<-data %>% filter(Species == "Pa")%>% filter(!Condition == "Sa Mono");nombre<-"P. aeruginosa"}
-  #then what kind of facet can be used
-  if(missing(facete)){facete=facet_grid(Condition~TimePoint);condicion <- "Strain";forma <- NULL}
-  else{facete <-facet_wrap(.~TimePoint,ncol = 6 );condicion <- "Condition";forma<-"Strain"}
-  ggplot()+
-    geom_point(data=data, aes_string(x="ZDistance", y="Value", color = condicion, shape = forma),size=1)+
-    scale_y_log10(name=expression(paste('Biomass from voxel counts' )), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-    #labs(title =expression(paste(italic(nombre), " biomass value per slice in SCFM2" )),  x = "Distance from bottom (z-slice)")+
-    labs(title =paste0(nombre, " biomass value per slice in SCFM2" ),  x = "Distance from bottom (z-slice)")+
-    facete
-}
-ggsave("Sa z-slice condition-timepoint1.png", plot = GraphSlices(ResultsData, "Sa"), path = figuresPath)
-ggsave("Sa z-slice timepoint.png", plot = GraphSlices(ResultsData, "Sa", "BLAH"), path = figuresPath)
-ggsave("Pa z-slice condition-timepoint.png", plot = GraphSlices(ResultsData, "Pa"), path = figuresPath)
-ggsave("Pa z-slice timepoint.png", plot = GraphSlices(ResultsData, "Pa", "BLAH"), path = figuresPath)
-#This graph shows how the distribution of biomass changes over time per experiment.
-GraphSlicesTime<-function(datos, bug, strain){
-  if(bug=="Sa"){datos<-datos %>% filter(Species == "Sa")%>% filter(!Condition == "Pa Mono");nombre<-"S. aureus"}
-  if(bug=="Pa"){datos<-datos %>% filter(Species == "Pa")%>% filter(!Condition == "Sa Mono");nombre<-"P. aeruginosa"}
-  ggplot()+
-    geom_point(data=datos %>% filter(Strain == strain) , aes(x=ZDistance, y=Value, color = TimePoint),size=1)+
-    scale_y_log10(name=expression(paste('Biomass from voxel counts' )), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-    labs(title =paste(bug, "biomass value per slice in SCFM2 using",strain  ),  x = "Distance from bottom (z-slice)")+
-    facet_grid(Sample~Condition)
-}
-ggsave("Sa z-slice PA14wt grid.png", plot = GraphSlicesTime(ResultsData, "Sa", "PA14wt"), path = figuresPath)
-ggsave("Sa z-slice PA14mut grid.png", plot = GraphSlicesTime(ResultsData, "Sa", "PA14mut"), path = figuresPath)
-ggsave("Pa z-slice PA14wt grid.png", plot = GraphSlicesTime(ResultsData, "Pa", "PA14wt"), path = figuresPath)
-ggsave("Pa z-slice PA14mut grid.png", plot = GraphSlicesTime(ResultsData, "Pa", "PA14mut"), path = figuresPath)
-```
-
-```{r new threshold images}
-#To get the data from the new results folder I have to rewrite this function:
-GetResults<-function(sample, samplename){
-  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data1/',sample,'/results')#the path needs to be "Other Data1"
+#!!! two versions of the following function, one is for red subtract and the other one for the rest.
+GetAggregates<-function(sample, samplename){#iterate through files in folder
+  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Other Data1/', sample, '/aggregateSizes1')
   fileList<-list.files(path = folder, full.names = TRUE)
   growthDf<-data.frame()
-  for (position in 0:5){
-    currentPosition<-fileList[grep(paste0("p",position,"."),fileList)]
-    for (timepoint in 0:17){
-      currentTimePoint<-currentPosition[grep(paste0("t",GetNumber(timepoint),"_"),currentPosition)]
-      growthDf<-rbind(growthDf,ReadResultsFile(currentTimePoint, position, timepoint))}}
-  growthDf<-growthDf %>% mutate(Sample = samplename)
-return(growthDf)
-}
-#This is also useful so that I know how the pipeline works
-#first run MapResults which gets you all the data:
-wtResults1<-MapResults(PA14wt, names3)
-mutResults1<-MapResults(PA14mut, names3)
-#combine them:
-ResultsData1<-rbind(wtResults1,mutResults1)
-#Get stats:
-cleanResults1<-ResultsData1 %>% group_by(TimePoint,Sample,Strain,Condition,Species) %>% summarise(Totals = sum (Value))%>% mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))#this adds up all the data on each slice and then gets the log of that total
-cleanResultsStats1<-cleanResults1 %>% group_by(TimePoint,Strain,Condition,Species) %>% summarise(MeanTotals = mean(Totals), SDTotals = sd(Totals), MeanLogTotals = mean(LogTotals), SDLogTotals = sd(LogTotals)) %>% mutate(MeanLogTotalsRevd = 10^MeanLogTotals, SDLogTotalsRevd =10^(SDLogTotals))
-#Graph
-#This Graphs the raw results
-GraphGrowthCurves(cleanResults%>%filter(Strain%in%c("PA14wt","PA14mut")),cleanResultsStats%>%filter(Strain%in%c("PA14wt","PA14mut")),"Sa")
-GraphGrowthCurves(cleanResults1,cleanResultsStats1, "Sa")
-#This graphs the mean of the log totals along with the log of the totals themselves
-GraphGrowthCurvesExp(cleanResults%>%filter(Strain%in%c("PA14wt","PA14mut")),cleanResultsStats%>%filter(Strain%in%c("PA14wt","PA14mut")), "Sa")
-GraphGrowthCurvesExp(cleanResults1,cleanResultsStats1, "Sa")
-#This graphs only the mean of the log values, no other points
-GraphGrowthCurvesExpClean(cleanResults%>%filter(Strain%in%c("PA14wt","PA14mut")),cleanResultsStats%>%filter(Strain%in%c("PA14wt","PA14mut")), "Sa")
-GraphGrowthCurvesExpClean(cleanResults1,cleanResultsStats1, "Sa")
-#Isolate Sa
-cleanResultsSa1 <- cleanResults1 %>% filter(Species == "Sa")
-cleanResultsSaMono1<- cleanResultsSa1 %>% filter(Condition == "Sa Mono")
-ggplot()+
-  geom_point(data=cleanResultsSa1 %>% filter(Condition == "Sa Mono"), aes(x=TimePoint, y=Totals),  color = "Black", size=2)+
-  geom_smooth(data=cleanResultsSaMono1, aes(x=TimePoint, y=Totals), size=3, color = "red")+
-  scale_y_log10(limits= c(1e4,1e7), name=expression(paste('Biomass from voxel counts' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  labs(title =expression(paste(italic("S. aureus"), " growth in mono in SCFM2" )),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")
-
-#Now for Pa
-GraphGrowthCurvesExp(cleanResults1,cleanResultsStats1, "Pa")
-GraphGrowthCurvesExpClean(cleanResults1,cleanResultsStats1, "Pa")
-GraphGrowthCurvesExpCleanCoCulture<-function (dataStats){
-  ggplot()+
-    geom_line(data=dataStats %>% filter(!Condition %in% c("Pa Mono", "Sa Mono")), aes(x=TimePoint, y=MeanLogTotals,  color = Strain, linetype = Species), size=2)+
-    labs(title =paste("Growth in SCFM2" ),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control")+
-    facet_grid(.~Condition)
-}
-GraphGrowthCurvesExpCleanCoCulture(cleanResultsStats1)
-
-```
-#Functions for histograms
-```{r new threshold images aggregates functions and data collection}
-GetAggregates<-function(sample, samplename){
-  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data1/', sample, '/aggregateSizes1')
-  fileList<-list.files(path = folder, full.names = TRUE)
-  growthDf<-data.frame()
-  for (position in 0:5){
+  for (position in 0:2){#only positions that are used
     currentPosition<-fileList[grep(paste0("p_",position,"."),fileList)]
-    for (timepoint in 0:17){
+    for (timepoint in 0:6){#only important time points
       currentTimePoint<-currentPosition[grep(paste0("t_",GetNumber(timepoint),"p_"),currentPosition)]
@@
 
+MapAggregates<- function(listSamples, reps){#run it for all the samples
+  mappedData<-map2(listSamples, reps, GetAggregates) 
+  boundData<-bind_rows(mappedData) 
+  blah <-deparse(substitute(listSamples)) 
+  boundData<-boundData %>% mutate(Strain = blah)#needs to be two lines, it doesnt work if you do it directly
+  return(boundData)
+  }
+
 wtAggregates1<-MapAggregates(PA14wt, names3)
@@
 allAggregates<-bind_rows(wtAggregates1,mutAggregates1)
-allAggregates1<-allAggregates %>% filter(!Size<0.5) %>% filter(!(Position==1 & Species=="Sa")) %>% filter(!(Position==0 & Species=="Pa"))%>% filter(!Species =="")
-allAggregates1$Strain<-as.factor(allAggregates1$Strain)
-allAggregates1$Sample<-as.factor(allAggregates1$Sample)
-allAggregates1$TimePoint<-as.factor(allAggregates1$TimePoint)
-allAggregates1$Position<-as.factor(allAggregates1$Position)
-allAggregates1<-allAggregates1 %>% mutate(Condition = recode(Position, "0" = "Sa Mono", "1" = "Pa Mono", "2" = "Pa:Sa 1:1", "3" = "Pa:Sa 10:1", "4" = "Pa:Sa 1:100", "5" = "Pa:Sa 1:10" ))
+allAggregatesClean<-allAggregates %>% filter(!Size<0.5) %>% filter(!(Position==1 & Species=="Sa")) %>% filter(!(Position==0 & Species=="Pa"))%>% filter(!Species =="")#for some reason there are a bunch of "aggregates with no species, it may be a way in which the files are being handled.
 
+#allAggregatesClean1<-allAggregates %>% filter(!Species =="")%>% filter(!(Position==1 & Species=="Sa")) %>% filter(!(Position==0 & Species=="Pa"))#this is only to check for smaller aggregates biomass
+
+#quick evaluation of how much biomass is lost when you remove aggregates smaller than 0.5 um3:
+biomassInAllAggs<-allAggregatesClean1 %>% group_by(Species, Position, TimePoint, Strain) %>% summarise(Biomass = sum(Size))
+biomassIn0.5Aggs<-allAggregatesClean %>% group_by(Species, Position, TimePoint, Strain) %>% summarise(Biomass = sum(Size))
+biomassAggsComparison<-combine(biomassInAllAggs,biomassIn0.5Aggs)
+ggplot()+
+  geom_point(data = biomassAggsComparison,aes(x=TimePoint,y=Biomass, color = source, shape =Strain ),size=4)+
+  facet_grid(~Species)+
+  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+#so only a modest change in biomass, so it shouldnt be a problem.
+
+#now make them all factors
+allAggregatesClean$Strain<-as.factor(allAggregatesClean$Strain)
+allAggregatesClean$Sample<-as.factor(allAggregatesClean$Sample)
+allAggregatesClean$TimePoint<-as.factor(allAggregatesClean$TimePoint)
+allAggregatesClean$Position<-as.factor(allAggregatesClean$Position)
+allAggregatesClean<-allAggregatesClean %>% mutate(Condition = recode(Position, "0" = "Sa Mono", "1" = "Pa Mono", "2" = "Pa:Sa 1:1", "3" = "Pa:Sa 10:1", "4" = "Pa:Sa 1:100", "5" = "Pa:Sa 1:10" ))
+
+#redSubtract aggregates you have to change the "getAggregates function
+#!!! this is the second version of the function
+GetAggregates<-function(sample, samplename){#iterate through files in folder
+  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Other Data1/', sample, '/aggregateSizesRedSubtract')
+  fileList<-list.files(path = folder, full.names = TRUE)
+  growthDf<-data.frame()
+  position =2#red subtract only
+    currentPosition<-fileList[grep(paste0("p2"),fileList)]#only for red subtract
+    for (timepoint in 0:6){#only important time points
+      currentTimePoint<-currentPosition[grep(paste0("t",GetNumber(timepoint),"_p2"),currentPosition)]#this is for pa red subtract only
+      growthDf<-rbind(growthDf,ReadAggregateFile(currentTimePoint, position, timepoint))
+  }
+  growthDf<-growthDf %>% mutate(Sample = samplename)
+return(growthDf)
+}
+
+wtAggregates<-MapAggregates(PA14wt, names3)
+mutAggregates<-MapAggregates(PA14mut, names3)
+allAggregatesredSubtract<-bind_rows(wtAggregates,mutAggregates)
+allAggregatesredSubtractClean<-allAggregatesredSubtract %>% filter(!Size<0.5) %>% filter(!(Position==1 & Species=="Sa")) %>% filter(!(Position==0 & Species=="Pa"))%>% filter(!Species =="")#for some reason there are a bunch of "aggregates with no species, it may be a way in which the files are being handled.
+
+#also for the redsubtract
+allAggregatesredSubtractClean$Strain<-as.factor(allAggregatesredSubtractClean$Strain)
+allAggregatesredSubtractClean$Sample<-as.factor(allAggregatesredSubtractClean$Sample)
+allAggregatesredSubtractClean$TimePoint<-as.factor(allAggregatesredSubtractClean$TimePoint)
+allAggregatesredSubtractClean$Position<-as.factor(allAggregatesredSubtractClean$Position)
+allAggregatesredSubtractClean<-allAggregatesredSubtractClean %>% mutate(Condition = recode(Position, "0" = "Sa Mono", "1" = "Pa Mono", "2" = "Pa:Sa 1:1", "3" = "Pa:Sa 10:1", "4" = "Pa:Sa 1:100", "5" = "Pa:Sa 1:10" ))
 ```
@@
 #get some stats on aggregates
-allDataSummary<-allAggregates1 %>% group_by(Species, Condition, TimePoint, Sample, Strain) %>% summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), sDAggSize = sd(Size), maxSize = max(Size), minSize = min(Size))
-SaSummary<-allDataSummary %>% filter(Species == "Sa" & TimePoint == 7 & Condition == "Sa Mono") %>% ungroup()%>% summarise(MeanAgg = mean(meanAggSize) )
+allAggregateDataSummary<-allAggregatesClean %>% group_by(Species,Condition, TimePoint, Sample, Strain) %>% summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), sDAggSize = sd(Size), maxSize = max(Size), minSize = min(Size))
 
-##Figure 6
+allAggregateDataSummaryTime5wt<- allAggregateDataSummary %>% filter (TimePoint == 0) %>% filter(Strain=="PA14wt")%>% filter(Condition == "Pa:Sa 1:1") %>% filter(Species == "Pa")
+
+allAggregateredsubtractDataSummary<-allAggregatesredSubtractClean %>% group_by(Species,Condition, TimePoint, Sample, Strain) %>% summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), sDAggSize = sd(Size), maxSize = max(Size), minSize = min(Size))
+
+allAggregateredsubtractDataSummary0wt<- allAggregateredsubtractDataSummary %>% filter (TimePoint == 0) %>% filter(Strain=="PA14wt")%>% filter(Condition == "Pa:Sa 1:1") %>% filter(Species == "Pa")
+
+#now I have to remove the one condition and add it from the removed
+removeNonRedSubtractData<- allAggregateDataSummary %>% filter(!Condition == "Pa:Sa 1:1")
+removeNonRedSubtractData$Position<-as.factor(removeNonRedSubtractData$Position)
+removeNonRedSubtractData$Strain<-as.factor(removeNonRedSubtractData$Strain)
+removeNonRedSubtractData$Sample<-as.factor(removeNonRedSubtractData$Sample)
+removeNonRedSubtractData$TimePoint<-as.factor(removeNonRedSubtractData$TimePoint)
+
+combinedRedSubtractData<-bind_rows(removeNonRedSubtractData,allAggregateredsubtractDataSummary)
+
 #Summary figure for total aggregate numbers
 ggplot()+
-  geom_jitter(data = allDataSummary, aes(x = TimePoint, y= Aggs, color = Species, shape = Strain), width = 0, height = 0)+
-  geom_smooth(data = allDataSummary, aes(x = TimePoint, y= Aggs, color = Species, linetype = Strain, group = interaction(Species, Strain)))+
+  geom_jitter(data = allAggregateDataSummary, aes(x = TimePoint, y= Aggs, color = Species, shape = Strain), width = 0, height = 0)+
+  geom_smooth(data = allAggregateDataSummary, aes(x = TimePoint, y= Aggs, color = Species, linetype = Strain, group = interaction(Species, Strain)))+
   facet_wrap(.~Condition)+
@@
   ggtitle('Number of aggregates per experiment')+
-  labs(x = "Time (hours)",y = "Number of Aggregates") 
-#this is a decent outline of the aggregates but I need to still subset it
+  labs(x = "Time (hours)",y = "Number of Aggregates")+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+
 ggplot()+
-  geom_point(data = allDataSummary, aes(x = TimePoint, y= meanAggSize, color = Species,shape = "Mean"))+
-  geom_point(data = allDataSummary, aes(x = TimePoint, y= maxSize, color = Species, shape = "Max"))+
-  geom_point(data = allDataSummary, aes(x = TimePoint, y= biomass, color = Species, shape = "Total"))+  
-  geom_smooth(data = allDataSummary, aes(x = TimePoint, y= meanAggSize, color = Species, linetype = Strain, group = interaction(Species)))+
-  facet_wrap(Strain~Condition)+
+  geom_jitter(data = combinedRedSubtractData, aes(x = TimePoint, y= Aggs, color = Species, shape = Strain), width = 0, height = 0)+
+  geom_smooth(data = combinedRedSubtractData, aes(x = TimePoint, y= Aggs, color = Species, linetype = Strain, group = interaction(Species, Strain)))+
+  facet_wrap(.~Condition)+
+  scale_y_continuous(limits= c(0,1e4))+
+  ggtitle('Number of aggregates per experiment')+
+  labs(x = "Time (hours)",y = "Number of Aggregates")+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+#it turns out that there is little to no difference between the redsbutract images and the other ones =(
+#now we filter for only the time point that we care, which is hour 5:
+aggregatesDataTime5wt<- combinedRedSubtractData %>% filter (TimePoint == 5) %>% filter(Strain=="PA14wt")
+aggregatesDataTime5mut<- combinedRedSubtractData %>% filter (TimePoint == 5) %>% filter(Strain=="PA14mut")
+
+#this is a decent outline of the aggregates
+ggplot()+
+  geom_jitter(data = aggregatesDataTime5wt, aes(x = Condition, y= meanAggSize, color = Species,shape = "MeanSize"), height = 0)+
+  geom_jitter(data = aggregatesDataTime5wt, aes(x = Condition, y= maxSize, color = Species, shape = "MaxSize"), height = 0)+
+  geom_jitter(data = aggregatesDataTime5wt, aes(x = Condition, y= biomass, color = Species, shape = "TotalBiomass"), height = 0)+  
+  #geom_smooth(data = aggregatesDataTime5, aes(x = , y= meanAggSize, color = Species, linetype = Strain, group = interaction(Species)))+
+  facet_wrap(Species~.)+
   scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
   ggtitle('Aggregates summary: Mean, largest and total biomass')+
-  labs(x = "Time (hours)",y = "Biomass")+
-  scale_shape_manual(name="Metric",values=c(Mean=1, Max=2, Total=17))
+  labs(x = "Time (hours)",y = "um3")+
+  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
 

### 2020-07-15 Microscopy Data Clean.Rmd
added some ideas about the butterfly plot

@@
 library(purrr)
+library(plotrix)#this is for std.error function
+library(scales)#for negative log
 
@@
 ```
-#Functions for histograms
+#Reading aggregate data
 ```{r new threshold images aggregates functions and data collection}
@@
 allAggregatesClean$Strain<-as.factor(allAggregatesClean$Strain)
+allAggregatesClean$Species<-as.factor(allAggregatesClean$Species)
 allAggregatesClean$Sample<-as.factor(allAggregatesClean$Sample)
@@
 allAggregatesredSubtractClean$Strain<-as.factor(allAggregatesredSubtractClean$Strain)
+allAggregatesredSubtractClean$Species<-as.factor(allAggregatesredSubtractClean$Species)
 allAggregatesredSubtractClean$Sample<-as.factor(allAggregatesredSubtractClean$Sample)
@@
 ```
+At this point I have 2 dataframes with aggregate data: allAggregatesredSubtractClean and allAggregatesClean, so now I have to merge them properly.
+```{r agggregates stats and plots, include=FALSE}
+removeNonRedSubtractData<- allAggregatesClean %>% filter(!Condition == "Pa:Sa 1:1")#remove Pa:Sa 1:1 condition
+combinedRedSubtractData<-bind_rows(removeNonRedSubtractData,allAggregatesredSubtractClean)
 
-```{r new threshold agggregates, include=FALSE}
+combinedRedSubtractData$Condition<-as.factor(combinedRedSubtractData$Condition)
+combinedRedSubtractData$Species<-as.factor(combinedRedSubtractData$Species)
+combinedRedSubtractData$Position<-as.factor(combinedRedSubtractData$Position)
+#I have to do this because the data frames had different number of factors on those columns...
+
 #get some stats on aggregates
-allAggregateDataSummary<-allAggregatesClean %>% group_by(Species,Condition, TimePoint, Sample, Strain) %>% summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), sDAggSize = sd(Size), maxSize = max(Size), minSize = min(Size))
-
-allAggregateDataSummaryTime5wt<- allAggregateDataSummary %>% filter (TimePoint == 0) %>% filter(Strain=="PA14wt")%>% filter(Condition == "Pa:Sa 1:1") %>% filter(Species == "Pa")
-
-allAggregateredsubtractDataSummary<-allAggregatesredSubtractClean %>% group_by(Species,Condition, TimePoint, Sample, Strain) %>% summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), sDAggSize = sd(Size), maxSize = max(Size), minSize = min(Size))
-
-allAggregateredsubtractDataSummary0wt<- allAggregateredsubtractDataSummary %>% filter (TimePoint == 0) %>% filter(Strain=="PA14wt")%>% filter(Condition == "Pa:Sa 1:1") %>% filter(Species == "Pa")
-
-#now I have to remove the one condition and add it from the removed
-removeNonRedSubtractData<- allAggregateDataSummary %>% filter(!Condition == "Pa:Sa 1:1")
-removeNonRedSubtractData$Position<-as.factor(removeNonRedSubtractData$Position)
-removeNonRedSubtractData$Strain<-as.factor(removeNonRedSubtractData$Strain)
-removeNonRedSubtractData$Sample<-as.factor(removeNonRedSubtractData$Sample)
-removeNonRedSubtractData$TimePoint<-as.factor(removeNonRedSubtractData$TimePoint)
-
-combinedRedSubtractData<-bind_rows(removeNonRedSubtractData,allAggregateredsubtractDataSummary)
+allAggregateDataSummary<-combinedRedSubtractData %>% group_by(Species,Condition, TimePoint, Sample, Strain) %>% summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>% ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass ) %>% mutate(ConditionNew = recode(Condition, "Sa Mono" = "Mono", "Pa Mono" = "Mono","Pa:Sa 1:1" = "Co"))
 
@@
 
-ggplot()+
-  geom_jitter(data = combinedRedSubtractData, aes(x = TimePoint, y= Aggs, color = Species, shape = Strain), width = 0, height = 0)+
-  geom_smooth(data = combinedRedSubtractData, aes(x = TimePoint, y= Aggs, color = Species, linetype = Strain, group = interaction(Species, Strain)))+
-  facet_wrap(.~Condition)+
-  scale_y_continuous(limits= c(0,1e4))+
-  ggtitle('Number of aggregates per experiment')+
-  labs(x = "Time (hours)",y = "Number of Aggregates")+
-  theme_cowplot()+
-  theme(plot.title = element_text(hjust = 0.5))
-#it turns out that there is little to no difference between the redsbutract images and the other ones =(
 #now we filter for only the time point that we care, which is hour 5:
-aggregatesDataTime5wt<- combinedRedSubtractData %>% filter (TimePoint == 5) %>% filter(Strain=="PA14wt")
-aggregatesDataTime5mut<- combinedRedSubtractData %>% filter (TimePoint == 5) %>% filter(Strain=="PA14mut")
+aggregatesDataTime5wt<- allAggregateDataSummary %>% filter (TimePoint == 5) %>% filter(Strain=="PA14wt")
+aggregatesDataTime5mut<- allAggregateDataSummary %>% filter (TimePoint == 5) %>% filter(Strain=="PA14mut")
 
-#this is a decent outline of the aggregates
-ggplot()+
-  geom_jitter(data = aggregatesDataTime5wt, aes(x = Condition, y= meanAggSize, color = Species,shape = "MeanSize"), height = 0)+
-  geom_jitter(data = aggregatesDataTime5wt, aes(x = Condition, y= maxSize, color = Species, shape = "MaxSize"), height = 0)+
-  geom_jitter(data = aggregatesDataTime5wt, aes(x = Condition, y= biomass, color = Species, shape = "TotalBiomass"), height = 0)+  
-  #geom_smooth(data = aggregatesDataTime5, aes(x = , y= meanAggSize, color = Species, linetype = Strain, group = interaction(Species)))+
+#this is a decent outline of the aggregates data
+ggplot()+#for wt
+  geom_point(data = aggregatesDataTime5wt, aes(x = ConditionNew, y= meanAggSize, color = Species,shape = "MeanSize"))+
+  geom_point(data = aggregatesDataTime5wt, aes(x = ConditionNew, y= maxSize, color = Species, shape = "MaxSize"))+
+  geom_point(data = aggregatesDataTime5wt, aes(x = ConditionNew, y= biomass, color = Species, shape = "TotalBiomass"))+  
   facet_wrap(Species~.)+
   scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  ggtitle('Aggregates summary: Mean, largest and total biomass')+
-  labs(x = "Time (hours)",y = "um3")+
+  ggtitle('Aggregates: Mean, largest and total biomass (wild type)')+
+  labs(x = "",y = "Aggregate size (um3)")+
   scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
@@
   theme(plot.title = element_text(hjust = 0.5))
+
+ggplot()+#for mutant
+  geom_point(data = aggregatesDataTime5mut, aes(x = ConditionNew, y= meanAggSize, color = Species,shape = "MeanSize"))+
+  geom_point(data = aggregatesDataTime5mut, aes(x = ConditionNew, y= maxSize, color = Species, shape = "MaxSize"))+
+  geom_point(data = aggregatesDataTime5mut, aes(x = ConditionNew, y= biomass, color = Species, shape = "TotalBiomass"))+  
+  facet_wrap(Species~.)+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  ggtitle('Aggregates: Mean, largest and total biomass (pqsL mutant)')+
+  labs(x = "",y = "um3")+
+  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+
+#now do only average aggregate size:
+#wild type
+ggplot()+
+  geom_point(data = aggregatesDataTime5wt, aes(x = ConditionNew, y= meanAggSize, shape = Sample))+
+  geom_errorbar(data = aggregatesDataTime5wt, aes(x = ConditionNew, ymin= meanAggSize-seAggSize,ymax= meanAggSize+seAggSize))+
+  facet_grid(~Species, space = "free")+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  ggtitle('Mean Aggregate size per sample (wt)')+
+  labs(x = "",y = "Aggregate size (um3)")+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+#mutant
+ggplot()+
+  geom_point(data = aggregatesDataTime5mut, aes(x = ConditionNew, y= meanAggSize, shape = Sample))+
+  geom_errorbar(data = aggregatesDataTime5mut, aes(x = ConditionNew, ymin= meanAggSize-seAggSize,ymax= meanAggSize+seAggSize))+
+  facet_grid(~Species, space = "free")+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  ggtitle('Mean Aggregate size per sample (pqsL)')+
+  labs(x = "",y = "um3")+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+
+#very interesting...now do stats
+
+aggregatesDataTime5mutStats<-aggregatesDataTime5mut %>% group_by (Species,ConditionNew, Strain) %>% 
+  summarise(MeanAggs = mean(Aggs), SEAggs = std.error(Aggs), 
+            MeanBiomass = mean(biomass),SEBiomass = std.error(biomass), 
+            MeanAggSize = mean(meanAggSize), SEAggSize = std.error(meanAggSize))
+
+aggregatesDataTime5wtStats<-aggregatesDataTime5wt %>% group_by (Species,ConditionNew, Strain) %>% 
+  summarise(MeanAggs = mean(Aggs), SEAggs = std.error(Aggs), 
+            MeanBiomass = mean(biomass),SEBiomass = std.error(biomass), 
+            MeanAggSize = mean(meanAggSize), SEAggSize = std.error(meanAggSize))
+```
+
+```{r aggregate mean volume final figures}
+#final figures potentially for paper
+ggplot()+
+  geom_jitter(data = aggregatesDataTime5wt, aes(x = ConditionNew, y= meanAggSize), size = 1, height = 0, width = .3, shape = 1)+
+  geom_point(data = aggregatesDataTime5wtStats, aes(x = ConditionNew, y= MeanAggSize), size = 3, shape = 16)+
+  geom_errorbar(data = aggregatesDataTime5wtStats, aes(x = ConditionNew, ymin= MeanAggSize-SEAggSize,ymax= MeanAggSize+SEAggSize), width = .5)+
+  facet_grid(~Species, space = "free")+
+  scale_y_log10( limits = c(1e0,1e2))+
+  ggtitle('Aggregate size (wild type)')+
+  labs(x = "",y = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+
+ggplot()+
+  geom_jitter(data = aggregatesDataTime5mut, aes(x = ConditionNew, y= meanAggSize), size = 1, height = 0, width = .3, shape = 1)+
+  geom_point(data = aggregatesDataTime5mutStats, aes(x = ConditionNew, y= MeanAggSize), size = 3, shape = 16)+
+  geom_errorbar(data = aggregatesDataTime5mutStats, aes(x = ConditionNew, ymin= MeanAggSize-SEAggSize,ymax= MeanAggSize+SEAggSize), width = .5)+
+  facet_grid(~Species, space = "free")+
+  #scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1e0,1e2))+
+  scale_y_log10( limits = c(1e0,1e2))+
+  ggtitle('Aggregate size (pqsL mutant)')+
+  labs(x = "",y = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+```
+
+```{r aggregates extra metrics calculated}
 
@@
 
-```{r new threshold images histogram plots}
-allDataHistograms.5df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Histograms1/histograms5.csv',header=T)
-allDataHistograms.10df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Histograms1/histograms10.csv',header=T)
-allDataHistograms.50df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Histograms1/histograms50.csv',header=T)
-allDataHistograms.100df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Histograms1/histograms100.csv',header=T)
-allDataHistograms.100df<-allDataHistograms.100df %>% mutate(Coculture = recode(Condition, "Sa Mono" = "No", "Pa Mono" = "No", "Pa:Sa 1:1" = "Yes","Pa:Sa 10:1"= "Yes", "Pa:Sa 1:100" = "Yes", "Pa:Sa 1:10" = "Yes"))
-allDataHistograms.5df<-allDataHistograms.5df %>% mutate(Coculture = recode(Condition, "Sa Mono" = "No", "Pa Mono" = "No", "Pa:Sa 1:1" = "Yes","Pa:Sa 10:1"= "Yes", "Pa:Sa 1:100" = "Yes", "Pa:Sa 1:10" = "Yes"))
+```{r histogram plots data}
+allDataHistograms.5df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Histograms1/histograms5.csv',header=T)
+allDataHistograms.10df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Histograms1/histograms10.csv',header=T)
+allDataHistograms.50df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Histograms1/histograms50.csv',header=T)
+allDataHistograms.100df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Histograms1/histograms100.csv',header=T)
+
+hist.100<-allDataHistograms.100df %>% filter(TimePoint== 5) %>% filter( Condition %in% c("Sa Mono", "Pa Mono", "Pa:Sa 1:1")) %>% mutate(ConditionNew = recode(Condition, "Sa Mono" = "Mono", "Pa Mono" = "Mono", "Pa:Sa 1:1" = "Co"))
+allDataHistograms.5df <- allDataHistograms.5df %>% filter(TimePoint== 5) %>% filter( Condition %in% c("Sa Mono", "Pa Mono", "Pa:Sa 1:1")) %>% mutate(ConditionNew = recode(Condition, "Sa Mono" = "Mono", "Pa Mono" = "Mono", "Pa:Sa 1:1" = "Co"))
+
+#ok so I am going to try to do this...I can't do bar graphs because the width of the bars is too thin to be able to be seen by the viewer, so I am doing points
+#I also want to do mono and co pointing to opposite sides, but I haven't been able to do it with recode, so I'll manually do it.
+mono<- allDataHistograms.5df %>% filter(ConditionNew == "Mono") %>%  group_by(max, Species, ConditionNew, Strain) %>% summarise(Frequency = sum(frequency))
+co<- allDataHistograms.5df %>% filter(ConditionNew == "Co") %>% group_by(max, Species, ConditionNew, Strain) %>% summarise(Frequency = sum(frequency))
+
+#this is still showing the bins per sample, so I want to add the bins on each sample
+ggplot()+
+  geom_point(data = both %>% filter(Species == "Sa"), aes(y = max,x = CombinedFrequency, color = ConditionNew),stat = "identity", width = .6)+
+  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+                              #coord_flip() +  # Flip axes
+                              theme(plot.title = element_text(hjust = .5), 
+                                    axis.ticks = element_blank()) +   # Centre plot title
+                              theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))  # Color palette
+
+ggplot()+
+  geom_point(data = both %>% filter(Species == "Sa"& ConditionNew=="Mono"), 
+                 aes(x = max, y= -1000-CombinedFrequency,color = ConditionNew), size = 2, alpha = 0.8)+
+  geom_point(data = both %>% filter(Species == "Sa"& ConditionNew=="Co"), 
+                 aes(x = max, y=1000+CombinedFrequency, color = ConditionNew), size = 2, alpha = 0.8)+
+  #geom_label(aes(x = max, y = 0, label = max), 
+#         inherit.aes = F,
+#         size = 3.5, label.padding = unit(0.0, "lines"), label.size = 0,
+#         label.r = unit(0.0, "lines"), fill = "#EFF2F4", alpha = 0.9, color = "#5D646F")+
+  scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  #scale_y_continuous(breaks = c(c(-2, -1.5, -1, -0.5, 0) + -0.3, c(0, 0.5, 1, 1.5, 2)+0.3),
+   #              labels = c("2", "1.5", "1", "0.5", "0", "0", "0.5", "1", "1.5", "2"))+
+  facet_wrap(~Strain, ncol = 2)+
+  coord_flip()+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))  # Color palette
+
+#######
+#testing negative exponential
+reverselog_trans <- function(base = exp(1)) {
+    trans <- function(x) -log(x, base)
+    inv <- function(x) base^(-x)
+    trans_new(paste0("reverselog-", format(base)), trans, inv, 
+              log_breaks(base = base), 
+              domain = c(1e-100, Inf))
+}
+
+monoPlot<-ggplot()+
+  geom_point(data = mono %>% filter(Species == "Sa"),aes(x = max, y= Frequency), size = 2, alpha = 0.8)+
+  scale_y_continuous(trans=reverselog_trans(base=10),
+                     labels=trans_format("log10", scales::math_format(10^.x)))+
+  scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = c(1e0,5e5), position = "top")+
+  coord_flip()+
+  xlab("")+
+  ylab("Frequency")+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+
+coPlot<-ggplot()+
+  geom_point(data = co %>% filter(Species == "Sa"),aes(x = max, y= Frequency), size = 2, alpha = 0.8)+
+  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = c(1e0,5e5))+
+  coord_flip()+
+  xlab("")+
+  ylab("Frequency")+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+
+########
 
@@
   ggplot()+
-    geom_point(data=df1,aes(x=max, y=frequency, color = Coculture, shape = Condition))+
+    geom_point(data=df1,aes(y=max, x=frequency, color = ConditionNew, shape = Strain))+
     scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
     scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-    xlab('Biomass (um^3)')+
-    ylab('Frequency')+
+    ylab('Biomass (um^3)')+
+    xlab('Frequency')+
+    #facet_wrap(~Sample, ncol=3)+
     ggtitle(paste0(title," Raw biomass Distribution (bin size = 100 um)"))+
-    facet_wrap(~TimePoint, nrow=4)
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
 }
+
 #This shows that the Sa biomass that gets eaten by Staph is from the largest aggregates, not from the small ones
@@
 plotHist3DBiomassCountsLog(allDataHistograms.100df %>% filter(Species == "Pa"), "Pa co-culture vs mono")
+plotHist3DBiomassCountsLog(allDataHistograms.5df %>% filter(Species == "Sa"), "Sa co-culture vs mono")
 

### 2020-07-15 Microscopy Data Clean.Rmd
wrote functions to make plots for histograms of aggregates. Tha figure should be done for now.

@@
 hist.100<-allDataHistograms.100df %>% filter(TimePoint== 5) %>% filter( Condition %in% c("Sa Mono", "Pa Mono", "Pa:Sa 1:1")) %>% mutate(ConditionNew = recode(Condition, "Sa Mono" = "Mono", "Pa Mono" = "Mono", "Pa:Sa 1:1" = "Co"))
-allDataHistograms.5df <- allDataHistograms.5df %>% filter(TimePoint== 5) %>% filter( Condition %in% c("Sa Mono", "Pa Mono", "Pa:Sa 1:1")) %>% mutate(ConditionNew = recode(Condition, "Sa Mono" = "Mono", "Pa Mono" = "Mono", "Pa:Sa 1:1" = "Co"))
+hist.5 <- allDataHistograms.5df %>% filter(TimePoint== 5) %>% filter( Condition %in% c("Sa Mono", "Pa Mono", "Pa:Sa 1:1")) %>% mutate(ConditionNew = recode(Condition, "Sa Mono" = "Mono", "Pa Mono" = "Mono", "Pa:Sa 1:1" = "Co"))
 
@@
 #I also want to do mono and co pointing to opposite sides, but I haven't been able to do it with recode, so I'll manually do it.
-mono<- allDataHistograms.5df %>% filter(ConditionNew == "Mono") %>%  group_by(max, Species, ConditionNew, Strain) %>% summarise(Frequency = sum(frequency))
-co<- allDataHistograms.5df %>% filter(ConditionNew == "Co") %>% group_by(max, Species, ConditionNew, Strain) %>% summarise(Frequency = sum(frequency))
+cleanHist.5<-hist.5 %>% group_by(max, Species, ConditionNew, Strain) %>% summarise(Frequency = sum(frequency))
+cleanHist.100<-hist.100 %>% group_by(max, Species, ConditionNew, Strain) %>% summarise(Frequency = sum(frequency))
+#However, one thing I want to try is to have different aggregate cutoffs... have 5 um bins up to 100um and then have the rest of the bins at 100 um3, so..
+only5Hist<- cleanHist.5 %>% filter (max<=100)
+only100Hist<- cleanHist.100 %>% filter (max>100)
+bin5and100Hist<-bind_rows(only5Hist,only100Hist)
 
-#this is still showing the bins per sample, so I want to add the bins on each sample
-ggplot()+
-  geom_point(data = both %>% filter(Species == "Sa"), aes(y = max,x = CombinedFrequency, color = ConditionNew),stat = "identity", width = .6)+
-  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-                              #coord_flip() +  # Flip axes
-                              theme(plot.title = element_text(hjust = .5), 
-                                    axis.ticks = element_blank()) +   # Centre plot title
-                              theme_cowplot()+
-    theme(plot.title = element_text(hjust = 0.5))  # Color palette
-
-ggplot()+
-  geom_point(data = both %>% filter(Species == "Sa"& ConditionNew=="Mono"), 
-                 aes(x = max, y= -1000-CombinedFrequency,color = ConditionNew), size = 2, alpha = 0.8)+
-  geom_point(data = both %>% filter(Species == "Sa"& ConditionNew=="Co"), 
-                 aes(x = max, y=1000+CombinedFrequency, color = ConditionNew), size = 2, alpha = 0.8)+
-  #geom_label(aes(x = max, y = 0, label = max), 
-#         inherit.aes = F,
-#         size = 3.5, label.padding = unit(0.0, "lines"), label.size = 0,
-#         label.r = unit(0.0, "lines"), fill = "#EFF2F4", alpha = 0.9, color = "#5D646F")+
-  scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  #scale_y_continuous(breaks = c(c(-2, -1.5, -1, -0.5, 0) + -0.3, c(0, 0.5, 1, 1.5, 2)+0.3),
-   #              labels = c("2", "1.5", "1", "0.5", "0", "0", "0.5", "1", "1.5", "2"))+
-  facet_wrap(~Strain, ncol = 2)+
-  coord_flip()+
-  theme_cowplot()+
-  theme(plot.title = element_text(hjust = 0.5))  # Color palette
-
-#######
-#testing negative exponential
-reverselog_trans <- function(base = exp(1)) {
+#function for negative log
+reverselog_trans <- function(base = exp(1)) {#dont know exactly how this works, but it does... 
     trans <- function(x) -log(x, base)
@@
 
+plotButterfly<-function (species, strain){
 monoPlot<-ggplot()+
-  geom_point(data = mono %>% filter(Species == "Sa"),aes(x = max, y= Frequency), size = 2, alpha = 0.8)+
+  geom_point(data = bin5and100Hist %>% filter(ConditionNew == "Mono"& Strain == strain & Species == species),
+             aes(x = max, y= Frequency), size = 2, shape = 1)+
   scale_y_continuous(trans=reverselog_trans(base=10),
                      labels=trans_format("log10", scales::math_format(10^.x)))+
-  scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = c(1e0,5e5), position = "top")+
+  scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = c(1e0,2e5), position = "top")+
   coord_flip()+
@@
 coPlot<-ggplot()+
-  geom_point(data = co %>% filter(Species == "Sa"),aes(x = max, y= Frequency), size = 2, alpha = 0.8)+
-  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = c(1e0,5e5))+
+  geom_point(data = bin5and100Hist %>% filter(ConditionNew == "Co"& Strain == strain & Species == species),
+             aes(x = max, y= Frequency),shape = 1, size = 2)+
+  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = c(1e0,2e4))+
+  scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = c(1e0,2e5))+
   coord_flip()+
@@
   theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5), axis.text.y=element_blank())
+
+plot_grid(monoPlot+ theme(plot.margin = unit(c(1, -1.1, 0, 0), "cm")),coPlot+ theme(plot.margin = unit(c(1, 2, 0, 0), "cm")), align='vh', axis = "l",labels = c("Mono-culture", "Co-culture"),hjust = c(-1, -1.8),nrow = 1)
+}
+plotButterfly("Sa", "PA14wt")
+plotButterfly("Sa", "PA14mut")
+plotButterfly("Pa", "PA14wt")
+plotButterfly("Pa", "PA14mut")
+
+#showed this to Dan, and he didnt like them =( so I'll just do them the boring old way)
+plotNonButterfly<-function (species, strain){
+monoPlot<-ggplot()+
+  geom_point(data = bin5and100Hist %>% filter(ConditionNew == "Mono"& Strain == strain & Species == species),
+             aes(x = max, y= Frequency), size = 2, shape = 1)+
+  #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = c(1e0,2e4))+
+  scale_y_log10(breaks = c(1, 10, 100, 1000, 10000), labels = c("1", "10", "100", "1,000", "10,000"),limits = c(1e0,2e4))+
+  scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = c(1e0,2e5))+
+  coord_flip()+
+  labs(y = "Frequency",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+  theme_cowplot()+
   theme(plot.title = element_text(hjust = 0.5))
 
+coPlot<-ggplot()+
+  geom_point(data = bin5and100Hist %>% filter(ConditionNew == "Co"& Strain == strain & Species == species),
+             aes(x = max, y= Frequency),shape = 1, size = 2)+
+  #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = c(1e0,2e4))+
+  scale_y_log10(breaks = c(1, 10, 100, 1000, 10000), labels = c("1", "10", "100", "1,000", "10,000"),limits = c(1e0,2e4))+
+  scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = c(1e0,2e5))+
+  coord_flip()+
+  labs(y = "Frequency",x = "")+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+
+plot_grid(monoPlot+ theme(plot.margin = unit(c(1, 0, 0, 0), "cm")),coPlot+ theme(plot.margin = unit(c(1, 1, 0, 0), "cm")), align='vh', axis = "l",labels = c("Mono-culture", "Co-culture"),hjust = c(-1.4, -1.9),nrow = 1)
+}
+plotNonButterfly("Sa", "PA14wt")
+plotNonButterfly("Sa", "PA14mut")
+plotNonButterfly("Pa", "PA14wt")
+plotNonButterfly("Pa", "PA14mut")
+
 ########
+```
 
+```{r extra stuff}
 plotHist3DBiomassCountsLog<-function(df1, title){
@@
 #This shows that the Sa biomass that gets eaten by Staph is from the largest aggregates, not from the small ones
-plotHist3DBiomassCountsLog(allDataHistograms.100df %>% filter(Species == "Sa"), "Sa co-culture vs mono")
-plotHist3DBiomassCountsLog(allDataHistograms.100df %>% filter(Species == "Pa"), "Pa co-culture vs mono")
-plotHist3DBiomassCountsLog(allDataHistograms.5df %>% filter(Species == "Sa"), "Sa co-culture vs mono")
+plotHist3DBiomassCountsLog(hist.100 %>% filter(Species == "Sa"), "Sa co-culture vs mono")
+plotHist3DBiomassCountsLog(hist.100 %>% filter(Species == "Pa"), "Pa co-culture vs mono")
+plotHist3DBiomassCountsLog(hist.5 %>% filter(Species == "Sa"), "Sa co-culture vs mono")
 

### 2020-07-21 Microscopy Data Clean.Rmd
Added the mixed aggregate analysis

@@
 ```
-
+#Mean Agregate size figure
 ```{r aggregate mean volume final figures}
 #final figures potentially for paper
-ggplot()+
+
+MeanAggSizeWtPlot<-ggplot()+
   geom_jitter(data = aggregatesDataTime5wt, aes(x = ConditionNew, y= meanAggSize), size = 1, height = 0, width = .3, shape = 1)+
@@
 
-ggplot()+
+MeanAggSizeMutPlot<-ggplot()+
   geom_jitter(data = aggregatesDataTime5mut, aes(x = ConditionNew, y= meanAggSize), size = 1, height = 0, width = .3, shape = 1)+
@@
 monoPlot<-ggplot()+
-  geom_point(data = bin5and100Hist %>% filter(ConditionNew == "Mono"& Strain == strain & Species == species),
+  geom_point(data = cleanHist.5 %>% filter(ConditionNew == "Mono"& Strain == strain & Species == species),
              aes(x = max, y= Frequency), size = 2, shape = 1)+
@@
 coPlot<-ggplot()+
-  geom_point(data = bin5and100Hist %>% filter(ConditionNew == "Co"& Strain == strain & Species == species),
+  geom_point(data = cleanHist.5 %>% filter(ConditionNew == "Co"& Strain == strain & Species == species),
              aes(x = max, y= Frequency),shape = 1, size = 2)+
@@
 plotNonButterfly("Pa", "PA14mut")
-
-########
 ```
@@
 ```
+#Mixed Aggregates Analysis
+```{r mixed aggregates import data} 
+ReadMixedAggregateFile<-function(sample, imageSource){#This function outputs total number of pixels in the csv file from matlab
+  file<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/MixedAggregates/', sample,imageSource, '.csv')
+  datos <-read.csv(file, header = TRUE)
+  colnames(datos)<-c('Size', 'Sa', 'Pa', 'Overlap', 'Slice')
+  datos<-datos %>% mutate(Sample = sample)
+  return(datos)
+}
+testReadMixedAggregateFile<-ReadMixedAggregateFile('5-8-19','RedSubtract')
+PA14mut<- c('4-24-19', '4-25-19', '5-8-19')
+#wt data retrieval
+mixedAggDataWtList<-map2(PA14wt,'RedSubtract', ReadMixedAggregateFile) 
+mixedAggDataWt<-bind_rows(mixedAggDataWtList)
+mixedAggDataWt<-mixedAggDataWt %>% mutate(Strain = "PA14wt")
+#mut data retrieval
+mixedAggDataMutList<-map2(PA14mut,'RedSubtract',ReadMixedAggregateFile) 
+mixedAggDataMut<-bind_rows(mixedAggDataMutList)
+mixedAggDataMut<-mixedAggDataMut %>% mutate(Strain = "PA14mut")
+
+#This is the data for all objects
+mixedAggDataAll<-bind_rows(mixedAggDataWt,mixedAggDataMut)
+
+#this is only the biomass, which is the only thing I can actually compare since this is 2D
+mixedAggDataAllSlim<-mixedAggDataAll%>% group_by(Sample, Strain) %>%
+  summarise (Aggregates = n(), PaBiomass = sum(Pa), SaBiomass = sum(Sa), TotalBiomass = sum(Size))
+
+#this includes all the other maybe relevant data
+mixedAggDataAllStats<-mixedAggDataAll%>% group_by(Sample, Strain) %>%
+  summarise (Aggregates = n(), PaBiomass = sum(Pa), SaBiomass = sum(Sa), TotalBiomass = sum(Size)) %>% mutate(MeanSizeSample =Aggregates/TotalBiomass) %>%
+  ungroup() %>% group_by(Strain) %>% 
+  mutate(PaBiomassStrain = sum(PaBiomass), SaBiomassStrain = sum(SaBiomass), TotalBiomassStrain = sum(TotalBiomass), AggregatesStrain = sum(Aggregates)) %>% mutate(MeanSizeStrain = AggregatesStrain/TotalBiomassStrain, Source = "All")
+
+#This is the data for mixed-species aggregates only
+mixedAggDataDual<-mixedAggDataAll %>% filter(Sa > 0 & Pa >0)
+
+#only biomass
+mixedAggDataDualSlim<-mixedAggDataDual %>% group_by(Sample, Strain) %>% summarise (AggregatesMixed = n(), PaBiomassMixed = sum(Pa), SaBiomassMixed = sum(Sa), TotalBiomassMixed = sum(Size))
+
+#Compare all objects to dual-species objects
+combinedMixedAggData<- bind_cols(mixedAggDataAllSlim, mixedAggDataDualSlim)
+combinedMixedAggData<-combinedMixedAggData %>% mutate(PercentAggs = AggregatesMixed/Aggregates, PercentPaBiomass =  PaBiomassMixed/PaBiomass*100, PercentSaBiomass =  SaBiomassMixed/SaBiomass*100, PercentTotalBiomass = TotalBiomassMixed/TotalBiomass*100) %>% group_by(Strain) %>% mutate(MeanAggs = mean (PercentAggs), MeanPaBiomass = mean(PercentPaBiomass), MeanSaBiomass = mean(PercentSaBiomass), MeanTotalBiomass = mean(PercentTotalBiomass), SETotalBiomass = std.error(PercentTotalBiomass))
+
+combinedMixedAggData$Strain <- factor(combinedMixedAggData$Strain, levels = c("PA14wt", "PA14mut"))
+### I think this is the final figure
+MixedAggregatePlot<-ggplot()+
+  geom_point(data = combinedMixedAggData,aes(x=Strain,y=PercentTotalBiomass ),size=1)+
+  geom_point(data = combinedMixedAggData,aes(x=Strain,y=MeanTotalBiomass, shape = Strain),size=3)+
+  geom_errorbar(data = combinedMixedAggData,aes(x=Strain,ymin=MeanTotalBiomass-SETotalBiomass, ymax =MeanTotalBiomass+SETotalBiomass),size=.2, width = .2)+
+  #labs(title ="Proportion of mixed species biomass")+
+  #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  scale_shape_manual(values = c(1,2),name = "", limits=c("PA14wt","PA14mut"))+
+  scale_x_discrete(breaks=c("PA14wt","PA14mut"), 
+                     labels = c(bquote(paste(" wild-type")),
+                                bquote(paste(italic(Delta*"pqsL")))))+
+  labs(y = "Percent mixed aggregates biomass", x = "")+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5),legend.position="none")
+
+#this includes all the other maybe relevant data but for dual-species aggregates only
+mixedAggDataDualStats<-mixedAggDataDual %>% group_by(Sample, Strain) %>%
+  summarise (Aggregates = n(), PaBiomass = sum(Pa), SaBiomass = sum(Sa), TotalBiomass = sum(Size)) %>% mutate(MeanSizeSample =Aggregates/TotalBiomass) %>%
+  ungroup() %>% group_by(Strain) %>% 
+  mutate(PaBiomassStrain = sum(PaBiomass), SaBiomassStrain = sum(SaBiomass), TotalBiomassStrain = sum(TotalBiomass), AggregatesStrain = sum(Aggregates)) %>% mutate(MeanSizeStrain = AggregatesStrain/TotalBiomassStrain, Source = "Mixed")
+
+```
+# Combining all Spatial Data
+
+```{r final figure}
+#So, I need the mean aggregate size figure first
+MeanAggSizeWtPlot
+MeanAggSizeMutPlot
+
+plotNonButterfly("Sa", "PA14wt")
+plotNonButterfly("Sa", "PA14mut")
+plotNonButterfly("Pa", "PA14wt")
+plotNonButterfly("Pa", "PA14mut")
+
+MixedAggregatePlot
+
+#Enrichment plot
+sa.paPlot<-ggplot()+
+  geom_point(data = enrichmentDataFinal %>% filter(Relation == "Sa->Pa"),aes(y=meanEnrichment, x = Strain, shape = Strain),size=4)+
+  geom_errorbar(data = enrichmentDataFinal %>% filter(Relation == "Sa->Pa"),
+                aes(ymin = meanEnrichment-sdEnrichment,ymax = meanEnrichment+sdEnrichment, x = Strain),size=.2, width = .1)+
+  labs( y = bquote(paste("Distance ("*mu*"m)")), x = "" ) +
+  scale_shape_manual(values = c(1,2),name = "", limits=c("wt","mut"),labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type")),
+                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL"))))+
+  scale_x_discrete(name ="", breaks = c("wt","mut"), labels =c("wild-type",expression(""*Delta*"pqsL")))+
+  ylim(1, 9)+
+  theme_cowplot()
+
+sa.saPlot<-ggplot()+
+  geom_point(data = enrichmentDataFinal %>% filter(Relation == "Sa->Sa"),aes(y=meanEnrichment, x = Strain, shape = Strain),size=4)+
+  geom_errorbar(data = enrichmentDataFinal %>% filter(Relation == "Sa->Sa"),
+                aes(ymin = meanEnrichment-sdEnrichment,ymax = meanEnrichment+sdEnrichment, x = Strain),size=.2, width = .1)+
+  labs( y = bquote(paste("Distance ("*mu*"m)")), x = "" ) +
+  scale_shape_manual(values = c(1,2),name = "", limits=c("wt","mut"),labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type")),
+                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL"))))+
+  scale_x_discrete(name ="", breaks = c("wt","mut"), labels =c("wild-type",expression(""*Delta*"pqsL")))+
+  ylim(1, 9)+
+  theme_cowplot()
+
+legendFigure3 <- get_legend(sa.saPlot + theme(legend.box.margin = margin(0, 0, 0, -10)))
+figure3 <- plot_grid(sa.saPlot+theme(legend.position="none"),sa.paPlot+theme(legend.position="none"),
+                      align='vh',labels = c("B", "C"),hjust = -1,nrow = 1)
+plot_grid(figure3,legendFigure3,rel_widths = c(4, 1.7))
+#plot_grid(sa.saPlot,sa.paPlot,align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)
+
+```

### 2020-07-23 Microscopy Data Clean.Rmd
added option to input data frame (to include vairable size bins) to histograms and flipped the coordinates

@@
 #showed this to Dan, and he didnt like them =( so I'll just do them the boring old way)
-plotNonButterfly<-function (species, strain){
+plotNonButterfly<-function (df,species, strain){
 monoPlot<-ggplot()+
-  geom_point(data = cleanHist.5 %>% filter(ConditionNew == "Mono"& Strain == strain & Species == species),
+  geom_point(data = df %>% filter(ConditionNew == "Mono"& Strain == strain & Species == species),
              aes(x = max, y= Frequency), size = 2, shape = 1)+
@@
   scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = c(1e0,2e5))+
-  coord_flip()+
   labs(y = "Frequency",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
@@
 coPlot<-ggplot()+
-  geom_point(data = cleanHist.5 %>% filter(ConditionNew == "Co"& Strain == strain & Species == species),
+  geom_point(data = df %>% filter(ConditionNew == "Co"& Strain == strain & Species == species),
              aes(x = max, y= Frequency),shape = 1, size = 2)+
@@
   scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = c(1e0,2e5))+
-  coord_flip()+
-  labs(y = "Frequency",x = "")+
+  labs(y = "",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
   theme_cowplot()+
@@
 }
-plotNonButterfly("Sa", "PA14wt")
-plotNonButterfly("Sa", "PA14mut")
-plotNonButterfly("Pa", "PA14wt")
-plotNonButterfly("Pa", "PA14mut")
+plotNonButterfly(only5Hist,"Sa", "PA14wt")
+plotNonButterfly(only5Hist,"Sa", "PA14mut")
+plotNonButterfly(only5Hist,"Pa", "PA14wt")
+plotNonButterfly(only5Hist, "Pa", "PA14mut")
+
+plotNonButterfly(bin5and100Hist,"Sa", "PA14wt")
+plotNonButterfly(bin5and100Hist,"Sa", "PA14mut")
+plotNonButterfly(bin5and100Hist,"Pa", "PA14wt")
+plotNonButterfly(bin5and100Hist, "Pa", "PA14mut")
 ```

### 2020-07-24 Microscopy Data Clean.Rmd
added plank vs aggregate and log bins graphs

@@
 
-```{r histogram plots data}
+```{r Aggregate histograms plots}
 allDataHistograms.5df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Histograms1/histograms5.csv',header=T)
@@
 #I also want to do mono and co pointing to opposite sides, but I haven't been able to do it with recode, so I'll manually do it.
-cleanHist.5<-hist.5 %>% group_by(max, Species, ConditionNew, Strain) %>% summarise(Frequency = sum(frequency))
+cleanHist.5<-hist.5 %>% group_by(max, Species, ConditionNew, Strain) %>% summarise(Frequency = sum(frequency))#Combine aggregates from all 3 samples
 cleanHist.100<-hist.100 %>% group_by(max, Species, ConditionNew, Strain) %>% summarise(Frequency = sum(frequency))
@@
 plotNonButterfly(bin5and100Hist, "Pa", "PA14mut")
+```
+```{r Aggregate histograms planktonic vs aggregte}
+hist.plank.Agg<-hist.5 %>%  group_by(Species, Sample,Condition,Strain)%>% 
+  mutate(Aggregation = case_when(max == 5 ~ "Planktonic",
+                        max>5 ~ "Aggregate")) %>% ungroup() %>% 
+  group_by(Species,Sample,Condition,Strain,Aggregation) %>% mutate(FrequencyAggregation = sum(frequency), BiomassAggregation = sum(BiomassBin), DensityAggregation = sum(Density))
+hist.plank.Agg.Stats<-hist.plank.Agg %>% group_by(Species,Condition, ConditionNew,Strain,Aggregation) %>%
+  summarise(MeanFreq = mean(FrequencyAggregation), SEFreq = std.error(FrequencyAggregation), MeanBiomass = mean(BiomassAggregation), SEBiomass = std.error(BiomassAggregation))
+
+PlotAggsPlank<- function(strain, titulo){
+ggplot()+
+  geom_col(data = hist.plank.Agg.Stats %>% filter(Strain == strain),aes(x=ConditionNew,y=MeanBiomass, fill = Aggregation),size=3,position = position_dodge( width = .9))+
+  geom_errorbar(data = hist.plank.Agg.Stats%>% filter(Strain == strain),aes(x=ConditionNew,ymin=MeanBiomass-SEBiomass, ymax = MeanBiomass+SEBiomass),size=.5,position = position_dodge2( width = .6))+
+  facet_grid(.~Species)+
+  labs(title = titulo, x = "", y = "Biomass contribution")+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+}
+PlotAggsPlank("PA14wt", "wt")
+PlotAggsPlank("PA14wt", "pqsL")
+
+```
+```{r Aggregate histograms logarithmic bins}
+#Now I need to do histograms with bins in a log scale, but for this I want to use the raw data that includes biomass per bin and density.
+#let's start by revisiting the original data set and just filter one sample to simplify things:
+hist.5.rep1<-hist.5 %>% filter(Sample == "rep1"&Condition == "Pa Mono"&Strain=="PA14mut")
+hist.5.rep1.logBins<-hist.5.rep1 %>% 
+  mutate(LogBin = case_when(max <= 10 ~ 10,
+                        max<= 100    ~ 100,
+                        max<= 1000   ~ 1000,
+                        max<= 10000  ~ 10000,
+                        max<= 100000 ~ 100000,
+                        max > 100000 ~ 1000000)) %>% 
+  group_by(LogBin) %>% mutate(FrequencyLogBin = sum(frequency), BiomassLogBin = sum(BiomassBin), DensityLogBin = sum(Density))
+#Now this is the real case
+hist.5.LogBin<-hist.5 %>%  group_by(Species, Sample,Condition,Strain)%>% 
+  mutate(LogBin = case_when(max <= 10 ~ 10,
+                        max<= 100    ~ 100,
+                        max<= 1000   ~ 1000,
+                        max<= 10000  ~ 10000,
+                        max<= 100000 ~ 100000,
+                        max > 100000 ~ 1000000)) %>% ungroup() %>% 
+  group_by(Species, Sample,Condition,Strain,LogBin) %>% mutate(FrequencyLogBin = sum(frequency), BiomassLogBin = sum(BiomassBin), DensityLogBin = sum(Density))
+
+#this is easier to put in bar graphs
+hist.5.LogBinSummarize<-hist.5 %>%  group_by(Sample,Species,Condition,Strain)%>% 
+  mutate(LogBin = case_when(max <= 10 ~ 10,
+                        max<= 100    ~ 100,
+                        max<= 1000   ~ 1000,
+                        max<= 10000  ~ 10000,
+                        max<= 100000 ~ 100000,
+                        max > 100000 ~ 1000000)) %>% ungroup() %>% 
+  group_by(Species, Sample,Condition,ConditionNew,Strain,LogBin) %>% summarise(FrequencyLogBin = sum(frequency), BiomassLogBin = sum(BiomassBin), DensityLogBin = sum(Density))
+
+#Now separate them by strain, since I am doing that anyways
+hist.LogBin.wt <-hist.5.LogBin %>% filter(Strain == "PA14wt")
+hist.LogBin.mut<-hist.5.LogBin %>% filter(Strain == "PA14mut")
+PlotFreqLogBin<-function(strain, species,titulo){
+  df <-hist.5.LogBinSummarize%>% filter(Strain == strain & Species == species)
+  ggplot()+
+    geom_col(data = df,aes(x=as.factor(LogBin),y=FrequencyLogBin,  fill =Sample ),size=4)+
+    #geom_point(data = df,aes(x=as.factor(LogBin),y=FrequencyLogBin,  shape =Sample ),size=4)+
+    geom_label(data = df %>% filter(Sample == "rep1"),aes(x=as.factor(LogBin),y=1, label =round(BiomassLogBin*100,digits=1), color = "rep1"),size=4)+
+    geom_label(data = df%>% filter(Sample == "rep2"),aes(x=as.factor(LogBin),y=.325, label =round(BiomassLogBin[Sample=="rep2"]*100,digits=1), color = "rep2"),size=4)+
+    geom_label(data = df%>% filter(Sample == "rep3"),aes(x=as.factor(LogBin),y=.1, label =round(BiomassLogBin[Sample=="rep3"]*100,digits=1), color = "rep3"),size=4)+
+    labs(title = titulo)+
+    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_grid(.~ConditionNew)+
+    labs(y = "Frequency",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    guides(color = FALSE)+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+}
+PlotFreqLogBin("PA14wt", "Sa", "Sa WT")
+PlotFreqLogBin("PA14wt", "Pa", "Pa WT")
+PlotFreqLogBin("PA14mut", "Sa", "Sa pqsL")
+PlotFreqLogBin("PA14mut", "Pa", "Pa pqsL")
+
 ```

### 2020-07-28 Microscopy Data Clean.Rmd
updated figures

--- 2020-07-23 Microscopy Data Clean.Rmd
@@
 plotNonButterfly(bin5and100Hist, "Pa", "PA14mut")
+```
+```{r Aggregate histograms planktonic vs aggregte}
+
+#this is the summary beacuse I dont like further analyzing data after summarizing shit, so mutate at the top follows 
+hist.plank.Agg.Sumary<-hist.5 %>%  group_by(Species, Sample,Condition,Strain)%>% 
+  mutate(Aggregation = case_when(max == 5 ~ "Planktonic",
+                        max>5 ~ "Aggregate")) %>% ungroup() %>% 
+  group_by(Species,Sample,Condition,ConditionNew, Strain,Aggregation) %>% summarize(FrequencyAggregation = sum(frequency), BiomassAggregation = sum(BiomassBin), DensityAggregation = sum(Density))
+#now I have to do some t-tests, since I used the same cultures for mono and co for each replicate, paired t-tests are allowed.
+##### 
+#I know this sucks, but it's 1 AM so idgaf
+SaMonoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+SaCoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+SaWtAggTest<-t.test(x = SaMonoWtAggSum, y = SaCoWtAggSum, paired = T)
+SaMonoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+SaCoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Species == "Sa", ConditionNew == "Co", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+SaMutAggTest<-t.test(x = SaMonoMutAggSum, y = SaCoMutAggSum, paired = T)
+
+PaMonoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Pa Mono", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+PaCoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Species == "Pa", ConditionNew == "Co", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+PaWtAggTest<-t.test(x = PaMonoWtAggSum, y = PaCoWtAggSum, paired = T)
+PaMonoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Pa Mono", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+PaCoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Species == "Pa", ConditionNew == "Co", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+PaMutAggTest<-t.test(x = PaMonoMutAggSum, y = PaCoMutAggSum, paired = T)
+
+SaMonoWtVsMutAggTest<-t.test(x = SaMonoWtAggSum, y = SaMonoMutAggSum, paired = F)
+SaCoWtVsMutAggTest<-t.test(x = SaCoWtAggSum, y = SaCoMutAggSum, paired = F)
+PaMonoWtVsMutAggTest<-t.test(x = PaMonoWtAggSum, y = PaMonoMutAggSum, paired = F)
+PaCoWtVsMutAggTest<-t.test(x = PaCoWtAggSum, y = PaCoMutAggSum, paired = F)
+
+tTestDataAggvsPlank<-list(SaWtAggTest, SaMutAggTest, PaWtAggTest,PaMutAggTest,SaMonoWtVsMutAggTest,SaCoWtVsMutAggTest,PaMonoWtVsMutAggTest,PaCoWtVsMutAggTest)
+TtestTable<-name <- function(dataPoint) {
+  data <-data.frame(dataPoint$data.name, dataPoint$p.value)
+}
+tTestDataTable<-bind_rows(map(tTestDataAggvsPlank, TtestTable))
+#so, it turns out I only had to do either agg or plank since the variance is the same. COOL...
+
+#####
+#this is using mutate which is the same as above
+
+hist.plank.Agg.Stats<-hist.plank.Agg.Sumary %>% group_by(Species,Condition, ConditionNew,Strain,Aggregation) %>%
+  summarise(MeanFreq = mean(FrequencyAggregation), SEFreq = std.error(FrequencyAggregation), MeanBiomass = mean(BiomassAggregation), SEBiomass = std.error(BiomassAggregation))
+
+PlotAggsPlank<- function(strain, titulo){
+ggplot()+
+  geom_col(data = hist.plank.Agg.Stats %>% filter(Strain == strain),aes(x=ConditionNew,y=MeanBiomass, fill = Aggregation),size=3,position = position_dodge( width = .9))+
+  geom_errorbar(data = hist.plank.Agg.Stats%>% filter(Strain == strain),aes(x=ConditionNew,ymin=MeanBiomass-SEBiomass, ymax = MeanBiomass+SEBiomass),size=.5,position = position_dodge2( width = .6))+
+  facet_grid(.~Species)+
+  labs(title = titulo, x = "", y = "Biomass contribution")+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+}
+PlotAggsPlank("PA14wt", "wt")
+PlotAggsPlank("PA14mut", "pqsL")
+
+```
+```{r Aggregate histograms logarithmic bins}
+#Now I need to do histograms with bins in a log scale, but for this I want to use the raw data that includes biomass per bin and density.
+#let's start by revisiting the original data set and just filter one sample to simplify things:
+hist.5.rep1<-hist.5 %>% filter(Sample == "rep1"&Condition == "Pa Mono"&Strain=="PA14mut")
+hist.5.rep1.logBins<-hist.5.rep1 %>% 
+  mutate(LogBin = case_when(max <= 10 ~ 10,
+                        max<= 100    ~ 100,
+                        max<= 1000   ~ 1000,
+                        max<= 10000  ~ 10000,
+                        max<= 100000 ~ 100000,
+                        max > 100000 ~ 1000000)) %>% 
+  group_by(LogBin) %>% mutate(FrequencyLogBin = sum(frequency), BiomassLogBin = sum(BiomassBin), DensityLogBin = sum(Density))
+#Now this is the real case
+hist.5.LogBin<-hist.5 %>%  group_by(Species, Sample,Condition,Strain)%>% 
+  mutate(LogBin = case_when(max <= 10 ~ 10,
+                        max<= 100    ~ 100,
+                        max<= 1000   ~ 1000,
+                        max<= 10000  ~ 10000,
+                        max<= 100000 ~ 100000,
+                        max > 100000 ~ 1000000)) %>% ungroup() %>% 
+  group_by(Species, Sample,Condition,Strain,LogBin) %>% mutate(FrequencyLogBin = sum(frequency), BiomassLogBin = sum(BiomassBin), DensityLogBin = sum(Density))
+
+#this is easier to put in bar graphs
+hist.5.LogBinSummarize<-hist.5 %>% filter(!max == 5)%>%  group_by(Sample,Species,Condition,Strain)%>% 
+  mutate(LogBin = case_when(max <= 10 ~ 10,
+                        max<= 100    ~ 100,
+                        max<= 1000   ~ 1000,
+                        max<= 10000  ~ 10000,
+                        max<= 100000 ~ 100000,
+                        max > 100000 ~ 1000000)) %>% ungroup() %>% 
+  group_by(Species, Sample,Condition,ConditionNew,Strain,LogBin) %>% summarise(FrequencyLogBin = sum(frequency), BiomassLogBin = sum(BiomassBin), DensityLogBin = sum(Density))
+
+PlotFreqLogBin<-function(strain, species,titulo){
+  df <-hist.5.LogBinSummarize%>% filter(Strain == strain & Species == species)
+  ggplot()+
+    geom_col(data = df,aes(x=as.factor(LogBin),y=FrequencyLogBin,  fill =Sample ),size=4)+
+    #geom_point(data = df,aes(x=as.factor(LogBin),y=FrequencyLogBin,  shape =Sample ),size=4)+
+    geom_label(data = df %>% filter(Sample == "rep1"),aes(x=as.factor(LogBin),y=1, label =round(BiomassLogBin*100,digits=1), color = "rep1"),size=4)+
+    geom_label(data = df%>% filter(Sample == "rep2"),aes(x=as.factor(LogBin),y=.325, label =round(BiomassLogBin[Sample=="rep2"]*100,digits=1), color = "rep2"),size=4)+
+    geom_label(data = df%>% filter(Sample == "rep3"),aes(x=as.factor(LogBin),y=.1, label =round(BiomassLogBin[Sample=="rep3"]*100,digits=1), color = "rep3"),size=4)+
+    labs(title = titulo)+
+    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_grid(.~ConditionNew)+
+    labs(y = "Frequency",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    guides(color = FALSE)+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+}
+PlotFreqLogBin("PA14wt", "Sa", "Sa WT")
+PlotFreqLogBin("PA14wt", "Pa", "Pa WT")
+PlotFreqLogBin("PA14mut", "Sa", "Sa pqsL")
+PlotFreqLogBin("PA14mut", "Pa", "Pa pqsL")
+
 ```

### 2020-07-28 Paper Figures/Paper figures Scipts.Rmd
updated figures

@@
       geom_errorbar(data=statsData%>% filter(condition == "Shaking" & strain == "wt"),aes(x = time, ymin = logCFUmean-logCFUse, ymax=logCFUmean+logCFUse), width = 0, size = 0.5)+
-      geom_hline(yintercept=9.619, color='gray', linetype = "solid") + #Pa stirred
-      geom_hline(yintercept=9.13, color='gray', linetype = "dashed") + #Sa stirred
-      scale_linetype_manual(values = c( "solid","dashed"), labels = c("P.aeruginosa","S. aureus"))+
+      geom_hline(yintercept=9.619, color='red', linetype = "solid") + #Pa stirred
+      geom_hline(yintercept=9.13, color='red', linetype = "dashed") + #Sa stirred
+      scale_linetype_manual(values = c( "solid","dashed"), labels = c(bquote(paste(italic('P. aeruginosa'))),bquote(paste(italic('S. aureus')))))+
       labs(x = "Time (hours)", y = expression(paste(Log[10], " CFU")), linetype = "Species")+
@@
       scale_linetype_manual(values = c( "solid","dashed"), labels = c("stirred","static"))+
-      geom_hline(yintercept=8.88, color='gray', linetype = "dashed") +
-      geom_hline(yintercept=9.07, color='gray', linetype = "solid") +
+      geom_hline(yintercept=8.88, color='red', linetype = "dashed") +
+      geom_hline(yintercept=9.07, color='red', linetype = "solid") +
       labs(x = "Time (hours)", y = expression(paste(Log[10], " CFU")), linetype = "")+
@@
     prow <- plot_grid(shakingWtPlot+theme(legend.position="none"),staticWtPlot+theme(legend.position="none"),
-                      align='vh',labels = c("Stirred", "Static"),hjust = c(-3, -3.8),nrow = 1)
+                      align='vh',labels = c("Mixed", "Static"),hjust = c(-3, -3.8),nrow = 1)
     plot_grid(prow,legend,rel_widths = c(3, .4))
@@
     geom_errorbar(data=statsData%>% filter(condition == "Shaking" & strain == "mut"), aes(x = time, ymin = logCFUmean-logCFUse, ymax = logCFUmean+logCFUse), width = 0, size = 0.5)+
-    scale_linetype_manual(values = c( "solid","dashed"), labels = c("P.aeruginosa","S. aureus"))+
-    geom_hline(yintercept=9.13, color='gray', linetype = "dashed") +
-    geom_hline(yintercept=9.57, color='gray', linetype = "solid") +
+    scale_linetype_manual(values = c( "solid","dashed"), labels = c(bquote(paste(italic('P. aeruginosa'))),bquote(paste(italic('S. aureus')))))+
+    geom_hline(yintercept=9.13, color='red', linetype = "dashed") +
+    geom_hline(yintercept=9.57, color='red', linetype = "solid") +
     labs(x = "Time (hours)", y = expression(paste(Log[10], " CFU")), linetype = "Species")+
@@
     geom_errorbar(data=statsData%>% filter(condition == "Static" & strain ==  "mut"), aes(x = time, ymin = logCFUmean-logCFUse, ymax = logCFUmean+logCFUse), width = 0, size = 0.5)+
-    scale_linetype_manual(values = c( "solid","dashed"), labels = c("P.aeruginosa","S. aureus"))+
-    geom_hline(yintercept=8.88, color='gray', linetype = "dashed") +
-    geom_hline(yintercept=8.98, color='gray', linetype = "solid") +
+    scale_linetype_manual(values = c( "solid","dashed"), labels = c(bquote(paste(italic('P. aeruginosa'))),bquote(paste(italic('S. aureus')))))+
+    geom_hline(yintercept=8.88, color='red', linetype = "dashed") +
+    geom_hline(yintercept=8.98, color='red', linetype = "solid") +
     labs(x = "Time (hours)", y = expression(paste(Log[10], " CFU")), linetype = "")+
@@
   prow <- plot_grid(shakingMutPlot+theme(legend.position="none"),staticMutPlot+theme(legend.position="none"),
-                      align='vh',labels = c("Stirred", "Static"),hjust = c(-3, -3.8),nrow = 1)
+                      align='vh',labels = c("Mixed", "Static"),hjust = c(-3, -3.8),nrow = 1)
     plot_grid(prow,legend,rel_widths = c(3, .4))

### 2020-07-28 Staph killing assays/Staph killing report.Rmd
updated figures

@@
 ```{r zone of inhibition data input}
-diskFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/pqsL SCFM2/Staph killing assays/disk difussion assays.csv"
+diskFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/PaSa Project/Staph killing assays/disk difussion assays.csv"
 diskData <-read.csv(diskFile)
@@
 #this is the original Figure but it needs to be split in two parts
-    DiskPlot<-ggplot()+
-      geom_errorbar(data=diskDataStats1, aes(x = strain, ymin = meanBio - SDBio, ymax = meanBio + SDBio, group = condition),position = position_dodge(width = .6), width = .2)+
-      geom_point(data=diskDataStats1, aes(x=strain, y=meanBio, shape =CondStrain),position = position_dodge2(width = .6), size=3)+
+    DiskPlotSup<-ggplot()+
+      geom_errorbar(data=diskDataStats1, aes(x = condition, ymin = meanBio - SDBio, ymax = meanBio + SDBio, group = strain),position = position_dodge(width = .6), width = .2)+
+      geom_point(data=diskDataStats1, aes(x=condition, y=meanBio, shape =CondStrain, group = strain),position = position_dodge(width = .6), size=3)+
       scale_shape_manual(values = c(1,2,16,17),limits=c("wtStat","pqsLStat","wtShake", "pqsLShake"), 
@@
                                 bquote(paste(italic('P. aeruginosa '), Delta*"pqsL stirred"))))+
-      scale_x_discrete(name ="", breaks = c("wt","pqsl"), labels =c("wild-type",expression(""*Delta*"pqsL")))+
+      scale_x_discrete(name ="", breaks = c("static","shaking"), labels =c("Static","Mixed"))+
       labs( y = "Zone of inhibition (mm)", shape = "Growth condtion") +
@@
 
-    luminescencePlot<-ggplot()+
-      geom_line(data=luminescenceData1, aes(x=TimePoint, y=Mean, linetype = Condition, group = interaction (Strain, Condition)), size=.5,show.legend = FALSE)+
-      geom_point(data=luminescenceData1, aes(x=TimePoint, y=Mean, shape = CondStrain), size=3)+
+    luminescencePlotSup<-ggplot()+
+      geom_line(data=luminescenceData1%>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, linetype = Condition, group = interaction (Strain, Condition)), size=.5,show.legend = FALSE)+
+      geom_point(data=luminescenceData1%>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, shape = CondStrain), size=3)+
       scale_y_log10(name=expression(paste(italic('S. aureus'), " % luminescence vs control" )))+
@@
 
-    legendFigure2 <- get_legend(luminescencePlot + theme(legend.box.margin = margin(0, 0, 0, -10)))
-    figure2 <- plot_grid(DiskPlot+theme(legend.position="none"),luminescencePlot+theme(legend.position="none"),
+    legendFigureS3 <- get_legend(luminescencePlotSup + theme(legend.box.margin = margin(0, 0, 0, -10)))
+    figureS3 <- plot_grid(DiskPlotSup+theme(legend.position="none"),luminescencePlotSup+theme(legend.position="none"),
                       align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)
-    plot_grid(figure2,legendFigure2,rel_widths = c(6, 1.7))
+    plot_grid(figureS3,legendFigureS3,rel_widths = c(6, 1.7))
 ```
@@
                      labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type static")),
-                                bquote(paste(italic('P. aeruginosa'), " wild-type stirred"))))+
-      scale_x_discrete(name ="", breaks = c("static","shaking"), labels =c("Static","Stirred"))+
+                                bquote(paste(italic('P. aeruginosa'), " wild-type mixed"))))+
+      scale_x_discrete(name ="", breaks = c("static","shaking"), labels =c("Static","Mixed"))+
     ylim(0,17.5)+
-  labs( y = "Zone of inhibition (mm)", shape = "Growth condtion") +
+  labs( y = "Zone of inhibition (mm)", shape = "") +
       theme_cowplot(12)
@@
                      labels = c(bquote(paste(italic('P. aeruginosa '), Delta*"pqsL static")),
-                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL stirred"))))+
+                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL mixed"))))+
       ylim(0,17.5)+
-      scale_x_discrete(name ="", breaks = c("static","shaking"), labels =c("Static","Stirred"))+
+      scale_x_discrete(name ="", breaks = c("static","shaking"), labels =c("Static","Mixed"))+
       labs( y = "Zone of inhibition (mm)", shape = "Growth condtion") +
@@
                      labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type static")),
-                                bquote(paste(italic('P. aeruginosa'), " wild-type stirred"))))+
+                                bquote(paste(italic('P. aeruginosa'), " wild-type mixed"))))+
       theme(legend.position="top")+
@@
 
-    luminescencePlotMut<-
-      ggplot()+
-      geom_line(data=luminescenceData1 %>% filter (Strain == "pqsL") %>% filter (TimePoint<8), aes(x=TimePoint, y=Mean, group = Condition), size=.5, show.legend = FALSE)+
-      geom_point(data=luminescenceData1%>% filter (Strain == "pqsL") %>% filter (TimePoint<8), aes(x=TimePoint, y=Mean, shape = Condition), size=3)+
+    luminescencePlotMut<-ggplot()+
+      geom_line(data=luminescenceData1 %>% filter (Strain == "pqsL") %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, group = Condition), size=.5, show.legend = FALSE)+
+      geom_point(data=luminescenceData1%>% filter (Strain == "pqsL") %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, shape = Condition), size=3)+
       scale_y_log10(name=expression(paste(italic('S. aureus'), " % luminescence vs control" )),limits = c(1,121), labels = c(1,10,100),breaks = c(1, 10, 100))+
@@
                      labels = c(bquote(paste(italic('P. aeruginosa '), Delta*"pqsL static")),
-                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL stirred"))))+
+                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL mixed"))))+
       theme(legend.position="top")+

### 2020-07-28 Matlab scripts/mixedAggregates.m
matlab script for mixed aggregates

@@ -1,0 +1,59 @@
+slices = 91;%these are # of slices -1, the number on the file
+
+GetMixedAggregates('5-8-19', slices);
+GetMixedAggregates('3-13-19', slices);
+GetMixedAggregates('3-19-19', slices);
+GetMixedAggregates('4-17-19', slices);
+GetMixedAggregates('4-24-19', slices);
+GetMixedAggregates('4-25-19', slices);
+
+%PA14wt<- c('3-13-19', '3-19-19', '4-17-19')
+%PA14mut<- c('4-24-19', '4-25-19', '5-8-19')
+
+function GetMixedAggregates( date, slices)
+resultsfilePath = strcat('/Volumes/Seagate Backup Plus Drive/Good images/', date,'/mixedAggregatesData/');
+[~,~] = mkdir(resultsfilePath);
+totalSegments=0;%object counter
+results = zeros(1,5);%storing data
+for slice = 0:slices
+    name = strcat('/Volumes/Seagate Backup Plus Drive/Good images/', date,'/images1/','t05_p2_s', GetSlice(slice),'.tif');
+    I = im2double(imread(name));
+    [r, c, p] = size(I);%store size of picture
+    rgbImBi = im2bw(I , 0.01);%the idea of this is to convert an rgb image into a single color
+    ImR = squeeze(I(:,:,1));
+    ImG = squeeze(I(:,:,2));
+    [labels1,numLabels1] = bwlabel(rgbImBi);%combined image
+    results = [results;zeros(numLabels1, 5)];
+    for item = totalSegments+1:totalSegments+numLabels1
+        labels = zeros(r,c);%zero array to imprint each combined aggregate
+        zeroG = zeros(r,c);%zero array to imprint red portion of the aggregate
+        zeroR = zeros(r,c);%zero array to imprint green portion of the aggregate
+        labels(labels1==(item-totalSegments))=1;%pick the aggregate 
+        redInt = labels+ImR;%add red and combined binary images
+        greenInt = labels+ImG;%add green and combined binary images
+        aggregateSize = nnz(labels);%declare meaningful variable names
+        zeroG(greenInt==2)=1;%store green overlaping pixels on an array
+        zeroR(redInt==2)=1;%store blue overlaping pixels on an array
+        greenPixels = nnz(zeroG);%store amount of green overlap
+        redPixels = nnz(zeroR);%store amount of red overlap
+        overlap = redPixels+greenPixels-aggregateSize;
[…]

### 2020-07-28 PropOc Data 3D.Rmd
proportional occupancy script

--- 2020-04-28 R Analysis Scripts/PropOc Data 3D.Rmd
@@
 
-wt1.2Whole<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataAll/wt1-1000-2.csv"),header = T)
-wt2.2Whole<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataAll/wt2-1000-2.csv"),header = T)
-wt3.2Whole<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataAll/wt3-1000-2.csv"),header = T)
-
 ```
@@
 }
+
+ggplot()+ 
+    geom_point(data = wt1.1Whole.5log2 %>% filter (Source == "finalGG"),aes(x=Value,y=Frequency, color = Distance),size=2)+
+    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    #scale_x_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    #labs(title =paste( relation, timepoint))+
+    #scale_color_viridis(option = "D")+
+    scale_color_gradientn(colours = rainbow(5))+
+    xlim(0,1)+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
 
@@
     mutate(DensityCh = ifelse(Density ==max(Density), 1, 0 )) %>% filter(DensityCh==1) %>% ungroup()#find max density, check where it matches
-  df.summary<-df.summary %>% group_by(Distance, Source) %>% mutate(DoubledValues = sum(DensityCh))#this is just to find which values were repeated
+  #df.summary<-df.summary %>% group_by(Distance, Source) %>% mutate(DoubledValues = sum(DensityCh))#this is just to find which values were repeated
   return(df.summary)
@@
 
+allDeathCurvesLog2midAbsStats<-allDeathCurvesLog2midAbsStats%>% mutate(Relation = recode(Source, "finalGG" = "Pa->Pa","finalRG" = "Sa->Pa","finalRR" = "Sa->Sa","finalGR" = "Pa->Sa"))
 ggplot()+#log transform
   geom_pointrange(data = allDeathCurvesLog2midAbsStats,aes(x = Distance,y=meanLogValue,ymax=meanLogValue+sdLogValue,ymin=meanLogValue-sdLogValue, color=Strain),size=.5)+
-    labs(title ="50 percentile Density (Log)")+
-    facet_wrap( ~ Source, ncol = 2)+
+  facet_wrap( ~ Relation, ncol = 2)+
+  scale_color_grey(name = "Strain", labels = c( "HQNO-","Wild Type"))+  
   theme_cowplot()+
@@
 
+allDeathCurvesLog2midAbsEnrichment2<-allDeathCurvesLog2midAbsEnrichment2 %>% mutate(Relation = recode(Source, "finalGG" = "Pa->Pa","finalRG" = "Sa->Pa","finalRR" = "Sa->Sa","finalGR" = "Pa->Sa"))
+
+#this is the original figure I sent to Marvin
 ggplot()+
@@
   geom_jitter(data = allDeathCurvesLog2midAbsEnrichment2,aes(y=Distance, x = Strain, color = Strain, shape = Sample),size=2)+
-    labs(title ="50 percentile Enrichment by strain")+
-    facet_wrap( ~ Source, ncol = 2)+
-    #scale_color_gradientn(colours = rainbow(5))+
+  facet_wrap( ~ Relation, ncol = 2)+
   scale_shape_manual(values=c(0,1,2, 15,16,17))+
+  guides(shape = FALSE)+
+  scale_color_grey(name = "Strain", labels = c("HQNO-","Wild Type"))+  
   theme_cowplot()+
   theme(plot.title = element_text(hjust = 0.5))
+#Now I have to remove focus of Pa since there are too many of them
+enrichmentDataFinal<-allDeathCurvesLog2midAbsEnrichment2 %>% filter(Relation %in% c("Sa->Pa", "Sa->Sa"))
+enrichmentDataFinal$Strain <- factor(enrichmentDataFinal$Strain, levels = c("wt", "mut"))
+```
+
+```{r final figure for enrichment}
+sa.paPlot<-ggplot()+
+  geom_point(data = enrichmentDataFinal %>% filter(Relation == "Sa->Pa"),aes(y=meanEnrichment, x = Strain, shape = Strain),size=4)+
+  geom_errorbar(data = enrichmentDataFinal %>% filter(Relation == "Sa->Pa"),
+                aes(ymin = meanEnrichment-sdEnrichment,ymax = meanEnrichment+sdEnrichment, x = Strain),size=.2, width = .1)+
+  labs( y = bquote(paste("Distance ("*mu*"m)")), x = "" ) +
+  scale_shape_manual(values = c(1,2),name = "", limits=c("wt","mut"),labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type")),
+                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL"))))+
+  scale_x_discrete(name ="", breaks = c("wt","mut"), labels =c("wild-type",expression(""*Delta*"pqsL")))+
+  ylim(1, 9)+
+  theme_cowplot()
+
+sa.saPlot<-ggplot()+
+  geom_point(data = enrichmentDataFinal %>% filter(Relation == "Sa->Sa"),aes(y=meanEnrichment, x = Strain, shape = Strain),size=4)+
+  geom_errorbar(data = enrichmentDataFinal %>% filter(Relation == "Sa->Sa"),
+                aes(ymin = meanEnrichment-sdEnrichment,ymax = meanEnrichment+sdEnrichment, x = Strain),size=.2, width = .1)+
+  labs( y = bquote(paste("Distance ("*mu*"m)")), x = "" ) +
+  scale_shape_manual(values = c(1,2),name = "", limits=c("wt","mut"),labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type")),
+                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL"))))+
+  scale_x_discrete(name ="", breaks = c("wt","mut"), labels =c("wild-type",expression(""*Delta*"pqsL")))+
+  ylim(1, 9)+
+  theme_cowplot()
+
+legendFigure3 <- get_legend(sa.saPlot + theme(legend.box.margin = margin(0, 0, 0, -10)))
+figure3 <- plot_grid(sa.saPlot+theme(legend.position="none"),sa.paPlot+theme(legend.position="none"),
+                      align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)
+plot_grid(figure3,legendFigure3,rel_widths = c(4, 1.7))
+#plot_grid(sa.saPlot,sa.paPlot,align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)
+
+#p-value calculations
+pvalueEnrichmentGR<- allDeathCurvesLog2midAbsEnrichment2 %>% filter(Source == "finalGR") %>% filter(!Distance == 6.5)%>% filter(!Distance == 10.5)
+
+wtpvalueEnrichmentGR<-pvalueEnrichmentGR %>% filter(Strain=="wt")
+mutpvalueEnrichmentGR<-pvalueEnrichmentGR %>% filter(Strain=="mut")
+POTtest<-t.test(x = wtpvalueEnrichmentGR$EnrichmentDistance, y = mutpvalueEnrichmentGR$EnrichmentDistance, paired = T)
+POTtest
+
+pvalueEnrichmentRG<- allDeathCurvesLog2midAbsEnrichment2 %>% filter(Source == "finalRG") %>% filter(!Distance == 7.5)%>% filter(!Distance == 9.5) %>% filter(!Distance == 5.5) %>% filter(!Distance == 3.5) %>% ungroup() %>% slice(2:7)
+wtpvalueEnrichmentRG<-pvalueEnrichmentRG %>% filter(Strain=="wt")
+mutpvalueEnrichmentRG<-pvalueEnrichmentRG %>% filter(Strain=="mut")
+POGRTtest<-t.test(x = wtpvalueEnrichmentRG$EnrichmentDistance, y = mutpvalueEnrichmentRG$EnrichmentDistance, paired = T)
+POGRTtest
 

### 2020-07-29 Microscopy Data Clean.Rmd
added t-test for mixed aggregates

@@
 }
-testReadMixedAggregateFile<-ReadMixedAggregateFile('5-8-19','RedSubtract')
+
 PA14mut<- c('4-24-19', '4-25-19', '5-8-19')
@@
 
+#T-tests
+
+tTestMixWt<-combinedMixedAggData %>% filter(Strain == "PA14wt") %>% pull(PercentTotalBiomass)
+tTestMixMut<-combinedMixedAggData %>% filter(Strain == "PA14mut") %>% pull(PercentTotalBiomass)
+tTestMixAggs<-t.test(x = tTestMixWt, y = tTestMixMut, paired = F)
+
 ```

### 2020-08-06 Microscopy Data Clean.Rmd
figures 3 and 6 black and white

@@
 cleanHist.5<-hist.5 %>% group_by(max, Species, ConditionNew, Strain) %>% summarise(Frequency = sum(frequency))#Combine aggregates from all 3 samples
+meancleanHist.5<-hist.5 %>% group_by(max, Species, ConditionNew, Strain) %>% summarise(MeanFrequency = mean(frequency))#mean aggregates from all 3 samples
 cleanHist.100<-hist.100 %>% group_by(max, Species, ConditionNew, Strain) %>% summarise(Frequency = sum(frequency))
+meancleanHist.100<-hist.100 %>% group_by(max, Species, ConditionNew, Strain) %>% summarise(MeanFrequency = mean(frequency))
 #However, one thing I want to try is to have different aggregate cutoffs... have 5 um bins up to 100um and then have the rest of the bins at 100 um3, so..
@@
 bin5and100Hist<-bind_rows(only5Hist,only100Hist)
+
+meanOnly5Hist<- meancleanHist.5 %>% filter (max<=100)
+meanOnly100Hist<- meancleanHist.100 %>% filter (max>100)
+meanBin5and100Hist<-bind_rows(meanOnly5Hist,meanOnly100Hist)
 
@@
   group_by(Species,Sample,Condition,ConditionNew, Strain,Aggregation) %>% summarize(FrequencyAggregation = sum(frequency), BiomassAggregation = sum(BiomassBin), DensityAggregation = sum(Density))
+
 #now I have to do some t-tests, since I used the same cultures for mono and co for each replicate, paired t-tests are allowed.
@@
 hist.plank.Agg.Stats<-hist.plank.Agg.Sumary %>% group_by(Species,Condition, ConditionNew,Strain,Aggregation) %>%
-  summarise(MeanFreq = mean(FrequencyAggregation), SEFreq = std.error(FrequencyAggregation), MeanBiomass = mean(BiomassAggregation), SEBiomass = std.error(BiomassAggregation))
+  summarise(MeanFreq = mean(FrequencyAggregation), SEFreq = std.error(FrequencyAggregation), MeanBiomass = mean(BiomassAggregation), SEBiomass = std.error(BiomassAggregation),MeanDensity = mean(DensityAggregation), SEDensity = std.error(DensityAggregation) )
 
@@
 ```
-```{r Aggregate histograms logarithmic bins}
+
+```{r Aggregate histograms logarithmic bins, Figures 3 and 6}
 #Now I need to do histograms with bins in a log scale, but for this I want to use the raw data that includes biomass per bin and density.
 #let's start by revisiting the original data set and just filter one sample to simplify things:
+#####
 hist.5.rep1<-hist.5 %>% filter(Sample == "rep1"&Condition == "Pa Mono"&Strain=="PA14mut")
@@
     #geom_point(data = df,aes(x=as.factor(LogBin),y=FrequencyLogBin,  shape =Sample ),size=4)+
-    geom_label(data = df %>% filter(Sample == "rep1"),aes(x=as.factor(LogBin),y=1, label =round(BiomassLogBin*100,digits=1), color = "rep1"),size=4)+
+    geom_label(data = df %>% filter(Sample == "rep1"),aes(x=as.factor(LogBin),y=1, label =round(BiomassLogBin[Sample=="rep1"]*100,digits=1), color = "rep1"),size=4)+
     geom_label(data = df%>% filter(Sample == "rep2"),aes(x=as.factor(LogBin),y=.325, label =round(BiomassLogBin[Sample=="rep2"]*100,digits=1), color = "rep2"),size=4)+
@@
 }
-PlotFreqLogBin("PA14wt", "Sa", "Sa WT")
-PlotFreqLogBin("PA14wt", "Pa", "Pa WT")
-PlotFreqLogBin("PA14mut", "Sa", "Sa pqsL")
-PlotFreqLogBin("PA14mut", "Pa", "Pa pqsL")
+ #old stuff
+#####
 
+#New code as of 8-5-20: report mean frequencies and density across samples, instead of per sample.
+hist.5.LogBinSummarize<-hist.5 %>% filter(!max == 5)%>%  group_by(Sample,Species,Condition,Strain)%>% 
+  mutate(LogBin = case_when(max <= 10 ~ "(5, 10]",
+                        max<= 100    ~ "(10, 100]",
+                        max > 100 ~ paste0("(100, ",bquote("\U221E"), ")"))) %>% ungroup() %>% 
+  group_by(Species, Sample,Condition,ConditionNew,Strain,LogBin) %>% summarise(FrequencyLogBin = sum(frequency), BiomassLogBin = sum(BiomassBin), DensityLogBin = sum(Density)) %>% 
+  ungroup() %>% group_by(Species, Condition,ConditionNew,Strain,LogBin) %>% summarise(MeanFrequencyLogBin = mean(FrequencyLogBin),SEFrequencyLogBin = std.error(FrequencyLogBin),
+                                                                                      MeanBiomassLogBin = mean(BiomassLogBin), SEBiomassLogBin = std.error(BiomassLogBin),
+                                                                                      MeanDensityLogBin = mean(DensityLogBin),SEDensityLogBin = std.error(DensityLogBin)) 
+hist.5.LogBinSummarize$LogBin<-as.factor(hist.5.LogBinSummarize$LogBin)
+hist.5.LogBinSummarize$LogBin <- factor(hist.5.LogBinSummarize$LogBin, levels = c("(5, 10]","(10, 100]",paste0("(100, ",bquote("\U221E"), ")")))
+hist.5.LogBinSummarize$Species <- factor(hist.5.LogBinSummarize$Species, levels = c("Pa", "Sa"),
+                  labels = c('P. aeruginosa','S. aureus'))
+
+PlotFreqLogBin<-function(strain,titulo){
+  df <-hist.5.LogBinSummarize%>% filter(Strain == strain)
+  ggplot()+
+    geom_col(data = df, aes(x=LogBin,y=MeanFrequencyLogBin,  fill =ConditionNew ),size=4,position = position_dodge( width = .9))+
+    geom_errorbar(data = df,aes(x=LogBin,ymin=MeanFrequencyLogBin-SEFrequencyLogBin, ymax = MeanFrequencyLogBin+SEFrequencyLogBin, group =ConditionNew ),size=.5,position = position_dodge2( width = .6))+
+    #labs(title = titulo)+
+    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_grid(.~Species)+
+    labs(fill = "Condition",y = "Mean number of aggregates per Bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    guides(color = FALSE)+
+    scale_fill_grey()+
+    theme_cowplot(12)+
+    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(face = "italic"))
+}
+
+PlotFreqLogBin("PA14wt", "WT")
+PlotFreqLogBin("PA14mut", "pqsL")
+
+PlotDensityLogBin<-function(strain,titulo){
+  df <-hist.5.LogBinSummarize%>% filter(Strain == strain)
+  ggplot()+
+    geom_col(data = df, aes(x=LogBin,y=MeanBiomassLogBin*100, fill =ConditionNew),size=4,position = position_dodge( width = .9))+
+    geom_errorbar(data = df,aes(x=LogBin,ymin=(MeanBiomassLogBin-SEBiomassLogBin)*100, ymax = (MeanBiomassLogBin+SEBiomassLogBin)*100, group =ConditionNew ),size=.5,position = position_dodge2( width = .6))+
+    #labs(title = titulo)+
+    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_grid(.~Species)+
+    labs(fill = "Condition",y = "% biomass contribution per bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    guides(color = FALSE)+
+    scale_fill_grey()+
+    theme_cowplot(12)+
+    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(face = "italic"))
+}
+PlotDensityLogBin("PA14wt", "WT")
+PlotDensityLogBin("PA14mut", "pqsL")
 ```

### 2020-08-06 Paper Figures/Paper figures Scipts.Rmd
figures 3 and 6 black and white

@@
 Figures 2 and 5 are on document : "Staph killing assays.Rmd"
+```{r code Figures 3 and 6}
+hist.5.LogBinSummarize<-hist.5 %>% filter(!max == 5)%>%  group_by(Sample,Species,Condition,Strain)%>% 
+  mutate(LogBin = case_when(max <= 10 ~ "(5, 10]",
+                        max<= 100    ~ "(10, 100]",
+                        max > 100 ~ paste0("(100, ",bquote("\U221E"), ")"))) %>% ungroup() %>% 
+  group_by(Species, Sample,Condition,ConditionNew,Strain,LogBin) %>% summarise(FrequencyLogBin = sum(frequency), BiomassLogBin = sum(BiomassBin), DensityLogBin = sum(Density)) %>% 
+  ungroup() %>% group_by(Species, Condition,ConditionNew,Strain,LogBin) %>% summarise(MeanFrequencyLogBin = mean(FrequencyLogBin),SEFrequencyLogBin = std.error(FrequencyLogBin),
+                                                                                      MeanBiomassLogBin = mean(BiomassLogBin), SEBiomassLogBin = std.error(BiomassLogBin),
+                                                                                      MeanDensityLogBin = mean(DensityLogBin),SEDensityLogBin = std.error(DensityLogBin)) 
+hist.5.LogBinSummarize$LogBin<-as.factor(hist.5.LogBinSummarize$LogBin)
+hist.5.LogBinSummarize$LogBin <- factor(hist.5.LogBinSummarize$LogBin, levels = c("(5, 10]","(10, 100]",paste0("(100, ",bquote("\U221E"), ")")))
+hist.5.LogBinSummarize$Species <- factor(hist.5.LogBinSummarize$Species, levels = c("Pa", "Sa"),
+                  labels = c('P. aeruginosa','S. aureus'))
+
+PlotFreqLogBin<-function(strain,titulo){
+  df <-hist.5.LogBinSummarize%>% filter(Strain == strain)
+  ggplot()+
+    geom_col(data = df, aes(x=LogBin,y=MeanFrequencyLogBin,  fill =ConditionNew ),size=4,position = position_dodge( width = .9))+
+    geom_errorbar(data = df,aes(x=LogBin,ymin=MeanFrequencyLogBin-SEFrequencyLogBin, ymax = MeanFrequencyLogBin+SEFrequencyLogBin, group =ConditionNew ),size=.5,position = position_dodge2( width = .6))+
+    #labs(title = titulo)+
+    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_grid(.~Species)+
+    labs(fill = "Condition",y = "Mean number of aggregates per Bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    guides(color = FALSE)+
+    scale_fill_grey()+
+    theme_cowplot(12)+
+    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(face = "italic"))
+}
+
+PlotFreqLogBin("PA14wt", "WT")
+PlotFreqLogBin("PA14mut", "pqsL")
+
+PlotDensityLogBin<-function(strain,titulo){
+  df <-hist.5.LogBinSummarize%>% filter(Strain == strain)
+  ggplot()+
+    geom_col(data = df, aes(x=LogBin,y=MeanBiomassLogBin*100, fill =ConditionNew),size=4,position = position_dodge( width = .9))+
+    geom_errorbar(data = df,aes(x=LogBin,ymin=(MeanBiomassLogBin-SEBiomassLogBin)*100, ymax = (MeanBiomassLogBin+SEBiomassLogBin)*100, group =ConditionNew ),size=.5,position = position_dodge2( width = .6))+
+    #labs(title = titulo)+
+    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_grid(.~Species)+
+    labs(fill = "Condition",y = "% biomass contribution per bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    guides(color = FALSE)+
+    scale_fill_grey()+
+    theme_cowplot(12)+
+    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(face = "italic"))
+}
+PlotDensityLogBin("PA14wt", "WT")
+PlotDensityLogBin("PA14mut", "pqsL")
+
+```
 

### 2020-08-06 Microscopy Data Clean.Rmd
finished figure 7

@@
 }
-
+PA14wt<- c('3-13-19', '3-19-19', '4-17-19')
 PA14mut<- c('4-24-19', '4-25-19', '5-8-19')
@@
 #only biomass
-mixedAggDataDualSlim<-mixedAggDataDual %>% group_by(Sample, Strain) %>% summarise (AggregatesMixed = n(), PaBiomassMixed = sum(Pa), SaBiomassMixed = sum(Sa), TotalBiomassMixed = sum(Size))
+mixedAggDataDualSlim<-mixedAggDataDual %>% group_by(Sample, Strain) %>% 
+  summarise (AggregatesMixed = n(), PaBiomassMixed = sum(Pa), SaBiomassMixed = sum(Sa), TotalBiomassMixed = sum(Size))
 
 #Compare all objects to dual-species objects
-combinedMixedAggData<- bind_cols(mixedAggDataAllSlim, mixedAggDataDualSlim)
-combinedMixedAggData<-combinedMixedAggData %>% mutate(PercentAggs = AggregatesMixed/Aggregates, PercentPaBiomass =  PaBiomassMixed/PaBiomass*100, PercentSaBiomass =  SaBiomassMixed/SaBiomass*100, PercentTotalBiomass = TotalBiomassMixed/TotalBiomass*100) %>% group_by(Strain) %>% mutate(MeanAggs = mean (PercentAggs), MeanPaBiomass = mean(PercentPaBiomass), MeanSaBiomass = mean(PercentSaBiomass), MeanTotalBiomass = mean(PercentTotalBiomass), SETotalBiomass = std.error(PercentTotalBiomass))
+combinedMixedAggData<- merge(mixedAggDataAllSlim, mixedAggDataDualSlim, by = "Sample")
 
-combinedMixedAggData$Strain <- factor(combinedMixedAggData$Strain, levels = c("PA14wt", "PA14mut"))
+combinedMixedAggData<-combinedMixedAggData %>% 
+  mutate(PercentAggs = AggregatesMixed/Aggregates*100, PercentPaBiomass =  PaBiomassMixed/PaBiomass*100, 
+         PercentSaBiomass =  SaBiomassMixed/SaBiomass*100, PercentTotalBiomass = TotalBiomassMixed/TotalBiomass*100) %>% group_by(Strain.x) %>% 
+  mutate(MeanAggs = mean (PercentAggs), SEAggs = std.error (PercentAggs), 
+         MeanPaBiomass = mean(PercentPaBiomass),SEPaBiomass = std.error(PercentPaBiomass),
+         MeanSaBiomass = mean(PercentSaBiomass),SESaBiomass = std.error(PercentSaBiomass), 
+         MeanTotalBiomass = mean(PercentTotalBiomass), SETotalBiomass = std.error(PercentTotalBiomass))
+
+combinedMixedAggData$Strain.x <- factor(combinedMixedAggData$Strain.x, levels = c("PA14wt", "PA14mut"))
 ### I think this is the final figure
-MixedAggregatePlot<-ggplot()+
+MixedAggregateBiomassPlot<-ggplot()+
   geom_point(data = combinedMixedAggData,aes(x=Strain,y=PercentTotalBiomass ),size=1)+
@@
 
+#MixedAggregateFrequencyPlot<-
+  ggplot()+
+  geom_point(data = combinedMixedAggData,aes(x=Strain.x,y=PercentAggs ),size=1)+
+  geom_point(data = combinedMixedAggData,aes(x=Strain.x,y=MeanAggs, shape = Strain.x),size=3)+
+  geom_errorbar(data = combinedMixedAggData,aes(x=Strain.x,ymin=MeanAggs-SEAggs, ymax =MeanAggs+SEAggs),size=.2, width = .2)+
+  #labs(title ="Proportion of mixed species biomass")+
+  #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  scale_shape_manual(values = c(1,2),name = "", limits=c("PA14wt","PA14mut"))+
+  scale_x_discrete(breaks=c("PA14wt","PA14mut"), 
+                     labels = c(bquote(paste(" wild-type")),
+                                bquote(paste(italic(Delta*"pqsL")))))+
+  labs(y = "% mixed aggregates", x = "")+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5),legend.position="none")
+
 #this includes all the other maybe relevant data but for dual-species aggregates only
@@
 
-tTestMixWt<-combinedMixedAggData %>% filter(Strain == "PA14wt") %>% pull(PercentTotalBiomass)
-tTestMixMut<-combinedMixedAggData %>% filter(Strain == "PA14mut") %>% pull(PercentTotalBiomass)
-tTestMixAggs<-t.test(x = tTestMixWt, y = tTestMixMut, paired = F)
+tTestMixBiomassWt<-combinedMixedAggData %>% filter(Strain.x == "PA14wt") %>% pull(PercentTotalBiomass)
+tTestMixBiomassMut<-combinedMixedAggData %>% filter(Strain.x == "PA14mut") %>% pull(PercentTotalBiomass)
+tTestMixBiomass<-t.test(x = tTestMixBiomassWt, y = tTestMixBiomassMut, paired = F)
+
+tTestMixAggsWt<-combinedMixedAggData %>% filter(Strain.x == "PA14wt") %>% pull(PercentAggs)
+tTestMixAggsMut<-combinedMixedAggData %>% filter(Strain.x == "PA14mut") %>% pull(PercentAggs)
+tTestMixAggs<-t.test(x = tTestMixAggsWt, y = tTestMixAggsMut, paired = F)
 
@@
 plotNonButterfly("Pa", "PA14mut")
-
-MixedAggregatePlot
 
@@
 
-legendFigure3 <- get_legend(sa.saPlot + theme(legend.box.margin = margin(0, 0, 0, -10)))
-figure3 <- plot_grid(sa.saPlot+theme(legend.position="none"),sa.paPlot+theme(legend.position="none"),
+legendFigure7 <- get_legend(sa.saPlot + theme(legend.box.margin = margin(0, 0, 0, -10)))
+figure7 <- plot_grid(sa.saPlot+theme(legend.position="none"),sa.paPlot+theme(legend.position="none"),
                       align='vh',labels = c("B", "C"),hjust = -1,nrow = 1)
-plot_grid(figure3,legendFigure3,rel_widths = c(4, 1.7))
+plot_grid(figure7,legendFigure7,rel_widths = c(4, 1.7))
 #plot_grid(sa.saPlot,sa.paPlot,align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)

### 2020-08-06 Microscopy Data Clean.Rmd
updated t-tests

@@
   mutate(Aggregation = case_when(max == 5 ~ "Planktonic",
-                        max>5 ~ "Aggregate")) %>% ungroup() %>% 
-  group_by(Species,Sample,Condition,ConditionNew, Strain,Aggregation) %>% summarize(FrequencyAggregation = sum(frequency), BiomassAggregation = sum(BiomassBin), DensityAggregation = sum(Density))
+                        max>5 ~ "Aggregate")) %>% ungroup() %>% group_by(Species,Sample,Condition,ConditionNew, Strain,Aggregation) %>% summarize(FrequencyAggregation = sum(frequency), BiomassAggregation = sum(BiomassBin), DensityAggregation = sum(Density))
 
@@
 SaMonoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+SaMonoWtPlankSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14wt",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
+SaMonoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+SaMonoMutPlankSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14mut",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
+
 SaCoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
-SaWtAggTest<-t.test(x = SaMonoWtAggSum, y = SaCoWtAggSum, paired = T)
-SaMonoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+SaCoWtPlankSum<-hist.plank.Agg.Sumary %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14wt",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
 SaCoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Species == "Sa", ConditionNew == "Co", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
-SaMutAggTest<-t.test(x = SaMonoMutAggSum, y = SaCoMutAggSum, paired = T)
+SaCoMutPlankSum<-hist.plank.Agg.Sumary %>%filter(Species == "Sa", ConditionNew == "Co", Strain == "PA14mut",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
+
+#mono vs Co
+SaWtAggTest<-t.test(x = SaMonoWtAggSum, y = SaCoWtAggSum, paired = T)#wt
+SaMutAggTest<-t.test(x = SaMonoMutAggSum, y = SaCoMutAggSum, paired = T)#mutant
+#Plank vs Agg
+SaMonoWtAggVsPlankTest<-t.test(x = SaMonoWtAggSum, y = SaMonoWtPlankSum, paired = T)#wt
+SaMonoMutAggVsPlankTest<-t.test(x = SaMonoMutAggSum, y = SaMonoMutPlankSum, paired = T)#mutant
+SaCoWtAggVsPlankTest<-t.test(x = SaCoWtAggSum, y = SaCoWtPlankSum, paired = T)#wt
+SaCoMutAggVsPlankTest<-t.test(x = SaCoMutAggSum, y = SaCoMutPlankSum, paired = T)#mutant
+#wt vs mutant
+SaMonoWtVsMutAggTest<-t.test(x = SaMonoWtAggSum, y = SaMonoMutAggSum, paired = F)
+SaCoWtVsMutAggTest<-t.test(x = SaCoWtAggSum, y = SaCoMutAggSum, paired = F)
 
@@
 PaCoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Species == "Pa", ConditionNew == "Co", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
-PaWtAggTest<-t.test(x = PaMonoWtAggSum, y = PaCoWtAggSum, paired = T)
 PaMonoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Pa Mono", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
 PaCoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Species == "Pa", ConditionNew == "Co", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+
+PaMonoWtPlankSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Pa Mono", Strain == "PA14wt",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
+PaCoWtPlankSum<-hist.plank.Agg.Sumary %>%filter(Species == "Pa", ConditionNew == "Co", Strain == "PA14wt",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
+PaMonoMutPlankSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Pa Mono", Strain == "PA14mut",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
+PaCoMutPlankSum<-hist.plank.Agg.Sumary %>%filter(Species == "Pa", ConditionNew == "Co", Strain == "PA14mut",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
+
+PaWtAggTest<-t.test(x = PaMonoWtAggSum, y = PaCoWtAggSum, paired = T)
 PaMutAggTest<-t.test(x = PaMonoMutAggSum, y = PaCoMutAggSum, paired = T)
-
-SaMonoWtVsMutAggTest<-t.test(x = SaMonoWtAggSum, y = SaMonoMutAggSum, paired = F)
-SaCoWtVsMutAggTest<-t.test(x = SaCoWtAggSum, y = SaCoMutAggSum, paired = F)
 PaMonoWtVsMutAggTest<-t.test(x = PaMonoWtAggSum, y = PaMonoMutAggSum, paired = F)
@@
 
-tTestDataAggvsPlank<-list(SaWtAggTest, SaMutAggTest, PaWtAggTest,PaMutAggTest,SaMonoWtVsMutAggTest,SaCoWtVsMutAggTest,PaMonoWtVsMutAggTest,PaCoWtVsMutAggTest)
+PaMonoWtAggVsPlankTest<-t.test(x = PaMonoWtAggSum, y = PaMonoWtPlankSum, paired = T)
+PaCoWtAggVsPlankTest<-t.test(x = PaCoWtAggSum, y = PaCoWtPlankSum, paired = T)
+PaMonoMutAggVsPlankTest<-t.test(x = PaMonoMutAggSum, y = PaMonoMutPlankSum, paired = T)
+PaCoMutAggVsPlankTest<-t.test(x = PaCoMutAggSum, y = PaCoMutPlankSum, paired = T)
+
+tTestDataAggvsPlank<-list(SaWtAggTest,SaMutAggTest,SaMonoWtAggVsPlankTest,SaMonoMutAggVsPlankTest,
+                          SaCoWtAggVsPlankTest,SaCoMutAggVsPlankTest,SaMonoWtVsMutAggTest,SaCoWtVsMutAggTest,
+                          PaWtAggTest,PaMutAggTest,PaMonoWtAggVsPlankTest,PaMonoMutAggVsPlankTest,
+                          PaCoWtAggVsPlankTest,PaCoMutAggVsPlankTest,PaMonoWtVsMutAggTest,PaCoWtVsMutAggTest)
 TtestTable<-name <- function(dataPoint) {
@@
   labs(y = "% mixed aggregates", x = "")+
+  ylim(0,10)+
   theme_cowplot()+

### 2020-08-07 Paper Figures/Paper figures Scipts.Rmd
t-tests for histograms

--- 2020-07-28 Paper Figures/Paper figures Scipts.Rmd
@@
 
-```{r data Figure 1, include=FALSE}
+```{r code Figure 1ab and 2ab}
 #Data gathering functions:
@@
 PA14DataStats<-PA14Data%>% group_by(condition, bug, time,strain) %>% summarise(CFUmean = mean (CFU), CFUsd = sd(CFU), CFUse = std.error(CFU), logCFUmean = mean (logCFU), logCFUsd = sd(logCFU),logCFUse = std.error(logCFU))
-```
 
-```{r code Figure 1}
 GraphGrowthCurveLog1<-function (rawData, statsData){
@@
 
-    legend <- get_legend(shakingWtPlot + theme(legend.box.margin = margin(0, 0, 0, -10)))
+    legend <- get_legend(shakingWtPlot + theme(legend.box.margin = margin(0, 0, 0, 10)))
     prow <- plot_grid(shakingWtPlot+theme(legend.position="none"),staticWtPlot+theme(legend.position="none"),
-                      align='vh',labels = c("Mixed", "Static"),hjust = c(-3, -3.8),nrow = 1)
-    plot_grid(prow,legend,rel_widths = c(3, .4))
+                      align='vh',labels = c("A", "B"),nrow = 1)
+    plot_grid(prow,legend,rel_widths = c(3, 1))
     }
-#Graph logs
-GraphGrowthCurveLog1(PA14Data,PA14DataStats)
-```
-Figures 2 and 5 are on document : "Staph killing assays.Rmd"
 
-```{r Figure 4}
 GraphGrowthCurveLog2<-function (rawData, statsData){
@@
     theme_cowplot(12)
-  legend <- get_legend(shakingMutPlot + theme(legend.box.margin = margin(0, 0, 0, -10)))
+  legend <- get_legend(shakingMutPlot + theme(legend.box.margin = margin(0, 0, 0, 10)))
   prow <- plot_grid(shakingMutPlot+theme(legend.position="none"),staticMutPlot+theme(legend.position="none"),
-                      align='vh',labels = c("Mixed", "Static"),hjust = c(-3, -3.8),nrow = 1)
-    plot_grid(prow,legend,rel_widths = c(3, .4))
+                      align='vh',labels = c("A", "B"),nrow = 1)
+    plot_grid(prow,legend,rel_widths = c(3, 1))
 }
@@
 #Graph logs
-GraphGrowthCurveLog2(PA14Data,PA14DataStats)
+figure1AB<-GraphGrowthCurveLog1(PA14Data,PA14DataStats)
+figure1AB
+#Graph logs
+figure2AB<-GraphGrowthCurveLog2(PA14Data,PA14DataStats)
+figure2AB
+
+```
+```{r Figures 1cd, and 2cd}
+#data disk difussion
+#####
+diskFile<-"~/Documents/Whiteley/PROJECTS/PaSaProject/Staph killing assays/disk difussion assays.csv"
+diskData <-read.csv(diskFile)
+diskData$strain <- factor(diskData$strain, levels = c("wt", "pqsl"))
+diskData <- diskData %>% mutate(val1 = value1-6,val2 = value2-6,average = (val1+val2)/2 )#this removes the diameter of the disks
+diskDataStats<-diskData %>% group_by(strain, condition, bio.rep) %>% summarise(meanTech = mean(average)) %>% ungroup() %>%group_by(strain, condition) %>% summarise(meanBio = mean(meanTech), SDBio = std.error(meanTech))
+diskDataStats$strain <- factor(diskDataStats$strain, levels = c("wt", "pqsl"))
+diskDataStats1<-diskDataStats %>% mutate(
+  CondStrain = case_when(
+    condition == "shaking" & strain == "pqsl" ~ "pqsLShake",
+    condition == "shaking" & strain == "wt"~ "wtShake",
+    condition == "static" & strain == "pqsl"~ "pqsLStat",
+    condition == "static" & strain == "wt"~ "wtStat"))
+#####
+#t-tests disk difussion
+#####
+diskWtShaking<-diskData %>% filter(strain == "wt" & condition == "shaking")
+diskMutShaking<-diskData %>% filter(strain == "pqsl" & condition == "shaking")
+diskWtStatic<-diskData %>% filter(strain == "wt" & condition == "static")
+diskMutStatic<-diskData %>% filter(strain == "pqsl" & condition == "static")
+
+#there is no rep 1 for mutant strain, so remove first one from wt to make paired t-test
+diskWtStatic1<-diskData %>% filter(strain == "wt" & condition == "static") %>% filter(!bio.rep==1)
+diskWtShaking1<-diskData %>% filter(strain == "wt" & condition == "shaking")%>% filter(!bio.rep==1)
+
+#t-tests
+diskWtTtest<-t.test(x = diskWtShaking$avg, y = diskWtStatic$avg, paired = T)
+diskMutTtest<-t.test(x = diskMutShaking$avg, y = diskMutStatic$avg, paired = T)
+diskShakingTtest<-t.test(x = diskWtShaking1$avg, y = diskMutShaking$avg, paired = T)
+diskStaticTtest<-t.test(x = diskMutStatic$avg, y = diskWtStatic1$avg, paired = T)
+diskWtStaticMutShakingTtest<-t.test(x = diskMutShaking$avg, y = diskWtStatic1$avg, paired = T)
+diskMutStaticWtShakingTtest<-t.test(x = diskWtShaking1$avg, y = diskMutStatic$avg, paired = T)
+tTestDataDiskDifussion<-list(diskWtTtest, diskMutTtest,diskShakingTtest, diskStaticTtest, diskWtStaticMutShakingTtest,diskMutStaticWtShakingTtest)
+tTestDiskDifussionTable<-bind_rows(map(tTestDataDiskDifussion, TtestTable))
+#####
+#plot disk difussion
+#####
+ figure1C<-ggplot()+
+      geom_errorbar(data=diskDataStats1 %>% filter (strain == "wt"), aes(x = condition, ymin = meanBio - SDBio, ymax = meanBio + SDBio),width = .2)+
+      geom_point(data=diskDataStats1 %>% filter (strain == "wt"), aes(x=condition, y=meanBio, shape =condition), size=3)+
+      scale_shape_manual(values = c(1,2),limits=c("static","shaking"), 
+                     labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type static")),
+                                bquote(paste(italic('P. aeruginosa'), " wild-type mixed"))))+
+      scale_x_discrete(name ="", breaks = c("static","shaking"), labels =c("Static","Mixed"))+
+    ylim(0,17.5)+
+  labs( y = "Zone of inhibition (mm)", shape = "Growth condtion") +
+      theme_cowplot(12)
+
+    figure2C<-ggplot()+
+      geom_errorbar(data=diskDataStats1 %>% filter (strain == "pqsl"), aes(x = condition, ymin = meanBio - SDBio, ymax = meanBio + SDBio),width = .2)+
+      geom_point(data=diskDataStats1 %>% filter (strain == "pqsl"), aes(x=condition, y=meanBio, shape =condition), size=3)+
+      scale_shape_manual(values = c(16,17),limits=c("static","shaking"), 
+                     labels = c(bquote(paste(italic('P. aeruginosa '), Delta*"pqsL static")),
+                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL mixed"))))+
+      ylim(0,17.5)+
+      scale_x_discrete(name ="", breaks = c("static","shaking"), labels =c("Static","Mixed"))+
+      labs( y = "Zone of inhibition (mm)", shape = "Growth condtion") +
+      theme_cowplot(12)
+#####
+
+#luminesscence data
+#####
+luminescenceFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Staph killing assays/summary.csv"
+luminescenceData <-read.csv(luminescenceFile)
+luminescenceData<-luminescenceData %>% group_by(TimePoint, BioReplicate, Condition, Strain) %>% mutate(techMean = mean(Luminescence)) %>% ungroup() %>% group_by(TimePoint, Condition, Strain) %>% mutate(Mean = mean(techMean), SE =std.error(techMean)) %>% ungroup()
+#luminescenceData1<-luminescenceData %>%  
+#mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))#this adds up all the data on each slice and then gets the log of that total
+
+luminescenceData1<-luminescenceData %>% mutate(
+  CondStrain = case_when(
+    Condition == "shaking" & Strain == "pqsL" ~ "pqsLShake",
+    Condition == "shaking" & Strain == "wt"~ "wtShake",
+    Condition == "static" & Strain == "pqsL"~ "pqsLStat",
+    Condition == "static" & Strain == "wt"~ "wtStat"))
+#####
+
+#luminescence t-tests
+#####
+wtStatLuminescence<-luminescenceData1 %>% filter (CondStrain == "wtStat") %>% filter (TimePoint<7 &TechReplicate == 1)  %>% pull(techMean)
+wtMixedLuminescence<-luminescenceData1 %>% filter (CondStrain == "wtShake") %>% filter (TimePoint<7 &TechReplicate == 1) %>% pull(techMean)
+
+mutStatLuminescence<-luminescenceData1 %>% filter (CondStrain == "pqsLStat") %>% filter (TimePoint<7 &TechReplicate == 1)%>% pull(techMean)
+mutMixedLuminescence<-luminescenceData1 %>% filter (CondStrain == "pqsLShake") %>% filter (TimePoint<7 &TechReplicate == 1)%>% pull(techMean)
+
+tTestWtLuminescence<-t.test(x = wtStatLuminescence, y = wtMixedLuminescence, paired = T)
+tTestMutLuminescence<-t.test(x = mutStatLuminescence, y = mutMixedLuminescence, paired = T)
+
+tTestStatLuminescence<-t.test(x = wtStatLuminescence, y = mutStatLuminescence, paired = T)
+tTestMixedLuminescence<-t.test(x = wtMixedLuminescence, y = mutMixedLuminescence, paired = T)
+
+tTestWtStatVSMutMixedLuminescence<-t.test(x = wtStatLuminescence, y = mutMixedLuminescence, paired = T)
+tTestMutStatVSWtMixedLuminescence<-t.test(x = wtMixedLuminescence, y = mutStatLuminescence, paired = T)
+
+tTestDataLuminescence<-list(tTestWtLuminescence,tTestMutLuminescence,tTestStatLuminescence,tTestMixedLuminescence,
+                            tTestWtStatVSMutMixedLuminescence,tTestMutStatVSWtMixedLuminescence)
+TtestTable<-name <- function(dataPoint) {
+  data <-data.frame(dataPoint$data.name, dataPoint$p.value)
+}
+tTestLuminescenceTable<-bind_rows(map(tTestDataLuminescence, TtestTable))
+#####
+
+#luminescence plots
+#####    
+    figure1D<-ggplot()+
+      geom_line(data=luminescenceData1 %>% filter (Strain == "wt") %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, group = Condition), size=.5, show.legend = FALSE)+
+      geom_point(data=luminescenceData1%>% filter (Strain == "wt") %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, shape = Condition), size=3)+
+      scale_y_log10(name=expression(paste(italic('S. aureus'), " % luminescence" )), limits = c(1,121),labels = c(1, 10, 100),breaks = c(1, 10, 100))+
+      labs( x = "Time (minutes)",shape = "") +
+      scale_shape_manual(values = c(1,2),limits=c("static","shaking"), 
+                     labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type static")),
+                                bquote(paste(italic('P. aeruginosa'), " wild-type mixed"))))+
+      theme(legend.position="top")+
+      theme_cowplot(12)
+
+    figure2D<-ggplot()+
+      geom_line(data=luminescenceData1 %>% filter (Strain == "pqsL") %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, group = Condition), size=.5, show.legend = FALSE)+
+      geom_point(data=luminescenceData1%>% filter (Strain == "pqsL") %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, shape = Condition), size=3)+
+      scale_y_log10(name=expression(paste(italic('S. aureus'), " % luminescence" )),limits = c(1,121), labels = c(1,10,100),breaks = c(1, 10, 100))+
+      labs( x = "Time (minutes)",shape = "") +
+      scale_shape_manual(values = c(16,17),limits=c("static", "shaking"), 
+                     labels = c(bquote(paste(italic('P. aeruginosa '), Delta*"pqsL static")),
+                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL mixed"))))+
+      theme(legend.position="top")+
+      theme_cowplot(12)
+#####
+
+    legendFigure1C <- get_legend(figure1C + theme(legend.box.margin = margin(0, 0, 0, 10)))
+    plotsFigure1cd <- plot_grid(figure1C+theme(legend.position="none"),figure1D+theme(legend.position="none"),
+                      align='vh',labels = c("C", "D"),hjust = -1,nrow = 1)
+    figure1CD<-plot_grid(plotsFigure1cd,legendFigure1C,rel_widths = c(3, 1))
+
+    legendFigure2c <- get_legend(figure2C + theme(legend.box.margin = margin(0, 0, 0, 10)))
+    plotsFigure2cd <- plot_grid(figure2C+theme(legend.position="none"),figure2D+theme(legend.position="none"),
+                      align='vh',labels = c("C", "D"),hjust = -1,nrow = 1)
+    figure2CD<-plot_grid(plotsFigure2cd,legendFigure2c,rel_widths = c(3, 1))
+
+```
+
+```{r code Figures 1ef and 2ef}
+#get data biomass aggs vs planktonic
+#####
+allDataHistograms.5df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Histograms1/histograms5.csv',header=T)
+allDataHistograms.100df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Histograms1/histograms100.csv',header=T)
+hist.100<-allDataHistograms.100df %>% filter(TimePoint== 5) %>% filter( Condition %in% c("Sa Mono", "Pa Mono", "Pa:Sa 1:1")) %>% mutate(ConditionNew = recode(Condition, "Sa Mono" = "Mono", "Pa Mono" = "Mono", "Pa:Sa 1:1" = "Co"))
+hist.5 <- allDataHistograms.5df %>% filter(TimePoint== 5) %>% filter( Condition %in% c("Sa Mono", "Pa Mono", "Pa:Sa 1:1")) %>% mutate(ConditionNew = recode(Condition, "Sa Mono" = "Mono", "Pa Mono" = "Mono", "Pa:Sa 1:1" = "Co"))
+
+hist.plank.Agg.Sumary<-hist.5 %>%  group_by(Species, Sample,Condition,Strain)%>% 
+  mutate(Aggregation = case_when(max == 5 ~ "Planktonic",
+                        max>5 ~ "Aggregate")) %>% ungroup() %>% group_by(Species,Sample,Condition,ConditionNew, Strain,Aggregation) %>% summarize(FrequencyAggregation = sum(frequency), BiomassAggregation = sum(BiomassBin), DensityAggregation = sum(Density))
+
+hist.plank.Agg.Stats<-hist.plank.Agg.Sumary %>% group_by(Species,Condition, ConditionNew,Strain,Aggregation) %>%
+  summarise(MeanFreq = mean(FrequencyAggregation), SEFreq = std.error(FrequencyAggregation), MeanBiomass = mean(BiomassAggregation), SEBiomass = std.error(BiomassAggregation),MeanDensity = mean(DensityAggregation), SEDensity = std.error(DensityAggregation) )
+hist.plank.Agg.Stats$Species <- factor(hist.plank.Agg.Stats$Species, levels = c("Pa", "Sa"),
+                  labels = c('P. aeruginosa','S. aureus'))
+hist.plank.Agg.Stats$ConditionNew <- factor(hist.plank.Agg.Stats$ConditionNew, levels = c("Mono", "Co"))
+
+#####
+#t tests biomass aggs vs planktonic
+##### 
+#I know this sucks, but it's 1 AM so idgaf
+SaMonoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+SaMonoWtPlankSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14wt",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
+SaMonoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+SaMonoMutPlankSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Sa Mono", Strain == "PA14mut",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
+
+SaCoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+SaCoWtPlankSum<-hist.plank.Agg.Sumary %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14wt",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
+SaCoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Species == "Sa", ConditionNew == "Co", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+SaCoMutPlankSum<-hist.plank.Agg.Sumary %>%filter(Species == "Sa", ConditionNew == "Co", Strain == "PA14mut",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
+
+#mono vs Co
+SaWtAggTest<-t.test(x = SaMonoWtAggSum, y = SaCoWtAggSum, paired = T)#wt
+SaMutAggTest<-t.test(x = SaMonoMutAggSum, y = SaCoMutAggSum, paired = T)#mutant
+#Plank vs Agg
+SaMonoWtAggVsPlankTest<-t.test(x = SaMonoWtAggSum, y = SaMonoWtPlankSum, paired = T)#wt
+SaMonoMutAggVsPlankTest<-t.test(x = SaMonoMutAggSum, y = SaMonoMutPlankSum, paired = F)#mutant
+SaCoWtAggVsPlankTest<-t.test(x = SaCoWtAggSum, y = SaCoWtPlankSum, paired = T)#wt
+SaCoMutAggVsPlankTest<-t.test(x = SaCoMutAggSum, y = SaCoMutPlankSum, paired = T)#mutant
+#wt vs mutant
+SaMonoWtVsMutAggTest<-t.test(x = SaMonoWtAggSum, y = SaMonoMutAggSum, paired = F)
+SaCoWtVsMutAggTest<-t.test(x = SaCoWtAggSum, y = SaCoMutAggSum, paired = F)
+
+PaMonoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Pa Mono", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+PaCoWtAggSum<-hist.plank.Agg.Sumary %>%filter(Species == "Pa", ConditionNew == "Co", Strain == "PA14wt",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+PaMonoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Pa Mono", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+PaCoMutAggSum<-hist.plank.Agg.Sumary %>%filter(Species == "Pa", ConditionNew == "Co", Strain == "PA14mut",Aggregation == "Aggregate") %>% pull(BiomassAggregation)
+
+PaMonoWtPlankSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Pa Mono", Strain == "PA14wt",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
+PaCoWtPlankSum<-hist.plank.Agg.Sumary %>%filter(Species == "Pa", ConditionNew == "Co", Strain == "PA14wt",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
+PaMonoMutPlankSum<-hist.plank.Agg.Sumary %>%filter(Condition == "Pa Mono", Strain == "PA14mut",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
+PaCoMutPlankSum<-hist.plank.Agg.Sumary %>%filter(Species == "Pa", ConditionNew == "Co", Strain == "PA14mut",Aggregation == "Planktonic") %>% pull(BiomassAggregation)
+
+PaWtAggTest<-t.test(x = PaMonoWtAggSum, y = PaCoWtAggSum, paired = T)
+PaMutAggTest<-t.test(x = PaMonoMutAggSum, y = PaCoMutAggSum, paired = T)
+PaMonoWtVsMutAggTest<-t.test(x = PaMonoWtAggSum, y = PaMonoMutAggSum, paired = F)
+PaCoWtVsMutAggTest<-t.test(x = PaCoWtAggSum, y = PaCoMutAggSum, paired = F)
+
+PaMonoWtAggVsPlankTest<-t.test(x = PaMonoWtAggSum, y = PaMonoWtPlankSum, paired = T)
+PaCoWtAggVsPlankTest<-t.test(x = PaCoWtAggSum, y = PaCoWtPlankSum, paired = T)
+PaMonoMutAggVsPlankTest<-t.test(x = PaMonoMutAggSum, y = PaMonoMutPlankSum, paired = T)
+PaCoMutAggVsPlankTest<-t.test(x = PaCoMutAggSum, y = PaCoMutPlankSum, paired = T)
+
+tTestDataAggvsPlank<-list(SaWtAggTest,SaMutAggTest,SaMonoWtAggVsPlankTest,SaMonoMutAggVsPlankTest,
+                          SaCoWtAggVsPlankTest,SaCoMutAggVsPlankTest,SaMonoWtVsMutAggTest,SaCoWtVsMutAggTest,
+                          PaWtAggTest,PaMutAggTest,PaMonoWtAggVsPlankTest,PaMonoMutAggVsPlankTest,
+                          PaCoWtAggVsPlankTest,PaCoMutAggVsPlankTest,PaMonoWtVsMutAggTest,PaCoWtVsMutAggTest)
+TtestTable<-name <- function(dataPoint) {
+  data <-data.frame(dataPoint$data.name, dataPoint$p.value)
+}
+tTestDataTable<-bind_rows(map(tTestDataAggvsPlank, TtestTable))
+#so, it turns out I only had to do either agg or plank since the variance is the same. COOL...
+
+#####
+#plot biomass aggs vs planktonic
+#####
+PlotAggsPlank<- function(strain, titulo){
+ggplot()+
+  geom_col(data = hist.plank.Agg.Stats %>% filter(Strain == strain),aes(x=Aggregation,y=MeanBiomass, fill = ConditionNew),
+           size=3,position = position_dodge( width = .9),show.legend = FALSE)+
+  geom_errorbar(data = hist.plank.Agg.Stats%>% filter(Strain == strain),aes(x=Aggregation,ymin=MeanBiomass-SEBiomass, ymax = MeanBiomass+SEBiomass, group = ConditionNew),width = 0, size=.5,position = position_dodge(width = .9))+
+  facet_grid(.~Species)+
+    scale_fill_grey()+
+  labs(title = '', x = "", y = "Biomass contribution")+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(face = "italic"))
+}
+figure1E<-PlotAggsPlank("PA14wt", "wt")
+figure2E<-PlotAggsPlank("PA14mut", "pqsL")
+#####
+
+#get data frequency bins
+#####
+hist.5.LogBinData<-hist.5 %>% filter(!max == 5)%>%  group_by(Sample,Species,Condition,Strain)%>% 
+  mutate(LogBin = case_when(max <= 10 ~ "(5, 10]",
+                        max<= 100    ~ "(10, 100]",
+                        max > 100 ~ paste0("(100, ",bquote("\U221E"), ")"))) %>% ungroup() %>% 
+  group_by(Species, Sample,Condition,ConditionNew,Strain,LogBin) %>% summarise(FrequencyLogBin = sum(frequency), BiomassLogBin = sum(BiomassBin), DensityLogBin = sum(Density)) %>% ungroup()
+
+hist.5.LogBinSummarize<-hist.5.LogBinData%>% group_by(Species, Condition,ConditionNew,Strain,LogBin) %>%
+  summarise(MeanFrequencyLogBin = mean(FrequencyLogBin),SEFrequencyLogBin = std.error(FrequencyLogBin),
+            MeanBiomassLogBin = mean(BiomassLogBin), SEBiomassLogBin = std.error(BiomassLogBin),                                                              
+            MeanDensityLogBin = mean(DensityLogBin),SEDensityLogBin = std.error(DensityLogBin))
+
+hist.5.LogBinSummarize$LogBin<-as.factor(hist.5.LogBinSummarize$LogBin)
+hist.5.LogBinSummarize$LogBin <- factor(hist.5.LogBinSummarize$LogBin, levels = c("(5, 10]","(10, 100]",paste0("(100, ",bquote("\U221E"), ")")))
+hist.5.LogBinSummarize$Species <- factor(hist.5.LogBinSummarize$Species, levels = c("Pa", "Sa"),
+                  labels = c('P. aeruginosa','S. aureus'))
+hist.5.LogBinSummarize$ConditionNew <- factor(hist.5.LogBinSummarize$ConditionNew, levels = c("Mono", "Co"))
+#####
+#t tests frequency bins
+#####
+SaWtMono5<-hist.5.LogBinData %>%filter(Condition == "Sa Mono", Strain == "PA14wt",LogBin == "(5, 10]") %>% pull(FrequencyLogBin)
+SaMutMono5<-hist.5.LogBinData %>%filter(Condition == "Sa Mono", Strain == "PA14mut",LogBin == "(5, 10]") %>% pull(FrequencyLogBin)
+SaWtMono10<-hist.5.LogBinData %>%filter(Condition == "Sa Mono", Strain == "PA14wt",LogBin == "(10, 100]") %>% pull(FrequencyLogBin)
+SaMutMono10<-hist.5.LogBinData %>%filter(Condition == "Sa Mono", Strain == "PA14mut",LogBin == "(10, 100]") %>% pull(FrequencyLogBin)
+
+SaWtCo5<-hist.5.LogBinData %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14wt",LogBin == "(5, 10]") %>% pull(FrequencyLogBin)
+SaMutCo5<-hist.5.LogBinData %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14mut",LogBin == "(5, 10]") %>% pull(FrequencyLogBin)
+SaWtCo10<-hist.5.LogBinData %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14wt",LogBin == "(10, 100]") %>% pull(FrequencyLogBin)
+SaMutCo10<-hist.5.LogBinData %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14mut",LogBin == "(10, 100]") %>% pull(FrequencyLogBin)
+
+PaWtMono5<-hist.5.LogBinData %>%filter(Condition == "Pa Mono", Strain == "PA14wt",LogBin == "(5, 10]") %>% pull(FrequencyLogBin)
+PaMutMono5<-hist.5.LogBinData %>%filter(Condition == "Pa Mono", Strain == "PA14mut",LogBin == "(5, 10]") %>% pull(FrequencyLogBin)
+PaWtMono10<-hist.5.LogBinData %>%filter(Condition == "Pa Mono", Strain == "PA14wt",LogBin == "(10, 100]") %>% pull(FrequencyLogBin)
+PaMutMono10<-hist.5.LogBinData %>%filter(Condition == "Pa Mono", Strain == "PA14mut",LogBin == "(10, 100]") %>% pull(FrequencyLogBin)
+PaWtMono100<-hist.5.LogBinData %>%filter(Condition == "Pa Mono", Strain == "PA14wt",LogBin == paste0("(100, ",bquote("\U221E"), ")")) %>% pull(FrequencyLogBin)
+PaMutMono100<-hist.5.LogBinData %>%filter(Condition == "Pa Mono", Strain == "PA14mut",LogBin == paste0("(100, ",bquote("\U221E"), ")")) %>% pull(FrequencyLogBin)
+
+PaWtCo5<-hist.5.LogBinData %>%filter(Species =="Pa", ConditionNew == "Co", Strain == "PA14wt",LogBin == "(5, 10]") %>% pull(FrequencyLogBin)
+PaMutCo5<-hist.5.LogBinData %>%filter(Species =="Pa", ConditionNew == "Co", Strain == "PA14mut",LogBin == "(5, 10]") %>% pull(FrequencyLogBin)
+PaWtCo10<-hist.5.LogBinData %>%filter(Species =="Pa", ConditionNew == "Co", Strain == "PA14wt",LogBin == "(10, 100]") %>% pull(FrequencyLogBin)
+PaMutCo10<-hist.5.LogBinData %>%filter(Species =="Pa", ConditionNew == "Co", Strain == "PA14mut",LogBin == "(10, 100]") %>% pull(FrequencyLogBin)
+PaWtCo100<-hist.5.LogBinData %>%filter(Species =="Pa",ConditionNew=="Co",Strain == "PA14wt",LogBin == paste0("(100, ",bquote("\U221E"), ")")) %>% pull(FrequencyLogBin)
+PaMutCo100<-hist.5.LogBinData %>%filter(Species =="Pa",ConditionNew=="Co",Strain == "PA14mut",LogBin==paste0("(100, ",bquote("\U221E"), ")")) %>% pull(FrequencyLogBin)
+
+#Pa mono vs Co
+SaWt5<-t.test(x = SaWtMono5, y = SaWtCo5, paired = T)
+SaWt10<-t.test(x = SaWtMono10, y = SaWtCo10, paired = T)
+SaMut5<-t.test(x = SaMutMono5, y = SaMutCo5, paired = T)
+SaMut10<-t.test(x = SaMutMono10, y = SaMutCo10, paired = T)
+
+PaWt5<-t.test(x = PaWtMono5, y = PaWtCo5, paired = T)
+PaWt10<-t.test(x = PaWtMono10, y = PaWtCo10, paired = T)
+#PaWt100<-t.test(x = PaWtMono100, y = PaWtCo100, paired = T)
+PaMut5<-t.test(x = PaMutMono5, y = PaMutCo5, paired = T)
+PaMut10<-t.test(x = PaMutMono10, y = PaMutCo10, paired = T)
+#PaMut100<-t.test(x = PaMutMono100, y = PaMutCo100, paired = T)
+
+tTestDatAggSizes<-list(SaWt5,SaWt10,SaMut5,SaMut10,PaWt5,PaWt10,PaMut5,PaMut10)
+tTestAggSizesTable<-bind_rows(map(tTestDatAggSizes, TtestTable))
+
+#####
+#plot frequency bins
+#####
+PlotFreqLogBin<-function(strain,titulo){
+  df <-hist.5.LogBinSummarize%>% filter(Strain == strain)
+  ggplot()+
+    geom_col(data = df, aes(x=LogBin,y=MeanFrequencyLogBin,  fill =ConditionNew ),size=4,position = position_dodge( width = .9))+
+    geom_errorbar(data = df,aes(x=LogBin,ymin=MeanFrequencyLogBin-SEFrequencyLogBin, ymax = MeanFrequencyLogBin+SEFrequencyLogBin, group =ConditionNew ),width = 0, size= .5,position = position_dodge( width = .9))+
+    #labs(title = titulo)+
+    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_grid(.~Species)+
+    labs(fill = "Condition",y = "Mean number of aggregates per Bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    guides(color = FALSE)+
+    scale_fill_grey()+
+    theme_cowplot(12)+
+    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(face = "italic"))
+}
+
+figure1F<-PlotFreqLogBin("PA14wt", "WT")
+figure2F<-PlotFreqLogBin("PA14mut", "pqsL")
+#####
+figure1EF<-plot_grid(figure1E,figure1F,rel_widths = c(1,1.2),align='vh',labels = c("E", "F"),hjust = -1,nrow = 1)
+figure2EF<-plot_grid(figure2E,figure2F,rel_widths = c(1,1.2),align='vh',labels = c("E", "F"),hjust = -1,nrow = 1)
+```
+
+```{Make full figures 1 and 2}
+plot_grid(figure1AB,figure1CD,figure1EF, align='vh',nrow = 3, rel_heights = c(1,1,1.5))
+plot_grid(figure2AB,figure2CD,figure2EF, align='vh',nrow = 3, rel_heights = c(1,1,1.5))
+```
+
+```{r biomass per bin}
+PlotDensityLogBin<-function(strain,titulo){
+  df <-hist.5.LogBinSummarize%>% filter(Strain == strain)
+  ggplot()+
+    geom_col(data = df, aes(x=LogBin,y=MeanBiomassLogBin*100, fill =ConditionNew),size=4,position = position_dodge( width = .9))+
+    geom_errorbar(data = df,aes(x=LogBin,ymin=(MeanBiomassLogBin-SEBiomassLogBin)*100, ymax = (MeanBiomassLogBin+SEBiomassLogBin)*100, group =ConditionNew ),width = 0, size=.5,position = position_dodge(width = 1))+
+    #labs(title = titulo)+
+    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_grid(.~Species)+
+    labs(fill = "Condition",y = "% biomass contribution per bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    guides(color = FALSE)+
+    scale_fill_grey()+
+    theme_cowplot(12)+
+    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(face = "italic"))
+}
+PlotDensityLogBin("PA14wt", "WT")
+PlotDensityLogBin("PA14mut", "pqsL")
+
 ```

### 2020-08-07 Staph killing assays/Staph killing report.Rmd
tTest added

@@
 library(tidyr)
-library(growthcurver)
 library(plotrix)
@@
 ```{r zone of inhibition data input}
-diskFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/PaSa Project/Staph killing assays/disk difussion assays.csv"
+diskFile<-"~/Documents/Whiteley/PROJECTS/PaSaProject/Staph killing assays/disk difussion assays.csv"
 diskData <-read.csv(diskFile)
@@
 diskWtStaticMutShakingTtest<-t.test(x = diskMutShaking$avg, y = diskWtStatic1$avg, paired = T)
-tTestData<-list(diskWtTtest, diskMutTtest,diskShakingTtest, diskStaticTtest, diskWtStaticMutShakingTtest)
-TtestTable<-name <- function(dataPoint) {
-  data <-data.frame(dataPoint$data.name, dataPoint$p.value)
-}
-tTestDataTable<-bind_rows(map(tTestData, TtestTable))
+diskMutStaticWtShakingTtest<-t.test(x = diskWtShaking1$avg, y = diskMutStatic$avg, paired = T)
+tTestDataDiskDifussion<-list(diskWtTtest, diskMutTtest,diskShakingTtest, diskStaticTtest, diskWtStaticMutShakingTtest,diskMutStaticWtShakingTtest)
+tTestDiskDifussionTable<-bind_rows(map(tTestDataDiskDifussion, TtestTable))
 ```
@@
     plot_grid(figure5,legendFigure5,rel_widths = c(6, 1.7))
+```
+
+```{r t-tests}
+wtStatLuminescence<-luminescenceData1 %>% filter (CondStrain == "wtStat") %>% filter (TimePoint<7 &TechReplicate == 1)  %>% pull(techMean)
+wtMixedLuminescence<-luminescenceData1 %>% filter (CondStrain == "wtShake") %>% filter (TimePoint<7 &TechReplicate == 1) %>% pull(techMean)
+
+mutStatLuminescence<-luminescenceData1 %>% filter (CondStrain == "pqsLStat") %>% filter (TimePoint<7 &TechReplicate == 1)%>% pull(techMean)
+mutMixedLuminescence<-luminescenceData1 %>% filter (CondStrain == "pqsLShake") %>% filter (TimePoint<7 &TechReplicate == 1)%>% pull(techMean)
+
+tTestWtLuminescence<-t.test(x = wtStatLuminescence, y = wtMixedLuminescence, paired = T)
+tTestMutLuminescence<-t.test(x = mutStatLuminescence, y = mutMixedLuminescence, paired = T)
+
+tTestStatLuminescence<-t.test(x = wtStatLuminescence, y = mutStatLuminescence, paired = T)
+tTestMixedLuminescence<-t.test(x = wtMixedLuminescence, y = mutMixedLuminescence, paired = T)
+
+tTestWtStatVSMutMixedLuminescence<-t.test(x = wtStatLuminescence, y = mutMixedLuminescence, paired = T)
+tTestMutStatVSWtMixedLuminescence<-t.test(x = wtMixedLuminescence, y = mutStatLuminescence, paired = T)
+
+tTestDataLuminescence<-list(tTestWtLuminescence,tTestMutLuminescence,tTestStatLuminescence,tTestMixedLuminescence,
+                            tTestWtStatVSMutMixedLuminescence,tTestMutStatVSWtMixedLuminescence)
+TtestTable<-name <- function(dataPoint) {
+  data <-data.frame(dataPoint$data.name, dataPoint$p.value)
+}
+tTestLuminescenceTable<-bind_rows(map(tTestDataLuminescence, TtestTable))
 

### 2020-08-07 Microscopy Data.Rmd
added redSubtracted results

@@
 
-```{r threshold Sa by time}
+```{r threshold Sa by time (not useful)}
+
 #This function keeps getting changed but using the same name... so heads up on that
@@
 ```
-
+#Final Growth curves data
 ```{r Pa Growth curves from RedSubtracted Images}
@@
 redSubtractedData<-ProcessResults()#This was run using the "GetResults" function at the top..
-paRedSubtractResults<-redSubtractedData[[1]]%>% filter(Species == "Pa") %>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut"))
+redSubtractedDataSummary<-redSubtractedData[[1]]%>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut"))
+paRedSubtractResults<-redSubtractedDataSummary%>% filter(Species == "Pa")
+saRedSubtractResults<-redSubtractedDataSummary%>% filter(Species == "Sa")
+
 nonSubtractedData<-ProcessResults()
-paNonSubtractResults<-nonSubtractedData[[1]]%>% filter(Species == "Pa") %>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut"))
+nonSubtractedDataSummary<-nonSubtractedData[[1]]%>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut"))
+paNonSubtractResults<-nonSubtractedData[[1]]%>% filter(Species == "Pa") 
+saNonSubtractResults<-nonSubtractedData[[1]]%>% filter(Species == "Sa")
 
+#comparing the data from red 
 ggplot()+
-  geom_line(data=redSubtractedData[[1]]%>% filter(Species == "Pa") %>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=LogTotals),color = "red", size=2)+
-  geom_line(data=nonSubtractedData[[1]]%>% filter(Species == "Pa") %>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=LogTotals),color ="blue", size=2)+
+  geom_line(data=redSubtractedData[[1]]%>% filter(Species == "Pa") %>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=LogTotals),color = "red", size=.2)+
+  geom_line(data=nonSubtractedData[[1]]%>% filter(Species == "Pa") %>% filter(Condition == "Pa:Sa 1:1"& Strain %in% c("PA14wt", "PA14mut")), aes(x=TimePoint, y=LogTotals),color ="blue", size=.2)+
   facet_grid(Strain~Sample)+
@@
   theme_cowplot(12)
+
+#Compare biomass of Staph wt vs mutant from replicates
+
+saRedSubtractResults1<-saRedSubtractResults %>%ungroup() %>% group_by(Sample, TimePoint) %>% 
+  mutate (mutantAbsDifference = (abs(Totals -Totals[Strain == "PA14mut"])/Totals )) %>% 
+  mutate (mutantRatio = (Totals[Strain == "PA14mut"])/Totals ) %>% ungroup() %>% 
+  group_by(Strain) %>% mutate (repDifference1.2 = (abs(Totals[Sample == "rep1"] -Totals[Sample == "rep2"]))/Totals ) %>% 
+  mutate (repDifference2.3 = (abs(Totals[Sample == "rep2"] -Totals[Sample == "rep3"]))/Totals ) %>% 
+  mutate (repDifference1.3 = (abs(Totals[Sample == "rep1"] -Totals[Sample == "rep3"]))/Totals ) %>% ungroup()
+
+tidysaRedSubtractResults1<-saRedSubtractResults1 %>% gather(Comparison, Difference, -TimePoint, -Sample, -Strain, -Condition, -Species, -Totals, -LogTotals) %>% filter(!Difference == 0)
+
+ggplot()+#plotting the absolute difference between replicates and strains
+  geom_jitter(data = tidysaRedSubtractResults1 %>% filter(!Comparison=="mutantRatio"),
+              aes(x=TimePoint,y=Difference, color = Comparison),size=3, height = 0, width = .2)+
+  labs(title ="Variance comparison between strains and replicates")+
+  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+
+ggplot()+#plotting the absolute difference between strains only
+  geom_jitter(data = tidysaRedSubtractResults1 %>% filter(Comparison=="mutantRatio") %>% filter(!Difference == 1),
+              aes(x=TimePoint,y=Difference, color = Comparison, shape = Sample),size=3, height = 0, width = .2)+
+  labs(title ="Variance comparison mutant/wt")+
+  scale_y_log10(breaks = c(0.5,.25,1,2.5,5,10))+#breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
 

### 2020-08-07 Paper Figures/Paper figures Scipts.Rmd
added tTests

@@
 SaMutCo10<-hist.5.LogBinData %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14mut",LogBin == "(10, 100]") %>% pull(FrequencyLogBin)
+SaWtCo100<-hist.5.LogBinData %>%filter(Species =="Sa", ConditionNew == "Co", Strain=="PA14wt",LogBin == paste0("(100, ",bquote("\U221E"), ")")) %>% pull(FrequencyLogBin)
+SaMutCo100<-hist.5.LogBinData %>%filter(Species =="Sa", ConditionNew == "Co", Strain=="PA14mut",LogBin == paste0("(100, ",bquote("\U221E"), ")")) %>% pull(FrequencyLogBin)
 
@@
 
-#Pa mono vs Co
+#mono vs Co
 SaWt5<-t.test(x = SaWtMono5, y = SaWtCo5, paired = T)
@@
 
-tTestDatAggSizes<-list(SaWt5,SaWt10,SaMut5,SaMut10,PaWt5,PaWt10,PaMut5,PaMut10)
+#Wt vs pqsL
+SaWtMut5<-t.test(x = SaMutCo5, y = SaWtCo5, paired = F)
+SaWtMut10<-t.test(x = SaMutCo10, y = SaWtCo10, paired = F)
+#SaWtMut100<-t.test(x = SaMutCo100, y = SaWtCo100, paired = F)
+
+PaMonoWtMut5<-t.test(x = PaMutMono5, y = PaWtMono5, paired = F)
+PaMonoWtMut10<-t.test(x = PaMutMono10, y = PaWtMono10, paired = F)
+PaMonoWtMut100<-t.test(x = PaMutMono100, y = PaWtMono100, paired = F)
+
+PaCoWtMut5<-t.test(x = PaMutCo5, y = PaWtCo5, paired = F)
+PaCoWtMut10<-t.test(x = PaMutCo10, y = PaWtCo10, paired = F)
+PaCoWtMut100<-t.test(x = PaMutCo100, y = PaWtCo100, paired = F)
+
+tTestDatAggSizes<-list(SaWt5,SaWt10,SaMut5,SaMut10,PaWt5,PaWt10,PaMut5,PaMut10,SaWtMut5,SaWtMut10,
+                       PaMonoWtMut5,PaMonoWtMut10,PaMonoWtMut100,PaCoWtMut5,PaCoWtMut10,PaCoWtMut100)
 tTestAggSizesTable<-bind_rows(map(tTestDatAggSizes, TtestTable))

### 2020-08-17 Paper Figures/Paper figures Scipts.Rmd
aligned borders and standardize font on figures 1 and 2

@@
 
-GraphGrowthCurveLog1<-function (rawData, statsData){
+GraphGrowthCurveLog1<-function (Strain){
     shakingWtPlot<-ggplot()+
-      geom_line(data=statsData%>% filter(condition == "Shaking" & strain == "wt"), aes(x=time, y=logCFUmean, linetype = bug), size=.5)+
-      geom_errorbar(data=statsData%>% filter(condition == "Shaking" & strain == "wt"),aes(x = time, ymin = logCFUmean-logCFUse, ymax=logCFUmean+logCFUse), width = 0, size = 0.5)+
+      geom_line(data=PA14DataStats%>% filter(condition == "Shaking" & strain == Strain), aes(x=time, y=logCFUmean, linetype = bug), size=.5)+
+      geom_errorbar(data=PA14DataStats%>% filter(condition == "Shaking" & strain == Strain),aes(x = time, ymin = logCFUmean-logCFUse, ymax=logCFUmean+logCFUse), width = 0, size = 0.5)+
       geom_hline(yintercept=9.619, color='red', linetype = "solid") + #Pa stirred
@@
       scale_y_continuous(limits = c(4,10))+
-      scale_x_continuous(breaks = c(4,8,12,16))+
-      theme_cowplot(12)
+      scale_x_continuous(breaks = c(0,4,8,12,16))+
+      theme_cowplot(12)+
+      theme(plot.margin = unit(c(.5,0,0,.5), "cm"),
+            axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,2,0),size=11),
+            axis.title.y = element_text(margin = margin(0,0,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11),
+            legend.title = element_text(size=13),legend.text = element_text(size = 11))
 
     staticWtPlot<-ggplot()+
-      geom_line(data=statsData%>% filter(condition == "Static" & strain == "wt"), aes(x=time, y=logCFUmean, linetype = bug), size=.5)+
-      geom_errorbar(data=statsData%>% filter(condition == "Static" & strain == "wt"),aes(x = time,ymin=logCFUmean-logCFUse, ymax = logCFUmean+logCFUse), width = 0, size = 0.5)+
+      geom_line(data=PA14DataStats%>% filter(condition == "Static" & strain == Strain), aes(x=time, y=logCFUmean, linetype = bug), size=.5)+
+      geom_errorbar(data=PA14DataStats%>% filter(condition == "Static" & strain == Strain),aes(x = time,ymin=logCFUmean-logCFUse, ymax = logCFUmean+logCFUse), width = 0, size = 0.5)+
       scale_linetype_manual(values = c( "solid","dashed"), labels = c("stirred","static"))+
@@
       scale_y_continuous(limits=c(4,10))+
-      scale_x_continuous(breaks = c(4,8,12,16))+
-      theme_cowplot(12)
+      scale_x_continuous(breaks = c(0,4,8,12,16))+
+      theme_cowplot(12)+
+      theme(plot.margin = unit(c(.5,0,0,0), "cm"),
+            axis.title.x = element_text(margin = margin(0,0,0,0),size=13 ),axis.text.x = element_text(margin = margin(1,0,2,0),size=11),
+            axis.title.y = element_text(margin = margin(0,0,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,0,0),size=11))
 
-    legend <- get_legend(shakingWtPlot + theme(legend.box.margin = margin(0, 0, 0, 10)))
+    legend <- get_legend(shakingWtPlot + theme(legend.box.margin = margin(0, 0, 0, 35)))
     prow <- plot_grid(shakingWtPlot+theme(legend.position="none"),staticWtPlot+theme(legend.position="none"),
-                      align='vh',labels = c("A", "B"),nrow = 1)
+                      align='v',labels = c("A", "B"),nrow = 1,label_size= 20, label_x = .02, label_y = 1)
     plot_grid(prow,legend,rel_widths = c(3, 1))
-    }
 
-GraphGrowthCurveLog2<-function (rawData, statsData){
-  shakingMutPlot<-ggplot()+
-    geom_line(data=statsData%>% filter(condition == "Shaking" & strain ==  "mut"), aes(x=time, y=logCFUmean, linetype = bug), size=.5)+
-    geom_errorbar(data=statsData%>% filter(condition == "Shaking" & strain == "mut"), aes(x = time, ymin = logCFUmean-logCFUse, ymax = logCFUmean+logCFUse), width = 0, size = 0.5)+
-    scale_linetype_manual(values = c( "solid","dashed"), labels = c(bquote(paste(italic('P. aeruginosa'))),bquote(paste(italic('S. aureus')))))+
-    geom_hline(yintercept=9.13, color='red', linetype = "dashed") +
-    geom_hline(yintercept=9.57, color='red', linetype = "solid") +
-    labs(x = "Time (hours)", y = expression(paste(Log[10], " CFU")), linetype = "Species")+
-    scale_y_continuous(limits = c(4,10))+
-    scale_x_continuous(breaks = c(4,8,12,16))+
-    theme_cowplot(12)
-
-  staticMutPlot<-ggplot()+
-    geom_line(data=statsData%>% filter(condition == "Static" & strain == "mut"), aes(x=time, y=logCFUmean, linetype = bug), size=.5)+
-    geom_errorbar(data=statsData%>% filter(condition == "Static" & strain ==  "mut"), aes(x = time, ymin = logCFUmean-logCFUse, ymax = logCFUmean+logCFUse), width = 0, size = 0.5)+
-    scale_linetype_manual(values = c( "solid","dashed"), labels = c(bquote(paste(italic('P. aeruginosa'))),bquote(paste(italic('S. aureus')))))+
-    geom_hline(yintercept=8.88, color='red', linetype = "dashed") +
-    geom_hline(yintercept=8.98, color='red', linetype = "solid") +
-    labs(x = "Time (hours)", y = expression(paste(Log[10], " CFU")), linetype = "")+
-    scale_y_continuous(limits = c(4,10))+
-    scale_x_continuous(breaks = c(4,8,12,16))+
-    theme_cowplot(12)
-  legend <- get_legend(shakingMutPlot + theme(legend.box.margin = margin(0, 0, 0, 10)))
-  prow <- plot_grid(shakingMutPlot+theme(legend.position="none"),staticMutPlot+theme(legend.position="none"),
-                      align='vh',labels = c("A", "B"),nrow = 1)
-    plot_grid(prow,legend,rel_widths = c(3, 1))
     }
@@
 #Graph logs
-figure1AB<-GraphGrowthCurveLog1(PA14Data,PA14DataStats)
-figure1AB
-#Graph logs
-figure2AB<-GraphGrowthCurveLog2(PA14Data,PA14DataStats)
-figure2AB
+figure1AB<-GraphGrowthCurveLog1("wt")
+figure2AB<-GraphGrowthCurveLog1("mut")
 
@@
 tTestDiskDifussionTable<-bind_rows(map(tTestDataDiskDifussion, TtestTable))
-#####
-#plot disk difussion
-#####
- figure1C<-ggplot()+
-      geom_errorbar(data=diskDataStats1 %>% filter (strain == "wt"), aes(x = condition, ymin = meanBio - SDBio, ymax = meanBio + SDBio),width = .2)+
-      geom_point(data=diskDataStats1 %>% filter (strain == "wt"), aes(x=condition, y=meanBio, shape =condition), size=3)+
-      scale_shape_manual(values = c(1,2),limits=c("static","shaking"), 
-                     labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type static")),
-                                bquote(paste(italic('P. aeruginosa'), " wild-type mixed"))))+
-      scale_x_discrete(name ="", breaks = c("static","shaking"), labels =c("Static","Mixed"))+
-    ylim(0,17.5)+
-  labs( y = "Zone of inhibition (mm)", shape = "Growth condtion") +
-      theme_cowplot(12)
-
-    figure2C<-ggplot()+
-      geom_errorbar(data=diskDataStats1 %>% filter (strain == "pqsl"), aes(x = condition, ymin = meanBio - SDBio, ymax = meanBio + SDBio),width = .2)+
-      geom_point(data=diskDataStats1 %>% filter (strain == "pqsl"), aes(x=condition, y=meanBio, shape =condition), size=3)+
-      scale_shape_manual(values = c(16,17),limits=c("static","shaking"), 
-                     labels = c(bquote(paste(italic('P. aeruginosa '), Delta*"pqsL static")),
-                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL mixed"))))+
-      ylim(0,17.5)+
-      scale_x_discrete(name ="", breaks = c("static","shaking"), labels =c("Static","Mixed"))+
-      labs( y = "Zone of inhibition (mm)", shape = "Growth condtion") +
-      theme_cowplot(12)
 #####
@@
 
-#luminescence plots
+#plot disk difussion and luminescence 
 #####
+GraphStaphKilling<-function(Strain1,Strain2){ 
+figure1C<-ggplot()+
+      geom_errorbar(data=diskDataStats1 %>% filter (strain == Strain1), aes(x = condition, ymin = meanBio - SDBio, ymax = meanBio + SDBio),width = 0)+
+      geom_point(data=diskDataStats1 %>% filter (strain == Strain1), aes(x=condition, y=meanBio, shape =condition), size=3)+
+      scale_shape_manual(values = c(1,2),limits=c("shaking","static"), 
+                     labels = c(bquote(paste(italic('P. aeruginosa'), " mixed")),
+                                bquote(paste(italic('P. aeruginosa'), " static"))))+
+  #scale_shape_manual(values = c(16,17),limits=c("static", "shaking"), 
+      #               labels = c(bquote(paste(italic('P. aeruginosa '), Delta*"pqsL static")),
+      #                          bquote(paste(italic('P. aeruginosa '), Delta*"pqsL mixed"))))+
+      scale_x_discrete(name ="", breaks = c("static","shaking"), labels =c("Static","Mixed"))+
+    ylim(0,17.5)+
+  labs( y = "Zone of inhibition (mm)", shape = "Growth condtion") +
+      theme_cowplot(12)+
+  theme(plot.margin = unit(c(.5,0,0,.3), "cm"),
+        axis.text.x  = element_text(margin = margin(0,0,0,0),size=13),
+        axis.title.y = element_text(margin = margin(0,0,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11),
+        legend.title = element_text(size=13),legend.text = element_text(size = 11))
+
 figure1D<-ggplot()+
-      geom_line(data=luminescenceData1 %>% filter (Strain == "wt") %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, group = Condition), size=.5, show.legend = FALSE)+
-      geom_point(data=luminescenceData1%>% filter (Strain == "wt") %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, shape = Condition), size=3)+
-      scale_y_log10(name=expression(paste(italic('S. aureus'), " % luminescence" )), limits = c(1,121),labels = c(1, 10, 100),breaks = c(1, 10, 100))+
+      geom_line(data=luminescenceData1 %>% filter (Strain == Strain2) %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, group = Condition), size=.5, show.legend = FALSE)+
+      geom_point(data=luminescenceData1%>% filter (Strain == Strain2) %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, shape = Condition), size=3)+
+      geom_errorbar(data=luminescenceData1%>% filter (Strain == Strain2) %>% filter (TimePoint<7), aes(x=TimePoint, ymin=Mean-SE,ymax=Mean+SE), width = 0)+
+      scale_y_log10(name=expression(paste(italic('S. aureus'), " luminescence (%)" )), limits = c(1,121),labels = c(1, 10, 100),breaks = c(1, 10, 100))+
       labs( x = "Time (minutes)",shape = "") +
-      scale_shape_manual(values = c(1,2),limits=c("static","shaking"), 
-                     labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type static")),
-                                bquote(paste(italic('P. aeruginosa'), " wild-type mixed"))))+
-      theme(legend.position="top")+
-      theme_cowplot(12)
+      scale_shape_manual(values = c(1,2),limits=c("shaking","static"))+
+      theme_cowplot(12)+
+      theme(legend.position="top",plot.margin = unit(c(0,0,0,0), "cm"),
+            axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=11),
+            axis.title.y = element_text(margin = margin(0,0,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
 
-    figure2D<-ggplot()+
-      geom_line(data=luminescenceData1 %>% filter (Strain == "pqsL") %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, group = Condition), size=.5, show.legend = FALSE)+
-      geom_point(data=luminescenceData1%>% filter (Strain == "pqsL") %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, shape = Condition), size=3)+
-      scale_y_log10(name=expression(paste(italic('S. aureus'), " % luminescence" )),limits = c(1,121), labels = c(1,10,100),breaks = c(1, 10, 100))+
-      labs( x = "Time (minutes)",shape = "") +
-      scale_shape_manual(values = c(16,17),limits=c("static", "shaking"), 
-                     labels = c(bquote(paste(italic('P. aeruginosa '), Delta*"pqsL static")),
-                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL mixed"))))+
-      theme(legend.position="top")+
-      theme_cowplot(12)
+legendFigure1C <- get_legend(figure1C + theme(legend.box.margin = margin(0, 0, 0, 35)))
+plotsFigure1cd <- plot_grid(figure1C+theme(legend.position="none"),figure1D+theme(legend.position="none"),
+                      align='vh',labels = c("C", "D"),hjust = -1,nrow = 1,label_size= 20)
+plot_grid(plotsFigure1cd,legendFigure1C,rel_widths = c(3, 1))
+}   
+figure1CD<-GraphStaphKilling("wt","wt")
+figure2CD<-GraphStaphKilling("pqsl", "pqsL")
 #####
-
-    legendFigure1C <- get_legend(figure1C + theme(legend.box.margin = margin(0, 0, 0, 10)))
-    plotsFigure1cd <- plot_grid(figure1C+theme(legend.position="none"),figure1D+theme(legend.position="none"),
-                      align='vh',labels = c("C", "D"),hjust = -1,nrow = 1)
-    figure1CD<-plot_grid(plotsFigure1cd,legendFigure1C,rel_widths = c(3, 1))
-
-    legendFigure2c <- get_legend(figure2C + theme(legend.box.margin = margin(0, 0, 0, 10)))
-    plotsFigure2cd <- plot_grid(figure2C+theme(legend.position="none"),figure2D+theme(legend.position="none"),
-                      align='vh',labels = c("C", "D"),hjust = -1,nrow = 1)
-    figure2CD<-plot_grid(plotsFigure2cd,legendFigure2c,rel_widths = c(3, 1))
-
 ```
@@
 ggplot()+
-  geom_col(data = hist.plank.Agg.Stats %>% filter(Strain == strain),aes(x=Aggregation,y=MeanBiomass, fill = ConditionNew),
+  geom_col(data = hist.plank.Agg.Stats %>% filter(Strain == strain),aes(x=Aggregation,y=MeanBiomass*100, fill = ConditionNew),
            size=3,position = position_dodge( width = .9),show.legend = FALSE)+
-  geom_errorbar(data = hist.plank.Agg.Stats%>% filter(Strain == strain),aes(x=Aggregation,ymin=MeanBiomass-SEBiomass, ymax = MeanBiomass+SEBiomass, group = ConditionNew),width = 0, size=.5,position = position_dodge(width = .9))+
+  geom_errorbar(data = hist.plank.Agg.Stats%>% filter(Strain == strain),aes(x=Aggregation,ymin=(MeanBiomass-SEBiomass)*100, ymax = (MeanBiomass+SEBiomass)*100, group = ConditionNew),width = 0, size=.5,position = position_dodge(width = .9))+
+  scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)))+
   facet_grid(.~Species)+
   scale_fill_grey()+
-  labs(title = '', x = "", y = "Biomass contribution")+
+  labs(title = '', x = "", y = "Biomass contribution (%)")+
   theme_cowplot()+
-  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(face = "italic"))
+  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
+        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
+        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=13),
+        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
 }
@@
 hist.5.LogBinSummarize$LogBin<-as.factor(hist.5.LogBinSummarize$LogBin)
+new.rowWt <- data.frame(Species = 'Sa', Condition = "Pa:Sa 1:1",ConditionNew = "Co",Strain = "PA14wt", LogBin =paste0("(100, ",bquote("\U221E"), ")"), MeanFrequencyLogBin = 0,SEFrequencyLogBin = 0)
+new.rowMut <- data.frame(Species = 'Sa', Condition = "Pa:Sa 1:1",ConditionNew = "Co",Strain = "PA14mut", LogBin =paste0("(100, ",bquote("\U221E"), ")"), MeanFrequencyLogBin = 0,SEFrequencyLogBin = 0)
+hist.5.LogBinSummarize<-rbind(hist.5.LogBinSummarize, new.rowWt)
+hist.5.LogBinSummarize<-rbind(hist.5.LogBinSummarize, new.rowMut)
+
 hist.5.LogBinSummarize$LogBin <- factor(hist.5.LogBinSummarize$LogBin, levels = c("(5, 10]","(10, 100]",paste0("(100, ",bquote("\U221E"), ")")))
@@
 hist.5.LogBinSummarize$ConditionNew <- factor(hist.5.LogBinSummarize$ConditionNew, levels = c("Mono", "Co"))
+
 #####
@@
 #####
-PlotFreqLogBin<-function(strain,titulo){
+PlotFreqLogBin<-function(strain, itulo){
   df <-hist.5.LogBinSummarize%>% filter(Strain == strain)
@@
     #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+
     facet_grid(.~Species)+
-    labs(fill = "Condition",y = "Mean number of aggregates per Bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    labs(fill = "Condition",y = "Aggregates per bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
     guides(color = FALSE)+
+    scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)))+
     scale_fill_grey()+
-    theme_cowplot(12)+
-    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(face = "italic"))
+    theme_half_open()+
+    theme(plot.title = element_text(hjust = 0.5),
+          strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
+          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
+          plot.margin = unit(c(0,.5,0,.5), "cm"),
+          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=11),
+          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,2,2,0),size=11),
+          legend.title = element_text(size=13),legend.text = element_text(size = 11))
 }
-
 figure1F<-PlotFreqLogBin("PA14wt", "WT")
@@
 #####
-figure1EF<-plot_grid(figure1E,figure1F,rel_widths = c(1,1.2),align='vh',labels = c("E", "F"),hjust = -1,nrow = 1)
-figure2EF<-plot_grid(figure2E,figure2F,rel_widths = c(1,1.2),align='vh',labels = c("E", "F"),hjust = -1,nrow = 1)
+figure1EF<-plot_grid(figure1E,figure1F,rel_widths = c(1,1.2),align='vh',labels = c("E", "F"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)
+figure2EF<-plot_grid(figure2E,figure2F,rel_widths = c(1,1.2),align='vh',labels = c("E", "F"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)
 ```
@@
 ```{Make full figures 1 and 2}
-plot_grid(figure1AB,figure1CD,figure1EF, align='vh',nrow = 3, rel_heights = c(1,1,1.5))
-plot_grid(figure2AB,figure2CD,figure2EF, align='vh',nrow = 3, rel_heights = c(1,1,1.5))
+plots <- align_plots(figure1AB, figure1CD,align = 'vh', axis = 'l')
+plot_grid(plots[[1]],plots[[2]],figure1EF, align='vh',nrow = 3, rel_heights = c(1,1,1.5))
+
+plots <- align_plots(figure2AB, figure2CD,align = 'vh', axis = 'l')
+plot_grid(plots[[1]],plots[[2]],figure2EF, align='vh',nrow = 3, rel_heights = c(1,1,1.5))
+
 ```
-
 ```{r biomass per bin}
@@
 ```
-
 ```{r Tobramycin}
@@
 ```
-
 ```{r invasion ratios graphs}

### 2020-08-24 Paper Figures/Paper figures Scipts.Rmd
aesthetic changes

@@
 figure2EF<-plot_grid(figure2E,figure2F,rel_widths = c(1,1.2),align='vh',labels = c("E", "F"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)
+
 ```
@@
 ```
+
 ```{r biomass per bin}

### 2020-08-27 Paper Figures/Paper figures Scipts.Rmd
aligned figures 1 and 2

@@
 GraphGrowthCurveLog1<-function (Strain){
+  if(Strain == "wt"){etiqueta = bquote(paste(italic('P. aeruginosa')))}
+  if(Strain == "mut"){etiqueta = bquote(paste(italic('P. aeruginosa '*Delta*"pqsL")))}
     shakingWtPlot<-ggplot()+
@@
       geom_hline(yintercept=9.13, color='red', linetype = "dashed") + #Sa stirred
-      scale_linetype_manual(values = c( "solid","dashed"), labels = c(bquote(paste(italic('P. aeruginosa'))),bquote(paste(italic('S. aureus')))))+
-      labs(x = "Time (hours)", y = expression(paste(Log[10], " CFU")), linetype = "Species")+
+      scale_linetype_manual(values = c( "solid","dashed"), labels = c(etiqueta,bquote(paste(italic('S. aureus')))))+
+      labs(x = "Time (hours)", y = expression(paste(Log[10], " CFU")), linetype = "")+
       scale_y_continuous(limits = c(4,10))+
@@
 
-    legend <- get_legend(shakingWtPlot + theme(legend.box.margin = margin(0, 0, 0, 35)))
+    legend <- get_legend(shakingWtPlot + theme(legend.box.margin = margin(0, 0, 0, 10)))
     prow <- plot_grid(shakingWtPlot+theme(legend.position="none"),staticWtPlot+theme(legend.position="none"),
                       align='v',labels = c("A", "B"),nrow = 1,label_size= 20, label_x = .02, label_y = 1)
-    plot_grid(prow,legend,rel_widths = c(3, 1))
-
+    plot_grid(prow,legend,rel_widths = c(3,.6))
     }
@@
     ylim(0,17.5)+
-  labs( y = "Zone of inhibition (mm)", shape = "Growth condtion") +
+  labs( y = "Zone of inhibition (mm)", shape = "") +
       theme_cowplot(12)+
@@
 
-legendFigure1C <- get_legend(figure1C + theme(legend.box.margin = margin(0, 0, 0, 35)))
+legendFigure1C <- get_legend(figure1C + theme(legend.box.margin = margin(0, 0, 0, 10)))
 plotsFigure1cd <- plot_grid(figure1C+theme(legend.position="none"),figure1D+theme(legend.position="none"),
                       align='vh',labels = c("C", "D"),hjust = -1,nrow = 1,label_size= 20)
-plot_grid(plotsFigure1cd,legendFigure1C,rel_widths = c(3, 1))
+plot_grid(plotsFigure1cd,legendFigure1C,rel_widths = c(3, .6))
 }   
@@
     geom_errorbar(data = df,aes(x=LogBin,ymin=MeanFrequencyLogBin-SEFrequencyLogBin, ymax = MeanFrequencyLogBin+SEFrequencyLogBin, group =ConditionNew ),width = 0, size= .5,position = position_dodge( width = .9))+
-    #labs(title = titulo)+
-    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-
     facet_grid(.~Species)+
-    labs(fill = "Condition",y = "Aggregates per bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    labs(fill = "",y = "Aggregates per bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
     guides(color = FALSE)+
     scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)))+
-    scale_fill_grey()+
+    scale_fill_grey(labels = c("Mono-culture", "Co-culture"))+
     theme_half_open()+
     theme(plot.title = element_text(hjust = 0.5),
-          strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
+          strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
           strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
@@
           axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,2,2,0),size=11),
-          legend.title = element_text(size=13),legend.text = element_text(size = 11))
+          legend.title = element_text(size=13),legend.text = element_text(size = 11),
+          legend.position = c(0.79, 0.60))
 }
@@
 figure2EF<-plot_grid(figure2E,figure2F,rel_widths = c(1,1.2),align='vh',labels = c("E", "F"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)
-
 ```
@@
 ```
+```{r figure 3}
+MixedAggregateBiomassPlot<-ggplot()+
+  #geom_point(data = combinedMixedAggData,aes(x=Strain.x,y=PercentTotalBiomass ),size=1)+
+  geom_point(data = combinedMixedAggData,aes(x=Strain.x,y=MeanTotalBiomass),shape = 1, size=4)+
+  geom_errorbar(data = combinedMixedAggData,aes(x=Strain.x,ymin=MeanTotalBiomass-SETotalBiomass, ymax =MeanTotalBiomass+SETotalBiomass),size=.2, width = 0)+
+  scale_shape_manual(values = c(1,2),name = "", limits=c("PA14wt","PA14mut"))+
+  scale_x_discrete(breaks=c("PA14wt","PA14mut"), 
+                   labels = c(bquote(paste(italic("P. aeruginosa"), " wt")), bquote(paste(italic(Delta*"pqsL")))))+
+    labs(y = "Mixed aggregates biomass (%)", x = "")+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5),legend.position="none")
 
+MixedAggregateFrequencyPlot<-  ggplot()+
+  #geom_point(data = combinedMixedAggData,aes(x=Strain.x,y=PercentAggs ),size=1)+
+  geom_point(data = combinedMixedAggData,aes(x=Strain.x,y=MeanAggs),size=4, shape = 1)+
+  geom_errorbar(data = combinedMixedAggData,aes(x=Strain.x,ymin=MeanAggs-SEAggs, ymax =MeanAggs+SEAggs),size=.2, width = 0)+
+  scale_shape_manual(values = c(1,2),name = "", limits=c("PA14wt","PA14mut"))+
+  scale_x_discrete(breaks=c("PA14wt","PA14mut"), 
+                     labels = c(bquote(paste(italic("P. aeruginosa"), " wt")),bquote(paste(italic(Delta*"pqsL")))))+
+  labs(y = "Mixed aggregates (% frequency)", x = "")+
+  ylim(0,10)+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5),legend.position="none")
+
+sa.paPlot<-
+  ggplot()+
+  geom_point(data = enrichmentDataFinal %>% filter(Relation == "Sa->Pa"),aes(y=meanEnrichment, x = Strain),size=4, shape = 1)+
+  geom_errorbar(data = enrichmentDataFinal %>% filter(Relation == "Sa->Pa"),
+                aes(ymin = meanEnrichment-sdEnrichment,ymax = meanEnrichment+sdEnrichment, x = Strain),size=.2, width = 0)+
+  #labs( y = bquote(paste("Enrichment distance\n", italic("S. aureus") %->% italic("P. aeruginosa "),"("*mu*"m)")), x = "" ) +
+  labs(y = expression(atop("Enrichment distance ",paste(italic("S. aureus") %->% italic("P. aeruginosa "),"("*mu*"m)"))), x = "" ) +
+  scale_shape_manual(values = c(1,2),name = "", limits=c("wt","mut"),
+                     labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type")),
+                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL"))))+
+  scale_x_discrete(name ="", breaks = c("wt","mut"), 
+                   labels = c(bquote(paste(italic("P. aeruginosa"), " wt")), bquote(paste(italic(Delta*"pqsL")))))+
+  ylim(1, 9)+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5),legend.position="none")
+
+sa.saPlot<-
+  ggplot()+
+  geom_point(data = enrichmentDataFinal %>% filter(Relation == "Sa->Sa"),aes(y=meanEnrichment, x = Strain),size=4, shape = 1)+
+  geom_errorbar(data = enrichmentDataFinal %>% filter(Relation == "Sa->Sa"),
+                aes(ymin = meanEnrichment-sdEnrichment,ymax = meanEnrichment+sdEnrichment, x = Strain),size=.2, width = 0)+
+  labs(y = expression(atop("Enrichment distance ",paste(italic("S. aureus") %->% italic("S. aureus "),"("*mu*"m)"))), x = "" ) +
+  scale_shape_manual(values = c(1,2),name = "", limits=c("wt","mut"),labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type")),
+                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL"))))+
+  scale_x_discrete(name ="", breaks = c("wt","mut"), 
+                   labels = c(bquote(paste(italic("P. aeruginosa"), " wt")), bquote(paste(italic(Delta*"pqsL")))))+
+  ylim(1, 9)+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5),legend.position="none")
+
+figure7 <- plot_grid(MixedAggregateBiomassPlot,sa.saPlot,sa.paPlot,align='vh',labels = c("A","B", "C"),hjust = -1,nrow = 1)
+figure7
+```
 ```{r biomass per bin}
@@
 ```{r Tobramycin}
-#data wrangling
-cleanSCFM2DataTobSa <- newSCFMDataSa %>% group_by(timePoint, antibiotic, culture) %>% summarise(meanCFUratio = mean(ratioCFU), sdCFUratio = sd(ratioCFU),meanLogRatio = mean(ratiolog), sdLogRatio = sd(ratiolog))
+#data is on "SaPa TOB growth curves.Rmd"
+#End point bar graph with std error
+tobCFUPlot<-
+  ggplot() +
+  geom_col(data = wilcoxDataGood, aes (x = culture, y = meanLog, fill = antibiotic, group = antibiotic), position = position_dodge( ))+
+  geom_linerange(data = wilcoxDataGood, aes(x = culture, ymin = meanLog - seLog, ymax = meanLog + seLog,group = antibiotic),position = position_dodge(width = .9))+
+  scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)), breaks = c(0,2,4,6,8,10), labels =c(0,2,4,6,8,10))+
+  scale_x_discrete(name ="", breaks = c("mono","wt","mut"), 
+                   labels = c(expression(atop(italic("S. aureus"), paste("mono-culture"))), 
+                              expression(atop(italic("S. aureus +"), paste(italic("P. aeruginosa"), " wt"))), 
+                              expression(atop(italic("S. aureus +"), paste(italic("P. aeruginosa "*Delta*"pqsL"))))))+
+  labs(y = expression(paste(italic("S. aureus "), "CFU (",Log[10]),")"), x = "", fill = "") +
+  scale_fill_grey()+
+  theme_cowplot()+
+  theme_half_open()+
+  background_grid()
 
-#this is using CFUs
-ggplot()+
-  #geom_pointrange(data=cleanSCFM2DataTobSa,aes(x=timePoint, y = meanCFUratio, ymin = meanCFUratio - sdCFUratio, ymax = meanCFUratio + sdCFUratio, color = culture), size=1)+
-  geom_point(data=cleanSCFM2DataTobSa,aes(x=timePoint, y = meanCFUratio, color = culture), size=3)+
-  geom_errorbar(data=cleanSCFM2DataTobSa,aes(x=timePoint,ymin = meanCFUratio - sdCFUratio, ymax = meanCFUratio + sdCFUratio, color = culture), size=1)+
-  #geom_vline(xintercept=3, linetype = "dashed")+
-  scale_y_log10("Growth ratio compared to co-culture with wt", breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  #annotate("text", x = 3, y = 10e6, label = "TOB added")+
-  facet_grid(.~antibiotic)+
-  labs(x = "Time (hours)", color="Culture condition", shape =  "Antiobiotic/Control")
+tobPercentChangePlot<-
+  ggplot() +
+  geom_col(data = percentChange %>% filter(sample == "1-25-20"), aes (x = culture, y = 10^(MeanLogKill)))+
+  geom_linerange(data = percentChange, aes(x = culture, ymin = 10^(MeanLogKill - SeLogKill/2), ymax = 10^(MeanLogKill + SeLogKill/2)))+
+  scale_y_log10(expand = expand_scale(mult = c(0, 0.05)))+
+  scale_x_discrete(name ="", breaks = c("mono","wt","mut"), 
+                   labels = c(expression(atop(italic("S. aureus"), paste("mono-culture"))), 
+                              expression(atop(italic("S. aureus +"), paste(italic("P. aeruginosa"), " wt"))), 
+                              expression(atop(italic("S. aureus +"), paste(italic("P. aeruginosa "*Delta*"pqsL"))))))+
+  #labs(y = expression(atop("Enrichment distance ",paste(italic("S. aureus") %->% italic("S. aureus "),"("*mu*"m)"))), x = "" ) +
+  labs(y = expression(paste("Fold killing ", italic("S. aureus"))), x = "") +
+  scale_fill_grey()+
+  theme_cowplot()+
+  theme_half_open()+
+  background_grid()
 
-#This one is using logCFUs
-ggplot()+
-  geom_point(data=cleanSCFM2DataTobSa,aes(x=timePoint, y = meanLogRatio, color = culture), size=3)+
-  geom_errorbar(data=cleanSCFM2DataTobSa,aes(x=timePoint,ymin = meanLogRatio - sdLogRatio, ymax = meanLogRatio + sdLogRatio, color = culture), size=.5, width = 0)+
-  geom_hline(xintercept=3, linetype = "dashed")+
-  scale_y_continuous(limits = c(.6,1.6 ))+
-  #scale_y_log10("Growth ratio compared to co-culture with wt", breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = c(10e-0.2,10e0.2))+
-  annotate("text", x = 3, y = 1.4, label = "TOB added")+
-  facet_grid(.~antibiotic)+
-  labs(x = "Time (hours)", color="Culture condition", shape =  "Antiobiotic/Control") +
-  theme_cowplot(12)
-
-GraphTOBGrowthCurveLog<-function (){
-    controlPlot<-ggplot()+
-      geom_point(data=cleanSCFM2DataTobSa %>% filter(antibiotic=="Control", culture != "wt"),aes(x=timePoint, y = meanLogRatio, shape = culture), size=3)+
-      geom_errorbar(data=cleanSCFM2DataTobSa%>% filter(antibiotic=="Control", culture != "wt"),aes(x=timePoint,ymin = meanLogRatio - sdLogRatio, ymax = meanLogRatio + sdLogRatio), size=.5, width = 0.2)+
-      geom_hline(yintercept=1, linetype = "dashed")+
-      scale_y_continuous(limits = c(.6,1.6 ))+
-      labs(x = "Time (hours)", shape="Culture condition", y = "Log Growth ratio compared to wild-type co-culture ") +
-      theme_cowplot(12)
-
-    tobPlot<-ggplot()+
-      geom_point(data=cleanSCFM2DataTobSa %>% filter(antibiotic=="TOB", culture != "wt"),aes(x=timePoint, y = meanLogRatio, shape = culture), size=3)+
-      geom_errorbar(data=cleanSCFM2DataTobSa%>% filter(antibiotic=="TOB", culture != "wt"),aes(x=timePoint,ymin = meanLogRatio - sdLogRatio, ymax = meanLogRatio + sdLogRatio), size=.5, width = 0.2)+
-      scale_y_continuous(limits = c(.6,1.6 ))+
-      geom_hline(yintercept=1, linetype = "dashed")+
-      labs(x = "Time (hours)", y = "", color="Culture condition") +
-      theme_cowplot(12)
-
-    legend <- get_legend(controlPlot + theme(legend.box.margin = margin(0, 200, 300,0)))
-    prow <- plot_grid(controlPlot+theme(legend.position="none"),tobPlot+theme(legend.position="none"),align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)
+prow <- plot_grid(tobCFUPlot+theme(legend.position="none"),tobPercentChangePlot+theme(legend.position="none"),align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)
+legend <- get_legend(tobCFUPlot + theme(legend.box.margin = margin(0, 0, 0, -6)))
 plot_grid(prow,legend,rel_widths = c(3, .4))
-    }
-GraphTOBGrowthCurveLog()
+#this is the winner
+plot_grid(tobCFUPlot+theme(legend.position="none"),legend,tobPercentChangePlot+theme(legend.position="none"),align='vh',labels = c("A", "","B"),hjust = -1,nrow = 1,rel_widths = c(1,.15,1))
 ```

### 2020-08-27 Microscopy Data Clean.Rmd
cosmetic changes

@@
 library(scales)#for negative log
+library(stringr)
 
@@
 ### I think this is the final figure
-MixedAggregateBiomassPlot<-ggplot()+
-  geom_point(data = combinedMixedAggData,aes(x=Strain,y=PercentTotalBiomass ),size=1)+
-  geom_point(data = combinedMixedAggData,aes(x=Strain,y=MeanTotalBiomass, shape = Strain),size=3)+
-  geom_errorbar(data = combinedMixedAggData,aes(x=Strain,ymin=MeanTotalBiomass-SETotalBiomass, ymax =MeanTotalBiomass+SETotalBiomass),size=.2, width = .2)+
+#MixedAggregateBiomassPlot<-
+  ggplot()+
+  geom_point(data = combinedMixedAggData,aes(x=Strain.x,y=PercentTotalBiomass ),size=1)+
+  geom_point(data = combinedMixedAggData,aes(x=Strain.x,y=MeanTotalBiomass),shape = 1, size=3)+
+  geom_errorbar(data = combinedMixedAggData,aes(x=Strain.x,ymin=MeanTotalBiomass-SETotalBiomass, ymax =MeanTotalBiomass+SETotalBiomass),size=.2, width = 0)+
   #labs(title ="Proportion of mixed species biomass")+
@@
 plot_grid(figure7,legendFigure7,rel_widths = c(4, 1.7))
-#plot_grid(sa.saPlot,sa.paPlot,align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)
+figure7
+plot_grid(sa.saPlot,sa.paPlot,align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)
 

### 2020-09-01 Paper Figures/Paper figures Scipts.Rmd
Add the planktonic version of the aggregate to the t-test table - make the aggregate bins in percent of total aggregates instead of total aggregates run t-tests incorporate into the main figure - change figure 3 A to aggregate counts not biomass - Figure 3B and C remove p aeruginosa from the x axis and put it as a title  also make sure that the axis ticks are accurate and are correctly labeled Figure 4  get rid of fig b,  fix y axis label

@@
   geom_errorbar(data = hist.plank.Agg.Stats%>% filter(Strain == strain),aes(x=Aggregation,ymin=(MeanBiomass-SEBiomass)*100, ymax = (MeanBiomass+SEBiomass)*100, group = ConditionNew),width = 0, size=.5,position = position_dodge(width = .9))+
-  scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)))+
+  scale_y_continuous(expand = expand_scale(mult = c(0, 0.2)))+
   facet_grid(.~Species)+
@@
 
-#get data frequency bins
+#get data frequency bins THIS WAS substituted by counts percentage
 #####
@@
 hist.5.LogBinSummarize$ConditionNew <- factor(hist.5.LogBinSummarize$ConditionNew, levels = c("Mono", "Co"))
+#####
 
-#####
 #t tests frequency bins
@@
 PaCoWtMut100<-t.test(x = PaMutCo100, y = PaWtCo100, paired = F)
-
+#t-tests table
 tTestDatAggSizes<-list(SaWt5,SaWt10,SaMut5,SaMut10,PaWt5,PaWt10,PaMut5,PaMut10,SaWtMut5,SaWtMut10,
@@
 #####
+
 #plot frequency bins
@@
     guides(color = FALSE)+
-    scale_y_continuous(expand = expand_scale(mult = c(0, 0.05)))+
+    scale_y_continuous(expand = expand_scale(mult = c(0, 0.2)))+
     scale_fill_grey(labels = c("Mono-culture", "Co-culture"))+
@@
 #####
+
+#get data frequency bins proportion
+#####
+tESThist.5.LogBinData<-hist.5 %>% filter(!max == 5)%>%  group_by(Sample,Species,Condition,Strain)%>% 
+  mutate(LogBin = case_when(max <= 10 ~ "(5, 10]",
+                            max<= 100    ~ "(10, 100]",
+                            max > 100 ~ paste0("(100, ",bquote("\U221E"), ")")), AggOnlyBiomass = sum(suma), AggOnlyAggregates = sum(frequency)) %>% ungroup()
+
+test1<-tESThist.5.LogBinData%>% 
+  group_by(Species, Sample,Condition,ConditionNew,Strain,LogBin) %>% 
+  summarize(FrequencyLogBin = sum(frequency),DensityLogBin = (FrequencyLogBin)/AggOnlyAggregates) %>%  ungroup() %>%
+  group_by(Species, Condition,ConditionNew,Strain,LogBin) %>%
+mutate(MeanFrequencyLogBin = mean(FrequencyLogBin),SEFrequencyLogBin = std.error(FrequencyLogBin),
+          MeanDensityLogBin = mean(DensityLogBin), SEDensityLogBin = std.error(DensityLogBin))
+
+test1check<-test1 %>% filter(Species == "Sa", ConditionNew == "Mono", Strain == "PA14wt")
+test1check1<-distinct(test1check) %>% group_by(Sample) %>% mutate(suma = sum(DensityLogBin))
+
+test1Unique<-distinct(test1)
+#rows below add 
+new.rowWt.frequency <- data.frame(Species = 'Sa', Condition = "Pa:Sa 1:1",ConditionNew = "Co",Strain = "PA14wt", LogBin =paste0("(100, ",bquote("\U221E"), ")"), MeanDensityLogBin = 0,SEDensityLogBin = 0)
+new.rowMut.frequency <- data.frame(Species = 'Sa', Condition = "Pa:Sa 1:1",ConditionNew = "Co",Strain = "PA14mut", LogBin =paste0("(100, ",bquote("\U221E"), ")"), MeanDensityLogBin = 0,SEDensityLogBin = 0)
+test1Unique<-rbind(test1Unique, new.rowWt.frequency)
+test1Unique<-rbind(test1Unique, new.rowMut.frequency)
+
+test1Unique$LogBin <- factor(test1Unique$LogBin, levels = c("(5, 10]","(10, 100]",paste0("(100, ",bquote("\U221E"), ")")))
+test1Unique$ConditionNew <- factor(test1Unique$ConditionNew, levels = c("Mono", "Co"))
+#####
+
+#t-tests for frequency bins proportion
+#####
+SaWtMono5.proportion<-test1Unique %>%filter(Condition == "Sa Mono", Strain == "PA14wt",LogBin == "(5, 10]") %>% pull(DensityLogBin)
+SaMutMono5.proportion<-test1Unique %>%filter(Condition == "Sa Mono", Strain == "PA14mut",LogBin == "(5, 10]") %>% pull(DensityLogBin)
+SaWtMono10.proportion<-test1Unique %>%filter(Condition == "Sa Mono", Strain == "PA14wt",LogBin == "(10, 100]") %>% pull(DensityLogBin)
+SaMutMono10.proportion<-test1Unique %>%filter(Condition == "Sa Mono", Strain == "PA14mut",LogBin == "(10, 100]") %>% pull(DensityLogBin)
+
+SaWtCo5.proportion<-test1Unique %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14wt",LogBin == "(5, 10]") %>% pull(DensityLogBin)
+SaMutCo5.proportion<-test1Unique %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14mut",LogBin == "(5, 10]") %>% pull(DensityLogBin)
+SaWtCo10.proportion<-test1Unique %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14wt",LogBin == "(10, 100]") %>% pull(DensityLogBin)
+SaMutCo10.proportion<-test1Unique %>%filter(Species =="Sa", ConditionNew == "Co", Strain == "PA14mut",LogBin == "(10, 100]") %>% pull(DensityLogBin)
+SaWtCo100.proportion<-test1Unique %>%filter(Species =="Sa", ConditionNew == "Co", Strain=="PA14wt",LogBin == paste0("(100, ",bquote("\U221E"), ")")) %>% pull(DensityLogBin)
+SaMutCo100.proportion<-test1Unique %>%filter(Species =="Sa", ConditionNew == "Co", Strain=="PA14mut",LogBin == paste0("(100, ",bquote("\U221E"), ")")) %>% pull(DensityLogBin)
+
+PaWtMono5.proportion<-test1Unique %>%filter(Condition == "Pa Mono", Strain == "PA14wt",LogBin == "(5, 10]") %>% pull(DensityLogBin)
+PaMutMono5.proportion<-test1Unique %>%filter(Condition == "Pa Mono", Strain == "PA14mut",LogBin == "(5, 10]") %>% pull(DensityLogBin)
+PaWtMono10.proportion<-test1Unique %>%filter(Condition == "Pa Mono", Strain == "PA14wt",LogBin == "(10, 100]") %>% pull(DensityLogBin)
+PaMutMono10.proportion<-test1Unique %>%filter(Condition == "Pa Mono", Strain == "PA14mut",LogBin == "(10, 100]") %>% pull(DensityLogBin)
+PaWtMono100.proportion<-test1Unique %>%filter(Condition == "Pa Mono", Strain == "PA14wt",LogBin == paste0("(100, ",bquote("\U221E"), ")")) %>% pull(DensityLogBin)
+PaMutMono100.proportion<-test1Unique %>%filter(Condition == "Pa Mono", Strain == "PA14mut",LogBin == paste0("(100, ",bquote("\U221E"), ")")) %>% pull(DensityLogBin)
+
+PaWtCo5.proportion<-test1Unique %>%filter(Species =="Pa", ConditionNew == "Co", Strain == "PA14wt",LogBin == "(5, 10]") %>% pull(DensityLogBin)
+PaMutCo5.proportion<-test1Unique %>%filter(Species =="Pa", ConditionNew == "Co", Strain == "PA14mut",LogBin == "(5, 10]") %>% pull(DensityLogBin)
+PaWtCo10.proportion<-test1Unique %>%filter(Species =="Pa", ConditionNew == "Co", Strain == "PA14wt",LogBin == "(10, 100]") %>% pull(DensityLogBin)
+PaMutCo10.proportion<-test1Unique %>%filter(Species =="Pa", ConditionNew == "Co", Strain == "PA14mut",LogBin == "(10, 100]") %>% pull(DensityLogBin)
+PaWtCo100.proportion<-test1Unique %>%filter(Species =="Pa",ConditionNew=="Co",Strain == "PA14wt",LogBin == paste0("(100, ",bquote("\U221E"), ")")) %>% pull(DensityLogBin)
+PaMutCo100.proportion<-test1Unique %>%filter(Species =="Pa",ConditionNew=="Co",Strain == "PA14mut",LogBin==paste0("(100, ",bquote("\U221E"), ")")) %>% pull(DensityLogBin)
+
+#mono vs Co
+SaWt5.proportion<-t.test(x = SaWtMono5.proportion, y = SaWtCo5.proportion, paired = T)
+SaWt10.proportion<-t.test(x = SaWtMono10.proportion, y = SaWtCo10.proportion, paired = T)
+SaMut5.proportion<-t.test(x = SaMutMono5.proportion, y = SaMutCo5.proportion, paired = T)
+SaMut10.proportion<-t.test(x = SaMutMono10.proportion, y = SaMutCo10.proportion, paired = T)
+
+PaWt5.proportion<-t.test(x = PaWtMono5.proportion, y = PaWtCo5.proportion, paired = T)
+PaWt10.proportion<-t.test(x = PaWtMono10.proportion, y = PaWtCo10.proportion, paired = T)
+#PaWt100<-t.test(x = PaWtMono100, y = PaWtCo100, paired = T)
+PaMut5.proportion<-t.test(x = PaMutMono5.proportion, y = PaMutCo5.proportion, paired = T)
+PaMut10.proportion<-t.test(x = PaMutMono10.proportion, y = PaMutCo10.proportion, paired = T)
+#PaMut100<-t.test(x = PaMutMono100, y = PaMutCo100, paired = T)
+
+#Wt vs pqsL
+SaWtMut5.proportion<-t.test(x = SaMutCo5.proportion, y = SaWtCo5.proportion, paired = F)
+SaWtMut10.proportion<-t.test(x = SaMutCo10.proportion, y = SaWtCo10.proportion, paired = F)
+#SaWtMut100<-t.test(x = SaMutCo100, y = SaWtCo100, paired = F)
+
+PaMonoWtMut5.proportion<-t.test(x = PaMutMono5.proportion, y = PaWtMono5.proportion, paired = F)
+PaMonoWtMut10.proportion<-t.test(x = PaMutMono10.proportion, y = PaWtMono10.proportion, paired = F)
+PaMonoWtMut100.proportion<-t.test(x = PaMutMono100.proportion, y = PaWtMono100.proportion, paired = F)
+
+PaCoWtMut5.proportion<-t.test(x = PaMutCo5.proportion, y = PaWtCo5.proportion, paired = F)
+PaCoWtMut10.proportion<-t.test(x = PaMutCo10.proportion, y = PaWtCo10.proportion, paired = F)
+PaCoWtMut100.proportion<-t.test(x = PaMutCo100.proportion, y = PaWtCo100.proportion, paired = F)
+#t-tests table
+tTestDatAggSizes.proportion<-list(SaWt5.proportion,SaWt10.proportion,SaMut5.proportion,SaMut10.proportion,PaWt5.proportion,PaWt10.proportion,PaMut5.proportion,
+                       PaMut10.proportion,SaWtMut5.proportion,SaWtMut10.proportion,PaMonoWtMut5.proportion,PaMonoWtMut10.proportion,PaMonoWtMut100.proportion,
+                       PaCoWtMut5.proportion,PaCoWtMut10.proportion,PaCoWtMut100.proportion)
+tTestAggSizesTable.proportion<-bind_rows(map(tTestDatAggSizes.proportion, TtestTable))
+
+#####
+
+#plot frequency bins proportion
+test1Unique$Species <- factor(test1Unique$Species, levels = c("Pa", "Sa"),
+                                         labels = c('P. aeruginosa','S. aureus'))
+PlotFreqLogBinProp<-function(strain){
+  df <-test1Unique%>% filter(Strain == strain)
+  ggplot()+
+    geom_col(data = df, aes(x=LogBin,y=MeanDensityLogBin*100,  fill =ConditionNew ),size=4,position = position_dodge( width = .9))+
+    geom_errorbar(data = df,aes(x=LogBin,ymin=(MeanDensityLogBin-SEDensityLogBin)*100, ymax = (MeanDensityLogBin+SEDensityLogBin)*100, group = ConditionNew),width = 0, size= .5,position = position_dodge( width = .9))+
+    facet_grid(.~Species)+
+    labs(fill = "",y = "Aggregates per bin (% of total)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    guides(color = FALSE)+
+    scale_y_continuous(expand = expand_scale(mult = c(0, 0.2)))+
+    scale_fill_grey(labels = c("Mono-culture", "Co-culture"))+
+    theme_half_open()+
+    theme(plot.title = element_text(hjust = 0.5),
+          strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
+          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
+          plot.margin = unit(c(0,.5,0,.5), "cm"),
+          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=11),
+          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,2,2,0),size=11),
+          legend.title = element_text(size=13),legend.text = element_text(size = 11),
+          legend.position = c(0.79, 0.60))
+  }
+figure1F<-PlotFreqLogBinProp("PA14wt")
+figure2F<-PlotFreqLogBinProp("PA14mut")
+
 figure1EF<-plot_grid(figure1E,figure1F,rel_widths = c(1,1.2),align='vh',labels = c("E", "F"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)
 figure2EF<-plot_grid(figure2E,figure2F,rel_widths = c(1,1.2),align='vh',labels = c("E", "F"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)
+
 ```
@@
 plot_grid(plots[[1]],plots[[2]],figure2EF, align='vh',nrow = 3, rel_heights = c(1,1,1.5))
-
 ```
@@
   scale_shape_manual(values = c(1,2),name = "", limits=c("PA14wt","PA14mut"))+
-  scale_x_discrete(breaks=c("PA14wt","PA14mut"), 
-                     labels = c(bquote(paste(italic("P. aeruginosa"), " wt")),bquote(paste(italic(Delta*"pqsL")))))+
+  scale_x_discrete(name =expression(italic("P. aeruginosa")), breaks=c("PA14wt","PA14mut"), 
+                     labels = c("wt",bquote(paste(italic(Delta*"pqsL")))))+
   labs(y = "Mixed aggregates (% frequency)", x = "")+
@@
 
+#the enrichment data is on "propOc Data 3D.Rmd" but I changed the distance for Sa Sa to 1 because this is just the range
+enrichmentDataSpreadsheet<-read.csv("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Prop Oc Final Data/Enrichment distance.csv",header = TRUE)
+enrichmentDataSpreadsheet$Strain<-as.factor(enrichmentDataSpreadsheet$Strain)
+enrichmentDataSpreadsheet$Strain <- factor(enrichmentDataSpreadsheet$Strain, levels = c("wt","mut"))
+
 sa.paPlot<-
   ggplot()+
-  geom_point(data = enrichmentDataFinal %>% filter(Relation == "Sa->Pa"),aes(y=meanEnrichment, x = Strain),size=4, shape = 1)+
-  geom_errorbar(data = enrichmentDataFinal %>% filter(Relation == "Sa->Pa"),
+  geom_point(data = enrichmentDataSpreadsheet %>% filter(Relation == "Sa->Pa"),aes(y=meanEnrichment, x = Strain),size=4, shape = 1)+
+  geom_errorbar(data = enrichmentDataSpreadsheet %>% filter(Relation == "Sa->Pa"),
                 aes(ymin = meanEnrichment-sdEnrichment,ymax = meanEnrichment+sdEnrichment, x = Strain),size=.2, width = 0)+
   #labs( y = bquote(paste("Enrichment distance\n", italic("S. aureus") %->% italic("P. aeruginosa "),"("*mu*"m)")), x = "" ) +
-  labs(y = expression(atop("Enrichment distance ",paste(italic("S. aureus") %->% italic("P. aeruginosa "),"("*mu*"m)"))), x = "" ) +
+  labs(y = expression(atop("Enrichment distance ",paste(italic("S. aureus") %->% italic("P. aeruginosa "),"("*mu*"m)")))) +
   scale_shape_manual(values = c(1,2),name = "", limits=c("wt","mut"),
@@
                                 bquote(paste(italic('P. aeruginosa '), Delta*"pqsL"))))+
-  scale_x_discrete(name ="", breaks = c("wt","mut"), 
-                   labels = c(bquote(paste(italic("P. aeruginosa"), " wt")), bquote(paste(italic(Delta*"pqsL")))))+
-  ylim(1, 9)+
+  scale_x_discrete(name =expression(italic("P. aeruginosa")), breaks = c("wt","mut"), 
+                   labels = c("wt", bquote(paste(italic(Delta*"pqsL")))))+
+  ylim(0, 10)+
   theme_cowplot()+
@@
   ggplot()+
-  geom_point(data = enrichmentDataFinal %>% filter(Relation == "Sa->Sa"),aes(y=meanEnrichment, x = Strain),size=4, shape = 1)+
-  geom_errorbar(data = enrichmentDataFinal %>% filter(Relation == "Sa->Sa"),
+  geom_point(data = enrichmentDataSpreadsheet %>% filter(Relation == "Sa->Sa"),aes(y=meanEnrichment, x = Strain),size=4, shape = 1)+
+  geom_errorbar(data = enrichmentDataSpreadsheet %>% filter(Relation == "Sa->Sa"),
                 aes(ymin = meanEnrichment-sdEnrichment,ymax = meanEnrichment+sdEnrichment, x = Strain),size=.2, width = 0)+
@@
 
-figure7 <- plot_grid(MixedAggregateBiomassPlot,sa.saPlot,sa.paPlot,align='vh',labels = c("A","B", "C"),hjust = -1,nrow = 1)
+figure7 <- plot_grid(MixedAggregateFrequencyPlot,sa.saPlot,sa.paPlot,align='vh',labels = c("A","B", "C"),hjust = -1,nrow = 1)
 figure7
@@
                               expression(atop(italic("S. aureus +"), paste(italic("P. aeruginosa "*Delta*"pqsL"))))))+
-  labs(y = expression(paste(italic("S. aureus "), "CFU (",Log[10]),")"), x = "", fill = "") +
+  labs(y = expression(paste(italic("S. aureus ("), Log[10]," CFU)")), x = "", fill = "") +
   scale_fill_grey()+

### 2020-09-04 Paper Figures/Paper figures Scipts.Rmd
changed figure 1 and 2 by removing luminescence data panel

@@
 
-    legend <- get_legend(shakingWtPlot + theme(legend.box.margin = margin(0, 0, 0, 10)))
+    legend <- get_legend(shakingWtPlot + theme(legend.box.margin = margin(0, 0, 0, 0)))
     prow <- plot_grid(shakingWtPlot+theme(legend.position="none"),staticWtPlot+theme(legend.position="none"),
@@
 figure2AB<-GraphGrowthCurveLog1("mut")
-
 ```
@@
 luminescenceData <-read.csv(luminescenceFile) 
-luminescenceData<-luminescenceData %>% group_by(TimePoint, BioReplicate, Condition, Strain) %>% mutate(techMean = mean(Luminescence)) %>% ungroup() %>% group_by(TimePoint, Condition, Strain) %>% mutate(Mean = mean(techMean), SE =std.error(techMean)) %>% ungroup()
-#luminescenceData1<-luminescenceData %>%  
-#mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))#this adds up all the data on each slice and then gets the log of that total
-
+luminescenceData<-luminescenceData %>% group_by(TimePoint, Condition, Strain) %>% mutate(Mean = mean(Luminescence), SE =std.error(Luminescence)) %>% ungroup()
+write.csv(luminescenceData1, "/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Staph killing assays/summary2.csv")
 luminescenceData1<-luminescenceData %>% mutate(
@@
     Condition == "static" & Strain == "wt"~ "wtStat"))
+luminescenceData1<-luminescenceData1 %>%  mutate(LogTotals = ifelse(Luminescence>0, log10(Luminescence), 0), rep = (4*(TechReplicate-1))+BioReplicate)#this adds up all the data on each slice and then gets the log of that total
 #####
@@
 #####
-wtStatLuminescence<-luminescenceData1 %>% filter (CondStrain == "wtStat") %>% filter (TimePoint<7 &TechReplicate == 1)  %>% pull(techMean)
-wtMixedLuminescence<-luminescenceData1 %>% filter (CondStrain == "wtShake") %>% filter (TimePoint<7 &TechReplicate == 1) %>% pull(techMean)
+wtStatLuminescence<-luminescenceData1 %>% filter (CondStrain == "wtStat") %>% filter (TimePoint==10 &TechReplicate == 1)  %>% pull(LogTotals) 
+wtMixedLuminescence<-luminescenceData1 %>% filter (CondStrain == "wtShake") %>% filter (TimePoint==10 &TechReplicate == 1) %>% pull(LogTotals)
 
-mutStatLuminescence<-luminescenceData1 %>% filter (CondStrain == "pqsLStat") %>% filter (TimePoint<7 &TechReplicate == 1)%>% pull(techMean)
-mutMixedLuminescence<-luminescenceData1 %>% filter (CondStrain == "pqsLShake") %>% filter (TimePoint<7 &TechReplicate == 1)%>% pull(techMean)
+mutStatLuminescence<-luminescenceData1 %>% filter (CondStrain == "pqsLStat") %>% filter (TimePoint==10 &TechReplicate == 1)%>% pull(LogTotals)
+mutMixedLuminescence<-luminescenceData1 %>% filter (CondStrain == "pqsLShake") %>% filter (TimePoint==10 &TechReplicate == 1)%>% pull(LogTotals)
 
@@
 tTestLuminescenceTable<-bind_rows(map(tTestDataLuminescence, TtestTable))
+#this is only comparing the last time point of the log transformed data
+
+timePoints<-seq(1,10)
+
+DoLm<-function(condstrain, bio){
+  rep1Data<-luminescenceData1 %>% filter (CondStrain == condstrain, rep == bio) %>% filter(TimePoint > 1) %>% filter(TimePoint<8)
+  #rep1Data<-luminescenceData1 %>% filter (CondStrain == condstrain, rep == bio) %>% filter(TimePoint<7) 
+  timePoints<-unique(rep1Data$TimePoint)
+  rep1lm<- lm(rep1Data$LogTotals ~ timePoints)
+  return(as.numeric(rep1lm$coefficients[[2]]))}
+
+wtStatLuminescenceSlope<- unlist(map2("wtStat", seq(1,8), DoLm))
+wtMixedLuminescenceSlope<- unlist(map2("wtShake", seq(1,8), DoLm))
+mutStatLuminescenceSlope<- unlist(map2("pqsLStat", seq(1,8), DoLm))
+mutMixedLuminescenceSlope<- unlist(map2("pqsLShake", seq(1,8), DoLm))
+#Anova
+blah<-combine(wtStatLuminescenceSlope,wtMixedLuminescenceSlope,mutStatLuminescenceSlope,mutMixedLuminescenceSlope)
+res.aov <- aov(data ~ source, data = blah)
+# Summary of the analysis
+summary(res.aov)
+TukeyHSD(res.aov)
+
+#t-tests
+tTestWtLuminescenceSlope<-t.test(x = wtStatLuminescenceSlope, y = wtMixedLuminescenceSlope, paired = T)
+tTestMutLuminescenceSlope<-t.test(x = mutStatLuminescenceSlope, y = mutMixedLuminescenceSlope, paired = T)
+
+tTestStatLuminescenceSlope<-t.test(x = wtStatLuminescenceSlope, y = mutStatLuminescenceSlope, paired = T)
+tTestMixedLuminescenceSlope<-t.test(x = wtMixedLuminescenceSlope, y = mutMixedLuminescenceSlope, paired = T)
+
+tTestWtStatVSMutMixedLuminescenceSlope<-t.test(x = wtStatLuminescenceSlope, y = mutMixedLuminescenceSlope, paired = T)
+tTestMutStatVSWtMixedLuminescenceSlope<-t.test(x = wtMixedLuminescenceSlope, y = mutStatLuminescenceSlope, paired = T)
+
+tTestDataLuminescenceSlope<-list(tTestWtLuminescenceSlope,tTestMutLuminescenceSlope,tTestStatLuminescenceSlope,tTestMixedLuminescenceSlope,
+                            tTestWtStatVSMutMixedLuminescenceSlope,tTestMutStatVSWtMixedLuminescenceSlope)
+
+tTestLuminescenceTableLast<-bind_rows(map(tTestDataLuminescenceSlope, TtestTable))
+
+tTestLuminescenceTableLast
 #####
@@
       geom_errorbar(data=diskDataStats1 %>% filter (strain == Strain1), aes(x = condition, ymin = meanBio - SDBio, ymax = meanBio + SDBio),width = 0)+
-      geom_point(data=diskDataStats1 %>% filter (strain == Strain1), aes(x=condition, y=meanBio, shape =condition), size=3)+
-      scale_shape_manual(values = c(1,2),limits=c("shaking","static"), 
-                     labels = c(bquote(paste(italic('P. aeruginosa'), " mixed")),
-                                bquote(paste(italic('P. aeruginosa'), " static"))))+
+      geom_point(data=diskDataStats1 %>% filter (strain == Strain1), aes(x=condition, y=meanBio), size=3)+
+      #scale_shape_manual(values = c(1,2),limits=c("shaking","static"), labels = c(bquote(paste(italic('P. aeruginosa'), " mixed")),bquote(paste(italic('P. aeruginosa'), " static"))))+
   #scale_shape_manual(values = c(16,17),limits=c("static", "shaking"), 
@@
       #                          bquote(paste(italic('P. aeruginosa '), Delta*"pqsL mixed"))))+
-      scale_x_discrete(name ="", breaks = c("static","shaking"), labels =c("Static","Mixed"))+
-    ylim(0,17.5)+
+      scale_x_discrete(name =expression(paste(italic('P. aeruginosa'), 'culture')), breaks = c("static","shaking"), labels =c("Static","Mixed"))+
+    ylim(0,15.1)+
   labs( y = "Zone of inhibition (mm)", shape = "") +
       theme_cowplot(12)+
-  theme(plot.margin = unit(c(.5,0,0,.3), "cm"),
+
+  theme(plot.margin = unit(c(.5,.5,0,.5), "cm"),
         axis.text.x  = element_text(margin = margin(0,0,0,0),size=13),
-        axis.title.y = element_text(margin = margin(0,0,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11),
+        axis.title.y = element_text(margin = margin(0,0,0,0),size=13),
+        axis.text.y = element_text(margin = margin(0,0,2,0),size=11),
         legend.title = element_text(size=13),legend.text = element_text(size = 11))
+        #legend.position = c(0.79, 0.60))
 
@@
       geom_errorbar(data=luminescenceData1%>% filter (Strain == Strain2) %>% filter (TimePoint<7), aes(x=TimePoint, ymin=Mean-SE,ymax=Mean+SE), width = 0)+
-      scale_y_log10(name=expression(paste(italic('S. aureus'), " luminescence (%)" )), limits = c(1,121),labels = c(1, 10, 100),breaks = c(1, 10, 100))+
+      scale_y_log10(name=expression(paste(italic('S. aureus'), " luminescence (%)" )), limits = c(.1,121),labels = c(0.1,1, 10, 100),breaks = c(0.1,1, 10, 100))+
       labs( x = "Time (minutes)",shape = "") +
@@
 
-legendFigure1C <- get_legend(figure1C + theme(legend.box.margin = margin(0, 0, 0, 10)))
-plotsFigure1cd <- plot_grid(figure1C+theme(legend.position="none"),figure1D+theme(legend.position="none"),
-                      align='vh',labels = c("C", "D"),hjust = -1,nrow = 1,label_size= 20)
-plot_grid(plotsFigure1cd,legendFigure1C,rel_widths = c(3, .6))
+legendFigure1C <- get_legend(figure1C + theme(legend.box.margin = margin(0, 0, 0, 0)))
+#plotsFigure1cd <- plot_grid(figure1C+theme(legend.position="none"),figure1D+theme(legend.position="none"), align='vh',labels = c("C", "D"),hjust = -1,nrow = 1,label_size= 20)
+##plotsFigure1c <- plot_grid(figure1C+theme(legend.position="none"),legendFigure1C, align='vh',labels = c("C"),rel_widths = c(1,.7),hjust = -1,nrow = 1,label_size= 20,label_x = 0, label_y = 1)
+plotsFigure1c <- plot_grid(figure1C+theme(legend.position="none"),align='vh',labels = c("C"),hjust = -1,nrow = 1,label_size= 20,
+                           label_x = 0, label_y = 1)
+#plot_grid(plotsFigure1cd,legendFigure1C,rel_widths = c(1,.1))
 }   
@@
 test1Unique$LogBin <- factor(test1Unique$LogBin, levels = c("(5, 10]","(10, 100]",paste0("(100, ",bquote("\U221E"), ")")))
-test1Unique$ConditionNew <- factor(test1Unique$ConditionNew, levels = c("Mono", "Co"))
+
 #####
@@
 #plot frequency bins proportion
-test1Unique$Species <- factor(test1Unique$Species, levels = c("Pa", "Sa"),
-                                         labels = c('P. aeruginosa','S. aureus'))
+test1Unique$Species <- factor(test1Unique$Species, levels = c("Pa", "Sa"),labels = c('P. aeruginosa','S. aureus'))
+test1Unique$ConditionNew <- factor(test1Unique$ConditionNew, levels = c("Mono", "Co"))
 PlotFreqLogBinProp<-function(strain){
@@
 
-figure1EF<-plot_grid(figure1E,figure1F,rel_widths = c(1,1.2),align='vh',labels = c("E", "F"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)
-figure2EF<-plot_grid(figure2E,figure2F,rel_widths = c(1,1.2),align='vh',labels = c("E", "F"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)
+figure1EF<-plot_grid(figure1E,figure1F,rel_widths = c(1,1.2),align='vh',labels = c("D", "E"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)
+figure2EF<-plot_grid(figure2E,figure2F,rel_widths = c(1,1.2),align='vh',labels = c("D", "E"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)
 
@@
 ```{Make full figures 1 and 2}
-plots <- align_plots(figure1AB, figure1CD,align = 'vh', axis = 'l')
-plot_grid(plots[[1]],plots[[2]],figure1EF, align='vh',nrow = 3, rel_heights = c(1,1,1.5))
+top_Row1<-plot_grid(figure1AB,figure1CD,align='vh',nrow = 1, rel_widths = c(2,1))
+plot_grid(top_Row1,figure1EF, align='v',nrow = 2, rel_heights = c(1,1.5))
 
-plots <- align_plots(figure2AB, figure2CD,align = 'vh', axis = 'l')
-plot_grid(plots[[1]],plots[[2]],figure2EF, align='vh',nrow = 3, rel_heights = c(1,1,1.5))
+top_Row2<-plot_grid(figure2AB,figure2CD,align='vh',nrow = 1, rel_widths = c(2,1))
+plot_grid(top_Row2,figure2EF, align='v',nrow = 2, rel_heights = c(1,1.5))
+
 ```
@@
   #labs( y = bquote(paste("Enrichment distance\n", italic("S. aureus") %->% italic("P. aeruginosa "),"("*mu*"m)")), x = "" ) +
-  labs(y = expression(atop("Enrichment distance ",paste(italic("S. aureus") %->% italic("P. aeruginosa "),"("*mu*"m)")))) +
+  labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("S. aureus") %->% italic("P. aeruginosa "))))) +
   scale_shape_manual(values = c(1,2),name = "", limits=c("wt","mut"),
@@
                 aes(ymin = meanEnrichment-sdEnrichment,ymax = meanEnrichment+sdEnrichment, x = Strain),size=.2, width = 0)+
-  labs(y = expression(atop("Enrichment distance ",paste(italic("S. aureus") %->% italic("S. aureus "),"("*mu*"m)"))), x = "" ) +
+  labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("S. aureus") %->% italic("S. aureus ")))), x = "" ) +
   scale_shape_manual(values = c(1,2),name = "", limits=c("wt","mut"),labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type")),

### 2021-02-11 Paper Figures/Paper figures Scipts.Rmd
making figures for paper

@@
 }
-
+TtestTable<-name <- function(dataPoint) {
+  data <-data.frame(dataPoint$data.name, dataPoint$p.value)
+}
 PA14 = c('2-11-19','2-7-19','2-5-19')
@@
       theme_cowplot(12)+
-      theme(plot.margin = unit(c(.5,0,0,.5), "cm"),
+      theme(plot.margin = unit(c(.5,1,0,.5), "cm"),
             axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,2,0),size=11),
@@
       geom_hline(yintercept=9.07, color='red', linetype = "solid") +
+      scale_linetype_manual(values = c( "solid","dashed"), labels = c(etiqueta,bquote(paste(italic('S. aureus')))))+
       labs(x = "Time (hours)", y = expression(paste(Log[10], " CFU")), linetype = "")+
@@
       theme_cowplot(12)+
-      theme(plot.margin = unit(c(.5,0,0,0), "cm"),
-            axis.title.x = element_text(margin = margin(0,0,0,0),size=13 ),axis.text.x = element_text(margin = margin(1,0,2,0),size=11),
+      theme(plot.margin = unit(c(.5,.5,0,1), "cm"),
+            axis.title.x = element_text(margin = margin(0,0,0,0),size=13 ),axis.text.x = element_text(margin = margin(1,0,2,0),size=11),#this is  for the x-axis text: "Time (hours)"
             axis.title.y = element_text(margin = margin(0,0,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,0,0),size=11))
 
-    legend <- get_legend(shakingWtPlot + theme(legend.box.margin = margin(0, 0, 0, 0)))
-    prow <- plot_grid(shakingWtPlot+theme(legend.position="none"),staticWtPlot+theme(legend.position="none"),
+    #legend <- get_legend(shakingWtPlot + theme(legend.box.margin = margin(0, 0, 0, 0)))
+    plot_grid(shakingWtPlot+theme(legend.position=c(.6,.4)),staticWtPlot+theme(legend.position=c(.6,.4)),
                       align='v',labels = c("A", "B"),nrow = 1,label_size= 20, label_x = .02, label_y = 1)
-    plot_grid(prow,legend,rel_widths = c(3,.6))
+    #plot_grid(prow,legend,rel_widths = c())
+    #legend positions for wt are .7,.6, for mutant is .6, .4
     }
-
 #Graph logs
@@
 #####
+#This is the data for normalizing the data with the yields
+paYields<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/pqsL SCFM2/Pa growth yields 16 hrs/Pa growth yields 16 hrs.csv',header=T)
+paYieldsSummary<-paYields %>% group_by(condition, strain, bio.rep) %>% summarise(CFUs = mean(bugs)) %>% ungroup()
+
+paYieldsSummaryFinal<-paYieldsSummary%>% group_by(condition, strain) %>% summarise(CFU = mean(CFUs)) %>%
+  mutate(CondStrain = case_when(
+    condition == "shaking" & strain == "pqsL" ~ "pqsLShake",
+    condition == "shaking" & strain == "wt"~ "wtShake",
+    condition == "static" & strain == "pqsL"~ "pqsLStat",
+    condition == "static" & strain == "wt"~ "wtStat")) %>% ungroup()%>% 
+  mutate(logCFU = log10(CFU)) %>% mutate(normalization = CFU/CFU[CondStrain=="wtShake"])#normalized it to wt shaking
+
 diskFile<-"~/Documents/Whiteley/PROJECTS/PaSaProject/Staph killing assays/disk difussion assays.csv"
@@
 diskData$strain <- factor(diskData$strain, levels = c("wt", "pqsl"))
-diskData <- diskData %>% mutate(val1 = value1-6,val2 = value2-6,average = (val1+val2)/2 )#this removes the diameter of the disks
-diskDataStats<-diskData %>% group_by(strain, condition, bio.rep) %>% summarise(meanTech = mean(average)) %>% ungroup() %>%group_by(strain, condition) %>% summarise(meanBio = mean(meanTech), SDBio = std.error(meanTech))
-diskDataStats$strain <- factor(diskDataStats$strain, levels = c("wt", "pqsl"))
-diskDataStats1<-diskDataStats %>% mutate(
+
+#to normalize this I am going to have to change the way this works, diameter is the value measure and the disk is 6 in diameter
+diskData <- diskData %>% mutate(radius1 = value1/2,radius2 = value2/2,meanRadii = (val1+val2)/2 ) %>% mutate(area = pi*(meanRadii^2))#this removes the diameter of the disks
+diskData1<-diskData %>% mutate(
   CondStrain = case_when(
@@
     condition == "static" & strain == "wt"~ "wtStat"))
+
+#normalized counts
+normInhibition<-merge(paYieldsSummaryFinal, diskData1, by= "CondStrain") %>% mutate(normInhibit = area/normalization)
+diskDataStats<-normInhibition %>% group_by(strain.x, condition.x,CondStrain, bio.rep) %>% summarise(meanTech = mean(area)) %>% ungroup() %>%group_by(strain.x, condition.x) %>% summarise(meanBio = mean(meanTech), SDBio = std.error(meanTech))
+diskDataStats$strain <- factor(diskDataStats$strain.x, levels = c("wt", "pqsl"))
+write.csv(normInhibition, "~/Documents/Whiteley/PROJECTS/PaSaProject/Staph killing assays/normalized disk difussion assays.csv")
 #####
@@
 #####
-diskWtShaking<-diskData %>% filter(strain == "wt" & condition == "shaking")
-diskMutShaking<-diskData %>% filter(strain == "pqsl" & condition == "shaking")
-diskWtStatic<-diskData %>% filter(strain == "wt" & condition == "static")
-diskMutStatic<-diskData %>% filter(strain == "pqsl" & condition == "static")
+diskWtShaking<-normInhibition %>% filter(strain.x == "wt" & condition.x == "shaking")
+diskMutShaking<-normInhibition %>% filter(strain.x == "pqsL" & condition.x == "shaking")
+diskWtStatic<-normInhibition %>% filter(strain.x == "wt" & condition.x == "static")
+diskMutStatic<-normInhibition %>% filter(strain.x == "pqsL" & condition.x == "static")
 
 #there is no rep 1 for mutant strain, so remove first one from wt to make paired t-test
-diskWtStatic1<-diskData %>% filter(strain == "wt" & condition == "static") %>% filter(!bio.rep==1)
-diskWtShaking1<-diskData %>% filter(strain == "wt" & condition == "shaking")%>% filter(!bio.rep==1)
+diskWtStatic1<-normInhibition %>% filter(strain.x == "wt" & condition.x == "static") %>% filter(!bio.rep==1)
+diskWtShaking1<-normInhibition %>% filter(strain.x == "wt" & condition.x == "shaking")%>% filter(!bio.rep==1)
 
 #t-tests
-diskWtTtest<-t.test(x = diskWtShaking$avg, y = diskWtStatic$avg, paired = T)
-diskMutTtest<-t.test(x = diskMutShaking$avg, y = diskMutStatic$avg, paired = T)
-diskShakingTtest<-t.test(x = diskWtShaking1$avg, y = diskMutShaking$avg, paired = T)
-diskStaticTtest<-t.test(x = diskMutStatic$avg, y = diskWtStatic1$avg, paired = T)
-diskWtStaticMutShakingTtest<-t.test(x = diskMutShaking$avg, y = diskWtStatic1$avg, paired = T)
-diskMutStaticWtShakingTtest<-t.test(x = diskWtShaking1$avg, y = diskMutStatic$avg, paired = T)
+diskWtTtest<-t.test(x = diskWtShaking$area, y = diskWtStatic$area, paired = T)
+diskMutTtest<-t.test(x = diskMutShaking$area, y = diskMutStatic$area, paired = T)
+diskShakingTtest<-t.test(x = diskWtShaking1$area, y = diskMutShaking$area, paired = T)
+diskStaticTtest<-t.test(x = diskMutStatic$area, y = diskWtStatic1$area, paired = T)
+diskWtStaticMutShakingTtest<-t.test(x = diskMutShaking$area, y = diskWtStatic1$area, paired = T)
+diskMutStaticWtShakingTtest<-t.test(x = diskWtShaking1$area, y = diskMutStatic$area, paired = T)
 tTestDataDiskDifussion<-list(diskWtTtest, diskMutTtest,diskShakingTtest, diskStaticTtest, diskWtStaticMutShakingTtest,diskMutStaticWtShakingTtest)
@@
                             tTestWtStatVSMutMixedLuminescence,tTestMutStatVSWtMixedLuminescence)
-TtestTable<-name <- function(dataPoint) {
-  data <-data.frame(dataPoint$data.name, dataPoint$p.value)
-}
+
 tTestLuminescenceTable<-bind_rows(map(tTestDataLuminescence, TtestTable))
@@
 #####
-GraphStaphKilling<-function(Strain1,Strain2){ 
+GraphStaphKilling<-function(Strain){ 
 figure1C<-ggplot()+
-      geom_errorbar(data=diskDataStats1 %>% filter (strain == Strain1), aes(x = condition, ymin = meanBio - SDBio, ymax = meanBio + SDBio),width = 0)+
-      geom_point(data=diskDataStats1 %>% filter (strain == Strain1), aes(x=condition, y=meanBio), size=3)+
-      #scale_shape_manual(values = c(1,2),limits=c("shaking","static"), labels = c(bquote(paste(italic('P. aeruginosa'), " mixed")),bquote(paste(italic('P. aeruginosa'), " static"))))+
-  #scale_shape_manual(values = c(16,17),limits=c("static", "shaking"), 
-      #               labels = c(bquote(paste(italic('P. aeruginosa '), Delta*"pqsL static")),
-      #                          bquote(paste(italic('P. aeruginosa '), Delta*"pqsL mixed"))))+
-      scale_x_discrete(name =expression(paste(italic('P. aeruginosa'), 'culture')), breaks = c("static","shaking"), labels =c("Static","Mixed"))+
-    ylim(0,15.1)+
-  labs( y = "Zone of inhibition (mm)", shape = "") +
+      geom_errorbar(data=diskDataStats %>% filter (strain.x == Strain), aes(x = condition.x, ymin = meanBio - SDBio, ymax = meanBio + SDBio),width = 0)+
+      geom_point(data=diskDataStats %>% filter (strain.x == Strain), aes(x=condition.x, y=meanBio), size=3)+
+      scale_x_discrete(name =expression(paste(italic('P. aeruginosa'), ' culture')), breaks = c("static","shaking"), labels =c("Static","Mixed"))+
+    ylim(0,450)+
+  labs( y = bquote('Zone of inhibition ('*mm^2*")"), shape = "") +
+
       theme_cowplot(12)+
 
-  theme(plot.margin = unit(c(.5,.5,0,.5), "cm"),
+  theme(plot.margin = unit(c(.5,.5,0,1), "cm"),
         axis.text.x  = element_text(margin = margin(0,0,0,0),size=13),
@@
         #legend.position = c(0.79, 0.60))
+legendFigure1C <- get_legend(figure1C + theme(legend.box.margin = margin(0, 0, 0, 0)))
 
-figure1D<-ggplot()+
-      geom_line(data=luminescenceData1 %>% filter (Strain == Strain2) %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, group = Condition), size=.5, show.legend = FALSE)+
-      geom_point(data=luminescenceData1%>% filter (Strain == Strain2) %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, shape = Condition), size=3)+
-      geom_errorbar(data=luminescenceData1%>% filter (Strain == Strain2) %>% filter (TimePoint<7), aes(x=TimePoint, ymin=Mean-SE,ymax=Mean+SE), width = 0)+
-      scale_y_log10(name=expression(paste(italic('S. aureus'), " luminescence (%)" )), limits = c(.1,121),labels = c(0.1,1, 10, 100),breaks = c(0.1,1, 10, 100))+
-      labs( x = "Time (minutes)",shape = "") +
-      scale_shape_manual(values = c(1,2),limits=c("shaking","static"))+
-      theme_cowplot(12)+
-      theme(legend.position="top",plot.margin = unit(c(0,0,0,0), "cm"),
-            axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=11),
-            axis.title.y = element_text(margin = margin(0,0,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
-
-legendFigure1C <- get_legend(figure1C + theme(legend.box.margin = margin(0, 0, 0, 0)))
-#plotsFigure1cd <- plot_grid(figure1C+theme(legend.position="none"),figure1D+theme(legend.position="none"), align='vh',labels = c("C", "D"),hjust = -1,nrow = 1,label_size= 20)
-##plotsFigure1c <- plot_grid(figure1C+theme(legend.position="none"),legendFigure1C, align='vh',labels = c("C"),rel_widths = c(1,.7),hjust = -1,nrow = 1,label_size= 20,label_x = 0, label_y = 1)
 plotsFigure1c <- plot_grid(figure1C+theme(legend.position="none"),align='vh',labels = c("C"),hjust = -1,nrow = 1,label_size= 20,
@@
 }
-figure1CD<-GraphStaphKilling("wt","wt")
-figure2CD<-GraphStaphKilling("pqsl", "pqsL")
+
+figure1CD<-GraphStaphKilling("wt")
+figure2CD<-GraphStaphKilling("pqsL")
 #####
+ggplot()+
+  geom_errorbar(data=diskDataStats %>% filter (strain.x == "wt"), aes(x = condition.x, ymin = meanBio - SDBio, ymax = meanBio + SDBio),width = 0)+
+  geom_point(data=diskDataStats %>% filter (strain.x == "wt"), aes(x=condition.x, y=meanBio), size=3)
+
 ```
@@
 hist.plank.Agg.Stats<-hist.plank.Agg.Sumary %>% group_by(Species,Condition, ConditionNew,Strain,Aggregation) %>% 
-  summarise(MeanFreq = mean(FrequencyAggregation), SEFreq = std.error(FrequencyAggregation), MeanBiomass = mean(BiomassAggregation), SEBiomass = std.error(BiomassAggregation),MeanDensity = mean(DensityAggregation), SEDensity = std.error(DensityAggregation) )
+  mutate(MeanFreq = mean(FrequencyAggregation), SDFreq = sd(FrequencyAggregation), MeanBiomass = mean(BiomassAggregation), SDBiomass = sd(BiomassAggregation),MeanDensity = mean(DensityAggregation), SDDensity = sd(DensityAggregation) )
 hist.plank.Agg.Stats$Species <- factor(hist.plank.Agg.Stats$Species, levels = c("Pa", "Sa"),
@@
            size=3,position = position_dodge( width = .9),show.legend = FALSE)+
-  geom_errorbar(data = hist.plank.Agg.Stats%>% filter(Strain == strain),aes(x=Aggregation,ymin=(MeanBiomass-SEBiomass)*100, ymax = (MeanBiomass+SEBiomass)*100, group = ConditionNew),width = 0, size=.5,position = position_dodge(width = .9))+
-  scale_y_continuous(expand = expand_scale(mult = c(0, 0.2)))+
+  #geom_point(data = hist.plank.Agg.Stats %>% filter(Strain == strain),aes(x=Aggregation,y=BiomassAggregation*100, group = ConditionNew),           shape = 1,size=2,position = position_dodge( width = .9),show.legend = FALSE)+
+  geom_errorbar(data = hist.plank.Agg.Stats%>% filter(Strain == strain),aes(x=Aggregation,ymin=(MeanBiomass-SDBiomass)*100, ymax = (MeanBiomass+SDBiomass)*100, group = ConditionNew),width = 0, size=.5,position = position_dodge(width = .9))+
+  scale_y_continuous(limits = c(0,103),expand = expand_scale(mult = c(0, 0)))+
   facet_grid(.~Species)+
@@
   group_by(Species, Condition,ConditionNew,Strain,LogBin) %>%
-mutate(MeanFrequencyLogBin = mean(FrequencyLogBin),SEFrequencyLogBin = std.error(FrequencyLogBin),
-          MeanDensityLogBin = mean(DensityLogBin), SEDensityLogBin = std.error(DensityLogBin))
+mutate(MeanFrequencyLogBin = mean(FrequencyLogBin),SDFrequencyLogBin = sd(FrequencyLogBin),
+          MeanDensityLogBin = mean(DensityLogBin), SDDensityLogBin = sd(DensityLogBin))
 
@@
 #rows below add 
-new.rowWt.frequency <- data.frame(Species = 'Sa', Condition = "Pa:Sa 1:1",ConditionNew = "Co",Strain = "PA14wt", LogBin =paste0("(100, ",bquote("\U221E"), ")"), MeanDensityLogBin = 0,SEDensityLogBin = 0)
-new.rowMut.frequency <- data.frame(Species = 'Sa', Condition = "Pa:Sa 1:1",ConditionNew = "Co",Strain = "PA14mut", LogBin =paste0("(100, ",bquote("\U221E"), ")"), MeanDensityLogBin = 0,SEDensityLogBin = 0)
+new.rowWt.frequency <- data.frame(Species = 'Sa', Condition = "Pa:Sa 1:1",ConditionNew = "Co",Strain = "PA14wt", LogBin =paste0("(100, ",bquote("\U221E"), ")"), MeanDensityLogBin = 0,SDDensityLogBin = 0)
+new.rowMut.frequency <- data.frame(Species = 'Sa', Condition = "Pa:Sa 1:1",ConditionNew = "Co",Strain = "PA14mut", LogBin =paste0("(100, ",bquote("\U221E"), ")"), MeanDensityLogBin = 0,SDDensityLogBin = 0)
 test1Unique<-rbind(test1Unique, new.rowWt.frequency)
@@
     geom_col(data = df, aes(x=LogBin,y=MeanDensityLogBin*100,  fill =ConditionNew ),size=4,position = position_dodge( width = .9))+
-    geom_errorbar(data = df,aes(x=LogBin,ymin=(MeanDensityLogBin-SEDensityLogBin)*100, ymax = (MeanDensityLogBin+SEDensityLogBin)*100, group = ConditionNew),width = 0, size= .5,position = position_dodge( width = .9))+
+    #geom_jitter(data = df, aes(x=LogBin,y=DensityLogBin*100, group = ConditionNew),shape = 1,size=2,position = position_dodge( width = .9))+
+    geom_errorbar(data = df,aes(x=LogBin,ymin=(MeanDensityLogBin-SDDensityLogBin)*100, ymax = (MeanDensityLogBin+SDDensityLogBin)*100, group = ConditionNew),width = 0, size= .5,position = position_dodge( width = .9))+
     facet_grid(.~Species)+
@@
     guides(color = FALSE)+
-    scale_y_continuous(expand = expand_scale(mult = c(0, 0.2)))+
+    scale_y_continuous(limits = c(0,100), expand = expand_scale(mult = c(0, 0)))+
     scale_fill_grey(labels = c("Mono-culture", "Co-culture"))+
@@
 figure2EF<-plot_grid(figure2E,figure2F,rel_widths = c(1,1.2),align='vh',labels = c("D", "E"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)
-
 ```
@@
 ```{Make full figures 1 and 2}
-top_Row1<-plot_grid(figure1AB,figure1CD,align='vh',nrow = 1, rel_widths = c(2,1))
+top_Row1<-plot_grid(figure1AB,figure1CD,align='vh',nrow = 1, rel_widths = c(2.5,1))
 plot_grid(top_Row1,figure1EF, align='v',nrow = 2, rel_heights = c(1,1.5))
+ggsave2("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/GrowthCurves/Figure 2.tiff",
+        plot = ggplot2::last_plot(), scale = 1,width = 12,height = 7.7,units = "in", dpi = 1200,limitsize = TRUE)
 
-top_Row2<-plot_grid(figure2AB,figure2CD,align='vh',nrow = 1, rel_widths = c(2,1))
+top_Row2<-plot_grid(figure2AB,figure2CD,align='vh',nrow = 1, rel_widths = c(2.5,1))
 plot_grid(top_Row2,figure2EF, align='v',nrow = 2, rel_heights = c(1,1.5))
-
 ```
-```{r figure 3}
+```{r figure 4}
 MixedAggregateBiomassPlot<-ggplot()+
@@
 
-figure7 <- plot_grid(MixedAggregateFrequencyPlot,sa.saPlot,sa.paPlot,align='vh',labels = c("A","B", "C"),hjust = -1,nrow = 1)
-figure7
+figure4 <- plot_grid(MixedAggregateFrequencyPlot,sa.saPlot,sa.paPlot,align='vh',labels = c("A","B", "C"),hjust = -1,nrow = 1)
+figure4
 ```
@@
 #End point bar graph with std error
-tobCFUPlot<- 
+#tobCFUPlot<- 
   ggplot() +
